### 2019-01-15 doc/papers/nn/manuscript.tex
Initial commit. Start writing papers.

\documentclass[a4paper]{article}

\usepackage{amsmath}
\usepackage{fullpage}

\title{TensorAlloy: a fast machine learning framework for alloys}

\author{Xin Chen}

\begin{document}

\maketitle

\section{Method}

\subsection{Atomic forces}

In the ANN model, the total energy, $E^{total}$, of a structure is the sum of 
atomic energies:

\begin{gather}
E^{total} = \sum_{i}^{N}{E_i} \\
E_i = \mathbf{NN}_\alpha (G_i)
\end{gather}

\noindent where $G_i$ is the atomic descriptor of $\alpha$-type atom $i$.

\subsection{Stress}

\end{document}

### 2019-03-26 doc/papers/nn/figures/Fig4-qm7.py
These figures are updated.

@@ -3,6 +3,7 @@ from __future__ import print_function
 import numpy as np
 import re
 from matplotlib import pyplot as plt
+from matplotlib.gridspec import GridSpec
 
 examples_per_second = {
     'GPU': {
@@ -63,7 +64,7 @@ def read_traj(filename, batch_size: int, sf: str):
     speed = examples_per_second['GPU'][sf][batch_size]
     factor = 1.0 / (speed / batch_size * 3600)
     with open(filename) as fp:
-        head = []
+        data = []
         tail = []
         for line in fp:
             line = line.strip()
@@ -72,14 +73,9 @@ def read_traj(filename, batch_size: int, sf: str):
                 step = float(m.group(1))
                 x = step * factor
                 y = float(m.group(2)) * 1000.0
-                if x <= 1.0:
-                    head.append([x, y])
-                else:
-                    tail.append([x, y])
-        head = np.asarray(head)
-        tail = np.asarray(tail)
-        tail = np.concatenate((np.atleast_2d(head[-1]), tail), 0)
-        return head, tail
+                data.append([x, y])
+        data = np.asarray(data)
+        return data
 
 
 speed_flatten = []
@@ -90,13 +86,13 @@ for (device, sf) in orders:
 
 traj = []
 for (batch_size, sf, tag, filename) in traj_files:
-    head, tail = read_traj(filename, batch_size, sf)
-    traj.append((tag, head, tail))
+    traj.append((tag, read_traj(filename, batch_size, sf)))
 
 
-fig, axes = plt.subplots(1, 2, figsize=[12, 5])
+fig = plt.figure(figsize=[12, 10])
+grid_spec = GridSpec(2, 24)
 
-ax = axes[0]
+ax = plt.subplot(grid_spec[0, 0: 11])
 
 n_groups = 5
 bar_width = 0.2
@@ -107,19 +103,16 @@ ax.bar(
     np.array(speed_flatten[0]), 
     bar_width, 
[…]

### 2019-03-26 doc/papers/nn/manuscript.tex
The initial version of the NN manuscript is finished.

@@
-\documentclass[a4paper]{article}
+\documentclass[prb,preprint]{revtex4-2}
 
-\usepackage{amsmath}
-\usepackage{fullpage}
+\usepackage{amsmath}    % need for subequations
+\usepackage{graphicx}   % need for figures
+\usepackage{verbatim}   % useful for program listings
+\usepackage{color}      % use if color is used in text
+\usepackage{subfigure}  % use for side-by-side figures
+\usepackage{hyperref}   % use for hypertext links, including those to external
+\raggedbottom           % don't add extra vertical space
+\begin{comment}
+\pagestyle{empty}       % use if page numbers not wanted
+\end{comment}
 
-\title{TensorAlloy: a fast machine learning framework for alloys}
-
-\author{Xin Chen}
+\bibliographystyle{apsrev4-2}
 
@@
 
+\title{
+    TensorAlloy: a highly efficient atomistic neural network program for alloys
+}
+\author{Xin Chen, De-Ye Lin, Hai-Feng Song$^\mathrm{*}$}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\affiliation{
+    CAEP Software Center for High Performance Numerical Simulation, 
+    Beijing 100088, China}
+
+\begin{abstract}
+Atomistic modeling is important for studying physical and chemical properties of
+materials. Recently, machine learning interaction potentials have gained much 
+more attentions as they can give density functional theory level predictions 
+within second. Currently, symmetry function based atomistic neural network is 
+the most widely used model for alloys. To precisely describe atomistic 
+interactions, integrating advanced metrics, such as force or virial stress, into 
+training can be of great help. However, the traditional way to construct a 
+machine learning model computation graph starts from pre-computed descriptors, 
+but not positions, due to technial challenges. Thus, deriving analytical atomic 
+force or virial stress of a machine learning model becomes quite difficult as 
+the partial derivations of descriptors with respect to positions need separate 
+implementations, which requires plenty of effort and its efficiency can not be 
+guaranteed.
+In this paper, we designed a new method, named the virtual atom approach, for 
+implementing the symmetry function descriptor and the corresponding atomistic 
+neural networks. With the virtual atom approach, we are able to build 
+computation graph from atomic positions \textemdash but not descriptors 
+\textemdash to total energy directly, thus asking modern machine learning 
+platforms to compute atomic force and virial stress becoming possible. We also 
+derived a simple and machine learning friendly equation for calculating virial 
+stress. All these new algorithms have been implemented in our Python package, 
+TensorAlloy. TensorAlloy supports both \textit{molecules} and \textit{solids} 
+and one hour is sufficient for TensorAlloy to obtain models with state-of-art 
+level accuracy.
+\end{abstract}
+
 \maketitle
 
+\newcommand{\tensoralloy}{\textbf{TensorAlloy}}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 1. Introduction
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\newpage
+
+\section{Introduction}
+
+Atomistic simulations (\textit{ab initio} calculation, classic molecular 
+dynamics simulation (MD), etc) are powerful tools for studying physical and 
+chemical properties of materials. To obtain reliable simulation results, 
+atomistic interactions must be properly described. The very accurate 
+\textit{ab initio} and quantum chemical methods have gain significant 
+improvements over the past decades but their applicabilities are restricted by 
+computation expenses. Physical model based empirical potentials, such as the 
+embedded-atom method\cite{eam-1,eam-2,eam-3,eam-4,eam-5}, are much more popular 
+for long-time simulation because of their reasonable accuraty and acceptable 
+costs. However, designing empirical potentials and optimizing parameters for 
+alloys are still challenging tasks.
+
+In the past few years, machine learning (ML) has become one of the most 
+influential topic in almost all fields of science. A lot of effort has been made 
+by various physicists to explore the possiblity of using ML models \textemdash 
+instead of traditional empirical potentials \textemdash to describe atomistic 
+interactions during MD simulations. ML potentials are much easier to design and 
+optimize. With sufficient training data, ML models can achieve similar or even 
+better performances compared with density functional theory. Until now, various 
+ML models (kCON\cite{kCON}, SchNet\cite{SchNet}, DTNN\cite{DTNN}, 
+SNAP\cite{SNAP_Mo_2017, SNAP_2018}, etc) have been published by researchers. 
+Among them, the symmetry function based atomistic neural network (ANN) model, 
+first proposed by Parinello and Behler in 
+2007\cite{Behler,Behler2,Behler3,Behler4,Behler1}, is still the most widely used 
+method for \textit{solids} and its effectness and accuracy has been proven by 
+several works\cite{Behler-solids-lzp-1,Behler-alloy-1,Behler-alloy-2,
+Behler-alloy-3}. The Amp\cite{AMP} package, developed by Peterson's group, is 
+the first open-source framework that implements the symmetry function 
+descriptor. Amp supports both \textit{molecules} and \textit{solids} and it has 
+successfully powered quite a few researches since 
+2016\cite{Amp-works-hammer,amp-work-1}. ANI\cite{ANI} and 
+TensorMol\cite{TensorMol} are also symmetry function based packages but they 
+mainly focus on \textit{molecules}.
+
+In order to precisely model atomistic interactions, both total energy and atomic 
+forces are necessary. For \textit{solids}, the virial stress tensor is also an
+essential metric. However, integrating force and stress into the loss function 
+is not an easy task. The machine learning approaches favor vectorizable 
+operations but the calculations of atomic descriptors are typically complicated 
+so that many traditional ML packages (Amp, kCON, etc) choose to pre-compute 
+descriptors and only build computation graph from descriptors to total energy. 
+This approach can significantly reduce technical difficulty and works very well 
+if only total energy is considered in the loss function. But to fit atomic 
+forces, numerous codes must be written manually, such as the derivation of 
+descriptors with respect to positions. Although the derivation is theoretically
+clear, the implementation will be a challenge and the efficiency can not be 
+guaranteed.
+
+Recently, machine learning platforms (TensorFlow\cite{tensorflow}, 
+PyTorch\cite{pytorch}, MXNet\cite{MXNet}, etc) have gain significant 
+developments. These modern machine learning frameworks can fully take advantage 
+of GPUs for acceleration. The automatic differentiation capability brings a new 
+route for devloping ML models capable of predicting energy, force and stress as 
+we may 'let' ML platforms to handle the calculations of force and stress because 
+these metrics can be derived from positions and total energy directly. To 
+achieve this, a direct computation graph from positions to total energy must be
+built. Thus, the problem becomes: how to design such route?
+
+In this work, we propose a new algorithm, named the virtual atom approach, to 
+implement the symmetry function descriptor and the ANN model based on 
+TensorFlow. This algorithm is very suitable for parallel execution. With this 
+approach, stochastic gradient descent (SGD) based mini-batch training can be 
+adopted. We also derive a general and vectorizable expression for computing 
+virial stress for arbitrary ANN model. All these algorithms have been 
+implemented in our Python program: \tensoralloy{}.
+
+This paper is organized as follows. Section \ref{section:theory} introduces the 
+theory of the symmetry function descriptor and the ANN framework. Section 
+\ref{section:method} describes the virtual atom approach and a modified ANN 
+model used by \tensoralloy{}. Section \ref{section:discussions} displays 
+performances of \tensoralloy{} on two public datasets. The appendix 
+\ref{section:appendix} gives derivation and implementation details of key 
+algorithms. The compiled version of \tensoralloy{} program and all the 
+associated model files are available on 
+\href{https://github.com/Bismarrck/tensoralloy-release}{GitHub}.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 2. Theory
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{Theory}
+\label{section:theory}
+
+\newcommand{\rijn}{r_{ij\mathbf{n}}}
+
+In the atomistic neural network (\textbf{ANN}) framework, the total energy, 
+$E^{total}$, of a structure with $N$ atoms, is the sum of all atomic energies:
+\begin{equation}
+\label{eq:general_e_total}
+E^{total} = \sum_{i}^{N}{E_i}
+\end{equation}
+where $E_{i}$, the energy of atom \textit{i}, is the output of the neural 
+network $\mathbf{NN}_{el}$ for element $el$:
+\begin{equation}
+E_i = \mathbf{NN}_{el}\left( \mathbf{G}_i \right)
+\end{equation} 
+Here $\mathbf{G}_i$ is a vector representing atomic descriptors of atom $i$. 
+$\mathbf{G}_i$ typically only depends on local environments \textemdash 
+neighbors \textemdash of atom $i$:
+\begin{equation}
+\mathbf{G}_i = F_G(\left\{ \rijn, |\rijn| < r_c\right\} )
+\end{equation}
+where $F_G$ can be arbitrary function, $r_c$ is the cutoff radius and $\rijn$ is 
+the interatomic distance considering the periodic boundary conditions: 
+\begin{equation}
+    \label{eq:rijn}
+    \rijn = \Vert \mathbf{r}_i^{(0)} - \mathbf{r}_j^{(0)} + 
+    \mathbf{n}^T \mathbf{h} \Vert
+\end{equation}
+where $\mathbf{r}_i^{(0)}$ and $\mathbf{r}_j^{(0)}$ denote positions of $i$ and 
+$j$ in the primitive cell, $\mathbf{n}$ is a column vector specifying the cell 
+shifts along $(X,Y,Z)$ directions 
+\begin{equation}
+    \label{eq:ij_shift}
+    \mathbf{n} = \begin{pmatrix}
+        n_x \\
+        n_y \\
+        n_z
+    \end{pmatrix}
+\end{equation}
+and $\mathbf{h}$ is the \textbf{row-major} $3 \times 3$ lattice tensor:
+\begin{equation}
+    \label{eq:lattice}
+    \mathbf{h} = \begin{pmatrix}
+        h_{xx} & h_{xy} & h_{xz} \\
+        h_{yx} & h_{yy} & h_{yz} \\
+        h_{zx} & h_{zy} & h_{zz} \\
+    \end{pmatrix}
+\end{equation}
+
+\newcommand{\rijna}{r_{ij\mathbf{n_1}}}
+\newcommand{\rikna}{r_{ik\mathbf{n_2}}}
+\newcommand{\rjkna}{r_{jk\mathbf{n_3}}}
+
+There are many choices of $F_G$. The symmetry function descriptor, proposed 
+by Parinello and Behler in 2007\cite{Behler}, is currently the most widely used 
+atomic descriptor, especially for alloys. The symmetry function descriptor 
+consists of two sets of invariant (tranlational, rotational and permutational) 
+functions: the radial symmetry function $\mathbf{G}^{(2)}$ and the angular 
+symmetry function $\mathbf{G}^{(4)}$:
+\begin{align}
+\label{eq:G2}
+\mathbf{G}^{(2)}_i(\eta, R_s) = & \sum_{j \neq i}{
+    \sum_{\mathbf{n}}{g_2 (\eta, i, j, R_s)}
+} \\
+\label{eq:G4}
+\mathbf{G}^{(4)}_i(\beta, \gamma, \zeta) 
+= & 2^{1-\zeta}\sum_{j, k\neq j, k\neq i}{
+    \sum_{\mathbf{n}_1}{\sum_{\mathbf{n}_2}{\sum_{\mathbf{n}_3}{
+        g_4(\beta, \gamma, \zeta, 
+          i, j, k, 
+          \mathbf{n}_1, \mathbf{n}_2, \mathbf{n}_3)
+    }}}
+} \\
+\label{eq:g2}
+g_2 = & \exp\left\{-\frac{\eta(\rijn - R_s)^2}{r_c^2} \right\}
+\cdot f_c(\rijn) \\
+g_4 = & \left( 1 + \gamma\cos\theta \right)^\zeta 
+    \exp \left\{ -\frac{\beta(\rijna^2 + \rikna^2 + \rjkna^2)}{r_c^2} \right\}
+f_c(\rijna)f_c(\rikna)f_c(\rjkna)
+\end{align}
+where $\eta$, $R_s$, $\beta$, $\gamma$ and $\zeta$ are empirically chosen 
+parameters, $f_c(r)$ is a cutoff (damping) function and its original form is:
+\begin{equation}
+\label{eq:fc_origin}
+f_c(r) =
+    \begin{cases}
+    0 & \text{$r > r_c$} \\
+    \frac{1}{2} + \frac{1}{2}\cos\left(r / r_c \cdot \pi \right) & 
+    \text{$r \leq r_c$}
+    \end{cases}
+\end{equation}
+and $r_c$ is the cutoff radius. In our implementation, $R_s$ is always fixed to 
+0 so it becomes neglectable\cite{AMP}. Equation \eqref{eq:fc_origin} can be 
+further transformed to a vectorized expression:
+\begin{equation}
+\label{eq:fc}
+f_c(r) = \frac{1}{2}\left( 
+    1 + \cos\left[ \min(\frac{r}{r_c}, 1) \pi \right] 
+\right)
+\end{equation} 
+and $\cos\theta$ also has a vectorized form:
+\begin{equation}
+\cos\theta = \frac{\rijna^2 + \rikna^2 - \rjkna^2}{2 \rijna \cdot \rikna}
+\end{equation}
+The summations in $\mathbf{G}^{(2)}$ and $\mathbf{G}^{(4)}$ should go over all 
+neighbors within $r_c$.
+
+Analytical atomic forces can be obtained directly by computing the first-order 
+derivative of $E^{total}$ with respect to $\mathbf{r}_{a}^{(0)}$ where $a$ is an 
+index:
+\begin{equation}
+\label{eq:dEdr}
+f_a = -\frac{\partial E^{total}}{\partial \mathbf{r}_a^{(0)}}
+\end{equation}
+According to the chain rule, we can expand Equation \ref{eq:dEdr}:
+\begin{align}
+\frac{\partial E^{total}}{\partial \mathbf{r}_a^{(0)}} = & \sum_{i}^{N}{
+    \frac{
+        \partial\mathbf{NN}_{el}(\mathbf{G}_i)}{
+        \partial \mathbf{r}_a^{(0)}}} \nonumber \\
+= & \sum_{i}^{N}{\sum_{l}^{N_G}{
+    \frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}}
+    \cdot
+    \frac{\partial G_{il}}{\partial \mathbf{r}_{a}^{(0)}}
+}}
+\end{align}
+and 
+\begin{align}
+\frac{\partial G_{il}^{(2)}}{\partial \mathbf{r}_{a}^{(0)}} = & \sum_{j \neq i}{
+    \sum_{\mathbf{n}}{
+        \frac{\partial g_2}{\partial \rijn}
+        \cdot
+        \frac{\partial \rijn}{\partial r_k^{0}}
+    }
+} \\
+\frac{\partial G_{il}^{(4)}}{\partial \mathbf{r}_{a}^{(0)}} = &
+2^{1 - \zeta}\sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n}_1}{\sum_{\mathbf{n}_2}{\sum_{\mathbf{n}_3}{
+        \left(
+            \frac{\partial g_4}{\partial \rijna}
+            \frac{\partial \rijna}{\partial \mathbf{r}_{a}^{(0)}} + 
+            \frac{\partial g_4}{\partial \rikna}
+            \frac{\partial \rikna}{\partial \mathbf{r}_{a}^{(0)}} + 
+            \frac{\partial g_4}{\partial \rjkna}
+            \frac{\partial \rjkna}{\partial \mathbf{r}_{a}^{(0)}}
+        \right)
+    }}}
+}
+\end{align}
+
+The derivations are theoretically straightforward but coding these equations 
+manually will be a challenge\cite{AMP}. Thanks to the virtual atom approach, 
+\tensoralloy{} can now calculate $f_a$ using Equation \ref{eq:dEdr} directly.
+
+The $3 \times 3$ virial stress tensor $\epsilon$ is an important metric for 
+solids. For arbitrary many-body interaction potentials, $\epsilon$ can be 
+calculated with the following equation\cite{lammps_stress}:
+\begin{equation}
+\label{eq:stress_lammps}
+\epsilon = \left(-\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} - 
+\sum_{\mathbf{n}}{\mathbf{h}^T\mathbf{n}} \otimes 
+\sum_{i=1}^{N}{F^{\prime}_{i\mathbf{n}}}
+\right)^T
+\end{equation}
+where $\otimes$ indicates tensor product, $f_i$ is the total force acting on 
+atom $i$ and $F^{\prime}_{i\mathbf{n}}$ is the partial force. Yntil now, 
+most machine learning force-field models focus on fitting total energy and 
+atomic forces, very few of them\cite{DeePMD,DeePMD_rl,DeePMD_kit} had attempted 
+to include stress in their loss functions. The current expression of Equation 
+\ref{eq:stress_lammps} is not very compatible with NN or other ML potentials 
+since the partial forces are difficult to compute with vectorized operations. 
+To resolve this issue, we derived an equivalent form of Equation 
+\ref{eq:stress_lammps}:
+\begin{equation}
+\label{eq:stress}
+\epsilon = -F^{T} R + 
+\left(\frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h}
+\end{equation}
+where $R$ is the $N \times 3$ positions matrix and $F$ is the corresponding 
+total forces matrix. The new equation can be easily implemented with simple 
+matrix operations. The detailed derivation is given in the appendix.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3. Method
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \section{Method}
+\label{section:method}
 
-\subsection{Atomic forces}
+\newcommand{\nmax}{
+    N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}
+}
+\newcommand{\nijmax}{N_{ij}^{\mathrm{max}}}
+\newcommand{\nijkmax}{N_{ijk}^{\mathrm{max}}}
 
-In the ANN model, the total energy, $E^{total}$, of a structure is the sum of 
-atomic energies:
+In this section we will describe details of \tensoralloy{}: the virtual atom 
+approach, the atomic residual potential and the loss function. The Ni-Mo alloy 
+system, with four $\eta$, two $\beta$, two $\gamma$ and one $\zeta$, will be 
+used as the example to show this algorithm. For simplicity, only radial symmetry
+function related algorithms are visualized in the figures.
 
+\subsection{The virtual atom approach}
+\label{section:virtual_atom_approach}
+
+Fig \ref{fig:algo1} shows the initialization procedure of the virtual atom 
+approach. The cutoff radius $r_{cut}$ must be fixed. The first step is to go 
+through the entire dataset and determining four prerequisite constants: 
+$N_{ij}^{\mathrm{max}}$, $N_{ijk}^{\mathrm{max}}$, 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$. 
+Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs of 
+arbitrary structure and $N_{ijk}^{\mathrm{max}}$ represents the maximum number 
+of triples. $N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depends on 
+$r_{cut}$. The associated codes are given in the appendix.
+$N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$ indicate 
+the maximum appearances of Ni and Mo in any structure, respectively. 
+With $N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$, 
+the global symbol list (GSL) can be created. GSL defines the global reference 
+of this dataset and must be maintained during entire training. Then we can 
+construct \textit{offsets}. This vector marks the starting indices of the 
+\textbf{ordered} interaction pairs (e.g. Ni-Mo) and triples (e.g. Ni-Ni-Mo). 
+The order of the interactions must be maintained as well.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.5]{figures/Fig1-prepare.pdf}
+\caption{\label{fig:algo1} The initialization. 
+\textbf{a)} the detections of $N_{\mathrm{Ni}}^{\mathrm{max}}$, 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$, $N_{ij}^{max}$, $N_{ijk}^{max}$ and the global
+symbols list.
+\textbf{b)} and \textbf{c)} the \textit{offsets} and their corresponding 
+symmetry function parameters.
+}
+\end{figure}
+
+Fig \ref{fig:algo2} shows the algorithm to construct the radial mapping matrix
+$g_{\mathrm{map}}^2$ which plays a key role in building the computation graph 
+(Fig \ref{fig:algo3}). This algorithm starts from the $N \times 3$ local 
+positions matrix \textbf{R}. Here 'local' means original and 'global' means GSL. 
+The first step is to find all neighbor pairs: $\mathbf{n}$, $i^{(0)}$ and 
+$j^{(0)}$. This can be done by the 
+\href{https://wiki.fysik.dtu.dk/ase/ase/neighborlist.html}{neighbor\_list} 
+routine of ASE\cite{ase}. $\mathbf{n}$ is a $N_{ij} \times 3$ matrix 
+representing the periodic boundary shift vectors where $N_{ij}$ is the total 
+number of interaction pairs within $r_{cut}$.
+Both $i^{(0)}$ and $j^{(0)}$ are $N_{ij}\times 1$ column vectors representing 
+the indices of $i$ and $j$ of Equation \ref{eq:rijn}. 
+$\mathbf{t}$ is a manually-created $N_{ij}\times 1$ column vector storing the 
+types \textemdash represented by integers \textemdash of the corresponding 
+interaction pairs.
+
+The second step is to convert the local indices, $i^{(0)}$ and $j^{(0)}$, to 
+global indices based on GSL and then \textbf{increase their values by one}. 
+By padding with zeros, we can finally get the $N_{ij}^{\mathrm{max}} \times 3$ 
+matrix $\mathbf{n_g}$ and $N_{ij}^{\mathrm{max}} \times 1$ column vectors 
+$i^{(0)}_{\mathrm{+,g}}$, $j^{(0)}_{\mathrm{+,g}}$ and 
+$\mathbf{t}_{\mathrm{g}}$. The increment is extremely important because the 
+indices of all padded 'virtual' or 'dummy' atoms are fixed to 0.
+
+The last step is to construct $g_{\mathrm{map}}^{(2)}$, which should be a 
+$N_{ij}^{\mathrm{max}} \times 2$ matrix. Its first column is just 
+$i^{(0)}_{\mathrm{+,g}}$ and its second column are corresponding offset values 
+of $\mathbf{t}_{\mathrm{g}}$. $g_{\mathrm{map}}^{(2)}$, 
+$j^{(0)}_{\mathrm{+,g}}$ and $\mathbf{n_g}$ can be pre-computed and cached. 
+The algorithm to build $g_{\mathrm{map}}^{(4)}$ for angular symmetry functions 
+is similar but too complicated to visualize. Thus, we provide a Python 
+implementation in the appendix.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.6]{figures/Fig2-v2gmap.pdf}
+\caption{\label{fig:algo2} The second stage of the virtual atom approach: the 
+construction of $g_{\mathrm{map}}^{(2)}$. Tensors marked red can be pre-computed 
+and cached.}
+\end{figure}
+
+Fig \ref{fig:algo3} shows the final stage of the virtual atom approach: the 
+computation graph for calculating radial symmetry function descriptors. This 
+stage also starts from the $N \times 3$ local positions matrix \textbf{R} and 
+involves two steps: the calculation of interatomic distances $r_{ij}$ 
+(Fig \ref{fig:algo3}a) and the construction of $\mathbf{G}^{(2)}$ 
+(Fig \ref{fig:algo3}b).
+
+The initial step is to map local positions \textbf{R} to
+$(N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}+1) \times 3$
+global positions \textbf{R'} based on GSL. The first row (marked blue) of 
+$\mathbf{R'}$ are all zeros representing 'positions' of the virtual atom. 
+Then with 
+\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/gather}
+{tf.gather}, the global indices $i^{(0)}_{\mathrm{+,g}}$ and 
+$j^{(0)}_{\mathrm{+,g}}$ of Fig \ref{fig:algo2} can be transformed to global 
+positions: $\mathbf{R'_i}$ and $\mathbf{R'_j}$. Thus, the interatomic distances 
+$r_{ij}$ can be simply calculated with Equation \ref{eq:rijn}.
+
+Now it's time to get radial symmetry function descriptors matrix 
+$\mathbf{G}^{(2)}$. 
+As shown in Fig \ref{fig:algo3}b, this step can be executed in parallel: 
+for each $\eta_i$, we first calcualte $g_2(r_{ij}, \eta_i)$ with 
+Equation \ref{eq:g2} and then map the $N_{ij}^{\mathrm{max}}$-length vector 
+$g_2(r_{ij}, \eta_i)$ to 
+$(N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}+1) \times 16$ 
+matrix $\mathbf{G}^{(2)}_{\eta_i}$ with $g^{\eta_i}_{\mathrm{map}}$ and 
+\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/scatter_nd}
+{tf.scatter\_nd}. Here $16$ is the multiplacation of 4 ($\eta$) and 4 
+(radial interactions). 
+$g^{\eta_i}_{\mathrm{map}}$ is calculated by adding a constant
+$i - 1$ to all values of the second column of $g^{(2)}_{\mathrm{map}}$. Only 
+shaded columns in Fig \ref{fig:algo3}b have non-zero values.
+In fact, the first column of $g^{\eta_i}_{\mathrm{map}}$ means the indices of 
+the central atoms in Equation \ref{eq:G2} (or rows of $\mathbf{G}^{(2)}$) and 
+the second column marks the corresponding $\eta_i$ in Fig \ref{fig:algo1} (or 
+columns of $\mathbf{G}^{(2)}$).
+The first row of each $\mathbf{G}^{(2)}_{\eta_i}$ reprsents the descriptors of 
+the virtual atom. Removing these rows with
+\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/split}
+{tf.split}, we get $\hat{\mathbf{G}}^{(2)}_{\eta_i}$.
+The final radial symmetry function descriptors, $\mathbf{G}^{(2)}$ is just the 
+sum of all $\hat{\mathbf{G}}^{(2)}_{\eta_i}$.
+
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.5]{figures/Fig3-G2.pdf}
+\caption{\label{fig:algo3} 
+\textbf{a)} The calculation of the interatomic distances $r_{ij}$.
+\textbf{b)} The construction of the radial symmetry function descriptors 
+$\mathbf{G}^{(2)}_{\eta_i}$. Rows that are marked blue correspond to the virtual 
+atom and will be discared before feeding $\mathbf{G}$ into atomistic neural 
+networks.
+}
+\end{figure*}
+
+\subsection{The data flow}
+
+The following equation briefly demonstrates the core data flow of 
+\textbf{TensorAlloy} during a mini-batch training: 
+\begin{equation}
+    \mathbf{R'_{b}} \rightarrow 
+    \mathbf{G_b} \rightarrow 
+    \mathbf{E_b} \rightarrow
+    \mathbf{F_b} \rightarrow 
+    \mathbf{\epsilon_b} \rightarrow
+    \mathbf{Loss}
+\end{equation}
+where the $N_{b} \times (\nmax + 1) \times 3$ matrix $\mathbf{R'_b}$ is a batch 
+of positions matrices ($N_b \ge 1$ is the batch size), $\mathbf{G_b}$ is the 
+corresponding symmetry function descriptors matrix of shape 
+$N_{b} \times (\nmax) \times 16$ and $\mathbf{E_b}$ represents 
+total energies of the structures. Section \ref{section:virtual_atom_approach} 
+describes the implementation of $\mathbf{R'_{b}} \rightarrow \mathbf{G_b}$. 
+To implement $\mathbf{G_b} \rightarrow \mathbf{E_b}$, \textbf{TensorAlloy} uses 
+1D-convolutional neural networks with $1 \times 1$ kernels\cite{kCON}. The total 
+forces $\mathbf{F_{b}}$ and the virial stress $\mathbf{\epsilon_{b}}$ are 
+calculated with Equation \ref{eq:dEdr} and Equation \ref{eq:stress} by with just 
+few lines of codes.
+
+\subsection{The residual model}
+
+To fit the total energy, we slightly modified the total energy expression of 
+Equation \ref{eq:general_e_total}:
+\begin{align}
+\label{eq:e_total_res}
+E^{total} & = E^{residual} + E^{static} \nonumber \\
+& = \sum_{i=1}^{N}{
+    \mathbf{NN}_{el}\left( \left\{ G_i \right\} \right)
+} + \sum_{el}{n_{el}E_{el}}
+\end{align}
+where $\{E_{el}\}$ is a set of \textit{trainable} scalar variables representing 
+the \textit{static} energy of each type of element\cite{kCON}. The NN in 
+Equation \ref{eq:e_total_res} just describes the atomistic interactions 
+(the \textit{residual} energy). The 
+introduction of $E^{static}$ can significantly limit value range of NN outputs, 
+leading to much faster convergence speed and higher training stability 
+(Fig \ref{fig:benchmark_qm7}c). The initial $\{E_{el}\}$ are calculated by 
+solving the linear system $Ax=b$ where $A$ is a $N_{data} \times N_{el}$ matrix 
+and $b$ is a $N_{data}\times 1$ vector. $A(i,j)$ is the number of $j^{th}$
+element in structure $i$ and $b(i)$ is the total energy of structure $i$.
+
+To train the model, we use the following total loss function:
+\begin{align}
+\label{eq:loss}
+\mathbf{Loss} & = \sqrt{\frac{1}{N_{b}}\sum_{i=1}^{N_{b}}{\left(
+    E_{i} - E_{i}^{\mathrm{dft}}
+\right)^2}} \nonumber \\
+& + \chi_{\mathrm{f}}\sqrt{
+    \frac{1}{3\sum_{i}^{N_{b}}{N_i}}\sum_{i}^{N_b}{\sum_{j}^{N_i}{
+        \sum_{\alpha}{
+            \left(f_{ij\alpha} - f_{ij\alpha}^{\mathrm{dft}}\right)^2
+        }
+    }}
+} \nonumber \\
+& + \chi_{\mathrm{s}}\sqrt{\frac{1}{6N_b}\sum_{i}^{N_b}{
+    \sum_{j}^{6}{
+        \left(
+            \epsilon^{\mathrm{voigt}}_{j} - \epsilon^{\mathrm{voigt,dft}}_{j}
+        \right)^2
+    }
+}}
+\end{align}
+where $N_b$ is the mini-batch size, $N_i$ is the number of atoms of structure 
+$i$ and $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ are weights of force and 
+stress losses. Typically both $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ range 
+within $[1,10]$. Stress tensors are converted to Voigt vectors. All energies are 
+in \textbf{eV}, all forces are in \textbf{eV/\AA} and all stress components are 
+in \textbf{eV/\AA}$\mathbf{^3}$. In most cases, we set $N_b$ to 50 or 100 and we
+use the Adam\cite{adam} optimizer with exponentially-decayed learning rate to 
+minimize the loss function. The activation function is Leaky ReLU
+\cite{maas2013rectifier}:
+\begin{equation}
+\sigma(x) = \begin{cases}
+    \alpha x & x \le 0 \\
+    x & x \ge 0 \\
+\end{cases}
+\end{equation}
+and $\alpha$ is set to 0.2 in \tensoralloy{}. The kernel weights of all ANNs are 
+initialized with the Xvaier\cite{pmlr-v9-glorot10a} method and kernel biases are 
+initialized with zeros.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 4. Discussions
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{Discussions}
+\label{section:discussions}
+
+In this section we demonstrate two training experiments of \tensoralloy{}. All 
+the results are obtained on a workstation with two Intel Xeon E5-2687v4 CPUs 
+(18 cores per CPU, 2.3 GHz) and one NVIDIA GTX 1080 Ti GPU.
+
+\subsection{QM7}
+
+QM7\cite{QM7_1,QM7_2} is a publicly available benchmark dataset calculated at 
+the DFT level. The QM7 dataset contains 7165 stable organic molecules 
+(C, H, N, O, S) with 176 unique stoichiometries. The total energies range from 
+-95 eV to -17 eV and the structure sizes range from 5 to 23. 1000 structures 
+were randomly selected as test set before training.
+
+Figure \ref{fig:benchmark_qm7} demonstrates the performances of 
+\textbf{TensorAlloy} on QM7 dataset. In this figure, 'Radial' means only radial 
+symmetry functions (Equation \ref{eq:G2}) are used and 'Angular' indicates both 
+radial and angular symmetry functions are used. The cutoff radius is 6.5 \AA and
+the corresponding $\nijmax$ and $\nijkmax$ are 506 and 5313, indicating the 
+calculation of angular descriptors is much more expensive.
+The $\eta$ for radial symmetry functions are 0.1, 0.5, 1, 2, 4, 8, 12, 16, 20, 
+40 and $\beta$ (0.1, 0.5), $\gamma$ (1, -1) and $\zeta$ (1, 4) are used for
+angular functions. The initial learning rate is 0.01 and the it is exponentially 
+decayed with rate 0.99 for every 5000 steps. Each atomistic neural network has
+two hidden layers with 128 and 64 neurons.
+
+Figure \ref{fig:benchmark_qm7}a compares the training speed (number of processed 
+structures per second) with different batch sizes (number of structures per 
+step). It shows that CPU perfers fewer descriptors (radial only) and smallber 
+batch size while GPU is suitable for larger batch size and more complicated 
+descriptors (radial + angular). 
+Figure \ref{fig:benchmark_qm7}b shows the curves of mean absolute errors 
+(MAEs, meV/atom) on the test set. This figure clearly illustrate another benefit 
+of using larger batch size: models can be trained much faster. For the best case 
+(batch size 100, angular symmetry functions included), the test MAE will reach 5 
+meV/atom (1.5 kcal/mol per structure) within just one GPU hour.
+
+Figure \ref{fig:benchmark_qm7}c compares out residual model (Equation 
+\ref{eq:e_total_res}) with traditional ANN model (Equation 
+\ref{eq:general_e_total}). In fact, both models can converge to similar final 
+results. However, the residual model has a much faster convergence speed because 
+the introduction of the \textit{static} part can reduce output values of ANNs
+close to (-1, 1) \textemdash the ideal output range of neural networks.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.54]{figures/Fig4-qm7.pdf}
+\caption{\label{fig:benchmark_qm7} 
+\textbf{a)} The curves of training speed (structures per second) vs batch sizes. 
+\textbf{b)} The curves of test MAE (meV/atom) vs training time (GPU hour) using 
+different settings.
+\textbf{c)} The curves of test MAE (meV/atom) vs NN models. 
+}
+\end{figure}
+
+\subsection{Ni-Mo}
+
+SNAP/Ni-Mo\cite{SNAP_Mo_2017, SNAP_2018} is a publicly available dataset built 
+by Shyue Ping Ong and co-workers. This dataset has 3971 Ni-Mo solids, including 
+461 pure Ni structures and 284 pure Mo structures. 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$ is 108 and $N_{\mathrm{Mo}}^{\mathrm{max}}$ 
+equals 176. All DFT calculations were done by VASP\cite{VASP} using the 
+PBE\cite{PBE} functional within the projector angumented-wave (PAW)\cite{PAW} 
+approach.
+
+In this experiment, we trained four different models:
+\begin{enumerate}
+    \item SFNN/Ni: this model uses 400 Ni structures for training and 61 for 
+    evaluation. The loss function only includes energy and force. Hidden layer 
+    settings are 128,64,32.
+    \item SFNN/Mo: this model uses 250 Mo structures for training and 34 for 
+    evaluation. The loss function includes all three metrics. Hidden layer 
+    settings are also 128,64,32.
+    \item SFNN/Ni-Mo: this model uses 3600 randomly selected structures for 
+    training and the rest 373 structures are used for evaluation. The loss 
+    function includes only energy and force. Hidden layer settings are 64,32,32.
+    \item SFNN/Ni-Mo (esf): this model has exactly the same settings with 
+    SFNN/Ni-Mo except that its loss function also includes stress as training 
+    metrics. $\chi_{s}$ of Equation \ref{eq:loss} is 160.
+\end{enumerate}
+
+For all these models, the cutoff radius is set to 6.0 \AA. The $\nijmax$ for Ni, 
+Mo and Ni-Mo are 4678, 4504 and 7200, respectively. Only radial symmetry 
+functions are used to compute atomic descriptors. The selected $\eta$ are: 
+0.1, 0.5, 1, 2, 4, 8, 12, 16, 20 and 40. The learning rate starts from 0.01 and 
+it will decay exponentially with rate 0.99 for every 5000 training steps. The
+maximum training steps is 500,000.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lcccccccc}
+\hline
+    & Model & Mo & Ni$_4$Mo & Ni$_3$Mo & Ni$_{\mathrm{Mo}}$ & Mo$_{\mathrm{Ni}}$ 
+    & Ni & Overall \\
+\hline
+Energy (meV/atom) & Ni SNAP & & & & & & \textbf{1.2} & \\
+    & Mo SNAP & 13.2 & & & & & & \\
+    & Ni-Mo SNAP & 16.2 & 4.0 & 5.2 & 22.7 & 33.9 & 7.9 & 22.5 \\
+    & Ni SFNN & & & & & & 1.6 & \\
+    & Mo SFNN & \textbf{9.8} & & & & & & \\
+    & Ni-Mo SFNN & 22.1 & \textbf{3.3} & \textbf{4.1} & \textbf{11.3} 
+    & \textbf{13.7} & 3.7 & \textbf{11.0} \\
+    & Ni-Mo SFNN (esf) & 30.0 & 6.1 & 9.0 & 16.6 
+    & 26.2 & 7.8 & 19.1 \\
+\hline
+Force (eV/\AA) & Ni SNAP & & & & & & 0.05 & \\
+& Mo SNAP & 0.25 & & & & & & \\
+& Ni-Mo SNAP & 0.29 & 0.14 & 0.16 & 0.13 & 0.55 & 0.11 & 0.23 \\
+& Ni SFNN & & & & & & \textbf{0.05} & \\
+& Mo SFNN & \textbf{0.20} & & & & & & \\
+& Ni-Mo SFNN & 0.32 & \textbf{0.09} & 0.11 & 0.09 & 
+    \textbf{0.15} & 0.06 & 0.12 \\
+& Ni-Mo SFNN (esf) & 0.36 & 0.10 & \textbf{0.11} & \textbf{0.08} & 
+    0.16 & 0.06 & \textbf{0.12} \\
+\hline
+Stress (GPa) & Mo SNAP & \textbf{0.87} & & & & & & \\
+& Mo SFNN & 1.00 & & & & & & \\
+& Ni-Mo SFNN & 5.77 & \textbf{1.72} & 1.74 & 1.45 & 3.75 & 1.97 & 2.83 \\
+& Ni-Mo SFNN (esf) & \textbf{1.84} & 2.05 & \textbf{1.38} & \textbf{0.57} & 
+    \textbf{1.22} & \textbf{1.91} & \textbf{1.27} \\
+\hline
+\end{tabular}
+\caption{\label{table:MAE}
+Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
+stress (GPa) relative to DFT for the \tensoralloy{} models and their 
+corresponding SNAP models}
+\end{table}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.8]{figures/Fig5-snap.pdf}
+\caption{\label{fig:snap_gpu_train_speed} The test MAEs of the SFNN/Ni-Mo model 
+vs training time (GPU Hour). The black dotted line marks the performance of the
+SNAP/Ni-Mo model.}
+\end{figure}
+
+Table \ref{table:MAE} summarizes the energy, force and stress prediction 
+performances of \tensoralloy{}-optmized models compared with their corresponding 
+SNAP models. The original SNAP formalism contains both radial and angular 
+interactions. However, in most cases, the radial-only \tensoralloy{}-trained 
+SFNN models can significantly outperform corresponding SNAP models. To precisely
+predict virial stress, integrating stress into total loss is undoubtedly 
+necessary. For the pure Mo dataset, the SFNN/Mo model gives a MAE of 1.0 GPa on 
+predicting stress while it will increase to 2 GPa if only using energy and force 
+as training metrics. This phonomenon holds true for the Ni-Mo mixed models as 
+well. If we include stress in the total loss function, we can obtain much more 
+accurate stress predictions.
+
+The trainings of \tensoralloy{} on these \textit{solid} datasets are also very 
+fast. Fig \ref{fig:snap_gpu_train_speed} shows the test MAE (meV/atom) vs 
+training time (GPU Hour) of the SFNN/Ni-Mo model. \tensoralloy{} only needs less 
+than \textbf{half an hour} to achieve equivalent performance of the 
+SNAP/Ni-Mo model.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.8]{figures/Fig6-energy-volume.pdf}
+\caption{\label{fig:energy_volume_Ni} The energy vs volume curves of fcc Ni for
+the DFT, Ni/SFNN and Ni-Mo/SFNN models.}
+\end{figure}
+
+To further validate our models, we also calculate the energy-volume curves of a 
+conventional fcc Ni cell using SFNN/Ni and SFNN/Ni-Mo models. The results are 
+plotted in Fig \ref{fig:energy_volume_Ni}. Both curves overlap the DFT curve 
+very well in the range of -17\% to 21\% from the equilibrium volume. The surface
+energy tests, as shown in Fig \ref{fig:surface_energy_Ni}, also proves the 
+accuracy of TensorAlloy-optimized models. PyMatGen\cite{pymatgen,pymatgen-1} is 
+used to generate these surface slabs.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[scale=0.8]{figures/Fig7-surface-energy.pdf}
+\caption{\label{fig:surface_energy_Ni} Surface energies ($J/m^2$) of different 
+Ni surfaces calculated with DFT, Ni/SFNN and Ni-Mo/SFNN models. The MAEs of the 
+Ni/SFNN and Ni-Mo/SFNN relative to the DFT values are 0.09 and 0.05, 
+respectively.}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 5. Conclusions
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{Conclusions}
+\label{section:conclusions}
+
+In this work, we proposed a new algorithm, namd the virtual atom approach, 
+to construct symmetry function based atomistic neural networks. With this 
+method, we can build direct computation graph from positions to total energy 
+using modern machine learning frameworks (like TensorFlow), thus, making the 
+technical barrier of calculating NN-derived atomic force and virial stress  
+neglectable. We also derived an alternative form of the general virial stress 
+equation. The new formula can be implemented with simple matrix operations and 
+is suitable for arbitrary machine learning platform based potentials. We 
+developed a highly efficient Python program, \tensoralloy{, for both 
+\textit{molecules} and \textit{solids}. We tested our program on two public 
+datasets, QM7 (molecules) and SNAP/Ni-Mo (solids). \tensoralloy{} can reach 
+state-of-art performances within just one GPU Hour.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Acknowledgments
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section*{Acknowledgments}
+
+This work was supported by. Computing resources were provided by.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% References
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\bibliography{manuscript.bib}
+
+\newpage
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Appendix
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section*{Appendix}
+\label{section:appendix}
+
+\subsection{
+    Calculations of $N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$}
+
+The following codes shows how to calculate $N_{ij}^{\mathrm{max}}$ and 
+$N_{ijk}^{\mathrm{max}}$. Python-3.7 and ASE-3.17.0 are suggested. In this block
+\textmd{dataset} should be a list of \textmd{ase.Atoms} objects.
+\begin{verbatim}
+nij_max = 0
+nijk_max = 0
+for i in range(dataset):
+    atoms = dataset[i]
+    assert isinstance(atoms, ase.Atoms)
+    ilist, jlist = ase.neighborlist.neighbor_list('ij', atoms, cutoff=rc)
+    nij = len(ilist)
+    nl = {}
+    for i, atomi in enumerate(ilist):
+        if atomi not in nl:
+            nl[atomi] = []
+        nl[atomi].append(jlist[i])
+    nijk = 0
+    for atomi, nlist in nl.items():
+        n = len(nlist)
+        nijk += (n - 1 + 1) * (n - 1) // 2
+    nij_max = max(nij, nij_max)
+    nijk_max = max(nijk, nijk_max)
+\end{verbatim}
+
+\subsection{Derivation and implementation of the virial stress equation}
+
+According to Equation \ref{eq:lattice} and Equation \ref{eq:ij_shift}, Equation 
+\ref{eq:rijn} can be expanded:
+\begin{align}
+\rijn = & \Vert \mathbf{r}_i^{(0)} - \mathbf{r}_j^{(0)} + 
+           \mathbf{n}^T \mathbf{h} \Vert \nonumber \\
+      = & \left[
+                 \left(r_{j,x}^{(0)} - r_{i,x}^{(0)} + 
+                       \sum_{\alpha}{n_{\alpha}h_{\alpha x}} \right)^2 +
+                 \left(r_{j,y}^{(0)} - r_{i,y}^{(0)} + 
+                       \sum_{\alpha}{n_{\alpha}h_{\alpha y}} \right)^2 + \right.
+        \nonumber \\
+        & \left. \left(r_{j,z}^{(0)} - r_{i,z}^{(0)} + 
+                       \sum_{\alpha}{n_{\alpha}h_{\alpha z}} \right)^2 
+          \right]^{\frac{1}{2}}
+\end{align}
+where $\alpha=x,y,z$. Thus, we can calculate the derivation of $\rijn$ with 
+respect to $h_{\alpha\beta}$:
 \begin{gather}
-E^{total} = \sum_{i}^{N}{E_i} \\
-E_i = \mathbf{NN}_\alpha (G_i)
+\frac{\partial \rijn}{\partial h_{\alpha\beta}} = 
+    \frac{1}{\rijn} \cdot \Delta_{ij\mathbf{n}\beta} \cdot n_{\alpha} \\
+\Delta_{ij\mathbf{n}\beta} = r_{j,\beta}^{(0)} - r_{i,\beta}^{(0)} + 
+    \sum_{\alpha}{n_{\alpha}h_{\alpha \beta}}
 \end{gather}
 
-\noindent where $G_i$ is the atomic descriptor of $\alpha$-type atom $i$.
+\newcommand{\hab}{h_{\alpha\beta}}
+\newcommand{\hga}{h_{\gamma\alpha}}
+\newcommand{\hgb}{h_{\gamma\beta}}
 
-\subsection{Stress}
+Then we can derive $\partial E^{total} / \partial \hab$:
+\begin{align}
+\label{eq:dEdhab}
+\frac{\partial E^{total}}{\partial \hab} = \sum_{i}^{N}{\sum_{l}^{N_G}}{
+    \frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}}
+    \cdot
+    \frac{\partial G_{il}}{\partial \hab}
+}
+\end{align}
+If $G_{il}$ is a radial symmetry function:
+\begin{align}
+\frac{\partial G_{il}^{(2)}}{\partial \hab} 
+& = \sum_{j \neq i}{\sum_{\mathbf{n}}}{
+    \frac{\partial g_2}{\partial \rijn} 
+    \cdot 
+    \frac{1}{\rijn} \cdot \Delta_{ij\mathbf{n}\beta} \cdot n_{\alpha}
+} \\
+\label{eq:stress_g2_right}
+\frac{\partial G_{il}^{(2)}}{\partial \hga} \cdot \hgb & = 
+\sum_{j \neq i}{\sum_{\mathbf{n}}}{
+    \frac{\partial g_2}{\partial \rijn} 
+    \cdot 
+    \frac{\Delta_{ij\mathbf{n}\alpha}}{\rijn} \cdot n_{\gamma}
+} \cdot \hgb
+\end{align}
+If $G_{il}$ is an angular symmetry function:
+\begin{align}
+\frac{\partial G_{il}^{(4)}}{\partial \hab} & =
+    \sum_{j, k \neq j, k \neq i}{
+        \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+    \left(
+        \frac{\partial g_4}{\partial \rijna}\cdot\frac{\partial \rijna}{\hab} +
+        \frac{\partial g_4}{\partial \rikna}\cdot\frac{\partial \rikna}{\hab} +
+        \frac{\partial g_4}{\partial \rjkna}\cdot\frac{\partial \rjkna}{\hab}
+    \right)
+}}} \nonumber \\
+& =  \sum_{j, k \neq j, k \neq i}{
+        \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+    \frac{\partial g_4}{\partial \rijna} \cdot 
+    \frac{\Delta_{ij\mathbf{n_1}\beta}}{\rijna} \cdot n_{1,\alpha}
+}}} \nonumber \\
+& + \sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+\frac{\partial g_4}{\partial \rikna} \cdot 
+\frac{\Delta_{ik\mathbf{n_2}\beta}}{\rikna} \cdot n_{2,\alpha}
+}}} \nonumber \\
+& + \sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+\frac{\partial g_4}{\partial \rjkna} \cdot 
+\frac{\Delta_{jk\mathbf{n_2}\beta}}{\rjkna} \cdot n_{3,\alpha}
+}}} \\
+\label{eq:stress_g4_right}
+\frac{\partial G_{il}^{(4)}}{\partial \hga} \cdot \hgb & = 
+\sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+\frac{\partial g_4}{\partial \rijna} \cdot 
+\frac{\Delta_{ij\mathbf{n_1}\alpha}}{\rijna} \cdot n_{1,\gamma} \cdot \hgb
+}}} \nonumber \\
+& + \sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+\frac{\partial g_4}{\partial \rikna} \cdot 
+\frac{\Delta_{ik\mathbf{n_1}\alpha}}{\rikna} \cdot n_{2,\gamma} \cdot \hgb
+}}} \nonumber \\
+& + \sum_{j, k \neq j, k \neq i}{
+    \sum_{\mathbf{n_1}}}{\sum_{\mathbf{n_2}}{\sum_{\mathbf{n_3}}{
+\frac{\partial g_4}{\partial \rjkna} \cdot 
+\frac{\Delta_{jk\mathbf{n_1}\alpha}}{\rjkna} \cdot n_{3,\gamma} \cdot \hgb
+}}}
+\end{align}
+Combining with Equation \ref{eq:dEdhab}, \ref{eq:stress_g2_right} and 
+\ref{eq:stress_g4_right}, we can now start deriving the right part of Equation 
+\ref{eq:stress}. To simplify the derivation, we just assume $G_{il}$ represents
+a radial function:
+\newcommand{\dE}{\partial{E^{total}}}
+\begin{align}
+\label{eq:dEdhTh_g2_expanded}
+\left(
+    \left(\frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h}
+\right)_{\alpha\beta} & = 
+\sum_{\gamma}{\frac{\dE}{\partial \hga} \hgb} \nonumber \\
+& = \sum_{\gamma}{\sum_{i}^{N}{\sum_{l}^{N_G}}{
+    \frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}}
+    \cdot
+    \sum_{j \neq i}{\sum_{\mathbf{n}}}{
+    \frac{\partial g_2}{\partial \rijn} 
+    \cdot 
+    \frac{\Delta_{ij\mathbf{n}\alpha}}{\rijn} \cdot n_{\gamma}} \hgb
+}} \nonumber \\
+& = \sum_{i}^{N}{\sum_{l}^{N_G}}{\sum_{j \neq i}{\sum_{\mathbf{n}}}{
+    \frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}}
+    \cdot
+    \frac{\partial g_2}{\partial \rijn} 
+    \cdot 
+    \frac{\Delta_{ij\mathbf{n}\alpha}}{\rijn}}
+    \sum_{\gamma}{\cdot n_{\gamma}\hgb}
+} \nonumber \\
+& = -\sum_{i}^{N}{\sum_{l}^{N_G}}{\sum_{j \neq i}{\sum_{\mathbf{n}}}{
+    f^{'}_{ij\mathbf{n}}
+    \sum_{\gamma}{\cdot n_{\gamma}\hgb}
+}}
+\end{align}
+where $f^{'}_{ij\mathbf{n}}$ is the partial force:
+\begin{equation}
+f^{'}_{ij\mathbf{n}} = 
+-\frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}} \cdot 
+\frac{\partial g_2}{\partial \rijn} \cdot 
+\frac{\Delta_{ij\mathbf{n}\alpha}}{\rijn}
+\end{equation}
+If $G_{il}$ is an angular symmetry function, we can also get a similar 
+expression. Thus,
+\begin{equation}
+\left(\frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h} =
+-\left(\sum_{\mathbf{n}}{\mathbf{h}^T\mathbf{n}} \otimes 
+\sum_{i=1}^{N}{F^{\prime}_{i\mathbf{n}}}\right)^T
+\end{equation}
+The left part of Equation \ref{eq:stress} can be calculated with 
+simple matrix multiplacation:
+\begin{equation}
+\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} = R^{T} F
+\end{equation}
+So finally we can derive the vectorized expression of virial stress:
+\begin{equation}
+\epsilon = -F^{T} R + \left( \frac{\dE}{\partial \mathbf{h}} \right)^T\mathbf{h}
+\end{equation}
+
+Now, the virial stress can be calculated with just a few lines of codes within 
+arbitrary Machine Learning framework (TensorFlow, PyTorch, etc). The following 
+codes are written in Python-3.7/TensorFlow-1.12, where \textit{energy} and 
+\textit{volume} are scalar tensors, \textit{cell} is a $3 \times 3$ tensor, 
+\textit{positions} is a $N\times 3$ tensor and \textit{forces} (the total forces 
+on these atoms) is also a $N\times 3$ tensor:
+\begin{verbatim}
+def get_virial_stress_tensor(energy, cell, volume, positions, forces):
+    dEdh = tf.gradients(energy, cell, name='dEdh)[0]
+    right = tf.matmul(tf.transpose(dEdh, name='dEdhT'), cell)
+    left = tf.matmul(tf.transpose(forces), positions)
+    stress = tf.add(tf.negative(left), right, name='stress')
+    stress = tf.div(stress, volume, name='virial')
+    return stress
+\end{verbatim}
+
+\newpage
+
+\subsection{Implementation of the $g^2_{\mathrm{map}}$}
+
+This function shows the calculation of $g^2_{\mathrm{map}}$. The returned dict
+contains $g^2_{\mathrm{map}}$, $i^{(0)}_{\mathrm{+,g}}$, 
+$j^{(0)}_{\mathrm{+,g}}$ and $\mathbf{n_g}$. $\nijmax$ should be provided in 
+advance. \textmd{interactions} is a list of \textmd{string} representing the 
+\textbf{ordered} interactions (e.g. \textmd{['NiNi','NiMo','MoMo','MoNi']}). 
+\textmd{offsets} is a list of integers marking the starting indices of the 
+\textmd{interactions}. As an example, if $N_{\eta}$ is 8, the \textmd{offsets}
+corresponding to \textmd{['NiNi','NiMo','MoMo','MoNi']} should be 
+\textmd{[0, 8, 16, 24]}.
+\textmd{local\_to\_global\_map} is a dict mapping local indices to global 
+indices.
+
+\begin{verbatim}
+def get_g2_map(atoms: Atoms, nij_max: int, interactions: list, 
+               local_to_global_map: dict, offsets: list):
+    g2_map = np.zeros((nij_max, 2), dtype=np.int32)
+    tlist = np.zeros(nij_max, dtype=np.int32)
+    symbols = atoms.get_chemical_symbols()
+    ilist, jlist, Slist = neighbor_list('ijS', atoms, rc)
+    nij = len(ilist)
+    tlist.fill(0)
+    for i in range(nij):
+        symboli = symbols[ilist[i]]
+        symbolj = symbols[jlist[i]]
+        tlist[i] = interactions.index('{}{}'.format(symboli, symbolj))
+    ilist = np.resize(ilist + 1, (nij_max, ))
+    jlist = np.resize(jlist + 1, (nij_max, ))
+    Slist = np.resize(Slist, (nij_max, 3))
+    for count in range(len(ilist)):
+        if ilist[count] == 0:
+            break
+        ilist[count] = local_to_global_map[ilist[count]]
+        jlist[count] = local_to_global_map[jlist[count]]
+    g2_map[:, 0] = ilist
+    g2_map[:, 1] = offsets[tlist]
+    return {"g2_map": g2_map, "ilist": ilist, "jlist": jlist, 
+            "shift": np.asarray(Slist)}
+\end{verbatim}
+
+\newpage
+
+\subsection{Implementation of the $g^4_{\mathrm{map}}$}
+
+The construction of $g^4_{\mathrm{map}}$ is similar to $g^2_{\mathrm{map}}$. 
+$\nijkmax$ should be provided in advance. 
+\textmd{global\_to\_local\_map} is the reverse dict of 
+\textmd{local\_to\_global\_map}.
+\begin{verbatim}
+def get_g4_map(atoms: Atoms, g2_map: dict, interactions: list, 
+               offsets: list, global_to_local_map: dict, nijk_max: int):
+    g4_map = np.zeros((nijk_max, 2), dtype=np.int32)
+    ijk = np.zeros((nijk_max, 3), dtype=np.int32)
+    n1 = np.zeros((nijk_max, 3), dtype=np.float32)
+    n2 = np.zeros((nijk_max, 3), dtype=np.float32)
+    n3 = np.zeros((nijk_max, 3), dtype=np.float32)
+    symbols = atoms.get_chemical_symbols()
+    indices = {}
+    vectors = {}
+    for i, atomi in enumerate(g2["ilist"]):
+        if atomi == 0:
+            break
+        if atomi not in indices:
+            indices[atomi] = []
+            vectors[atomi] = []
+        indices[atomi].append(g2["jlist"][i])
+        vectors[atomi].append(g2["shift"][i])
+    count = 0
+    for atomi, nl in indices.items():
+        indexi = global_to_local_map[atomi]
+        symboli = symbols[indexi]
+        prefix = '{}'.format(symboli)
+        for j in range(len(nl)):
+            atomj = nl[j]
+            indexj = global_to_local_map[atomj]
+            symbolj = symbols[indexj]
+            for k in range(j + 1, len(nl)):
+                atomk = nl[k]
+                indexk = global_to_local_map[atomk]
+                symbolk = symbols[indexk]
+                interaction = '{}{}'.format(
+                    prefix, ''.join(sorted([symbolj, symbolk])))
+                ijk[count] = atomi, atomj, atomk
+                n1[count] = vectors[atomi][j]
+                n2[count] = vectors[atomi][k]
+                n3[count] = vectors[atomi][k] - vectors[atomi][j]
+                index = interactions.index(interaction)
+                g4_map[count, 0] = atomi
+                g4_map[count, 1] = offsets[index]
+                count += 1
+    return {"g4_map": g4_map, "ij": ij, "ik": ik, "jk": jk, 
+            "n1": n1, "n2": n2, "n3": n3}
+\end{verbatim}
 

### 2019-04-23 tensoralloy/nn/dataclasses.py
`slots` are added for most of these dataclasses.

@@ -4,21 +4,58 @@ This module defines data classes for `tensoralloy.nn` package.
 """
 from __future__ import print_function, absolute_import
 
-from dataclasses import dataclass
+from dataclasses import dataclass, fields
 from typing import List, Union
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
 
+def add_slots(cls):
+    """
+    A decorator to put __slots__ on a dataclass with fields with defaults.
+
+    Need to create a new class, since we can't set __slots__ after a class has
+    been created.
+
+    References
+    ----------
+    https://github.com/ericvsmith/dataclasses/blob/master/dataclass_tools.py
+
+    """
+    # Make sure __slots__ isn't already set.
+    if '__slots__' in cls.__dict__:
+        raise TypeError(f'{cls.__name__} already specifies __slots__')
+
+    # Create a new dict for our new class.
+    cls_dict = dict(cls.__dict__)
+    field_names = tuple(f.name for f in fields(cls))
+    cls_dict['__slots__'] = field_names
+    for field_name in field_names:
+        # Remove our attributes, if present. They'll still be
+        #  available in _MARKER.
+        cls_dict.pop(field_name, None)
+    # Remove __dict__ itself.
+    cls_dict.pop('__dict__', None)
+    # And finally create the class.
+    qualname = getattr(cls, '__qualname__', None)
+    cls = type(cls)(cls.__name__, cls.__bases__, cls_dict)
+    if qualname is not None:
+        cls.__qualname__ = qualname
+    return cls
+
+
+@add_slots
 @dataclass
 class _LossOptions:
     """
     The basic options for a loss.
     """
+
     weight: float = 1.0
 
 
+@add_slots
 @dataclass
 class EnergyLossOptions(_LossOptions):
     """
@@ -27,54 +64,79 @@ class EnergyLossOptions(_LossOptions):
     per_atom_loss: bool = False
 
 
+@add_slots
 @dataclass
 class ForcesLossOptions(_LossOptions):
+    """
+    No extra option for the loss of forces.
+    """
     pass
 
 
+@add_slots
 @dataclass
 class StressLossOptions(_LossOptions):
     """
     Special options for the loss of stress tensors.
     """
+
     use_rmse: bool = True
 
 
+@add_slots
 @dataclass
 class PressureLossOptions(_LossOptions):
+    """
+    No extra option for the loss of total pressure.
+    """
     pass
 
 
+@add_slots
 @dataclass
[…]

### 2019-04-23 tensoralloy/nn/tests/test_dataclasses.py
Add some tests for the dataclasses.

@@ -1,0 +1,47 @@
+#!coding=utf-8
+"""
+This module defines unit tests of the data classes.
+"""
+from __future__ import print_function, absolute_import
+
+import nose
+
+from nose.tools import assert_equal, assert_raises
+
+from tensoralloy.nn.dataclasses import OptParameters, LossParameters
+from tensoralloy.utils import AttributeDict
+
+__author__ = 'Xin Chen'
+__email__ = 'Bismarrck@me.com'
+
+
+def test_dataclasses():
+    """
+    Test some data classes.
+    """
+    hparams = AttributeDict(
+        opt=AttributeDict(decay_steps=100, method='rmsprop'),
+        loss=AttributeDict(
+            energy=AttributeDict(per_atom_loss=True),
+            elastic=AttributeDict(crystals=['Ni'],
+                                  constraint=AttributeDict(stress_weight=1.5))
+        )
+    )
+
+    opt_parameters = OptParameters(**hparams.opt)
+
+    assert_equal(opt_parameters.decay_steps, 100)
+    assert_equal(opt_parameters.method, 'rmsprop')
+
+    loss_parameters = LossParameters(**hparams.loss)
+
+    assert_equal(loss_parameters.energy.per_atom_loss, True)
+    assert_equal(loss_parameters.elastic.crystals, ['Ni'])
+    assert_equal(loss_parameters.elastic.constraint.stress_weight, 1.5)
+
+    with assert_raises(Exception):
+        _ = OptParameters(**AttributeDict(decay_method='adam'))
+
+
+if __name__ == "__main__":
+    nose.run()

### 2019-04-23 tensoralloy/train/training.py
The method `get_hparams` is updated.

@@ -18,11 +18,12 @@ from tensorflow_estimator import estimator as tf_estimator
 
 from tensoralloy.dataset import Dataset
 from tensoralloy.io.input import InputReader
-from tensoralloy.io.input.reader import nested_set
 from tensoralloy.nn.basic import BasicNN
 from tensoralloy.nn import EamFsNN, EamAlloyNN, AtomicNN, AtomicResNN
 from tensoralloy.nn.eam.potentials import available_potentials
-from tensoralloy.utils import set_logging_configs, AttributeDict
+from tensoralloy.nn.dataclasses import TrainParameters, OptParameters
+from tensoralloy.nn.dataclasses import LossParameters
+from tensoralloy.utils import set_logging_configs, AttributeDict, nested_set
 from tensoralloy.utils import check_path
 from tensoralloy.dtypes import set_float_precision
 
@@ -107,9 +108,9 @@ class TrainingManager:
         hparams = AttributeDict(
             seed=self._reader['seed'],
             precision=self._reader['precision'],
-            train=AttributeDict(self._reader['train']),
-            opt=AttributeDict(self._reader['opt']),
-            loss=AttributeDict(self._reader['nn.loss']),
+            train=TrainParameters(**self._reader['train']),
+            opt=OptParameters(**self._reader['opt']),
+            loss=LossParameters(**self._reader['nn.loss']),
             debug=AttributeDict(self._reader['debug'])
         )
 

### 2019-04-23 tensoralloy/nn/tests/test_basic_nn.py
Fix the tests.

@@ -175,9 +175,9 @@ def test_build_nn_with_properties():
             loss_parameters = LossParameters()
             loss_parameters.elastic.crystals = ['Ni']
             loss_parameters.elastic.weight = 0.1
-            loss_parameters.elastic.constrain_options.forces_weight = 1.0
-            loss_parameters.elastic.constrain_options.stress_weight = 0.1
-            loss_parameters.elastic.constrain_options.use_kbar = True
+            loss_parameters.elastic.constraint.forces_weight = 1.0
+            loss_parameters.elastic.constraint.stress_weight = 0.1
+            loss_parameters.elastic.constraint.use_kbar = True
 
             mode = tf_estimator.ModeKeys.TRAIN
 

### 2019-04-23 tensoralloy/nn/tests/test_elastic.py

@@ -30,7 +30,7 @@ def test_read_external_crystal():
     builtin = built_in_crystals['Ni3Mo']
 
     assert_equal(builtin.name, crystal.name)
-    assert_equal(len(builtin.elastic_constants), len(crystal.elastic_constants))
+    assert_equal(7, len(crystal.elastic_constants))
 
     for elastic_constant in crystal.elastic_constants:
         assert_in(elastic_constant, builtin.elastic_constants)

### 2019-04-23 tensoralloy/nn/eam/potentials/mishin.py
Minor update. This module is still under development.

@@ -14,6 +14,21 @@ __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
 
+def mishin_cutoff(x):
+    """
+    The cutoff function:
+
+        psi(x) = x**4 / (1 + x**4)  x <  0
+                 0                  x >= 0
+
+    """
+    with tf.name_scope("Psi"):
+        x = tf.nn.relu(-x, name='ix')
+        x4 = tf.pow(x, 4, name='x4')
+        one = tf.constant(1.0, dtype=x.dtype, name='one')
+        return tf.math.truediv(x4, one + x4, name='psi')
+
+
 class MishinH(EamAlloyPotential):
     """
     The ADP potential functions of the Mishin H-style.
@@ -40,21 +55,6 @@ class MishinH(EamAlloyPotential):
         Return the default parameters.
         """
         return {}
-
-    @staticmethod
-    def cutoff(x):
-        """
-        The cutoff function:
-
-            psi(x) = x**4 / (1 + x**4)  x <  0
-                     0                  x >= 0
-
-        """
-        with tf.name_scope("Psi"):
-            x = tf.nn.relu(-x, name='ix')
-            x4 = tf.pow(x, 4, name='x4')
-            one = tf.constant(1.0, dtype=x.dtype, name='one')
-            return tf.math.truediv(x4, one + x4, name='psi')
 
     def phi(self, r: tf.Tensor, kbody_term: str, variable_scope: str,
             verbose=False):
@@ -102,7 +102,7 @@ class MishinH(EamAlloyPotential):
 
             drc = tf.subtract(r, rc, name='dr')
             drh = tf.math.truediv(drc, h, name='drh')
-            psi = self.cutoff(drh)
+            psi = mishin_cutoff(drh)
 
             dr0 = tf.math.subtract(r, R0, name='dr0')
             dr1 = tf.math.subtract(r, R1, name='dr1')
@@ -153,7 +153,7 @@ class MishinH(EamAlloyPotential):
 
             dr = tf.subtract(r, rc, name='dr')
             drh = tf.math.truediv(dr, h, name='drh')
-            psi = self.cutoff(drh)
+            psi = mishin_cutoff(drh)
 
             rz1 = tf.pow(r, z1, name='rz1')
             e1 = tf.exp(-r * a1, name='e1')
@@ -261,7 +261,7 @@ class MishinH(EamAlloyPotential):
 
[…]

### 2019-04-23 doc/papers/nn/manuscript.tex
Team revision is done. The version is CPC.v1.

@@
-\documentclass[prb,preprint]{revtex4-2}
+\documentclass[preprint]{revtex4-2}
 
@@
 }
-\author{Xin Chen, De-Ye Lin, Hai-Feng Song$^\mathrm{*}$}
+\author{Xin Chen}
+\author{Xing-Yu Gao}
+\author{Ya-Fan Zhao}
+\author{De-Ye Lin}
+\email{lindeye0716@163.com}
+\author{Wei-Dong Chu}
+\author{Hai-Feng Song}
+\email{song\_haifeng@iapcm.ac.cn}
 \affiliation{
@@
     Beijing 100088, China}
-
 \affiliation{
@@
 materials. Recently, machine learning interaction potentials have gained much 
-more attentions as they can give density functional theory level predictions 
-within second. Currently, symmetry function based atomistic neural network is 
-the most widely used model for alloys. To precisely describe atomistic 
-interactions, integrating advanced metrics, such as force or virial stress, into 
-training can be of great help. However, the traditional way to construct a 
+more attentions as they can provide density functional theory level predictions 
+within negligible time. Currently, the symmetry function descriptor based 
+atomistic neural network is the most widely used model for modeling alloys. 
+To precisely describe complex potential energy surfaces, integrating advanced 
+metrics, such as force or virial stress, into training can be of great help. 
+However, the traditional way to construct a 
 machine learning model computation graph starts from pre-computed descriptors, 
 but not positions, due to technial challenges. Thus, deriving analytical atomic 
-force or virial stress of a machine learning model becomes quite difficult as 
+force and virial stress of a machine learning model becomes quite difficult as 
 the partial derivations of descriptors with respect to positions need separate 
-implementations, which requires plenty of effort and its efficiency can not be 
+implementations, which requires plenty of efforts and its efficiency can not be 
 guaranteed.
@@
 stress. All these new algorithms have been implemented in our Python package, 
-TensorAlloy. TensorAlloy supports both \textit{molecules} and \textit{solids} 
-and one hour is sufficient for TensorAlloy to obtain models with state-of-art 
-level accuracy.
+TensorAlloy. TensorAlloy supports constructing machine learning interaction 
+potentials for both \textit{molecules} and \textit{solids} and one hour is 
+sufficient for TensorAlloy to obtain models with state-of-art level accuracy.
 \end{abstract}
@@
 computation expenses. Physical model based empirical potentials, such as the 
-embedded-atom method\cite{eam-1,eam-2,eam-3,eam-4,eam-5}, are much more popular 
-for long-time simulation because of their reasonable accuraty and acceptable 
-costs. However, designing empirical potentials and optimizing parameters for 
-alloys are still challenging tasks.
+embedded-atom method\cite{eam-1,eam-2,eam-3,eam-4,eam-5} or its variants (
+modified embedded-atom method\cite{eam-5,meam-1,meam-2,meam-3}, 
+angular-dependent interaction potential\cite{adp-1,adp-2,adp-3}, etc), are much 
+more popular for long-time simulation because of their reasonable accuraty and 
+acceptable costs. 
+However, designing empirical potentials and optimizing parameters for 
+alloys are still challenging tasks\cite{eam-5, adp-2, SNAP_2018}.
 
@@
 instead of traditional empirical potentials \textemdash to describe atomistic 
-interactions during MD simulations. ML potentials are much easier to design and 
+interactions during MD simulations\cite{kCON,SchNet,DTNN,SNAP_2018,SNAP_Mo_2017,
+ANI,TensorMol}. ML potentials are much easier to design and 
 optimize. With sufficient training data, ML models can achieve similar or even 
-better performances compared with density functional theory. Until now, various 
-ML models (kCON\cite{kCON}, SchNet\cite{SchNet}, DTNN\cite{DTNN}, 
-SNAP\cite{SNAP_Mo_2017, SNAP_2018}, etc) have been published by researchers. 
-Among them, the symmetry function based atomistic neural network (ANN) model, 
-first proposed by Parinello and Behler in 
-2007\cite{Behler,Behler2,Behler3,Behler4,Behler1}, is still the most widely used 
-method for \textit{solids} and its effectness and accuracy has been proven by 
-several works\cite{Behler-solids-lzp-1,Behler-alloy-1,Behler-alloy-2,
-Behler-alloy-3}. The Amp\cite{AMP} package, developed by Peterson's group, is 
-the first open-source framework that implements the symmetry function 
-descriptor. Amp supports both \textit{molecules} and \textit{solids} and it has 
-successfully powered quite a few researches since 
-2016\cite{Amp-works-hammer,amp-work-1}. ANI\cite{ANI} and 
+better performances compared with density functional theory.
+The symmetry function based atomistic neural network (ANN) model, first proposed 
+by Parinello and Behler in 2007\cite{Behler,Behler2,Behler3,Behler4,Behler1}, 
+is still the most widely used method for \textit{solids} and its effectness and 
+accuracy has been proven by several 
+works\cite{Behler-solids-lzp-1,Behler-alloy-1,Behler-alloy-2, Behler-alloy-3}.
+Until now, various ML implementations\cite{AMP,ANI,TensorMol} have been 
+published by researchers. The Amp\cite{AMP} package, developed by Peterson's 
+group, is the first open-source framework that implements the symmetry function 
+descriptor. Amp can be used to learn interaction potentials for both 
+\textit{molecules} and \textit{solids} and it has successfully powered quite a 
+few researches since 2016\cite{Amp-works-hammer,amp-work-1}. ANI\cite{ANI} and 
 TensorMol\cite{TensorMol} are also symmetry function based packages but they 
@@
 descriptors with respect to positions. Although the derivation is theoretically
-clear, the implementation will be a challenge and the efficiency can not be 
+clear, the implementation is challenging and the efficiency can not be 
 guaranteed.
@@
 \ref{section:appendix} gives derivation and implementation details of key 
-algorithms. The compiled version of \tensoralloy{} program and all the 
-associated model files are available on 
-\href{https://github.com/Bismarrck/tensoralloy-release}{GitHub}.
+algorithms. The \tensoralloy{} program can be obtained on request.
 
@@
 Here $\mathbf{G}_i$ is a vector representing atomic descriptors of atom $i$. 
-$\mathbf{G}_i$ typically only depends on local environments \textemdash 
-neighbors \textemdash of atom $i$:
+$\mathbf{G}_i$ typically only depends on local environments, i.e.  
+neighbors of atom $i$:
 \begin{equation}
@@
 \end{equation}
-and $r_c$ is the cutoff radius. In our implementation, $R_s$ is always fixed to 
-0 so it becomes neglectable\cite{AMP}. Equation \eqref{eq:fc_origin} can be 
-further transformed to a vectorized expression:
+and $r_c$ is the cutoff radius. $R_s$ may be fixed to zero \cite{AMP}. 
+Equation \eqref{eq:fc_origin} can be further transformed to a vectorized 
+expression:
 \begin{equation}
@@
 
-The derivations are theoretically straightforward but coding these equations 
-manually will be a challenge\cite{AMP}. Thanks to the virtual atom approach, 
-\tensoralloy{} can now calculate $f_a$ using Equation \ref{eq:dEdr} directly.
-
-The $3 \times 3$ virial stress tensor $\epsilon$ is an important metric for 
-solids. For arbitrary many-body interaction potentials, $\epsilon$ can be 
-calculated with the following equation\cite{lammps_stress}:
+The derivations are theoretically straightforward but their implementations are 
+challenging \cite{AMP}. Later we will provide a new approach to address this 
+problem.
+
+The $3 \times 3$ virial stress tensor $\epsilon$ is an important metric to 
+describe solids under deformation or external pressure. For arbitrary many-body 
+interaction potentials, $\epsilon$ can be calculated with the following equation
+\cite{lammps_stress}:
 \begin{equation}
 \label{eq:stress_lammps}
-\epsilon = \left(-\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} - 
+V \cdot \epsilon = \left(-\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} - 
 \sum_{\mathbf{n}}{\mathbf{h}^T\mathbf{n}} \otimes 
@@
 \end{equation}
-where $\otimes$ indicates tensor product, $f_i$ is the total force acting on 
-atom $i$ and $F^{\prime}_{i\mathbf{n}}$ is the partial force. Yntil now, 
-most machine learning force-field models focus on fitting total energy and 
-atomic forces, very few of them\cite{DeePMD,DeePMD_rl,DeePMD_kit} had attempted 
-to include stress in their loss functions. The current expression of Equation 
-\ref{eq:stress_lammps} is not very compatible with NN or other ML potentials 
-since the partial forces are difficult to compute with vectorized operations. 
-To resolve this issue, we derived an equivalent form of Equation 
-\ref{eq:stress_lammps}:
+where $V$ is the volume, $\otimes$ indicates tensor product, $f_i$ is the total 
+force acting on atom $i$ and $F^{\prime}_{i\mathbf{n}}$ is the partial force. 
+Until now, most machine learning force-field models focus on fitting total 
+energy and atomic forces, very few of them\cite{DeePMD,DeePMD_rl,DeePMD_kit} had 
+attempted to include stress in their loss functions. 
+The current expression of Equation \ref{eq:stress_lammps} is not very compatible 
+with NN or other ML potentials since the partial forces are difficult to compute 
+with vectorized operations. To resolve this issue, we derived an equivalent form 
+of Equation \ref{eq:stress_lammps}:
 \begin{equation}
 \label{eq:stress}
-\epsilon = -F^{T} R + 
+V \cdot \epsilon = -F^{T} R + 
 \left(\frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h}
 \end{equation}
-where $R$ is the $N \times 3$ positions matrix and $F$ is the corresponding 
-total forces matrix. The new equation can be easily implemented with simple 
-matrix operations. The detailed derivation is given in the appendix.
+where $R$ is the $N \times 3$ positions matrix and $F$ is the 
+corresponding total forces matrix. The new equation can be easily implemented 
+with simple matrix operations. The detailed derivation is given in the appendix.
 
@@
 In this section we will describe details of \tensoralloy{}: the virtual atom 
-approach, the atomic residual potential and the loss function. The Ni-Mo alloy 
-system, with four $\eta$, two $\beta$, two $\gamma$ and one $\zeta$, will be 
-used as the example to show this algorithm. For simplicity, only radial symmetry
-function related algorithms are visualized in the figures.
+approach, the atomic residual potential and the loss function. 
+The Ni-Mo binary alloy system will be used as the example to show this 
+algorithm. The virtual atom approach is built upon TensorFlow. For simplicity, 
+only radial symmetry function related algorithms are visualized in the figures.
 
@@
 $N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$. 
-Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs of 
-arbitrary structure and $N_{ijk}^{\mathrm{max}}$ represents the maximum number 
-of triples. $N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depends on 
+Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs 
+and $N_{ijk}^{\mathrm{max}}$ represents the maximum number of triples in 
+arbitrary structure. 
+$N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depend on 
 $r_{cut}$. The associated codes are given in the appendix.
@@
 \includegraphics[scale=0.5]{figures/Fig1-prepare.pdf}
-\caption{\label{fig:algo1} The initialization. 
-\textbf{a)} the detections of $N_{\mathrm{Ni}}^{\mathrm{max}}$, 
+\caption{\label{fig:algo1} The initialization step. 
+\textbf{a)} describes the detections of $N_{\mathrm{Ni}}^{\mathrm{max}}$, 
 $N_{\mathrm{Ni}}^{\mathrm{max}}$, $N_{ij}^{max}$, $N_{ijk}^{max}$ and the global
 symbols list.
-\textbf{b)} and \textbf{c)} the \textit{offsets} and their corresponding 
-symmetry function parameters.
+The \textit{offsets} of radial and angular functions and their corresponding 
+symmetry function parameters are in \textbf{b)} and \textbf{c)}, respectively.
 }
@@
 forces $\mathbf{F_{b}}$ and the virial stress $\mathbf{\epsilon_{b}}$ are 
-calculated with Equation \ref{eq:dEdr} and Equation \ref{eq:stress} by with just 
-few lines of codes.
+calculated with Equation \ref{eq:dEdr} and Equation \ref{eq:stress} directly.
 
@@
 introduction of $E^{static}$ can significantly limit value range of NN outputs, 
-leading to much faster convergence speed and higher training stability 
+leading to faster convergence speed and higher training stability 
 (Fig \ref{fig:benchmark_qm7}c). The initial $\{E_{el}\}$ are calculated by 
@@
 in \textbf{eV/\AA}$\mathbf{^3}$. In most cases, we set $N_b$ to 50 or 100 and we
-use the Adam\cite{adam} optimizer with exponentially-decayed learning rate to 
+use the ADAM\cite{adam} optimizer with exponentially-decayed learning rate to 
 minimize the loss function. The activation function is Leaky ReLU
@@
 symmetry functions (Equation \ref{eq:G2}) are used and 'Angular' indicates both 
-radial and angular symmetry functions are used. The cutoff radius is 6.5 \AA and
-the corresponding $\nijmax$ and $\nijkmax$ are 506 and 5313, indicating the 
-calculation of angular descriptors is much more expensive.
-The $\eta$ for radial symmetry functions are 0.1, 0.5, 1, 2, 4, 8, 12, 16, 20, 
-40 and $\beta$ (0.1, 0.5), $\gamma$ (1, -1) and $\zeta$ (1, 4) are used for
-angular functions. The initial learning rate is 0.01 and the it is exponentially 
-decayed with rate 0.99 for every 5000 steps. Each atomistic neural network has
-two hidden layers with 128 and 64 neurons.
+radial and angular symmetry functions are used. The cutoff radius is 6.5 \AA.
+The corresponding $\nijmax$ and $\nijkmax$ are 506 and 5313, respectively, 
+indicating the calculation of angular descriptors is much more expensive.
+Values of $\eta$ for radial symmetry functions are 0.1, 0.5, 1, 2, 4, 8, 12, 16, 
+20, 40 and $\beta$ (0.1, 0.5), $\gamma$ (1, -1) and $\zeta$ (1, 4) are used for
+angular functions. $R_s$ is fixed to zero. The initial learning rate is 0.01 and 
+then it is exponentially decayed with rate 0.99 for every 5000 steps. 
+Each atomistic neural network has two hidden layers with 128 and 64 neurons.
 
@@
 \caption{\label{fig:snap_gpu_train_speed} The test MAEs of the SFNN/Ni-Mo model 
-vs training time (GPU Hour). The black dotted line marks the performance of the
-SNAP/Ni-Mo model.}
+vs training time (GPU Hour). The black dotted line marks the final performance 
+of the SNAP/Ni-Mo model \cite{SNAP_2018}.}
 \end{figure}
@@
     \includegraphics[scale=0.8]{figures/Fig7-surface-energy.pdf}
-\caption{\label{fig:surface_energy_Ni} Surface energies ($J/m^2$) of different 
-Ni surfaces calculated with DFT, Ni/SFNN and Ni-Mo/SFNN models. The MAEs of the 
-Ni/SFNN and Ni-Mo/SFNN relative to the DFT values are 0.09 and 0.05, 
-respectively.}
+\caption{\label{fig:surface_energy_Ni} Surface formation energies ($J/m^2$) of 
+different Ni surfaces calculated by DFT, Ni/SFNN and Ni-Mo/SFNN models. 
+The MAEs of the Ni/SFNN and Ni-Mo/SFNN relative to the DFT values are 0.09 and 
+0.05, respectively.}
 \end{figure}
@@
 
-This work was supported by. Computing resources were provided by.
+This work was supported by the National Key Research and Development Program of 
+China under Grant No. 2016YFB0201203, the Science Challenge Project under Grant 
+No. TZ2018002 and the National Natural Science Foundation of China under Grant 
+No. U1630250.
 
@@
 & = -\sum_{i}^{N}{\sum_{l}^{N_G}}{\sum_{j \neq i}{\sum_{\mathbf{n}}}{
-    f^{'}_{ij\mathbf{n}}
+    f^{'}_{ij\mathbf{n}\alpha}
     \sum_{\gamma}{\cdot n_{\gamma}\hgb}
@@
 \begin{equation}
-f^{'}_{ij\mathbf{n}} = 
+f^{'}_{ij\mathbf{n}\alpha} = 
 -\frac{\partial \mathbf{NN}_{el}(\mathbf{G}_i)}{\partial G_{il}} \cdot 

### 2019-04-26 tensoralloy/cli.py
The `PrintEvaluationSummaryProgram` is refined.

@@ -5,6 +5,7 @@ This module defines the command-line main function of `tensoralloy`.
 from __future__ import print_function, absolute_import
 
 import tensorflow as tf
+import pandas as pd
 import numpy as np
 import argparse
 import glob
@@ -331,111 +332,70 @@ class PrintEvaluationSummaryProgram(CLIProgram):
         super(PrintEvaluationSummaryProgram, self).config_subparser(subparser)
 
     @staticmethod
-    def print_evaluation_summary(logfile, eval_forces=False, eval_stress=False):
+    def print_evaluation_summary(logfile) -> pd.DataFrame:
         """
         Summarize the evalutaion results of the logfile.
         """
-        e_patt = re.compile(r".*tensorflow\s+INFO\s+.*global\sstep\s(\d+):.*"
-                            r"Energy/mae/atom\s=\s([0-9.]+),.*")
 
-        ef_patt = re.compile(r".*tensorflow\s+INFO\s+.*global\sstep\s(\d+):.*"
-                             r"Energy/mae/atom\s=\s([0-9.]+),.*"
-                             r"Forces/mae\s=\s([0-9.]+),.*")
-
-        efs_patt = re.compile(r".*tensorflow\s+INFO\s+.*global\sstep\s(\d+):.*"
-                              r"Energy/mae/atom\s=\s([0-9.]+),.*"
-                              r"Forces/mae\s=\s([0-9.]+),.*"
-                              r"Stress/mae\s=\s([0-9.]+),.*"
-                              r"Stress/relative\s=\s([0-9.]+),.*")
-
-        if not eval_forces:
-            patt = e_patt
-        elif not eval_stress:
-            patt = ef_patt
-        else:
-            patt = efs_patt
-
-        energy = []
-        forces = []
-        stress = []
-        stress_rel = []
-        steps = []
+        global_step_patt = re.compile(r".*tensorflow\s+INFO\s+Saving\sdict"
+                                      r"\sfor\sglobal\sstep\s(\d+):(.*)")
+        key_value_pair_patt = re.compile(r"\s+(.*)\s=\s([0-9.-]+)")
+        pid_patt = re.compile(r".*tensorflow\s+INFO\s+pid=(\d+)")
+        results = {}
 
         with open(logfile) as fp:
             for line in fp:
                 line = line.strip()
-                m = patt.search(line)
-                if m:
-                    steps.append(int(m.group(1)))
-                    energy.append(float(m.group(2)))
-                    if eval_forces:
[…]

### 2019-04-26 tensoralloy/tests/test_cli.py

@@ -1,0 +1,47 @@
+#!coding=utf-8
+"""
+This module defines tests of the `CLI` module.
+"""
+from __future__ import print_function, absolute_import
+
+import nose
+import unittest
+
+from os.path import join, exists
+from os import remove
+from nose.tools import assert_equal
+
+from tensoralloy.cli import PrintEvaluationSummaryProgram
+from tensoralloy.test_utils import test_dir
+
+__author__ = 'Xin Chen'
+__email__ = 'Bismarrck@me.com'
+
+
+class PrintSummaryTest(unittest.TestCase):
+
+    def setUp(self):
+        """
+        The setup function.
+        """
+        self.csv_file = join(test_dir(), 'summary.csv')
+
+    def test_print_summary(self):
+        """
+        Test `PrintEvaluationSummaryProgram`.
+        """
+        program = PrintEvaluationSummaryProgram()
+        df = program.print_evaluation_summary(join(test_dir(), "logfile"))
+        assert_equal(df.index.tolist(), [200, 400])
+        assert_equal(exists(self.csv_file), True)
+
+    def tearDown(self):
+        """
+        The cleanup function.
+        """
+        if exists(self.csv_file):
+            remove(self.csv_file)
+
+
+if __name__ == "__main__":
+    nose.run()

### 2019-04-26 tensoralloy/nn/basic.py
During the evaluation stage elastic constants will also be calculated.

@@ -459,9 +459,7 @@ class BasicNN:
                 weight=loss_parameters.l2.weight,
                 collections=collections)
 
-            # Elastic constants will only be computed during training.
-            if mode == tf_estimator.ModeKeys.TRAIN and \
-                    'elastic' in self._minimize_properties:
+            if 'elastic' in self._minimize_properties:
                 losses.elastic = elastic_ops.get_elastic_constant_loss(
                     nn=self,
                     list_of_crystal=loss_parameters.elastic.crystals,
@@ -654,6 +652,11 @@ class BasicNN:
                         ops_dict['Stress/relative'] = \
                             tf.metrics.mean(upper / lower)
                     metrics.update(ops_dict)
+
+            if 'elastic' in self._minimize_properties:
+                for tensor in tf.get_collection(GraphKeys.EVAL_METRICS):
+                    if tensor.op.name.startswith("Elastic"):
+                        metrics[tensor.op.name] = (tensor, tf.no_op())
 
             return metrics
 

### 2019-04-26 tensoralloy/nn/elastic.py

@@ -360,6 +360,7 @@ def get_elastic_constant_loss(nn,
                             name='bar')
                     constraints['stress'].append(value)
                     tf.add_to_collection(GraphKeys.TRAIN_METRICS, value)
+                    tf.add_to_collection(GraphKeys.EVAL_METRICS, value)
 
                 with tf.name_scope("Cijkl"):
                     for elastic_constant in crystal.elastic_constants:
@@ -381,6 +382,7 @@ def get_elastic_constant_loss(nn,
                                                  name=f'C{vi}{vj}/weight'))
 
                         tf.add_to_collection(GraphKeys.TRAIN_METRICS, cijkl)
+                        tf.add_to_collection(GraphKeys.EVAL_METRICS, cijkl)
 
         with tf.name_scope("Loss"):
 

### 2019-04-26 doc/papers/nn/manuscript.tex
Version is CPC.v2. This manuscript has been submitted.

@@
 \affiliation{
-    Institute of Applied Physics and Computational Math, 
+    Institute of Applied Physics and Computational Mathematics, 
     Beijing 100088, China}
@@
 machine learning model computation graph starts from pre-computed descriptors, 
-but not positions, due to technial challenges. Thus, deriving analytical atomic 
+but not positions, due to technical challenges. Thus, deriving analytical atomic 
 force and virial stress of a machine learning model becomes quite difficult as 

### 2019-06-26 doc/papers/nn/figures/Fig4-qm7.py
Figures, data and codes for the revised manuscript.

@@ -1,102 +1,50 @@
+#!coding=utf-8
 from __future__ import print_function
 
 import numpy as np
-import re
+import pandas as pd
+
 from matplotlib import pyplot as plt
 from matplotlib.gridspec import GridSpec
-
-examples_per_second = {
-    'GPU': {
-        'Angular': {
-            1: 120,
-            10: 780,
-            20: 1600,
-            50: 2400,
-            100: 2800,
-        },
-        'Radial': {
-            1: 90,
-            10: 1000,
-            20: 2400,
-            50: 6000,
-            100: 10800,
-        }
-    },
-    'CPU': {
-        'Angular': {
-            1: 270,
-            10: 690,
-            20: 750,
-            50: 610,
-            100: 660,
-        },
-        'Radial': {
-            1: 400,
-            10: 2800,
-            20: 3800,
-            50: 5100,
-            100: 5800,
-        }
-    }
-}
 
 orders = [
     ('CPU', 'Radial'), ('CPU', 'Angular'), 
     ('GPU', 'Radial'), ('GPU', 'Angular'),
 ]
 
-traj_files = [
-    (1, 'Radial', 'Radial / Batch Size 1', 'fig4-traj/g2.1.gpu.traj'),
-    (50, 'Radial', 'Radial / Batch Size 50', 'fig4-traj/g2.50.gpu.traj'),
-    (100, 'Radial', 'Radial / Batch Size 100', 'fig4-traj/g2.100.gpu.traj'),
-    (1, 'Angular', 'Angular / Batch Size 1', 'fig4-traj/g4.1.gpu.traj'),
-    (50, 'Angular', 'Angular / Batch Size 50', 'fig4-traj/g4.50.gpu.traj'),
-    (100, 'Angular', 'Angular / Batch Size 100', 'fig4-traj/g4.100.gpu.traj'),
-]
-
-traj_patt = re.compile(r"Step\s=\s+(\d+)\sy_mae/atom\s=\s+([0-9.]+)")
-
-
-def read_traj(filename, batch_size: int, sf: str):
-    """ 
-    Read the trajectory and return the MAE/time(GPU) curve.
-    """
-    speed = examples_per_second['GPU'][sf][batch_size]
-    factor = 1.0 / (speed / batch_size * 3600)
-    with open(filename) as fp:
-        data = []
-        tail = []
[…]

### 2019-06-26 doc/papers/nn/figures/cpc_speed.py

@@ -1,0 +1,146 @@
+from __future__ import print_function, absolute_import
+
+import numpy as np
+
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MultipleLocator
+
+__author__ = 'Xin Chen'
+__email__ = 'Bismarrck@me.com'
+
+
+workstation = """
+Number of atoms: 2000
+* ASE neighbor time: 0.5930616855621338
+* Python feed dict time: 1.5961778163909912
+* TensorFlow execution time: 0.04986286163330078
+Number of atoms: 6750
+* ASE neighbor time: 1.2973895072937012
+* Python feed dict time: 3.7827587127685547
+* TensorFlow execution time: 0.12984418869018555
+Number of atoms: 16000
+* ASE neighbor time: 3.7363853454589844
+* Python feed dict time: 9.718251943588257
+* TensorFlow execution time: 0.17889857292175293
+Number of atoms: 31250
+* ASE neighbor time: 5.931849002838135
+* Python feed dict time: 16.419432401657104
+* TensorFlow execution time: 0.3449971675872803
+Number of atoms: 54000
+* ASE neighbor time: 10.83665919303894
+* Python feed dict time: 28.86913824081421
+* TensorFlow execution time: 0.6041886806488037
+Number of atoms: 85750
+* ASE neighbor time: 19.667125940322876
+* Python feed dict time: 51.148345708847046
+* TensorFlow execution time: 0.38422513008117676
+Number of atoms: 128000
+* ASE neighbor time: 26.636351346969604
+* Python feed dict time: 70.64423513412476
+* TensorFlow execution time: 1.0043096542358398"""
+
+
+cpu_only = """Number of atoms: 2000
+* ASE neighbor time: 0.623563289642334
+* Python feed dict time: 1.633838415145874
+* TensorFlow execution time: 0.10250282287597656
+Number of atoms: 6750
+* ASE neighbor time: 1.3154628276824951
+* Python feed dict time: 3.6260945796966553
+* TensorFlow execution time: 0.32638072967529297
+Number of atoms: 16000
+* ASE neighbor time: 3.5952367782592773
+* Python feed dict time: 9.219270467758179
+* TensorFlow execution time: 0.6607975959777832
+Number of atoms: 31250
[…]

### 2019-06-26 doc/papers/nn/figures/snap_train_curve.py

@@ -1,0 +1,58 @@
+#!coding-utf-8
+
+from __future__ import print_function
+
+import pandas as pd
+
+from scipy.interpolate import interp1d
+from matplotlib import pyplot as plt
+from matplotlib.ticker import MultipleLocator
+
+df = pd.read_csv("snap.summary.csv")
+
+
+gpu_hours = df['global_step'] / 600.0 / 60.0
+y_list = df["Energy/mae/atom"] * 1000.0
+f_list = df["Forces/mae"]
+
+
+y_spline = interp1d(gpu_hours, y_list)
+
+yx = None
+yy = None
+step0 = int(min(gpu_hours) / 0.01) + 1
+stept = int(max(gpu_hours) / 0.01)
+
+for step in range(step0, stept):
+    t = step * 0.01
+    if yx is None:
+        yt = y_spline(t)
+        if yt <= 22.5:
+            yx = t
+            yy = yt
+            break
+
+
+fig, ax1 = plt.subplots(1, 1, figsize=[6, 4])
+
+ax1.plot(gpu_hours, y_list, "r-")
+
+ax1.set_xlabel("GPU Hour", fontsize=16)
+ax1.set_ylabel("Energy MAE (meV/atom)", fontsize=14, color='r')
+ax1.yaxis.set_minor_locator(MultipleLocator(1))
+
+assert isinstance(ax1, plt.Axes)
+ax1.set_yscale('log')
+ax1.plot((yx, yx), (0.0, yy), linestyle="--", color='r', linewidth=0.8)
+
+
+ax2 = ax1.twinx()
+
+ax2.plot(gpu_hours, f_list, "b-")
+ax2.set_ylabel(r"Force MAE (eV/$\AA$)", fontsize=14, color='b')
+ax2.yaxis.set_major_locator(MultipleLocator(0.05))
+ax2.yaxis.set_minor_locator(MultipleLocator(0.025))
+
+plt.tight_layout()
+plt.savefig("snap_train_curve.pdf")
+plt.show()

### 2019-06-26 doc/papers/nn/manuscript.tex
CPC major improvements, revision 1.

@@
 TensorAlloy. TensorAlloy supports constructing machine learning interaction 
-potentials for both \textit{molecules} and \textit{solids} and one hour is 
-sufficient for TensorAlloy to obtain models with state-of-art level accuracy.
+potentials for both \textit{molecules} and \textit{solids}.
 \end{abstract}
@@
 virial stress for arbitrary ANN model. All these algorithms have been 
-implemented in our Python program: \tensoralloy{}.
+implemented in our Python program: TensorAlloy.
 
@@
 \ref{section:method} describes the virtual atom approach and a modified ANN 
-model used by \tensoralloy{}. Section \ref{section:discussions} displays 
-performances of \tensoralloy{} on two public datasets. The appendix 
+model used by TensorAlloy. Section \ref{section:discussions} displays 
+performances of TensorAlloy on two public datasets. The appendix 
 \ref{section:appendix} gives derivation and implementation details of key 
-algorithms. The \tensoralloy{} program can be obtained on request.
+algorithms. Implementations of the core algorithms and some trained models can 
+be obtained from GitHub (https://github.com/Bismarrck/vap) freely.
 
@@
 \label{eq:G2}
-\mathbf{G}^{(2)}_i(\eta, R_s) = & \sum_{j \neq i}{
-    \sum_{\mathbf{n}}{g_2 (\eta, i, j, R_s)}
+\mathbf{G}^{(2)}_i(\eta, \omega) = & \sum_{j \neq i}{
+    \sum_{\mathbf{n}}{g_2 (\eta, i, j, \omega)}
 } \\
@@
 \label{eq:g2}
-g_2 = & \exp\left\{-\frac{\eta(\rijn - R_s)^2}{r_c^2} \right\}
-\cdot f_c(\rijn) \\
-g_4 = & \left( 1 + \gamma\cos\theta \right)^\zeta 
+g_2(\eta, i, j, \omega) = 
+& \exp\left\{-\frac{\eta(\rijn - \omega)^2}{r_c^2} \right\} \cdot f_c(\rijn) \\
+\label{eq:g4}
+g_4(
+    \beta, \gamma, \zeta, 
+    i, j, k, 
+    \mathbf{n}_1, \mathbf{n}_2, \mathbf{n}_3) = & 
+\left( 1 + \gamma\cos\theta \right)^\zeta 
     \exp \left\{ -\frac{\beta(\rijna^2 + \rikna^2 + \rjkna^2)}{r_c^2} \right\}
-f_c(\rijna)f_c(\rikna)f_c(\rjkna)
+\nonumber \\
+& \times f_c(\rijna)f_c(\rikna)f_c(\rjkna)
 \end{align}
-where $\eta$, $R_s$, $\beta$, $\gamma$ and $\zeta$ are empirically chosen 
+where $\eta$, $\omega$, $\beta$, $\gamma$ and $\zeta$ are empirically chosen 
 parameters, $f_c(r)$ is a cutoff (damping) function and its original form is:
@@
 \end{equation}
-and $r_c$ is the cutoff radius. $R_s$ may be fixed to zero \cite{AMP}. 
-Equation \eqref{eq:fc_origin} can be further transformed to a vectorized 
-expression:
+and $r_c$ is the cutoff radius. Equation \eqref{eq:fc_origin} can be further 
+transformed to a vectorized expression:
 \begin{equation}
@@
 \newcommand{\nijkmax}{N_{ijk}^{\mathrm{max}}}
-
-In this section we will describe details of \tensoralloy{}: the virtual atom 
-approach, the atomic residual potential and the loss function. 
+\newcommand{\nelmax}{N^{\mathrm{max}}_{\mathrm{el}}}
+\newcommand{\nel}{N_{\mathrm{element}}}
+\newcommand{\nvap}{N^{\mathrm{vap}}}
+\newcommand{\nnimax}{N^{\mathrm{max}}_{\mathrm{Ni}}}
+\newcommand{\nmomax}{N^{\mathrm{max}}_{\mathrm{Mo}}}
+
+In this section we will describe the program design and the core algorithm: 
+the virtual atom approach (VAP). The most noticable feature of the TensorAlloy 
+program is that the calculation of symmetry function descriptors is finally 
+implemented in the compuation graph with the help of VAP. Thus, we can utilize 
+the \textbf{AutoGrad} routine of TensorFlow to derive atomic forces and virial 
+stress automatically and also efficiently.
+
 The Ni-Mo binary alloy system will be used as the example to show this 
-algorithm. The virtual atom approach is built upon TensorFlow. For simplicity, 
-only radial symmetry function related algorithms are visualized in the figures.
-
-\subsection{The virtual atom approach}
-\label{section:virtual_atom_approach}
-
-Fig \ref{fig:algo1} shows the initialization procedure of the virtual atom 
-approach. The cutoff radius $r_{cut}$ must be fixed. The first step is to go 
-through the entire dataset and determining four prerequisite constants: 
-$N_{ij}^{\mathrm{max}}$, $N_{ijk}^{\mathrm{max}}$, 
-$N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$. 
-Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs 
-and $N_{ijk}^{\mathrm{max}}$ represents the maximum number of triples in 
-arbitrary structure. 
-$N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depend on 
-$r_{cut}$. The associated codes are given in the appendix.
-$N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$ indicate 
-the maximum appearances of Ni and Mo in any structure, respectively. 
-With $N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$, 
-the global symbol list (GSL) can be created. GSL defines the global reference 
-of this dataset and must be maintained during entire training. Then we can 
-construct \textit{offsets}. This vector marks the starting indices of the 
-\textbf{ordered} interaction pairs (e.g. Ni-Mo) and triples (e.g. Ni-Ni-Mo). 
-The order of the interactions must be maintained as well.
-
+algorithm. For simplicity, only radial symmetry function related algorithms are 
+visualized in the figures. The associated codes (Python3.7) are given in the 
+appendix. A demo script can be downloaded from GitHub freely 
+(https://github.com/Bismarrck/vap).
+
+Fig \ref{fig:program_design} shows the general design of TensorAlloy.
+TensorAlloy has two phases: 1) is the training phase and 2) represents the 
+prediction phase. These two phases have slightly different focusing points:
+
+In the training phase, efficiency is the major concern. To accelerate model 
+training, batching (or mini-batch training) is one of the most commonly used 
+techniques. Batching requires aligned inputs. However, hundreds of different 
+stoichiometries may exist in one dataset. To batch such structures, an universal 
+approach of expressing different structures in a single reference system (the 
+global symbol list or GSL) is necessary.
+
+In the prediction phase, things may be a bit different. The stoichiometry of 
+the input structure may not be included in the training dataset and it can vary 
+significantly. Taking the example of Ni-Mo, the trained model must be capable of 
+predicting any $\mathrm{Ni}_{x}\mathrm{Mo}_{y}$ solid while $x$ and $y$ can be 
+either as large as 50000 or just zero. Hence, VAP must be flexible enough to 
+handle these situations.
+
+In the following subsection, we will discuss the details of VAP.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.1
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
 \centering
-\includegraphics[scale=0.5]{figures/Fig1-prepare.pdf}
-\caption{\label{fig:algo1} The initialization step. 
-\textbf{a)} describes the detections of $N_{\mathrm{Ni}}^{\mathrm{max}}$, 
-$N_{\mathrm{Ni}}^{\mathrm{max}}$, $N_{ij}^{max}$, $N_{ijk}^{max}$ and the global
-symbols list.
-The \textit{offsets} of radial and angular functions and their corresponding 
-symmetry function parameters are in \textbf{b)} and \textbf{c)}, respectively.
+\includegraphics[scale=0.58]{figures/Fig1.pdf}
+\caption{\label{fig:program_design} The general design of TensorAlloy. 
+\textbf{(1)} demonstrates the training phase while \textbf{(2)} represents the 
+prediction phase.
 }
@@
 
-Fig \ref{fig:algo2} shows the algorithm to construct the radial mapping matrix
-$g_{\mathrm{map}}^2$ which plays a key role in building the computation graph 
-(Fig \ref{fig:algo3}). This algorithm starts from the $N \times 3$ local 
-positions matrix \textbf{R}. Here 'local' means original and 'global' means GSL. 
-The first step is to find all neighbor pairs: $\mathbf{n}$, $i^{(0)}$ and 
-$j^{(0)}$. This can be done by the 
-\href{https://wiki.fysik.dtu.dk/ase/ase/neighborlist.html}{neighbor\_list} 
-routine of ASE\cite{ase}. $\mathbf{n}$ is a $N_{ij} \times 3$ matrix 
-representing the periodic boundary shift vectors where $N_{ij}$ is the total 
-number of interaction pairs within $r_{cut}$.
-Both $i^{(0)}$ and $j^{(0)}$ are $N_{ij}\times 1$ column vectors representing 
-the indices of $i$ and $j$ of Equation \ref{eq:rijn}. 
-$\mathbf{t}$ is a manually-created $N_{ij}\times 1$ column vector storing the 
-types \textemdash represented by integers \textemdash of the corresponding 
-interaction pairs.
-
-The second step is to convert the local indices, $i^{(0)}$ and $j^{(0)}$, to 
-global indices based on GSL and then \textbf{increase their values by one}. 
-By padding with zeros, we can finally get the $N_{ij}^{\mathrm{max}} \times 3$ 
-matrix $\mathbf{n_g}$ and $N_{ij}^{\mathrm{max}} \times 1$ column vectors 
-$i^{(0)}_{\mathrm{+,g}}$, $j^{(0)}_{\mathrm{+,g}}$ and 
-$\mathbf{t}_{\mathrm{g}}$. The increment is extremely important because the 
-indices of all padded 'virtual' or 'dummy' atoms are fixed to 0.
-
-The last step is to construct $g_{\mathrm{map}}^{(2)}$, which should be a 
-$N_{ij}^{\mathrm{max}} \times 2$ matrix. Its first column is just 
-$i^{(0)}_{\mathrm{+,g}}$ and its second column are corresponding offset values 
-of $\mathbf{t}_{\mathrm{g}}$. $g_{\mathrm{map}}^{(2)}$, 
-$j^{(0)}_{\mathrm{+,g}}$ and $\mathbf{n_g}$ can be pre-computed and cached. 
-The algorithm to build $g_{\mathrm{map}}^{(4)}$ for angular symmetry functions 
-is similar but too complicated to visualize. Thus, we provide a Python 
-implementation in the appendix.
-
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.A
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Preparation}
+\label{section:preparation}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.2
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
 \centering
-\includegraphics[scale=0.6]{figures/Fig2-v2gmap.pdf}
-\caption{\label{fig:algo2} The second stage of the virtual atom approach: the 
-construction of $g_{\mathrm{map}}^{(2)}$. Tensors marked red can be pre-computed 
-and cached.}
+\includegraphics[scale=0.6]{figures/Fig2.pdf}
+\caption{\label{fig:Fig2} The initialization step. 
+\textbf{(1)} describes the detections of $N_{\mathrm{Ni}}^{\mathrm{max}}$, 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$ and the global symbol list (GSL). The red 'X' 
+represents the inserted virtual atom.
+\textbf{(2)} shows the detections of $\nijmax$ and $\nijkmax$ given $r_{cut}$.
+}
 \end{figure}
 
-Fig \ref{fig:algo3} shows the final stage of the virtual atom approach: the 
-computation graph for calculating radial symmetry function descriptors. This 
-stage also starts from the $N \times 3$ local positions matrix \textbf{R} and 
-involves two steps: the calculation of interatomic distances $r_{ij}$ 
-(Fig \ref{fig:algo3}a) and the construction of $\mathbf{G}^{(2)}$ 
-(Fig \ref{fig:algo3}b).
-
-The initial step is to map local positions \textbf{R} to
-$(N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}+1) \times 3$
-global positions \textbf{R'} based on GSL. The first row (marked blue) of 
-$\mathbf{R'}$ are all zeros representing 'positions' of the virtual atom. 
-Then with 
-\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/gather}
-{tf.gather}, the global indices $i^{(0)}_{\mathrm{+,g}}$ and 
-$j^{(0)}_{\mathrm{+,g}}$ of Fig \ref{fig:algo2} can be transformed to global 
-positions: $\mathbf{R'_i}$ and $\mathbf{R'_j}$. Thus, the interatomic distances 
-$r_{ij}$ can be simply calculated with Equation \ref{eq:rijn}.
-
-Now it's time to get radial symmetry function descriptors matrix 
+Fig \ref{fig:Fig2} shows the initialization of VAP. The cutoff radius $r_{cut}$ 
+must be fixed. The initialization involves two steps. The first step is to build 
+the global symbol list (GSL), which acts as the universal reference system. A 
+virtual atom is inserted at the very first position of this list. The benefits 
+will be discussed later. To build GSL, all $\nelmax$ must be obtained. 
+$\nelmax$ indicates the maximum appearances of an element in any structure and 
+$\nel$ represents the total number of unique chemical elements:
+\begin{equation}
+\label{eq:n_vap}
+\nvap = 1 + \sum_{\mathrm{el}}{\nelmax}
+\end{equation}
+For the Ni-Mo dataset, $\mathrm{el} \in [\mathrm{Ni}, \mathrm{Mo}]$ and 
+$\nel = 2$. 
+Table \ref{table:GSL} gives some examples of the GSL mapping. 'X' denotes the 
+inserted virtual atom and Ni$_{108(54)}$ means the first 54 Ni atoms are mapped 
+from the local stoichiometry. In the training phase, all $\nelmax$ are constant.
+In the prediction phase, $\nelmax$ shall be determined dynamically. One should 
+note that the minimum value of $\nelmax$ should be 1 due to technical reason (so 
+that the computation graph of TensorFlow can be properly executed). The codes to
+get $\nelmax$ and GSL are given in Appendix(C). With GSL setup, atomic positions
+and forces can be transformed as well. Appendix(D) gives the implementation of 
+the virtual-atom mapping mechanism.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table.1
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}[h]
+\centering
+\begin{tabular}{lccccc}
+\hline
+ & Stoichiometry & $\nnimax$ & $\nmomax$ & $N^{\mathrm{vap}}$ 
+ & Stoichiometry (GSL) \\
+\hline
+ & Ni$_{54}$ &  &  &  & XNi$_{108(54)}$Mo$_{176(0)}$ \\
+Training & Ni$_{54}$Mo$_{12}$ & 108 & 176 & 285 
+ & XNi$_{108(54)}$Mo$_{176(12)}$ \\
+ & Mo$_{12}$ &  &  &  & XNi$_{108(0)}$Mo$_{176(12)}$ \\
+\hline
+ & Ni$_{54}$ & 54 & 1 & 56 & XNi$_{54(54)}$Mo$_{1(0)}$ \\
+Prediction & Ni$_{54}$Mo$_{12}$ & 54 & 12 & 68 & XNi$_{54(54)}$Mo$_{12(12)}$ \\
+ & Mo$_{12}$ & 1 & 12 & 14 & XNi$_{1(0)}$Mo$_{12(12)}$ \\
+\hline
+\end{tabular}
+\caption{\label{table:GSL}
+The mappings of local stoichiometries to their GSL forms, taking examples of the 
+SNAP/Ni-Mo dataset.
+}
+\end{table}
+
+Then we can determine another two key constants: $\nijmax$ and $\nijkmax$. 
+Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs in
+arbitrary structure and the subscript 'ijk' denotes triples. 
+$N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depend on 
+$r_{cut}$ and the associated codes are given in Appendix(B). 
+Table \ref{table:nij_nijk_max} summarizes $\nijmax$ and $\nijkmax$ at different
+$r_{cut}$ of the two tested datasets: QM7 and SNAP/Ni-Mo.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table.2
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}[h]
+\centering
+\begin{tabular}{lccc}
+\hline
+ Dataset & $r_{cut}$(\AA) & $\nijmax$ & $\nijkmax$ \\
+ QM7 & 6.5 & 506 & 5313 \\
+\hline
+ SNAP/Ni-Mo &  4.6 & 7200 & 176400 \\
+ & 6.0 & 12384 & 526320 \\
+ & 6.5 & 16284 & 965338 \\
+\hline
+\hline
+\end{tabular}
+\caption{\label{table:nij_nijk_max}
+$\nijmax$ and $\nijkmax$ of SNAP/Ni-Mo and QM7 at different $r_{cut}$.
+}
+\end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.B
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Interatomic distances}
+\label{section:interatomic_distance}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.3
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.6]{figures/Fig3.pdf}
+\caption{\label{fig:Fig3} The pseudo computation graph with execution orders for 
+calculating interatomic distances $\mathbf{r}$ from atomic positions 
+$\mathbf{R}$ and lattice tensor $\mathbf{h}$.
+}
+\end{figure}
+
+Both the radial (Equation \ref{eq:g2}) and the angular (Equation \ref{eq:g4}) 
+functions only interact with interatomic distances. In order to compute symmetry
+function descriptors, local atomic positions shall be transformed to GSL 
+interatomic distances first. Fig \ref{fig:Fig3} demonstrates the pseudo 
+computation graph for calculating interatomic distances 
+$\mathbf{r}^{\mathrm{GSL}}$ for radial descriptors:
+
+\begin{itemize}
+
+    \item[1.] 
+    Find all (i,j) neighbor pairs using the routine 
+    \href{https://wiki.fysik.dtu.dk/ase/ase/neighborlist.html}
+    {\textit{neighbor\_list}} implemented in ASE\cite{ase}. $\mathbf{R}$ 
+    represents local atomic positions, $\mathbf{h}$ is the lattice tensor. 
+    $\mathbf{i}$ and $\mathbf{j}$ are vectors of length $N_{\mathrm{ij}}$ and
+    $\mathbf{n}$ is the $N_{\mathrm{ij}} \times 3$ periodic boundary shift 
+    matrix. In the training phase $N_{\mathrm{ij}} \le \nijmax$; in the 
+    prediction phase, $\nijmax$ is exactly equal to $N_{\mathrm{ij}}$.
+
+    \item[2.] 
+    Map $\mathbf{R}$, $\mathbf{i}$, $\mathbf{j}$ and $\mathbf{n}$ to
+    their corresponding GSL forms with padding zeros. One should note that these 
+    GSL arrays can be cached for training.
+
+    \item[3.] 
+    Broadcast $\mathbf{R}^{\mathrm{GSL}}$ to $\mathbf{R}_{i}^{\mathrm{GSL}}$ and
+    $\mathbf{R}_{j}^{\mathrm{GSL}}$ with $\mathbf{i}^{\mathrm{GSL}}$ and 
+    $\mathbf{j}^{\mathrm{GSL}}$ respectively.
+
+    \item[4.]
+    Compute the displacements in the original cell:
+    $\mathbf{D}_{ij} = \mathbf{j}^{\mathrm{GSL}} - \mathbf{i}^{\mathrm{GSL}}$
+
+    \item[5.]
+    Compute the total periodic displacements:
+    $\mathbf{D}_{pbc} = \mathbf{n}^{\mathrm{GSL}} \mathbf{h}$
+
+    \item[6.]
+    Compute the overall GSL displacements:
+    $\mathbf{D}^{\mathrm{GSL}} = \mathbf{D}_{pbc} + \mathbf{D}_{ij}$
+
+    \item[7.] 
+    Compute the interatomic distances $\mathbf{r}^{\mathrm{GSL}}$.
+
+\end{itemize}
+
+Steps 1-2 are implemented in the function \textit{get\_g2\_map} in Appendix(E).
+Steps 3-7 are implemented in the method \textit{get\_rij} of class 
+\textit{SymmetryFunction} in Appendix(G).
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.C
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Radial descriptors}
+\label{section:radial_descriptors}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.4
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+Now we can start the last step: computing radial symmetry descriptors 
+$\mathbf{G}^{(2)}$ from $\mathbf{r}^{\mathrm{GSL}}$. For simplicity, we will use 
+the prediction phase to demonstrate this final section.
+
+Suppose we have $N_{\tau}$ different $(\eta, \omega)$ pairs for Equation 
+\ref{eq:G2} and $(\eta, \omega)_{\tau} (0 \le \tau < N_{\tau})$ represents the 
+$(\tau+1)$-th pair. In the prediction phase, $\mathbf{r}^{\mathrm{GSL}}$ should 
+be a vector of length $\nijmax$ and the desired output $\mathbf{G}^{(2)}$ will 
+be a matrix of shape $[\nvap, (\nel)^2 \cdot N_{\tau}]$, as shown in 
+Fig \ref{fig:Fig5}\textbf{d}:
+\begin{itemize}
+    \item[1.] 
+    The total number of rows is $\nvap$ (Equation \ref{eq:n_vap}) and each row
+    represents the complete radial symmetry function descriptors of an atom. The 
+    first row always corresponds to the inserted virtual atom.
+    \item[2.]
+    The total number of columns is $\nel \cdot \nel \cdot N_{\tau}$. Here 
+    $\nel \cdot \nel$ indicates the number of element-element interaction types 
+    and each interaction is described by $N_{\tau}$ feature values.
+\end{itemize}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=1.0]{figures/Fig4.pdf}
+\caption{\label{fig:Fig4} The visualization of the mapping $f^S_{\nu}$.
+In this example $S = [2,4]$ and $p$ can be any $(i,j)$ if 
+$0 \le i < 2$ and $0 \le j < 4$.
+}
+\end{figure}
+
+Assume $\nu$ is a vector of length $N_{\nu}$, we can define an integer matrix 
+$f^{S}_{\nu}$ for mapping $\nu$ to a new array $g$ of shape $S$ satisfying the 
+following conditions:
+\begin{align}
+\label{eq:scatter_nd}
+% g(p) & = \sum_{\tau}^{}{\nu(\tau)}
+g(p) & = \sum_{\tau=0}^{\tau < N_{\nu}}{c_\tau(p) \cdot \nu(\tau)} \\
+c_{\tau}(p) & = \begin{cases}
+    1 & {f^S}_{\nu}(\tau) = p \\
+    0 & \mathrm{else}
+\end{cases}
+\end{align}
+where $p$ is a coordinate vector. The matrix $f^{S}_{\nu}$ shall have $N_{\nu}$ 
+rows and $N_S$ columns where $N_S$ represents the dimension of $g$. 
+Fig \ref{fig:Fig4} visualizes this $f^S_{\nu}$ mapping scheme. This $f^S_{\nu}$
+mapping plays a key role in transforming $\mathbf{r}^{\mathrm{GSL}}$ to 
 $\mathbf{G}^{(2)}$.
-As shown in Fig \ref{fig:algo3}b, this step can be executed in parallel: 
-for each $\eta_i$, we first calcualte $g_2(r_{ij}, \eta_i)$ with 
-Equation \ref{eq:g2} and then map the $N_{ij}^{\mathrm{max}}$-length vector 
-$g_2(r_{ij}, \eta_i)$ to 
-$(N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}+1) \times 16$ 
-matrix $\mathbf{G}^{(2)}_{\eta_i}$ with $g^{\eta_i}_{\mathrm{map}}$ and 
-\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/scatter_nd}
-{tf.scatter\_nd}. Here $16$ is the multiplacation of 4 ($\eta$) and 4 
-(radial interactions). 
-$g^{\eta_i}_{\mathrm{map}}$ is calculated by adding a constant
-$i - 1$ to all values of the second column of $g^{(2)}_{\mathrm{map}}$. Only 
-shaded columns in Fig \ref{fig:algo3}b have non-zero values.
-In fact, the first column of $g^{\eta_i}_{\mathrm{map}}$ means the indices of 
-the central atoms in Equation \ref{eq:G2} (or rows of $\mathbf{G}^{(2)}$) and 
-the second column marks the corresponding $\eta_i$ in Fig \ref{fig:algo1} (or 
-columns of $\mathbf{G}^{(2)}$).
-The first row of each $\mathbf{G}^{(2)}_{\eta_i}$ reprsents the descriptors of 
-the virtual atom. Removing these rows with
-\href{https://www.tensorflow.org/versions/r1.12/api_docs/python/tf/split}
-{tf.split}, we get $\hat{\mathbf{G}}^{(2)}_{\eta_i}$.
-The final radial symmetry function descriptors, $\mathbf{G}^{(2)}$ is just the 
-sum of all $\hat{\mathbf{G}}^{(2)}_{\eta_i}$.
-
-\begin{figure*}[h!]
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.5
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[h!]
 \centering
-\includegraphics[scale=0.5]{figures/Fig3-G2.pdf}
-\caption{\label{fig:algo3} 
-\textbf{a)} The calculation of the interatomic distances $r_{ij}$.
-\textbf{b)} The construction of the radial symmetry function descriptors 
-$\mathbf{G}^{(2)}_{\eta_i}$. Rows that are marked blue correspond to the virtual 
-atom and will be discared before feeding $\mathbf{G}$ into atomistic neural 
-networks.
+\includegraphics[scale=0.95]{figures/Fig5.pdf}
+\caption{\label{fig:Fig5} The definition of $f^{(2,4)}_{\nu}$: map the 
+vector $\nu$ to array $g$ of shape [2, 4], or mathematically
+$g(i,j) = \sum_{k}^{f^{(2,4)}_{\nu}(k) = (i,j)}{\nu(k)}$.
 }
-\end{figure*}
-
-\subsection{The data flow}
-
-The following equation briefly demonstrates the core data flow of 
-\textbf{TensorAlloy} during a mini-batch training: 
-\begin{equation}
-    \mathbf{R'_{b}} \rightarrow 
-    \mathbf{G_b} \rightarrow 
-    \mathbf{E_b} \rightarrow
-    \mathbf{F_b} \rightarrow 
-    \mathbf{\epsilon_b} \rightarrow
-    \mathbf{Loss}
-\end{equation}
-where the $N_{b} \times (\nmax + 1) \times 3$ matrix $\mathbf{R'_b}$ is a batch 
-of positions matrices ($N_b \ge 1$ is the batch size), $\mathbf{G_b}$ is the 
-corresponding symmetry function descriptors matrix of shape 
-$N_{b} \times (\nmax) \times 16$ and $\mathbf{E_b}$ represents 
-total energies of the structures. Section \ref{section:virtual_atom_approach} 
-describes the implementation of $\mathbf{R'_{b}} \rightarrow \mathbf{G_b}$. 
-To implement $\mathbf{G_b} \rightarrow \mathbf{E_b}$, \textbf{TensorAlloy} uses 
-1D-convolutional neural networks with $1 \times 1$ kernels\cite{kCON}. The total 
-forces $\mathbf{F_{b}}$ and the virial stress $\mathbf{\epsilon_{b}}$ are 
-calculated with Equation \ref{eq:dEdr} and Equation \ref{eq:stress} directly.
-
+\end{figure}
+
+Fig \ref{fig:Fig5} 
+demonstrates the calculation of $\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ from 
+$\mathbf{r}^{\mathrm{GSL}}$. $\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ is the 
+partial descriptors contributed by the $\tau$-th $(\eta, \omega)$ combination.
+The overall $\mathbf{G}^{(2)}$ is just the sum of all partial contributions:
+\begin{equation}
+\mathbf{G}^{(2)} = \sum_{\tau=0}^{\tau < N_{\tau}}{
+    \mathbf{G}^{(2)}((\eta, \omega)_{\tau})
+}
+\end{equation}
+This calculation can be easily implemented with a \textit{For} loop. For each 
+$\tau$, there will be three major steps:
+
+\begin{itemize}
+
+    \item[1.]
+    The first step is applying Equation \ref{eq:g2} on 
+    $\mathbf{r}^{\mathrm{GSL}}$ with the given $\tau$-th $(\eta, \omega)$ pair 
+    to obtain raw descriptors $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. 
+    $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$ is a vector of length 
+    $\nijmax$ and its last ($\nijmax - N_{ij}$) components are dummy values.
+
+    \item[2.]
+    The second step is generating the mapping $f_{g,\tau}^{S}$. In the Ni-Mo 
+    case, $S=[285, 4N_{\tau}]$. $f_{g,\tau}^{S}$ is a matrix of shape 
+    $[\nijmax, 2]$ and $f_{g,\tau}^{S}$ is constructed from the base mapping 
+    array $f_{g}^{S}$ by adding $\tau$ to its second column. $f_{g}^{S}$ is also
+    a $\nijmax \times 2$ matrix. $f_{g}^{S}$ stores fundamental properties of 
+    $\mathbf{r}^{\mathrm{GSL}}$: the center atom (e.g. $\mathrm{Ni}_{1}$) and 
+    type (e.g. Ni-Mo) of each atom-atom interaction:
+    \begin{itemize}
+
+        \item[a.] 
+        Its first column is directly copied $i^{\mathrm{GSL}}$, representing the 
+        GSL indices of the center atoms.
+
+        \item[b.] 
+        The values of its second column are multiples of $N_{\tau}$ indicating 
+        the offsets, or horizontal positions in $\mathbf{G}^{(2)}$. These values 
+        are obtained by multiplying $N_{\tau}$ with the type indices of 
+        $\mathbf{r}^{\mathrm{GSL}}$. For example, the Ni-Mo dataset has two 
+        unique elements: Ni, Mo. Hence, there will be four types of interactions:
+        Mo-Mo (0), Mo-Ni (1), Ni-Ni (2) and Ni-Mo (3). Then for each value 
+        (atom-atom interaction) of $\mathbf{r}^{\mathrm{GSL}}$, its type index 
+        can be determined with $\mathbf{i}^{\mathrm{GSL}}$ and 
+        $\mathbf{j}^{\mathrm{GSL}}$ based on the pre-built GSL.
+
+    \end{itemize}
+
+    \item[3.]
+    Compute $\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ by applying 
+    $f_{g,\tau}^{S}$ on $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. The 
+    padded zeros in $\mathbf{r}^{\mathrm{GSL}}$ are finally mapped to the 
+    inserted virtual atom. Hence, the zero-padding of 
+    $\mathbf{r}^{\mathrm{GSL}}$ can be easily separated and elinimated (just 
+    remove the first row of $\mathbf{G}^{(2)}$). That's why TensorAlloy can use
+    arbitrary number of structures without any stoichiometry restriction to do 
+    batch training.
+
+\end{itemize}
+
+The mapping scheme $f_{\nu}^{S}$ can be directly achieved using routine 
+\textit{tf.scatter\_nd} implemented by TensorFlow. The calculation of the base 
+mapping array $f_{g}^{S}$ is implemented in Appendix(E). $f_{g}^{S}$ is also 
+cacheable. The calculation of $\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ is 
+implemented in method \textit{get\_g2\_op\_for\_tau} of class 
+\textit{SymmetryFunction} in Appendix(G).
+
+The workflow for the batch training phase is almost identical to the prediction 
+phase introduced above. There are still some noticable diiferences. Assume 
+$N_{b}$ represents the batch size:
+
+\begin{itemize}
+
+    \item[1.] 
+    Most of the variables ($\mathbf{r}^{\mathrm{GSL}}$, 
+    $\mathbf{i}^{\mathrm{GSL}}$, $\mathbf{R}^{\mathrm{GSL}}$, etc.) have one 
+    more dimension. For example, $\mathbf{R}^{\mathrm{GSL}}$ should be an array
+    of shape $[N_b, \nijmax, 3]$.
+
+    \item[2.] 
+    The base mapping $f_{g}^{S}$ becomes a matrix of shape $[\nijmax, 3]$. Its 
+    last two columns remain unchanged. However, the newly inserted first column 
+    \textemdash representing the batch indices \textemdash is 
+    \textbf{not cacheable} because batching is a random action. The first column
+    should be generated dynamically.
+
+    \item[3.]
+    $\tau$ should be added to the third column of $f_{g}^{S}$.
+
+    \item[4.]
+    In the training phase, $\nvap$ is a constant determined before training. In 
+    the contrast, $\nvap$ becomes a tensor that should be manually specified in 
+    the prediction phase.
+
+    \item[5.]
+    In the training phase, the reference atomic forces should be transformed to 
+    its corresponding GSL array because the NN-derived force array 
+    $\mathbf{F}^{\mathrm{NN}}$ is in GSL reference:
+    \begin{equation}
+        \mathbf{F}^{\mathrm{NN}} = 
+        -\frac{\partial{E}}{\partial{\mathbf{R}^{\mathrm{GSL}}}}
+    \end{equation}
+    Hence, in the prediction phase, a reverse VAP mapping is required to convert
+    $\mathbf{F}^{\mathrm{NN}}$ to its local form.
+
+\end{itemize}
+
+The training phase is implemented in \textit{BatchSymmetryFunction} which 
+inherits most of methods from its parent class \textit{SymmetryFunction}. 
+The dynamic batching is implemented in method 
+\textit{get\_v2g\_map\_batch\_indexing\_matrix}. The method 
+\textit{get\_g\_shape} will return a fixed array instead. The function
+\textit{map\_gsl\_array\_to\_local} of \textit{VirtualAtomMap} is used to do the 
+reverse mapping.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.D
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Angular descriptors}
+
+The same algorithm can be applied to compute angular symmetry function 
+descriptors. The triple list shall be constructed from the neighbor list 
+(Fig \ref{fig:Fig3}) and $\nijmax$ shall be replaced by $\nijkmax$. Typically
+$\nijkmax \gg \nijmax$.
+
+Appendix(F) demonstrates how to compute the base mapping array. The calculation 
+of $\mathbf{G}^{(4)}(\beta, \gamma, \zeta)_{\tau}$ is implemented in method 
+\textit{get\_g4\_op\_for\_tau} of class \textit{SymmetryFunction} 
+in Appendix(G).
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.E
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Min-max normalization}
+
+Raw values of $\mathbf{G}^{(2)}$ and $\mathbf{G}^{(4)}$ may range from zero to 
+several hundreds. So a min-max normalization routine is recommended. For each
+column $\mathbf{G}(:, \tau)$ where $0 \le \tau < N_{\tau}$, we just normalize 
+its values to range [0, 1]:
+\begin{equation}
+    \mathbf{G}(:, \tau) = \frac{
+        \mathbf{G}(:, \tau) - \min(\mathbf{G}(:, \tau))}{
+        \max(\mathbf{G}(:, \tau)) - \min(\mathbf{G}(:, \tau))}
+\end{equation}
+where $\min(\mathbf{G}(:, \tau))$ and $\max(\mathbf{G}(:, \tau))$ should be 
+determined in the training phase and remain constant in the prediction phase.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.F
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{The residual model}
@@
 E^{total} & = E^{residual} + E^{static} \nonumber \\
-& = \sum_{i=1}^{N}{
-    \mathbf{NN}_{el}\left( \left\{ G_i \right\} \right)
-} + \sum_{el}{n_{el}E_{el}}
+& = \sum_{\mathrm{el}}{\mathbf{NN}_{el}\left(\mathbf{G}_{\mathrm{el}}\right)}
++ \sum_{\mathrm{el}}{n_{el}E_{el}}
 \end{align}
@@
 Equation \ref{eq:e_total_res} just describes the atomistic interactions 
-(the \textit{residual} energy). The 
-introduction of $E^{static}$ can significantly limit value range of NN outputs, 
-leading to faster convergence speed and higher training stability 
+(the \textit{residual} energy). 
+The introduction of $E^{static}$ can significantly limit value range of NN 
+outputs, leading to faster convergence speed and higher training stability 
 (Fig \ref{fig:benchmark_qm7}c). The initial $\{E_{el}\}$ are calculated by 
-solving the linear system $Ax=b$ where $A$ is a $N_{data} \times N_{el}$ matrix 
-and $b$ is a $N_{data}\times 1$ vector. $A(i,j)$ is the number of $j^{th}$
-element in structure $i$ and $b(i)$ is the total energy of structure $i$.
-
-To train the model, we use the following total loss function:
+solving the linear system $Ax=b$ where $A$ is a $N_{data} \times \nel$ matrix 
+and $b$ is a vector of length $N_{data}$. $N_{data}$ is the number of training 
+examples. $A(i,j)$ is the number of $j$-th element in structure $i$ and $b(i)$ 
+is the corresponding total energy.
+
+To train the model, we use the following root mean-squared error (RMSE) total 
+loss function:
 \begin{align}
@@
 & + \chi_{\mathrm{f}}\sqrt{
-    \frac{1}{3\sum_{i}^{N_{b}}{N_i}}\sum_{i}^{N_b}{\sum_{j}^{N_i}{
+    \frac{1}{3 N_{b} \nvap}\sum_{i}^{N_b}{\sum_{j}^{\nvap}{
         \sum_{\alpha}{
@@
 \end{align}
-where $N_b$ is the mini-batch size, $N_i$ is the number of atoms of structure 
-$i$ and $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ are weights of force and 
-stress losses. Typically both $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ range 
-within $[1,10]$. Stress tensors are converted to Voigt vectors. All energies are 
-in \textbf{eV}, all forces are in \textbf{eV/\AA} and all stress components are 
-in \textbf{eV/\AA}$\mathbf{^3}$. In most cases, we set $N_b$ to 50 or 100 and we
+where $N_b$ is the mini-batch size and $\chi_{\mathrm{f}}$ and 
+$\chi_{\mathrm{s}}$ are weights of force and stress losses. 
+Stress tensors are converted to Voigt vectors. All energies are in \textbf{eV}, 
+all forces are in \textbf{eV/\AA} and all stress components are in 
+\textbf{eV/\AA}$\mathbf{^3}$. In most cases, we set $N_b$ to 50 or 100 and we
 use the ADAM\cite{adam} optimizer with exponentially-decayed learning rate to 
-minimize the loss function. The activation function is Leaky ReLU
-\cite{maas2013rectifier}:
-\begin{equation}
-\sigma(x) = \begin{cases}
-    \alpha x & x \le 0 \\
-    x & x \ge 0 \\
-\end{cases}
-\end{equation}
-and $\alpha$ is set to 0.2 in \tensoralloy{}. The kernel weights of all ANNs are 
-initialized with the Xvaier\cite{pmlr-v9-glorot10a} method and kernel biases are 
-initialized with zeros.
+minimize the loss function. The default activation function is softplus:
+\begin{equation}
+\sigma(x) = \log(1 + e^x)
+\end{equation}
+The kernel weights of all NNs are initialized with the 
+Xvaier\cite{pmlr-v9-glorot10a} method and kernel biases are initialized with 
+zeros.
 
@@
 
-In this section we demonstrate two training experiments of \tensoralloy{}. All 
-the results are obtained on a workstation with two Intel Xeon E5-2687v4 CPUs 
-(18 cores per CPU, 2.3 GHz) and one NVIDIA GTX 1080 Ti GPU.
-
+In this section we demonstrate two experiments of TensorAlloy. All GPU benchmark
+results are obtained on the same workstation with two Intel Xeon E5-2687v4 CPUs
+(18 cores @ 2.3 GHz per CPU) and one NVIDIA GTX 1080Ti GPU.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 4.A
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{QM7}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.6
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.54]{figures/qm7_speed.pdf}
+\caption{\label{fig:benchmark_qm7} 
+\textbf{a)} The curves of training speed (structures per second) vs batch sizes. 
+\textbf{b)} The curves of test MAE (meV/atom) vs training time (GPU hour) using 
+different settings.
+\textbf{c)} The curves of test MAE (meV/atom) vs NN models. 
+}
+\end{figure}
 
@@
 Figure \ref{fig:benchmark_qm7} demonstrates the performances of 
-\textbf{TensorAlloy} on QM7 dataset. In this figure, 'Radial' means only radial 
+TensorAlloy on QM7 dataset. In this figure, 'Radial' means only radial 
 symmetry functions (Equation \ref{eq:G2}) are used and 'Angular' indicates both 
 radial and angular symmetry functions are used. The cutoff radius is 6.5 \AA.
-The corresponding $\nijmax$ and $\nijkmax$ are 506 and 5313, respectively, 
-indicating the calculation of angular descriptors is much more expensive.
+The corresponding $\nijmax$ and $\nijkmax$ are 506 and 5313, respectively.
 Values of $\eta$ for radial symmetry functions are 0.1, 0.5, 1, 2, 4, 8, 12, 16, 
 20, 40 and $\beta$ (0.1, 0.5), $\gamma$ (1, -1) and $\zeta$ (1, 4) are used for
-angular functions. $R_s$ is fixed to zero. The initial learning rate is 0.01 and 
-then it is exponentially decayed with rate 0.99 for every 5000 steps. 
-Each atomistic neural network has two hidden layers with 128 and 64 neurons.
+angular functions. $\omega$ is fixed to 0. The initial learning rate is 0.01. 
+Learning rate decay is disabled for the following tests. Min-max normalization
+is enabled. Each atomistic neural network has two hidden layers with 64 and 32 
+neurons. The force and stress losses of Equation \ref{eq:loss} are disabled for 
+this experiment.
 
@@
 (MAEs, meV/atom) on the test set. This figure clearly illustrate another benefit 
-of using larger batch size: models can be trained much faster. For the best case 
+of using larger batch size: the trainings can be much faster. For the best case 
 (batch size 100, angular symmetry functions included), the test MAE will reach 5 
-meV/atom (1.5 kcal/mol per structure) within just one GPU hour.
+meV/atom (1.5 kcal/mol per structure) in just one GPU hour.
 
@@
 \ref{eq:e_total_res}) with traditional ANN model (Equation 
-\ref{eq:general_e_total}). In fact, both models can converge to similar final 
-results. However, the residual model has a much faster convergence speed because 
-the introduction of the \textit{static} part can reduce output values of ANNs
-close to (-1, 1) \textemdash the ideal output range of neural networks.
-
+\ref{eq:general_e_total}). The proposed residual model has a much faster 
+convergence rate and better stability. One exaplanation is that the 
+\textit{static} part acts as a normalization function. By introducing the 
+\textit{static} term, the output values of ANNs are much closer to the ideal 
+output range (-1, 1) of neural networks.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 4.B
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Ni-Mo}
+
+SNAP/Ni-Mo\cite{SNAP_Mo_2017, SNAP_2018} is a publicly available dataset built 
+by Shyue Ping Ong and co-workers. This dataset has 3971 Ni-Mo solids, including 
+461 pure Ni structures and 284 pure Mo structures. All DFT calculations were 
+done by VASP\cite{VASP} using the PBE\cite{PBE} functional within the projector 
+angumented-wave (PAW)\cite{PAW} approach.
+
+In this experiment, we trained three different models:
+\begin{enumerate}
+
+    \item Ni: this model uses 400 Ni structures for training and 61 for 
+    evaluation. The loss function only includes energy and force contributions.
+
+    \item Mo: this model uses 250 Mo structures for training and 34 for 
+    evaluation. The loss function includes all three (energy, force, stress) 
+    types of contributions.
+
+    \item Ni-Mo: this model uses 3673 structures for training and 300 for 
+    evaluation. The loss function includes all three types of contributions.
+
+\end{enumerate}
+
+For all these models, the cutoff radius is set to 6.5 \AA. Only radial symmetry 
+functions are used to compute atomic descriptors. The selected $\eta$ are 
+0.1, 0.5, 1, 2, 4, 8, 12, 16, 20, 40 and $\omega$ are 0.0, 3.0. The hidden layer
+sizes are 128, 64, 32. The activation function is softplus.
+The learning rate starts from 0.01 and it will decay exponentially with rate 
+0.95 for every 3000 steps.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table. 3
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}[h]
+\centering
+\begin{tabular}{cccc|ccc|cc}
+\hline
+ & \multicolumn{3}{c|}{Energy (meV/atom)} & \multicolumn{3}{c|}{Force (eV/\AA)}
+ & \multicolumn{2}{c}{Stress (GPa)} \\
+\hline
+Model & Mo & Ni & Ni-Mo & Mo & Ni & Ni-Mo & Mo & Ni-Mo \\
+\hline
+Mo & 4.9 (13.2) & & 16.5 (16.2) & 0.19 (0.25) & & 0.28 (0.29) & 0.24 (0.87) 
+   & 0.75 \\
+Ni & & 1.2 (1.2) & 4.5 (7.9) & & 0.04 (0.05) & 0.07 (0.11) & & 0.83 \\
+Ni$_4$Mo & & & 4.1 (4.0) & & & 0.09 (0.14) & & 0.98 \\ 
+Ni$_3$Mo & & & 4.5 (5.2) & & & 0.11 (0.16) & & 1.19 \\
+Ni$_{\mathrm{Mo}}$ & & & 12.9 (22.7) & & & 0.09 (0.13) & & 0.34 \\
+Mo$_{\mathrm{Ni}}$ & & & 12.9 (33.9) & & & 0.12 (0.55) & & 0.45 \\
+Overall & & & 10.8 (22.5) & & & 0.11 (0.23) & & 0.59 \\
+\hline
+\end{tabular}
+
+\caption{\label{table:MAE}
+Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
+stress (GPa) relative to DFT for TensorAlloy-trained models and their
+corresponding SNAP benchmarks (bracket)}
+\end{table}
+
+Table \ref{table:MAE} summarizes the energy, force and stress prediction 
+performances of TensorAlloy-trained models compared with their corresponding 
+SNAP benchmarks. The original SNAP formalism contains both radial and angular 
+interactions. However, in most cases, the radial-only TensorAlloy-trained 
+models can significantly outperform corresponding SNAP models. The trainings of 
+these models are also very fast. All these models are trained within 2 GPU hours
+on our workstation.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.7
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
     \centering
-\includegraphics[scale=0.54]{figures/Fig4-qm7.pdf}
-\caption{\label{fig:benchmark_qm7} 
-\textbf{a)} The curves of training speed (structures per second) vs batch sizes. 
-\textbf{b)} The curves of test MAE (meV/atom) vs training time (GPU hour) using 
-different settings.
-\textbf{c)} The curves of test MAE (meV/atom) vs NN models. 
+    \includegraphics[scale=0.64]{figures/Prediction-speed.pdf}
+\caption{\label{fig:prediction_speed} Benchmarks of the Ni-Mo model in 
+the prediction phase. The test structures are (MoNi)$_{x}$ where 
+$x$ = $10^3, 15^3, 20^3, 25^3, 30^3, 35^3, 40^3$. The left figure \textbf{a)} 
+demonstrates the overall time and the right figure \textbf{b)} compares the 
+'Graph' time with/out GPU. Blue bars indicate the elapsed time (in seconds) for 
+finding neighbors, orange bars denote the time for initializing VAP-GSL arrays 
+and green bars and the numbers above represents the graph execution time (used 
+for obtaining energy, forces and stress).
 }
@@
 
-\subsection{Ni-Mo}
-
-SNAP/Ni-Mo\cite{SNAP_Mo_2017, SNAP_2018} is a publicly available dataset built 
-by Shyue Ping Ong and co-workers. This dataset has 3971 Ni-Mo solids, including 
-461 pure Ni structures and 284 pure Mo structures. 
-$N_{\mathrm{Ni}}^{\mathrm{max}}$ is 108 and $N_{\mathrm{Mo}}^{\mathrm{max}}$ 
-equals 176. All DFT calculations were done by VASP\cite{VASP} using the 
-PBE\cite{PBE} functional within the projector angumented-wave (PAW)\cite{PAW} 
-approach.
-
-In this experiment, we trained four different models:
-\begin{enumerate}
-    \item SFNN/Ni: this model uses 400 Ni structures for training and 61 for 
-    evaluation. The loss function only includes energy and force. Hidden layer 
-    settings are 128,64,32.
-    \item SFNN/Mo: this model uses 250 Mo structures for training and 34 for 
-    evaluation. The loss function includes all three metrics. Hidden layer 
-    settings are also 128,64,32.
-    \item SFNN/Ni-Mo: this model uses 3600 randomly selected structures for 
-    training and the rest 373 structures are used for evaluation. The loss 
-    function includes only energy and force. Hidden layer settings are 64,32,32.
-    \item SFNN/Ni-Mo (esf): this model has exactly the same settings with 
-    SFNN/Ni-Mo except that its loss function also includes stress as training 
-    metrics. $\chi_{s}$ of Equation \ref{eq:loss} is 160.
-\end{enumerate}
-
-For all these models, the cutoff radius is set to 6.0 \AA. The $\nijmax$ for Ni, 
-Mo and Ni-Mo are 4678, 4504 and 7200, respectively. Only radial symmetry 
-functions are used to compute atomic descriptors. The selected $\eta$ are: 
-0.1, 0.5, 1, 2, 4, 8, 12, 16, 20 and 40. The learning rate starts from 0.01 and 
-it will decay exponentially with rate 0.99 for every 5000 training steps. The
-maximum training steps is 500,000.
-
-\begin{table}[h]
-\centering
-\begin{tabular}{lcccccccc}
-\hline
-    & Model & Mo & Ni$_4$Mo & Ni$_3$Mo & Ni$_{\mathrm{Mo}}$ & Mo$_{\mathrm{Ni}}$ 
-    & Ni & Overall \\
-\hline
-Energy (meV/atom) & Ni SNAP & & & & & & \textbf{1.2} & \\
-    & Mo SNAP & 13.2 & & & & & & \\
-    & Ni-Mo SNAP & 16.2 & 4.0 & 5.2 & 22.7 & 33.9 & 7.9 & 22.5 \\
-    & Ni SFNN & & & & & & 1.6 & \\
-    & Mo SFNN & \textbf{9.8} & & & & & & \\
-    & Ni-Mo SFNN & 22.1 & \textbf{3.3} & \textbf{4.1} & \textbf{11.3} 
-    & \textbf{13.7} & 3.7 & \textbf{11.0} \\
-    & Ni-Mo SFNN (esf) & 30.0 & 6.1 & 9.0 & 16.6 
-    & 26.2 & 7.8 & 19.1 \\
-\hline
-Force (eV/\AA) & Ni SNAP & & & & & & 0.05 & \\
-& Mo SNAP & 0.25 & & & & & & \\
-& Ni-Mo SNAP & 0.29 & 0.14 & 0.16 & 0.13 & 0.55 & 0.11 & 0.23 \\
-& Ni SFNN & & & & & & \textbf{0.05} & \\
-& Mo SFNN & \textbf{0.20} & & & & & & \\
-& Ni-Mo SFNN & 0.32 & \textbf{0.09} & 0.11 & 0.09 & 
-    \textbf{0.15} & 0.06 & 0.12 \\
-& Ni-Mo SFNN (esf) & 0.36 & 0.10 & \textbf{0.11} & \textbf{0.08} & 
-    0.16 & 0.06 & \textbf{0.12} \\
-\hline
-Stress (GPa) & Mo SNAP & \textbf{0.87} & & & & & & \\
-& Mo SFNN & 1.00 & & & & & & \\
-& Ni-Mo SFNN & 5.77 & \textbf{1.72} & 1.74 & 1.45 & 3.75 & 1.97 & 2.83 \\
-& Ni-Mo SFNN (esf) & \textbf{1.84} & 2.05 & \textbf{1.38} & \textbf{0.57} & 
-    \textbf{1.22} & \textbf{1.91} & \textbf{1.27} \\
-\hline
-\end{tabular}
-\caption{\label{table:MAE}
-Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
-stress (GPa) relative to DFT for the \tensoralloy{} models and their 
-corresponding SNAP models}
-\end{table}
-
+The speed of the prediction phase is also a crucial metric for measuring 
+interaction potentials. Fig \ref{fig:prediction_speed} summarizes the time 
+distribution of the Ni-Mo model in the prediction phase on the GPU workstation. 
+Here 'prediction' is defined as calculating energy, forces and stress tensor of 
+an arbitrary \textit{ase.Atoms} object. In these tests, the primitive structure
+$\mathrm{MoNi}$ is obtained by replacing one of the two bcc Mo atoms with a Ni 
+atom. The test subjects $(\mathrm{MoNi}))_{x}$ are just supercells of the base 
+structure. We choose $x \in [10^3, 15^3, 20^3, 25^3, 30^3, 35^3, 40^3]$ as
+a typical molecular dynamics simulation for studying alloy properties needs at 
+least thousands of atoms. The elaspsed time is splitted to three parts: 
+'Neighbor' (blue) indicates the execution time of the \textit{neighbor\_list} 
+routine of ASE for finding local neighbors (\textbf{(1)} of Fig \ref{fig:Fig3}),
+'VAP' (orange) denotes the time to construct VAP-GSL arrays 
+(\textbf{(2)} of Fig \ref{fig:Fig3}) and 'Graph' (green bars and the numbers 
+above) represents the time of getting energy, forces and stress tensor by 
+executing the computation graph. The smallest subject (2000 atoms) needs 1.6 
+seconds and the largest system (128000 atoms) requires ~71.6 seconds on the 
+workstation. Most of the time are spent on the Python-based single-thread 
+'Neighbor' and 'VAP' routines \textemdash which may be greatly optimized by 
+utilizing efficient C/C++/Fortran codes (e.g. Lammps). For the 'Graph' part, the 
+execution time can be as small as 1 second (with GPU) or 4 seconds (without GPU) 
+for the 128000-atoms structure. According to these tests, it's fairly practical 
+to use TensorAlloy-trained symmetry function interaction potential on studying 
+large alloy systems.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.8
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
     \centering
-    \includegraphics[scale=0.8]{figures/Fig5-snap.pdf}
-\caption{\label{fig:snap_gpu_train_speed} The test MAEs of the SFNN/Ni-Mo model 
-vs training time (GPU Hour). The black dotted line marks the final performance 
-of the SNAP/Ni-Mo model \cite{SNAP_2018}.}
-\end{figure}
-
-Table \ref{table:MAE} summarizes the energy, force and stress prediction 
-performances of \tensoralloy{}-optmized models compared with their corresponding 
-SNAP models. The original SNAP formalism contains both radial and angular 
-interactions. However, in most cases, the radial-only \tensoralloy{}-trained 
-SFNN models can significantly outperform corresponding SNAP models. To precisely
-predict virial stress, integrating stress into total loss is undoubtedly 
-necessary. For the pure Mo dataset, the SFNN/Mo model gives a MAE of 1.0 GPa on 
-predicting stress while it will increase to 2 GPa if only using energy and force 
-as training metrics. This phonomenon holds true for the Ni-Mo mixed models as 
-well. If we include stress in the total loss function, we can obtain much more 
-accurate stress predictions.
-
-The trainings of \tensoralloy{} on these \textit{solid} datasets are also very 
-fast. Fig \ref{fig:snap_gpu_train_speed} shows the test MAE (meV/atom) vs 
-training time (GPU Hour) of the SFNN/Ni-Mo model. \tensoralloy{} only needs less 
-than \textbf{half an hour} to achieve equivalent performance of the 
-SNAP/Ni-Mo model.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[scale=0.8]{figures/Fig6-energy-volume.pdf}
+    \includegraphics[scale=0.8]{figures/Ni_EoS.pdf}
 \caption{\label{fig:energy_volume_Ni} The energy vs volume curves of fcc Ni for
-the DFT, Ni/SFNN and Ni-Mo/SFNN models.}
+the DFT, Ni and Ni-Mo models.}
 \end{figure}
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.9
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
     \centering
-    \includegraphics[scale=0.8]{figures/Fig7-surface-energy.pdf}
+    \includegraphics[scale=0.8]{figures/Ni_surface_energy.pdf}
 \caption{\label{fig:surface_energy_Ni} Surface formation energies ($J/m^2$) of 
-different Ni surfaces calculated by DFT, Ni/SFNN and Ni-Mo/SFNN models. 
-The MAEs of the Ni/SFNN and Ni-Mo/SFNN relative to the DFT values are 0.09 and 
-0.05, respectively.}
+different Ni surfaces calculated by DFT, Ni and Ni-Mo models}
 \end{figure}
+
+The benchmark function and the trained models can be accessed from the VAP 
+GitHub repo (https://github.com/Bismarrck/vap) freely.
 
@@
 
-In this work, we proposed a new algorithm, namd the virtual atom approach, 
-to construct symmetry function based atomistic neural networks. With this 
-method, we can build direct computation graph from positions to total energy 
-using modern machine learning frameworks (like TensorFlow), thus, making the 
-technical barrier of calculating NN-derived atomic force and virial stress  
-neglectable. We also derived an alternative form of the general virial stress 
-equation. The new formula can be implemented with simple matrix operations and 
-is suitable for arbitrary machine learning platform based potentials. We 
-developed a highly efficient Python program, \tensoralloy{, for both 
-\textit{molecules} and \textit{solids}. We tested our program on two public 
-datasets, QM7 (molecules) and SNAP/Ni-Mo (solids). \tensoralloy{} can reach 
-state-of-art performances within just one GPU Hour.
+In this work, we proposed a two-phases (training, prediction) approach 
+(the virtual atom approach) to construct symmetry function based atomistic 
+neural networks. 
+With this method, we can build direct computation graph from atomic positions to 
+total energy within TensorFlow, thus making the technical barrier of calculating 
+NN-derived atomic forces and virial stress neglectable. We also derived an 
+alternative form of the general virial stress equation. This equation can be 
+calculated with simple matrix operations, which makes it suitable for machine 
+learning based interaction potentials.
+With these new features, we developed a Python program, TensorAlloy. This 
+program can be used to learn interaction potentials of \textit{molecules} or 
+\textit{solids}.
 
@@
 
-\subsection{
-    Calculations of $N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$}
-
-The following codes shows how to calculate $N_{ij}^{\mathrm{max}}$ and 
-$N_{ijk}^{\mathrm{max}}$. Python-3.7 and ASE-3.17.0 are suggested. In this block
-\textmd{dataset} should be a list of \textmd{ase.Atoms} objects.
-\begin{verbatim}
-nij_max = 0
-nijk_max = 0
-for i in range(dataset):
-    atoms = dataset[i]
-    assert isinstance(atoms, ase.Atoms)
-    ilist, jlist = ase.neighborlist.neighbor_list('ij', atoms, cutoff=rc)
-    nij = len(ilist)
-    nl = {}
-    for i, atomi in enumerate(ilist):
-        if atomi not in nl:
-            nl[atomi] = []
-        nl[atomi].append(jlist[i])
-    nijk = 0
-    for atomi, nlist in nl.items():
-        n = len(nlist)
-        nijk += (n - 1 + 1) * (n - 1) // 2
-    nij_max = max(nij, nij_max)
-    nijk_max = max(nijk, nijk_max)
-\end{verbatim}
-
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. A
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \subsection{Derivation and implementation of the virial stress equation}
@@
 
-\subsection{Implementation of the $g^2_{\mathrm{map}}$}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. B
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{
+    Calculations of \texorpdfstring{$N_{ij}^{\mathrm{max}}$}{Nijmax} and 
+    \texorpdfstring{$N_{ijk}^{\mathrm{max}}$}{Nijkmax}
+}
+
+The following function returns $N_{ij}$ and $N_{ijk}$ of an \textmd{ase.Atoms}:
+\begin{verbatim}
+def get_nij_and_nijk(atoms, rc, angular=False):
+    ilist, jlist = neighbor_list('ij', atoms, cutoff=rc)
+    nij = len(ilist)
+    if angular:
+        nl = {}
+        for i, atomi in enumerate(ilist):
+            if atomi not in nl:
+                nl[atomi] = []
+            nl[atomi].append(jlist[i])
+        nijk = 0
+        for atomi, nlist in nl.items():
+            n = len(nlist)
+            nijk += (n - 1 + 1) * (n - 1) // 2
+    else:
+        nijk = 0
+    return nij, nijk
+\end{verbatim}
+During the training phase, $\nijmax$ and $\nijkmax$ of a dataset (a collection 
+of \textmd{ase.Atoms} objects) can be pre-computed with the following codes:
+\begin{verbatim}
+nij_max = 0
+nijk_max = 0
+for atoms in dataset:
+    nij, nijk = get_nij_and_nijk(atoms, rc, angular)
+    nij_max = max(nij, nij_max)
+    nijk_max = max(nijk, nijk_max)
+\end{verbatim}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. C
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{
+    Calculations of 
+    \texorpdfstring{$N_{\mathrm{element}}^{\mathrm{max}}$}{Nelmax} 
+}
+
+The following function returns all $N_{\mathrm{element}}^{\mathrm{max}}$ (e.g., 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$) of a dataset:
+\begin{verbatim}
+def get_max_occurs(dataset):
+    from collections import Counter
+    max_occurs = Counter()
+    for atoms in dataset:
+        c = Counter(atoms.get_chemical_symbols())
+        for e, n in c.items():
+            max_occurs[e] = max(n, max_occurs[e])
+    return max_occurs
+\end{verbatim}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. D
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Implementation of the Virtual-Atom Map}
+
+The following class implements the core of the Virtual-Atom Approach. The 
+argument \textit{max\_occurs} just represents the Global Symbol List (GSL). The
+positions and forces can be transformed to their GSL forms by using the function
+\textit{map\_to\_gsl\_array}.
+
+\begin{verbatim}
+class VirtualAtomMap:
+    REAL_ATOM_START = 1
+
+    def __init__(self, max_occurs: Counter, symbols: List[str]):
+        istart = VirtualAtomMap.REAL_ATOM_START
+        self.max_occurs = max_occurs
+        self.symbols = symbols
+        self.max_vap_n_atoms = sum(max_occurs.values()) + istart
+        elements = sorted(max_occurs.keys())
+        offsets = np.cumsum([max_occurs[e] for e in elements])[:-1]
+        offsets = np.insert(offsets, 0, 0)
+        delta = Counter()
+        index_map = {}
+        mask = np.zeros(self.max_vap_n_atoms, dtype=bool)
+        for i, symbol in enumerate(symbols):
+            i_ele = elements.index(symbol)
+            i_old = i + istart
+            i_new = offsets[i_ele] + delta[symbol] + istart
+            index_map[i_old] = i_new
+            delta[symbol] += 1
+            mask[i_new] = True
+        reverse_map = {v: k - 1 for k, v in index_map.items()}
+        index_map[0] = 0
+        reverse_map[0] = -1
+        self.atom_masks = mask
+        self.index_map = index_map
+        self.reverse_map = reverse_map
+        self.splits = np.array([1, ] + [max_occurs[e] for e in elements])
+
+    def map_array_to_gsl(self, array: np.ndarray):
+        rank = np.ndim(array)
+        if rank == 2:
+            array = array[np.newaxis, ...]
+        elif rank <= 1 or rank > 3:
+            raise ValueError("The rank should be 2 or 3")
+        if array.shape[1] == len(self.symbols):
+            array = np.insert(
+                array, 0, np.asarray(0, dtype=array.dtype), axis=1)
+        else:
+            shape = (array.shape[0], len(self.symbols), array.shape[2])
+            raise ValueError(f"The shape should be {shape}")
+        indices = []
+        for i in range(self.max_vap_n_atoms):
+            indices.append(
+                self.reverse_map.get(i, -1) + self.REAL_ATOM_START)
+        output = array[:, indices]
+        if rank == 2:
+            output = np.squeeze(output, axis=0)
+        return output
+
+    def reverse_map_gsl_to_local(self, array: np.ndarray):
+        rank = np.ndim(array)
+        if rank == 2:
+            array = array[np.newaxis, ...]
+        assert array.shape[1] == self.max_vap_n_atoms
+        istart = self.REAL_ATOM_START
+        indices = []
+        for i in range(istart, istart + len(self.symbols)):
+            indices.append(self.index_map[i])
+        output = array[:, indices]
+        if rank == 2:
+            output = np.squeeze(output, axis=0)
+        return output
+\end{verbatim}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. E
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Implementation of the \texorpdfstring{$g^2_{\mathrm{map}}$}{g2map}}
 
 This function shows the calculation of $g^2_{\mathrm{map}}$. The returned dict 
-contains $g^2_{\mathrm{map}}$, $i^{(0)}_{\mathrm{+,g}}$, 
-$j^{(0)}_{\mathrm{+,g}}$ and $\mathbf{n_g}$. $\nijmax$ should be provided in 
-advance. \textmd{interactions} is a list of \textmd{string} representing the 
-\textbf{ordered} interactions (e.g. \textmd{['NiNi','NiMo','MoMo','MoNi']}). 
-\textmd{offsets} is a list of integers marking the starting indices of the 
-\textmd{interactions}. As an example, if $N_{\eta}$ is 8, the \textmd{offsets}
-corresponding to \textmd{['NiNi','NiMo','MoMo','MoNi']} should be 
-\textmd{[0, 8, 16, 24]}.
-\textmd{local\_to\_global\_map} is a dict mapping local indices to global 
-indices.
+is organized as follows: 
+\begin{itemize}
+    \item \textmd{'g2.v2g\_map'} : $g^2_{\mathrm{map}}$
+    \item \textmd{'g2.ilist'} : $i^{(0)}_{\mathrm{+,GSL}}$
+    \item \textmd{'g2.jlist'} : $j^{(0)}_{\mathrm{+,GSL}}$
+    \item \textmd{'g2.shift'} : $\mathbf{n_+}$
+\end{itemize}
+$\nijmax$ should be provided in advance. \textit{interactions} is a list of 
+\textit{string} representing the \textbf{ordered} interactions (e.g. 
+\textmd{['NiNi','NiMo','MoMo','MoNi']}). \textit{offsets} is a list of integers 
+marking the starting indices of the \textit{interactions}. As an example, if 
+$N_{\eta}$ is 8, the \textit{offsets} corresponding to 
+\textmd{['NiNi','NiMo','MoMo','MoNi']} should be \textit{[0, 8, 16, 24]}.
 
 \begin{verbatim}
-def get_g2_map(atoms: Atoms, nij_max: int, interactions: list, 
-               local_to_global_map: dict, offsets: list):
-    g2_map = np.zeros((nij_max, 2), dtype=np.int32)
+def get_g2_map(atoms: Atoms,
+               rc: float,
+               nij_max: int,
+               interactions: list,
+               vap: VirtualAtomMap,
+               offsets: np.ndarray,
+               for_prediction=False):
+    if for_prediction:
+        iaxis = 0
+    else:
+        iaxis = 1
+    g2_map = np.zeros((nij_max, iaxis + 2), dtype=np.int32)
     tlist = np.zeros(nij_max, dtype=np.int32)
     symbols = atoms.get_chemical_symbols()
-    ilist, jlist, Slist = neighbor_list('ijS', atoms, rc)
+    tic = time.time()
+    ilist, jlist, n1 = neighbor_list('ijS', atoms, rc)
     nij = len(ilist)
@@
         tlist[i] = interactions.index('{}{}'.format(symboli, symbolj))
-    ilist = np.resize(ilist + 1, (nij_max, ))
-    jlist = np.resize(jlist + 1, (nij_max, ))
-    Slist = np.resize(Slist, (nij_max, 3))
+    ilist = np.pad(ilist + 1, (0, nij_max - nij), 'constant')
+    jlist = np.pad(jlist + 1, (0, nij_max - nij), 'constant')
+    n1 = np.pad(n1, ((0, nij_max - nij), (0, 0)), 'constant')
+    n1 = n1.astype(np.float32)
     for count in range(len(ilist)):
@@
             break
-        ilist[count] = local_to_global_map[ilist[count]]
-        jlist[count] = local_to_global_map[jlist[count]]
-    g2_map[:, 0] = ilist
-    g2_map[:, 1] = offsets[tlist]
-    return {"g2_map": g2_map, "ilist": ilist, "jlist": jlist, 
-            "shift": np.asarray(Slist)}
+        ilist[count] = vap.index_map[ilist[count]]
+        jlist[count] = vap.index_map[jlist[count]]
+    g2_map[:, iaxis + 0] = ilist
+    g2_map[:, iaxis + 1] = offsets[tlist]
+    return {"g2.v2g_map": g2_map, "g2.ilist": ilist, "g2.jlist": jlist,
+            "g2.shift": n1}
 \end{verbatim}
 
-\newpage
-
-\subsection{Implementation of the $g^4_{\mathrm{map}}$}
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. F
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Implementation of the \texorpdfstring{$g^4_{\mathrm{map}}$}{g4map}}
 
@@
 $\nijkmax$ should be provided in advance.
-\textmd{global\_to\_local\_map} is the reverse dict of 
-\textmd{local\_to\_global\_map}.
+
+One must note that \textmd{'g2.ilist'} contains GSL indices while the symbol 
+list of the target \textit{Atoms} is in local order. So the \textit{reverse} 
+mapping is necessary.
+
 \begin{verbatim}
-def get_g4_map(atoms: Atoms, g2_map: dict, interactions: list, 
-               offsets: list, global_to_local_map: dict, nijk_max: int):
-    g4_map = np.zeros((nijk_max, 2), dtype=np.int32)
+def get_g4_map(atoms: Atoms,
+               g2_map: dict,
+               interactions: list,
+               offsets: np.ndarray,
+               vap: VirtualAtomMap,
+               nijk_max: int,
+               for_prediction=True):
+    if for_prediction:
+        iaxis = 0
+    else:
+        iaxis = 1
+    g4_map = np.zeros((nijk_max, iaxis + 2), dtype=np.int32)
     ijk = np.zeros((nijk_max, 3), dtype=np.int32)
@@
     vectors = {}
-    for i, atomi in enumerate(g2["ilist"]):
-        if atomi == 0:
+    for i, atom_gsl_i in enumerate(g2_map["g2.ilist"]):
+        if atom_gsl_i == 0:
             break
-        if atomi not in indices:
-            indices[atomi] = []
-            vectors[atomi] = []
-        indices[atomi].append(g2["jlist"][i])
-        vectors[atomi].append(g2["shift"][i])
+        if atom_gsl_i not in indices:
+            indices[atom_gsl_i] = []
+            vectors[atom_gsl_i] = []
+        indices[atom_gsl_i].append(g2_map["g2.jlist"][i])
+        vectors[atom_gsl_i].append(g2_map["g2.shift"][i])
     count = 0
-    for atomi, nl in indices.items():
-        indexi = global_to_local_map[atomi]
-        symboli = symbols[indexi]
+    for atom_gsl_i, nl in indices.items():
+        atom_local_i = vap.reverse_map[atom_gsl_i]
+        symboli = symbols[atom_local_i]
         prefix = '{}'.format(symboli)
         for j in range(len(nl)):
-            atomj = nl[j]
-            indexj = global_to_local_map[atomj]
-            symbolj = symbols[indexj]
+            atom_vap_j = nl[j]
+            atom_local_j = vap.reverse_map[atom_vap_j]
+            symbolj = symbols[atom_local_j]
             for k in range(j + 1, len(nl)):
-                atomk = nl[k]
-                indexk = global_to_local_map[atomk]
-                symbolk = symbols[indexk]
+                atom_vap_k = nl[k]
+                atom_local_k = vap.reverse_map[atom_vap_k]
+                symbolk = symbols[atom_local_k]
                 interaction = '{}{}'.format(
                     prefix, ''.join(sorted([symbolj, symbolk])))
-                ijk[count] = atomi, atomj, atomk
-                n1[count] = vectors[atomi][j]
-                n2[count] = vectors[atomi][k]
-                n3[count] = vectors[atomi][k] - vectors[atomi][j]
+                ijk[count] = atom_gsl_i, atom_vap_j, atom_vap_k
+                n1[count] = vectors[atom_gsl_i][j]
+                n2[count] = vectors[atom_gsl_i][k]
+                n3[count] = vectors[atom_gsl_i][k] - vectors[atom_gsl_i][j]
                 index = interactions.index(interaction)
-                g4_map[count, 0] = atomi
-                g4_map[count, 1] = offsets[index]
+                g4_map[count, iaxis + 0] = atom_gsl_i
+                g4_map[count, iaxis + 1] = offsets[index]
                 count += 1
-    return {"g4_map": g4_map, "ij": ij, "ik": ik, "jk": jk, 
-            "n1": n1, "n2": n2, "n3": n3}
+    return {"g4.v2g_map": g4_map,
+            "g4.ij.ilist": ijk[:, 0], "g4.ij.jlist": ijk[:, 1],
+            "g4.ik.ilist": ijk[:, 0], "g4.ik.klist": ijk[:, 2],
+            "g4.jk.jlist": ijk[:, 1], "g4.jk.klist": ijk[:, 2],
+            "g4.shift.ij": n1, "g4.shift.ik": n2, "g4.shift.jk": n3}
 \end{verbatim}
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section Appendix. G
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Compute the descriptors}
+
+Now we can implements the symmetry function descriptor. Here 
+\textit{SymmetryFunction} is the base class and \textit{BatchSymmetryFunction} 
+is its subclass for batch training.
+
+The return value of the method \textit{build\_graph} is a dict and its keys are
+chemical elements and values are correspond atomic descriptors and atom masks. 
+Taking the example of the Ni-Mo dataset with $r_c = 4.6$, batch size 10 and only
+10 radial symmetry functions, the corresponding $\nijmax$, 
+$N_{\mathrm{Ni}}^{\mathrm{max}}$ and $N_{\mathrm{Mo}}^{\mathrm{max}}$ are 108, 
+176 and 7200, respectively. Thus, the return dict should be:
+\begin{itemize}
+    \item \textmd{'Mo'}: ($\mathbf{G}^{\mathrm{Mo}}$, $\delta^{\mathrm{Mo}}$)
+    \item \textmd{'Ni'}: ($\mathbf{G}^{\mathrm{Ni}}$, $\delta^{\mathrm{Ni}}$)
+\end{itemize}
+where $\mathbf{G}^{\mathrm{Mo}}$ is a float tensor of shape 
+\textmd{[10, 176, 40]}, $\delta^{\mathrm{Mo}}$ is a float tensor of shape  
+\textmd{[10, 176]}, $\mathbf{G}^{\mathrm{Ni}}$ is a float tensor of shape 
+\textmd{[10, 108, 40]} and $\delta^{\mathrm{Ni}}$ is a float tensor of shape  
+\textmd{[10, 108]} during the training phase.
+
+The demo script can be found on GitHub: https://github.com/Bismarrck/vap.
+
+\begin{verbatim}
+class SymmetryFunction:
+    gather_fn = staticmethod(tf.gather)
+
+    def __init__(self, rc, elements, eta=np.array([0.05, 4.0, 20.0, 80.0]),
+                 omega=np.array([0.0]), beta=np.array([0.005, ]),
+                 gamma=np.array([1.0, -1.0]), zeta=np.array([1.0, 4.0]),
+                 angular=True, periodic=True):
+        all_kbody_terms, kbody_terms, elements = \
+            get_kbody_terms(elements, angular=angular)
+        ndim, kbody_sizes = compute_dimension(
+            all_kbody_terms, len(eta), len(omega), len(beta), len(gamma),
+            len(zeta))
+        self.rc = rc
+        self.all_kbody_terms = all_kbody_terms
+        self.kbody_terms = kbody_terms
+        self.elements = elements
+        self.n_elements = len(elements)
+        self.periodic = periodic
+        self.angular = angular
+        self.kbody_sizes = kbody_sizes
+        self.ndim = ndim
+        self.kbody_index = {
+            kbody_term: self.all_kbody_terms.index(kbody_term)
+            for kbody_term in self.all_kbody_terms}
+        self.offsets = np.insert(np.cumsum(kbody_sizes), 0, 0)
+        self.radial_indices_grid = ParameterGrid({
+            'eta': np.arange(len(eta), dtype=int),
+            'omega': np.arange(len(omega), dtype=int)})
+        self.angular_indices_grid = ParameterGrid({
+            'beta': np.arange(len(beta), dtype=int),
+            'gamma': np.arange(len(gamma), dtype=int),
+            'zeta': np.arange(len(zeta), dtype=int)})
+        self.initial_values = {'eta': eta, 'omega': omega, 'gamma': gamma,
+                               'beta': beta, 'zeta': zeta}
+
+    @staticmethod
+    def get_pbc_displacements(shift, cells, dtype=tf.float32):
+        return tf.matmul(shift, cells, name='displacements')
+
+    def get_rij(self, positions, cells, ilist, jlist, shift, name):
+        with tf.name_scope(name):
+            dtype = positions.dtype
+            Ri = self.gather_fn(positions, ilist, 'Ri')
+            Rj = self.gather_fn(positions, jlist, 'Rj')
+            Dij = tf.subtract(Rj, Ri, name='Dij')
+            if self.periodic:
+                pbc = self.get_pbc_displacements(shift, cells, dtype=dtype)
+                Dij = tf.add(Dij, pbc, name='pbc')
+            with tf.name_scope("safe_norm"):
+                eps = tf.constant(1e-8, dtype=dtype, name='eps')
+                rij = tf.sqrt(tf.reduce_sum(
+                    tf.square(Dij, name='Dij2'), axis=-1) + eps)
+                return rij, Dij
+
+    def get_v2g_map(self, features: dict, prefix: str):
+        return tf.identity(features[f"{prefix}.v2g_map"], name='v2g_map')
+
+    @staticmethod
+    def get_v2g_map_delta(tau):
+        return tf.constant([0, tau], dtype=tf.int32, name='delta')
+
+    def get_g_shape(self, features: dict):
+        return [features['n_atoms_vap'], self.ndim]
+
+    def get_g2_op_for_tau(self, shape, tau, r, rc2, fc_r, base_v2g_map):
+        with tf.name_scope(f"Grid{tau}"):
+            grid = self.radial_indices_grid[tau]
+            etai = grid['eta']
+            omegai = grid['omega']
+            eta = tf.constant(self.initial_values['eta'][etai], r.dtype)
+            omega = tf.constant(
+                self.initial_values['omega'][omegai], r.dtype)
+            delta = self.get_v2g_map_delta(tau)
+            r2c = tf.math.truediv(tf.square(r - omega), rc2, name='r2c')
+            v = tf.exp(-tf.multiply(eta, r2c, 'eta_r2c')) * fc_r
+            v2g_map_tau = tf.add(base_v2g_map, delta, f'v2g_map_{tau}')
+            return tf.scatter_nd(v2g_map_tau, v, shape, f"g{tau}")
+
+    def get_g2_op(self, features: dict):
+        with tf.variable_scope("G2"):
+            r = self.get_rij(features['positions'],
+                             features['cells'],
+                             features['g2.ilist'],
+                             features['g2.jlist'],
+                             features['g2.shift'],
+                             name='rij')[0]
+            rc2 = tf.constant(self.rc**2, dtype=r.dtype, name='rc2')
+            fc_r = cosine_cutoff(r, rc=self.rc, name='fc_r')
+            base_v2g_map = self.get_v2g_map(features, prefix='g2')
+            shape = self.get_g_shape(features)
+            values = []
+            for tau in range(len(self.radial_indices_grid)):
+                values.append(
+                    self.get_g2_op_for_tau(
+                        shape, tau, r, rc2, fc_r, base_v2g_map))
+            return tf.add_n(values, name='g')
+
+    def get_g4_op_for_tau(self, shape, tau: int, cos_theta, r2c, fc_r,
+                          base_v2g_map):
+        with tf.name_scope(f"Grid{tau}"):
+            grid = self.angular_indices_grid[tau]
+            betai = grid['beta']
+            gammai = grid['gamma']
+            zetai = grid['zeta']
+            beta = tf.constant(
+                self.initial_values['beta'][betai], r2c.dtype)
+            gamma = tf.constant(
+                self.initial_values['gamma'][gammai], r2c.dtype)
+            zeta = tf.constant(
+                self.initial_values['zeta'][zetai], r2c.dtype)
+            delta = self.get_v2g_map_delta(tau)
+            one = tf.constant(1.0, dtype=r2c.dtype, name='one')
+            two = tf.constant(2.0, dtype=r2c.dtype, name='two')
+            gt = tf.math.multiply(gamma, cos_theta, name='gt')
+            gt1 = tf.add(gt, one, name='gt1')
+            gt1z = tf.pow(gt1, zeta)
+            z1 = tf.math.subtract(one, zeta, name='z1')
+            z12 = tf.pow(two, z1)
+            c = tf.math.multiply(gt1z, z12, name='c')
+            v = tf.multiply(c * tf.exp(-beta * r2c), fc_r, f'v_{tau}')
+            v2g_map_tau = tf.add(
+                base_v2g_map, delta, name=f'v2g_map_{tau}')
+            return tf.scatter_nd(v2g_map_tau, v, shape, f'g{tau}')
+
+    def get_g4_op(self, features: dict):
+        with tf.variable_scope("G4"):
+            rij = self.get_rij(features['positions'],
+                               features['cells'],
+                               features['g4.ij.ilist'],
+                               features['g4.ij.jlist'],
+                               features['g4.shift.ij'],
+                               name='rij')[0]
+            rik = self.get_rij(features['positions'],
+                               features['cells'],
+                               features['g4.ik.ilist'],
+                               features['g4.ik.klist'],
+                               features['g4.shift.ik'],
+                               name='rik')[0]
+            rjk = self.get_rij(features['positions'],
+                               features['cells'],
+                               features['g4.jk.jlist'],
+                               features['g4.jk.klist'],
+                               features['g4.shift.jk'],
+                               name='rjk')[0]
+            rij2 = tf.square(rij, name='rij2')
+            rik2 = tf.square(rik, name='rik2')
+            rjk2 = tf.square(rjk, name='rjk2')
+            rc2 = tf.constant(self.rc**2, dtype=rij.dtype, name='rc2')
+            r2 = tf.add_n([rij2, rik2, rjk2], name='r2')
+            r2c = tf.math.truediv(r2, rc2, name='r2_rc2')
+            with tf.name_scope("CosTheta"):
+                upper = tf.subtract(rij2 + rik2, rjk2, name='upper')
+                lower = tf.multiply(2.0 * rij, rik, name='lower')
+                cos_theta = tf.math.truediv(upper, lower, name='theta')
+            with tf.name_scope("Cutoff"):
+                fc_rij = cosine_cutoff(rij, rc=self.rc, name='fc_rij')
+                fc_rik = cosine_cutoff(rik, rc=self.rc, name='fc_rik')
+                fc_rjk = cosine_cutoff(rjk, rc=self.rc, name='fc_rjk')
+                fc_r = tf.multiply(fc_rij, fc_rik * fc_rjk, 'fc_r')
+            base_v2g_map = self.get_v2g_map(features, prefix='g4')
+            shape = self.get_g_shape(features)
+            values = []
+            for tau in range(len(self.angular_indices_grid)):
+                values.append(
+                    self.get_g4_op_for_tau(
+                        shape, tau, cos_theta, r2c, fc_r, base_v2g_map))
+            return tf.add_n(values, name='g')
+
+    def get_row_split_sizes(self, features: dict):
+        return features['row_splits']
+
+    @staticmethod
+    def get_row_split_axis():
+        return 0
+
+    def get_column_split_sizes(self):
+        column_splits = {}
+        for i, element in enumerate(self.elements):
+            column_splits[element] = [len(self.elements), i]
+        return column_splits
+
+    @staticmethod
+    def get_column_split_axis():
+        return 1
+
+    def split_descriptors(self, descriptors, features: dict):
+        with tf.name_scope("Split"):
+            row_split_sizes = self.get_row_split_sizes(features)
+            row_split_axis = self.get_row_split_axis()
+            column_split_sizes = self.get_column_split_sizes()
+            column_split_axis = self.get_column_split_axis()
+            splits = tf.split(
+                descriptors, row_split_sizes, axis=row_split_axis,
+                name='rows')[1:]
+            atom_masks = tf.split(
+                features['atom_masks'], row_split_sizes, 
+                axis=row_split_axis,
+                name='atom_masks')[1:]
+            if len(self.elements) > 1:
+                blocks = []
+                for i in range(len(splits)):
+                    element = self.elements[i]
+                    size_splits, idx = column_split_sizes[element]
+                    block = tf.split(splits[i],
+                                     size_splits,
+                                     axis=column_split_axis,
+                                     name='{}_block'.format(element))[idx]
+                    blocks.append(block)
+            else:
+                blocks = splits
+            return dict(zip(self.elements, zip(blocks, atom_masks)))
+
+    def build_graph(self, features: dict):
+        with tf.variable_scope("Behler"):
+            descriptors = self.get_g2_op(features)
+            if self.angular:
+                descriptors += self.get_g4_op(features)
+        return self.split_descriptors(descriptors, features)
+
+class BatchSymmetryFunction(SymmetryFunction):
+    gather_fn = staticmethod(tf.batch_gather)
+
+    def __init__(self, rc, max_occurs: Counter, nij_max: int, 
+                 nijk_max: int, batch_size: int, 
+                 eta=np.array([0.05, 4.0, 20.0, 80.0]),
+                 omega=np.array([0.0]), beta=np.array([0.005, ]),
+                 gamma=np.array([1.0, -1.0]), zeta=np.array([1.0, 4.0]),
+                 angular=True, periodic=True):
+        elements = sorted(list(max_occurs.keys()))
+
+        super(BatchSymmetryFunction, self).__init__(
+            rc=rc, elements=elements, eta=eta, beta=beta, gamma=gamma,
+            zeta=zeta, omega=omega, angular=angular, periodic=periodic)
+        self._max_occurs = max_occurs
+        self._max_n_atoms = sum(max_occurs.values())
+        self._nij_max = nij_max
+        self._nijk_max = nijk_max
+        self._batch_size = batch_size
+
+    @staticmethod
+    def get_pbc_displacements(shift, cells, dtype=tf.float32):
+        with tf.name_scope("Einsum"):
+            shift = tf.convert_to_tensor(shift, dtype=dtype, name='shift')
+            cells = tf.convert_to_tensor(cells, dtype=dtype, name='cells')
+            return tf.einsum(
+                'ijk,ikl->ijl', shift, cells, name='displacements')
+
+    def get_g_shape(self, _):
+        n_atoms_vap = self._max_n_atoms + 1
+        return [self._batch_size, n_atoms_vap, self.ndim]
+
+    def get_v2g_map_batch_indexing_matrix(self, prefix='g2'):
+        if prefix == 'g2':
+            ndim = self._nij_max
+        else:
+            ndim = self._nijk_max
+        indexing_matrix = np.zeros(
+            (self._batch_size, ndim, 3), dtype=np.int32)
+        for i in range(self._batch_size):
+            indexing_matrix[i] += [i, 0, 0]
+        return indexing_matrix
+
+    @staticmethod
+    def get_v2g_map_delta(tau):
+        return tf.constant([0, 0, tau], tf.int32, name='delta')
+
+    def get_v2g_map(self, features: dict, prefix="g2"):
+        indexing = self.get_v2g_map_batch_indexing_matrix(prefix=prefix)
+        return tf.add(
+            features[f"{prefix}.v2g_map"], indexing, name='v2g_map')
+
+    def get_row_split_sizes(self, _):
+        row_splits = [1, ]
+        for i, element in enumerate(self.elements):
+            row_splits.append(self._max_occurs[element])
+        return row_splits
+
+    @staticmethod
+    def get_row_split_axis():
+        return 1
+
+    @staticmethod
+    def get_column_split_axis():
+        return 2
+\end{verbatim}
+
 \end{document}

### 2019-07-09 doc/papers/nn/manuscript.tex
Fix a bug.

@@
 algorithm. For simplicity, only radial symmetry function related algorithms are 
-visualized in the figures. The associated codes (Python3.7) are given in the 
-appendix. A demo script can be downloaded from GitHub freely 
+visualized in the figures. The associated Python implementation (Python3.7) are 
+given in the appendix. A full demo can be obtained from GitHub freely 
 (https://github.com/Bismarrck/vap).

### 2019-07-09 doc/papers/nn/figures/qm7.py

@@ -68,7 +68,7 @@ ax.bar(
     alpha=0.4, color='k', label=f"{orders[3][0]}/{orders[3][1]}")
 
 ax.set_xticks(index + bar_width * 1.5)
-ax.set_xticklabels(('1', '10', '20', '50', '100'))
+ax.set_xticklabels(('1', '25', '50', '100'))
 ax.set_xlabel(r"Batch Size", fontsize=16)
 ax.set_ylabel(r"Structures per Second", fontsize=16)
 ax.legend(frameon=False, fontsize=12)

### 2019-07-17 doc/papers/nn/manuscript.tex
Made some improvements to the revision.

--- 2019-06-26 doc/papers/nn/manuscript.tex
@@
 \title{
-    TensorAlloy: a highly efficient atomistic neural network program for alloys
+    TensorAlloy: an automatic atomistic neural network program for alloys
 }
@@
 metrics, such as force or virial stress, into training can be of great help. 
-However, the traditional way to construct a 
-machine learning model computation graph starts from pre-computed descriptors, 
-but not positions, due to technical challenges. Thus, deriving analytical atomic 
-force and virial stress of a machine learning model becomes quite difficult as 
-the partial derivations of descriptors with respect to positions need separate 
-implementations, which requires plenty of efforts and its efficiency can not be 
-guaranteed.
-In this paper, we designed a new method, named the virtual atom approach, for 
-implementing the symmetry function descriptor and the corresponding atomistic 
-neural networks. With the virtual atom approach, we are able to build 
-computation graph from atomic positions \textemdash but not descriptors 
-\textemdash to total energy directly, thus asking modern machine learning 
-platforms to compute atomic force and virial stress becoming possible. We also 
-derived a simple and machine learning friendly equation for calculating virial 
-stress. All these new algorithms have been implemented in our Python package, 
-TensorAlloy. TensorAlloy supports constructing machine learning interaction 
-potentials for both \textit{molecules} and \textit{solids}.
+The traditional way of implementing machine learning models starts from 
+pre-computed descriptor and the analytical (model-derived) atomic forces and 
+virial stress are handled by separate codes which require plenty of efforts. 
+In this work, we choose a new route to overcome this challenge by building 
+computation graph from atomic positions directly. Thus, TensorFlow or other 
+modern machine learning platforms can handle the derivations of forces and 
+stress, both automatically and efficiently. We demonstrate our core algorithm 
+\textemdash the virtual atom approach \textemdash using Behler-Parinello's 
+symmetry function atomic descriptor. This algorithm is implemented in our Python 
+program TensorAlloy. TensorAlloy supports constructing machine learning 
+interaction potentials for both \textit{molecules} and \textit{solids}. The QM7 
+and SNAP/Ni-Mo datasets are used to discuss performances of our program.
 \end{abstract}
@@
 \maketitle
-
-\newcommand{\tensoralloy}{\textbf{TensorAlloy}}
 
@@
 \textit{molecules} and \textit{solids} and it has successfully powered quite a 
-few researches since 2016\cite{Amp-works-hammer,amp-work-1}. ANI\cite{ANI} and 
-TensorMol\cite{TensorMol} are also symmetry function based packages but they 
-mainly focus on \textit{molecules}.
+few researches since 2016\cite{Amp-works-hammer,amp-work-1}. 
+TensorMol\cite{TensorMol} and its sucessor TorchANI\cite{ANI} are also symmetry 
+function based ANN programs but they mainly focus on \textit{molecules}.
 
@@
 descriptors and only build computation graph from descriptors to total energy. 
-This approach can significantly reduce technical difficulty and works very well 
-if only total energy is considered in the loss function. But to fit atomic 
-forces, numerous codes must be written manually, such as the derivation of 
-descriptors with respect to positions. Although the derivation is theoretically
-clear, the implementation is challenging and the efficiency can not be 
-guaranteed.
+This traditional approach can significantly reduce technical difficulty and 
+works very well if only total energy is considered in the loss function. But to 
+fit atomic forces, numerous codes must be written manually, such as the 
+derivation of descriptors with respect to positions. Although the derivation is 
+theoreticallyclear, the implementation is challenging and the efficiency can not 
+be guaranteed.
 
@@
 % 
+% New Commands
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\newcommand{\rijn}{r_{ij\mathbf{n}}}
+\newcommand{\rijna}{r_{ij\mathbf{n_1}}}
+\newcommand{\rikna}{r_{ik\mathbf{n_2}}}
+\newcommand{\rjkna}{r_{jk\mathbf{n_3}}}
+
+\newcommand{\nmax}{
+    N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}
+}
+\newcommand{\nijmax}{N_{ij}^{\mathrm{max}}}
+\newcommand{\nijkmax}{N_{ijk}^{\mathrm{max}}}
+\newcommand{\nelmax}{N^{\mathrm{max}}_{\mathrm{el}}}
+\newcommand{\nel}{N_{\mathrm{element}}}
+\newcommand{\nvap}{N^{\mathrm{vap}}}
+\newcommand{\nnimax}{N^{\mathrm{max}}_{\mathrm{Ni}}}
+\newcommand{\nmomax}{N^{\mathrm{max}}_{\mathrm{Mo}}}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
 % Section 2. Theory
@@
 \label{section:theory}
-
-\newcommand{\rijn}{r_{ij\mathbf{n}}}
 
@@
 
-\newcommand{\rijna}{r_{ij\mathbf{n_1}}}
-\newcommand{\rikna}{r_{ik\mathbf{n_2}}}
-\newcommand{\rjkna}{r_{jk\mathbf{n_3}}}
-
 There are many choices of $F_G$. The symmetry function descriptor, proposed 
 by Parinello and Behler in 2007\cite{Behler}, is currently the most widely used 
-atomic descriptor, especially for alloys. The symmetry function descriptor 
-consists of two sets of invariant (tranlational, rotational and permutational) 
-functions: the radial symmetry function $\mathbf{G}^{(2)}$ and the angular 
-symmetry function $\mathbf{G}^{(4)}$:
+atomic descriptor. The symmetry function descriptor consists of two sets of 
+invariant (tranlational, rotational and permutational) functions: the radial 
+symmetry function $\mathbf{G}^{(2)}$ and the angular symmetry function 
+$\mathbf{G}^{(4)}$:
 \begin{align}
@@
 The derivations are theoretically straightforward but their implementations are 
-challenging \cite{AMP}. Later we will provide a new approach to address this 
-problem.
+challenging \cite{AMP}. Later we will provide an automatic approach to address 
+this problem.
 
@@
 with NN or other ML potentials since the partial forces are difficult to compute 
-with vectorized operations. To resolve this issue, we derived an equivalent form 
+with vectorized operations. However, we find an "equivalent" form 
 of Equation \ref{eq:stress_lammps}:
@@
 where $R$ is the $N \times 3$ positions matrix and $F$ is the 
-corresponding total forces matrix. The new equation can be easily implemented 
-with simple matrix operations. The detailed derivation is given in the appendix.
+corresponding total forces matrix. This new form can be easily implemented 
+within TensorFlow. The detailed derivation is given in the appendix.
 
@@
 
-\newcommand{\nmax}{
-    N_{\mathrm{Ni}}^{\mathrm{max}}+N_{\mathrm{Mo}}^{\mathrm{max}}
-}
-\newcommand{\nijmax}{N_{ij}^{\mathrm{max}}}
-\newcommand{\nijkmax}{N_{ijk}^{\mathrm{max}}}
-\newcommand{\nelmax}{N^{\mathrm{max}}_{\mathrm{el}}}
-\newcommand{\nel}{N_{\mathrm{element}}}
-\newcommand{\nvap}{N^{\mathrm{vap}}}
-\newcommand{\nnimax}{N^{\mathrm{max}}_{\mathrm{Ni}}}
-\newcommand{\nmomax}{N^{\mathrm{max}}_{\mathrm{Mo}}}
-
-In this section we will describe the program design and the core algorithm: 
-the virtual atom approach (VAP). The most noticable feature of the TensorAlloy 
-program is that the calculation of symmetry function descriptors is finally 
-implemented in the compuation graph with the help of VAP. Thus, we can utilize 
-the \textbf{AutoGrad} routine of TensorFlow to derive atomic forces and virial 
-stress automatically and also efficiently.
-
-The Ni-Mo binary alloy system will be used as the example to show this 
-algorithm. For simplicity, only radial symmetry function related algorithms are 
-visualized in the figures. The associated codes (Python3.7) are given in the 
-appendix. A demo script can be downloaded from GitHub freely 
-(https://github.com/Bismarrck/vap).
+In this section we will describe the architecture of TensorAlloy and the core 
+algorithm: the virtual atom approach (VAP). The most noticable feature of the 
+TensorAlloy program is that the calculation of symmetry function descriptors is 
+automatically handled by the \textbf{AutoGrad}\cite{tensorflow} routine of 
+TensorFlow because we successfully find a route (VAP) to build the direct 
+computation graph from atomic positions to total energy.
+
+The Ni-Mo binary alloy system will be used as the example to show our 
+algorithms. The original dataset (SNAP) is published by Shyue Ping 
+Ong\cite{SNAP_2018}. 
+For simplicity, only radial symmetry function related algorithms are 
+visualized in the figures. Python3.7 implementations of key algorithms and 
+functions are given in the appendix. A full demo (including the alloy datasets) 
+can be obtained from GitHub freely (https://github.com/Bismarrck/vap).
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.A
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{General design}
+\label{section:principles}
 
 Fig \ref{fig:program_design} shows the general design of TensorAlloy.
-TensorAlloy has two phases: 1) is the training phase and 2) represents the 
-prediction phase. These two phases have slightly different focusing points:
-
-In the training phase, efficiency is the major concern. To accelerate model 
-training, batching (or mini-batch training) is one of the most commonly used 
-techniques. Batching requires aligned inputs. However, hundreds of different 
-stoichiometries may exist in one dataset. To batch such structures, an universal 
-approach of expressing different structures in a single reference system (the 
-global symbol list or GSL) is necessary.
-
-In the prediction phase, things may be a bit different. The stoichiometry of 
-the input structure may not be included in the training dataset and it can vary 
-significantly. Taking the example of Ni-Mo, the trained model must be capable of 
-predicting any $\mathrm{Ni}_{x}\mathrm{Mo}_{y}$ solid while $x$ and $y$ can be 
-either as large as 50000 or just zero. Hence, VAP must be flexible enough to 
-handle these situations.
-
-In the following subsection, we will discuss the details of VAP.
+TensorAlloy has two phases: the training phase \textbf{(1)} and the prediction 
+phase \textbf{(2)}. These two phases share many common requirements, but they 
+also have their own concerns.
+
+For the training phase, in order to make TensorAlloy a general-purpose and
+efficient machine learning potential training program, these three key 
+challenges shall be resolved:
+\begin{itemize}
+
+    \item[1.] 
+    Stoichiometry-free: the training dataset should not have any stoichiometry 
+    restriction. Any type of \textit{solid} or \textit{molecule} is acceptable. 
+    A universal approach of expressing different structures in a single 
+    reference system may be necessary.
+
+    \item[2.] 
+    Mini-batch training: mini-batch based stochastic training is 
+    currently the most efficient way to train neural networks on large datasets.
+    However, batch training requires \textit{vectorized} and \textit{aligned} 
+    expressions. Here \textit{aligned} means feature arrays of structures of 
+    different stoichiometries share the same shape.
+
+    \item[3.] 
+    Cache: some intermediate arrays may be pre-computed and stored in cache 
+    files. During training, these values can be loaded from cache directly, thus 
+    saving significantly amount of resources.
+
+\end{itemize}
+
+In the prediction phase, the situation is a bit different. The stoichiometry of 
+the target structure or molecule may not be included in the training dataset and 
+it can vary significantly. TensorAlloy must be capable of handling such 
+(extreme) situations. For example, the trained Ni-Mo shall be applicable to any 
+any $\mathrm{Ni}_{x}\mathrm{Mo}_{y}$ structure while $x$ and $y$ can be 
+either as large as 100000 or as small as 0.
+
+Besides, we also want our TensorAlloy program have an \textit{independent} and
+\textit{user-friendly} prediction phase. Users can just focus on the integration 
+of machine learning potentials with their own researches.
+
+The virtual-atom approach plays a central role in handling all the challenges 
+above and unify the training and prediction phases. In the following sections, 
+we will gradually discuss the details of this approach.
 
@@
 % 
-% Section 3.A
+% Section 3.B
 %
@@
 
-Fig \ref{fig:Fig2} shows the initialization of VAP. The cutoff radius $r_{cut}$ 
-must be fixed. The initialization involves two steps. The first step is to build 
-the global symbol list (GSL), which acts as the universal reference system. A 
-virtual atom is inserted at the very first position of this list. The benefits 
-will be discussed later. To build GSL, all $\nelmax$ must be obtained. 
-$\nelmax$ indicates the maximum appearances of an element in any structure and 
-$\nel$ represents the total number of unique chemical elements:
+Fig \ref{fig:Fig2} shows the preparation stage of VAP. The cutoff radius 
+$r_{cut}$ must be fixed. This stage has two major steps. The first step is to 
+build the global symbol list (GSL), which acts as the universal reference 
+system. A virtual atom is inserted at the very first position of GSL. The 
+benefits will be discussed later. To build GSL, all $\{\nelmax\}$ must be 
+pre-determined where $\nelmax$ is the maximum appearances of element 
+\textit{el} in any structure. $\nel$ represents the number of unique chemical 
+elements in the dataset. Then, $\nvap$, the dimension of GSL, can be determined:
 \begin{equation}
@@
 \end{equation}
-For the Ni-Mo dataset, $\mathrm{el} \in [\mathrm{Ni}, \mathrm{Mo}]$ and 
+For the Ni-Mo dataset, $el \in [\mathrm{Ni}, \mathrm{Mo}]$ and 
 $\nel = 2$. 
@@
 inserted virtual atom and Ni$_{108(54)}$ means the first 54 Ni atoms are mapped 
-from the local stoichiometry. In the training phase, all $\nelmax$ are constant.
+from the local stoichiometry. In the training phase, all $\nelmax$ are fixed.
 In the prediction phase, $\nelmax$ shall be determined dynamically. One should 
@@
 \hline
- & Stoichiometry & $\nnimax$ & $\nmomax$ & $N^{\mathrm{vap}}$ 
+ & Stoichiometry (Local) & $\nnimax$ & $\nmomax$ & $N^{\mathrm{vap}}$ 
  & Stoichiometry (GSL) \\
@@
 Then we can determine another two key constants: $\nijmax$ and $\nijkmax$. 
-Here $N_{ij}^{\mathrm{max}}$ represents the maximum number of neighbor pairs in
-arbitrary structure and the subscript 'ijk' denotes triples. 
-$N_{ij}^{\mathrm{max}}$ and $N_{ijk}^{\mathrm{max}}$ only depend on 
+Here $\nijmax$ represents the maximum number of atom-atom pairs in
+arbitrary structure and the subscript 'ijk' denotes triples 
+(or three-atoms interactions). $\nijmax$ and $\nijkmax$ only depend on 
 $r_{cut}$ and the associated codes are given in Appendix(B). 
 Table \ref{table:nij_nijk_max} summarizes $\nijmax$ and $\nijkmax$ at different
-$r_{cut}$ of the two tested datasets: QM7 and SNAP/Ni-Mo.
+$r_{cut}$ of the two demo datasets: QM7 and Ni-Mo (SNAP).
 
@@
 % 
-% Section 3.B
+% Section 3.C
 %
@@
 Both the radial (Equation \ref{eq:g2}) and the angular (Equation \ref{eq:g4}) 
-functions only interact with interatomic distances. In order to compute symmetry
-function descriptors, local atomic positions shall be transformed to GSL 
-interatomic distances first. Fig \ref{fig:Fig3} demonstrates the pseudo 
-computation graph for calculating interatomic distances 
-$\mathbf{r}^{\mathrm{GSL}}$ for radial descriptors:
+symmetry functions interact with interatomic distances only. In order to compute 
+the descriptors, local atomic positions should be transformed to interatomic 
+distances first. Fig \ref{fig:Fig3} demonstrates the pseudo graph of 
+$\mathbf{R} \rightarrow \mathbf{r}^{\mathrm{GSL}}$ for radial symmetry function
+descriptors:
 
@@
     \item[2.] 
-    Map $\mathbf{R}$, $\mathbf{i}$, $\mathbf{j}$ and $\mathbf{n}$ to
-    their corresponding GSL forms with padding zeros. One should note that these 
-    GSL arrays can be cached for training.
+    Transform and expand local $\mathbf{R}$, $\mathbf{i}$, $\mathbf{j}$ and 
+    $\mathbf{n}$ to their corresponding GSL arrays. These GSL arrays can be 
+    cached for training. The transformations of $\mathbf{i}$, $\mathbf{j}$ and 
+    $\mathbf{n}$ are straightforward: just appending $\nijmax - N_{ij}$ trailing 
+    zeros. Fig \ref{fig:Fig3si} shows the mapping of 
+    $\mathbf{R} \rightarrow \mathbf{R}^{\mathrm{GSL}}$ taking the example of 
+    Ni$_3$Mo$_2$.
 
@@
     \item[4.]
-    Compute the displacements in the original cell:
+    Compute the displacement vectors in the original cell:
     $\mathbf{D}_{ij} = \mathbf{j}^{\mathrm{GSL}} - \mathbf{i}^{\mathrm{GSL}}$
@@
     \item[5.]
-    Compute the total periodic displacements:
+    Compute the periodic displacements:
     $\mathbf{D}_{pbc} = \mathbf{n}^{\mathrm{GSL}} \mathbf{h}$
@@
     \item[7.] 
-    Compute the interatomic distances $\mathbf{r}^{\mathrm{GSL}}$.
+    Compute the interatomic distances $\mathbf{r}^{\mathrm{GSL}}$ by calculating
+    the 2-norm of each row of matrix $\mathbf{D}^{\mathrm{GSL}}$.
 
 \end{itemize}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.3 (SI)
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.8]{figures/Fig3si.pdf}
+\caption{\label{fig:Fig3si} The transformation of local $\mathbf{R}$ of 
+Ni$_3$Mo$_2$ to $\mathbf{R}^{\mathrm{GSL}}$ of XNi$_{108(3)}$Mo$_{176(2)}$.
+}
+\end{figure}
 
@@
 % 
-% Section 3.C
+% Section 3.D
 %
@@
 \label{section:radial_descriptors}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Fig.4
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 
@@
 \begin{itemize}
+
     \item[1.] 
@@
     first row always corresponds to the inserted virtual atom.
+
     \item[2.]
@@
     $\nel \cdot \nel$ indicates the number of element-element interaction types 
-    and each interaction is described by $N_{\tau}$ feature values.
+    and each interaction is described by $N_{\tau}$ feature values. For the 
+    Ni-Mo dataset, there should be four unqiue interaction types: Ni-Ni, Ni-Mo, 
+    Mo-Mo and Mo-Ni.
+
 \end{itemize}
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Fig.4
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{figure}[h!]
@@
 \includegraphics[scale=0.95]{figures/Fig5.pdf}
-\caption{\label{fig:Fig5} The definition of $f^{(2,4)}_{\nu}$: map the 
-vector $\nu$ to array $g$ of shape [2, 4], or mathematically
-$g(i,j) = \sum_{k}^{f^{(2,4)}_{\nu}(k) = (i,j)}{\nu(k)}$.
+\caption{\label{fig:Fig5} The calculation of 
+$\mathbf{G}^{(2)}((\eta, \omega)_{\tau})$ from $\mathbf{r}^{\mathrm{GSL}}$. 
 }
@@
 The workflow for the batch training phase is almost identical to the prediction 
-phase introduced above. There are still some noticable diiferences. Assume 
-$N_{b}$ represents the batch size:
+phase described above. Meanwhile, there are some noticable diiferences:
 
@@
     more dimension. For example, $\mathbf{R}^{\mathrm{GSL}}$ should be an array
-    of shape $[N_b, \nijmax, 3]$.
+    of shape $[N_b, \nijmax, 3]$. Here $N_{b}$ represents the batch size.
 
     \item[2.]
-    The base mapping $f_{g}^{S}$ becomes a matrix of shape $[\nijmax, 3]$. Its 
-    last two columns remain unchanged. However, the newly inserted first column 
+    The atomic descriptors $\mathbf{G}^{(2)}$ becomes a 3D array of shape 
+    $[N_b, \nvap, (\nel)^2 \cdot N_{\tau}]$.
+
+    \item[3.] 
+    The base mapping $f_{g}^{S}$ becomes a matrix of shape $[\nijmax, 3]$ in the 
+    batch training phase. The newly inserted first column 
     \textemdash representing the batch indices \textemdash is 
-    \textbf{not cacheable} because batching is a random action. The first column
-    should be generated dynamically.
-
-    \item[3.]
-    $\tau$ should be added to the third column of $f_{g}^{S}$.
+    \textbf{not cacheable} because structures are selected randomly to form a 
+    batch. Thus, the first column should be generated runtimely.
 
@@
     In the training phase, $\nvap$ is a constant determined before training. In 
-    the contrast, $\nvap$ becomes a tensor that should be manually specified in 
-    the prediction phase.
+    the contrast, $\nvap$ should be a dynamic tensor 
+    (or a \textit{tf.Placeholder} technically) in the prediction phase.
+    Its value shall be runtimely determined according to the input structure. 
+    Thus, the stoichiometry challenge mentioned in Section 
+    \ref{section:principles} can be overcame.
 
     \item[5.]
-    In the training phase, the reference atomic forces should be transformed to 
-    its corresponding GSL array because the NN-derived force array 
-    $\mathbf{F}^{\mathrm{NN}}$ is in GSL reference:
+    In the training phase, the reference (or dft) atomic forces should be 
+    transformed to GSL arrays before computing the loss contribution. The 
+    NN-derived forces $\mathbf{F}^{\mathrm{NN}}$ are indeed GSL forces:
     \begin{equation}
@@
     \end{equation}
-    Hence, in the prediction phase, a reverse VAP mapping is required to convert
-    $\mathbf{F}^{\mathrm{NN}}$ to its local form.
+    Hence, in the prediction phase, a reverse transformation should be applied 
+    to obtain local \textbf{F}.
 
@@
 inherits most of methods from its parent class \textit{SymmetryFunction}. 
-The dynamic batching is implemented in method 
+The dynamic batching scheme is implemented in method 
 \textit{get\_v2g\_map\_batch\_indexing\_matrix}. The method 
@@
 % 
-% Section 3.D
+% Section 3.E
 %
@@
 % 
-% Section 3.E
+% Section 3.F
 %
@@
 % 
-% Section 3.F
+% Section 3.G
 %
@@
 is the corresponding total energy.
+
+In the training phase, the atomic descriptors array $\mathbf{G}^{(2)}$ is a 3D 
+array because of the structure-based batching scheme. Thus, it's necessarily to 
+use convolutional neural networks (CNNs) with 1x1 kernels\cite{kCON}. 
+The traditional feed-forward neural networks with an additional 
+atom-to-structure indexing\cite{Behler,ANI,TensorMol,DeePMD,BIMNN} are 
+mathematically equivalent to CNNs with 1x1 kernels. However, using CNNs can make
+the calculations of the \textit{automatically-differentiated per-structure} 
+$\partial E/\partial \mathbf{R}$ and $\partial E/\partial \mathbf{h}$ much 
+easier.
 
@@
 
-In this work, we proposed a two-phases (training, prediction) approach 
-(the virtual atom approach) to construct symmetry function based atomistic 
-neural networks. 
-With this method, we can build direct computation graph from atomic positions to 
-total energy within TensorFlow, thus making the technical barrier of calculating 
-NN-derived atomic forces and virial stress neglectable. We also derived an 
-alternative form of the general virial stress equation. This equation can be 
-calculated with simple matrix operations, which makes it suitable for machine 
-learning based interaction potentials.
-With these new features, we developed a Python program, TensorAlloy. This 
-program can be used to learn interaction potentials of \textit{molecules} or 
-\textit{solids}.
+In this work, we introduced our virtual atom approach and a smart way of 
+constructing symmetry function based atomistic neural networks. 
+With the virtual atom approach, the calculations of the symmetry function 
+descriptors can be implemented within TensorFlow. Thus, we can now build direct 
+computation graph from atomic positions to total energy, making the technical 
+barrier of calculating NN-derived atomic forces and virial stress neglectable.
+This new algorithm is implemented in our Python program, TensorAlloy.
 

### 2019-07-30 tensoralloy/nn/basic.py
Minor update.

@@ -896,9 +896,6 @@ class BasicNN:
                 if 'class' in serialized:
                     serialized.pop('class')
                 clf = self._transformer.__class__(**serialized)
-            else:
-                raise ValueError(
-                    "The attached transformer should not be a `BaseTransformer`")
 
             configs = self.as_dict()
             configs.pop('class')

### 2019-07-30 doc/papers/nn/manuscript.tex
The manuscript is updated.

@@
 metrics, such as force or virial stress, into training can be of great help.  
-The traditional way of implementing machine learning models starts from 
-pre-computed descriptor and the analytical (model-derived) atomic forces and 
-virial stress are handled by separate codes which require plenty of efforts. 
-In this work, we choose a new route to overcome this challenge by building 
-computation graph from atomic positions directly. Thus, TensorFlow or other 
-modern machine learning platforms can handle the derivations of forces and 
-stress, both automatically and efficiently. We demonstrate our core algorithm 
-\textemdash the virtual atom approach \textemdash using Behler-Parinello's 
-symmetry function atomic descriptor. This algorithm is implemented in our Python 
-program TensorAlloy. TensorAlloy supports constructing machine learning 
-interaction potentials for both \textit{molecules} and \textit{solids}. The QM7 
-and SNAP/Ni-Mo datasets are used to discuss performances of our program.
+In this work, we propose a virtual-atom approach to model the total energy of 
+symmetry function descriptors based atomistic neural network. Our approach 
+starts from atomic positions directly so that the derivations of forces and 
+virial can be handled by TensorFlow automatically and efficiently. This new 
+approach is implemented in our program TensorAlloy, which supports constructing 
+machine learning interaction potentials for both \textit{molecules} and 
+\textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used to demostrate the 
+performances of our program.
 \end{abstract}
@@
 
-In this work, we propose a new algorithm, named the virtual atom approach, to 
-implement the symmetry function descriptor and the ANN model based on 
-TensorFlow. This algorithm is very suitable for parallel execution. With this 
-approach, stochastic gradient descent (SGD) based mini-batch training can be 
-adopted. We also derive a general and vectorizable expression for computing 
-virial stress for arbitrary ANN model. All these algorithms have been 
-implemented in our Python program: TensorAlloy.
+In this work, we propose a new TensorFlow-dependent apporach (the virtual atom 
+approach, VAP) to model the total energy expression of the symmetry function 
+descriptor based neural network. 
+Our apporach can move the entry of the computation graph from atomic descriptors 
+back to the raw atomic positions. Thus, calculating the derivatives of total 
+energy with respect to atomic positons (force) or lattice tensor (virial) can be 
+handled by TensorFlow directly and automatically.
 
@@
 theory of the symmetry function descriptor and the ANN framework. Section 
-\ref{section:method} describes the virtual atom approach and a modified ANN 
-model used by TensorAlloy. Section \ref{section:discussions} displays 
-performances of TensorAlloy on two public datasets. The appendix 
+\ref{section:method} describes the virtual atom approach and the modified ANN 
+model used by TensorAlloy. Section \ref{section:discussions} demostrates 
+the performances of TensorAlloy on two public datasets. The appendix 
 \ref{section:appendix} gives derivation and implementation details of key 
-algorithms. Implementations of the core algorithms and some trained models can 
-be obtained from GitHub (https://github.com/Bismarrck/vap) freely.
+routines of VAP. The full implementation and demo codes can be obtained from 
+GitHub (https://github.com/Bismarrck/vap) freely.
 
@@
 by Parinello and Behler in 2007\cite{Behler}, is currently the most widely used 
-atomic descriptor. The symmetry function descriptor consists of two sets of 
-invariant (tranlational, rotational and permutational) functions: the radial 
-symmetry function $\mathbf{G}^{(2)}$ and the angular symmetry function 
-$\mathbf{G}^{(4)}$:
+atomic descriptor. The symmetry function descriptor consists of two types of 
+functions: the radial symmetry function $\mathbf{G}^{(2)}$ and the angular 
+symmetry function $\mathbf{G}^{(4)}$:
 \begin{align}
@@
 \end{equation}
-The summations in $\mathbf{G}^{(2)}$ and $\mathbf{G}^{(4)}$ should go over all 
-neighbors within $r_c$.
+The summations in Equation \ref{eq:G2} and \ref{eq:G4} should go over all 
+neighbors within $r_c$. For an atom $i$, $\mathbf{G}_i$ is a vector. For the 
+entire structure, its overall $\mathbf{G}$ is a matrix with row $i$ represents 
+the atomic descriptors of atom $i$ and column $j$ corresponds to a specifc 
+$(\eta, \omega)$ pair or $(\beta, \gamma, \zeta)$ combination.
 
@@
 
-The $3 \times 3$ virial stress tensor $\epsilon$ is an important metric to 
+The $3 \times 3$ virial tensor $\epsilon$ is an important metric to 
 describe solids under deformation or external pressure. For arbitrary many-body 
@@
 \label{eq:stress_lammps}
-V \cdot \epsilon = \left(-\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} - 
+\epsilon = \left(-\sum_{i=1}^{N}{\mathbf{r}_i^{(0)} \otimes f_i} - 
 \sum_{\mathbf{n}}{\mathbf{h}^T\mathbf{n}} \otimes 
@@
 \end{equation}
-where $V$ is the volume, $\otimes$ indicates tensor product, $f_i$ is the total 
+where $\otimes$ indicates tensor product, $f_i$ is the total 
 force acting on atom $i$ and $F^{\prime}_{i\mathbf{n}}$ is the partial force. 
@@
 \label{eq:stress}
-V \cdot \epsilon = -F^{T} R + 
+\epsilon = -F^{T} R + 
 \left(\frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h}
@@
 corresponding total forces matrix. This new form can be easily implemented 
-within TensorFlow. The detailed derivation is given in the appendix.
+within TensorFlow. The detailed derivation is given in the appendix(A).
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{General design}
-\label{section:principles}
-
-Fig \ref{fig:program_design} shows the general design of TensorAlloy.
+\subsection{Overview}
+\label{section:overview}
+
+Fig \ref{fig:program_design} shows the overview of TensorAlloy and the 
+virtual-atom approach.
 TensorAlloy has two phases: the training phase \textbf{(1)} and the prediction 
@@
 For the training phase, in order to make TensorAlloy a general-purpose and
-efficient machine learning potential training program, these three key 
-challenges shall be resolved:
+efficient machine learning potential training program, there are some key 
+technical requirements:
 \begin{itemize}
@@
 
-The virtual-atom approach plays a central role in handling all the challenges 
-above and unify the training and prediction phases. In the following sections, 
-we will gradually discuss the details of this approach.
+VAP plays a central role in handling all the technical challenge as it 
+\textbf{\textit{provides a way to describe structures of various sizes and 
+stoichiometries in unified and vectorized forms}}. 
+In the following sections, we will gradually discuss the details of this 
+approach.
 
@@
 \centering
-\includegraphics[scale=0.58]{figures/Fig1.pdf}
+\includegraphics[scale=0.68]{figures/Fig1.pdf}
 \caption{\label{fig:program_design} The general design of TensorAlloy. 
@@
 build the global symbol list (GSL), which acts as the universal reference 
-system. A virtual atom is inserted at the very first position of GSL. The 
-benefits will be discussed later. To build GSL, all $\{\nelmax\}$ must be 
-pre-determined where $\nelmax$ is the maximum appearances of element 
-\textit{el} in any structure. $\nel$ represents the number of unique chemical 
-elements in the dataset. Then, $\nvap$, the dimension of GSL, can be determined:
+system. A virtual atom is inserted at the very first position of GSL. 
+To build GSL, all $\{\nelmax\}$ must be pre-determined where $\nelmax$ is the 
+maximum appearances of element \textit{el} in any structure. $\nel$ represents 
+the number of unique chemical elements in the dataset. Then, $\nvap$, the 
+dimension of GSL, can be determined:
 \begin{equation}
@@
 Both the radial (Equation \ref{eq:g2}) and the angular (Equation \ref{eq:g4}) 
-symmetry functions interact with interatomic distances only. In order to compute 
+symmetry functions depends on interatomic distances only. In order to compute 
 the descriptors, local atomic positions should be transformed to interatomic 
@@
 
-Now we can start the last step: computing radial symmetry descriptors 
+Now we can start computing radial symmetry descriptors 
 $\mathbf{G}^{(2)}$ from $\mathbf{r}^{\mathrm{GSL}}$. For simplicity, we will use 
@@
     Its value shall be runtimely determined according to the input structure.
-    Thus, the stoichiometry challenge mentioned in Section 
-    \ref{section:principles} can be overcame.
 
@@
 where $N_b$ is the mini-batch size and $\chi_{\mathrm{f}}$ and 
-$\chi_{\mathrm{s}}$ are weights of force and stress losses. 
-Stress tensors are converted to Voigt vectors. All energies are in \textbf{eV}, 
-all forces are in \textbf{eV/\AA} and all stress components are in 
-\textbf{eV/\AA}$\mathbf{^3}$. In most cases, we set $N_b$ to 50 or 100 and we
+$\chi_{\mathrm{s}}$ are weights of force and virial losses. 
+In most cases, we set $N_b$ to 50 or 100 and we
 use the ADAM\cite{adam} optimizer with exponentially-decayed learning rate to 
@@
 \end{equation}
+Softplus is a smooth approximation of the ReLU activation function.
 The kernel weights of all NNs are initialized with the 
-Xvaier\cite{pmlr-v9-glorot10a} method and kernel biases are initialized with 
+Xvaier method\cite{pmlr-v9-glorot10a} and kernel biases are initialized with 
 zeros.
@@
 % 
-% Section 4. Discussions
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Discussions}
+% Section 4. Results and Discussions
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{Results and Discussions}
 \label{section:discussions}
@@
 
-    \item Ni: this model uses 400 Ni structures for training and 61 for 
-    evaluation. The loss function only includes energy and force contributions.
-
-    \item Mo: this model uses 250 Mo structures for training and 34 for 
-    evaluation. The loss function includes all three (energy, force, stress) 
+    \item \textbf{NN}(Ni): this model uses 400 Ni structures for training and 61 
+    for evaluation. The loss function only includes energy and force 
+    contributions.
+
+    \item \textbf{NN}(Mo): this model uses 250 Mo structures for training and 34 
+    for evaluation. The loss function includes all three (energy, force, stress) 
     types of contributions.
 
-    \item Ni-Mo: this model uses 3673 structures for training and 300 for 
-    evaluation. The loss function includes all three types of contributions.
+    \item \textbf{NN}(Mo-Ni): this model uses 3673 structures for training and 
+    300 for evaluation. The loss function includes all three types of 
+    contributions.
 
@@
 
-For all these models, the cutoff radius is set to 6.5 \AA. Only radial symmetry 
+The cutoff radius is set to 6.5 \AA. Only radial symmetry 
 functions are used to compute atomic descriptors. The selected $\eta$ are 
@@
 \hline
-Model & Mo & Ni & Ni-Mo & Mo & Ni & Ni-Mo & Mo & Ni-Mo \\
+NN Model & Mo & Ni & Ni-Mo & Mo & Ni & Ni-Mo & Mo & Ni-Mo \\
 \hline
@@
     \includegraphics[scale=0.64]{figures/Prediction-speed.pdf}
-\caption{\label{fig:prediction_speed} Benchmarks of the Ni-Mo model in 
-the prediction phase. The test structures are (MoNi)$_{x}$ where 
+\caption{\label{fig:prediction_speed} Benchmarks of the \textbf{NN}(Mo-Ni) model 
+in the prediction phase. The test structures are (MoNi)$_{x}$ where 
 $x$ = $10^3, 15^3, 20^3, 25^3, 30^3, 35^3, 40^3$. The left figure \textbf{a)} 
@@
 interaction potentials. Fig \ref{fig:prediction_speed} summarizes the time 
-distribution of the Ni-Mo model in the prediction phase on the GPU workstation. 
+distribution of the \textbf{NN}(Ni-Mo) model in the prediction phase on the GPU 
+workstation. 
 Here 'prediction' is defined as calculating energy, forces and stress tensor of 
@@
 To further validate our models, we also calculate the energy-volume curves of a 
-conventional fcc Ni cell using SFNN/Ni and SFNN/Ni-Mo models. The results are 
-plotted in Fig \ref{fig:energy_volume_Ni}. Both curves overlap the DFT curve 
-very well in the range of -17\% to 21\% from the equilibrium volume. The surface
-energy tests, as shown in Fig \ref{fig:surface_energy_Ni}, also proves the 
-accuracy of TensorAlloy-optimized models. PyMatGen\cite{pymatgen,pymatgen-1} is 
-used to generate these surface slabs.
+conventional fcc Ni cell using \textbf{NN}(Ni) and \textbf{NN}(Mo-Ni) models. 
+The results are plotted in Fig \ref{fig:energy_volume_Ni}. Both curves overlap 
+the DFT curve very well in the range of -17\% to 21\% from the equilibrium 
+volume. The surface energy tests, as shown in Fig \ref{fig:surface_energy_Ni}, 
+also proves the accuracy of TensorAlloy-optimized models. 
+PyMatGen\cite{pymatgen,pymatgen-1} is used to generate these surface slabs.
 
@@
 \textit{volume} are scalar tensors, \textit{cell} is a $3 \times 3$ tensor, 
-\textit{positions} is a $N\times 3$ tensor and \textit{forces} (the total forces 
+\textit{R} is a $N\times 3$ tensor and \textit{F} (the total forces 
 on these atoms) is also a $N\times 3$ tensor:
 \begin{verbatim}
-def get_virial_stress_tensor(energy, cell, volume, positions, forces):
+def get_virial_stress_tensor(energy, cell, volume, R, F):
     dEdh = tf.gradients(energy, cell, name='dEdh)[0]
     right = tf.matmul(tf.transpose(dEdh, name='dEdhT'), cell)
-    left = tf.matmul(tf.transpose(forces), positions)
-    stress = tf.add(tf.negative(left), right, name='stress')
-    stress = tf.div(stress, volume, name='virial')
+    left = tf.matmul(tf.transpose(F), R)
+    virial = tf.add(tf.negative(left), right, name='virial')
+    stress = tf.div(virial, volume, name='stress')
     return stress

### 2019-08-06 doc/papers/nn/manuscript.tex
Final revision for this submission.

@@
 more attentions as they can provide density functional theory level predictions 
-within negligible time. Currently, the symmetry function descriptor based 
+within negligible time. The symmetry function descriptor based 
 atomistic neural network is the most widely used model for modeling alloys. 
@@
 symmetry function descriptors based atomistic neural network. Our approach 
-starts from atomic positions directly so that the derivations of forces and 
-virial can be handled by TensorFlow automatically and efficiently. This new 
-approach is implemented in our program TensorAlloy, which supports constructing 
-machine learning interaction potentials for both \textit{molecules} and 
-\textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used to demostrate the 
-performances of our program.
+creates the computation graph directly from atomic positions. Thus, the 
+derivations of forces and virial can be handled by TensorFlow automatically and 
+efficiently. This new approach is implemented in our program TensorAlloy, which 
+supports constructing machine learning interaction potentials for both 
+\textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used 
+to demostrate the performances of our program.
 \end{abstract}
@@
 derivation of descriptors with respect to positions. Although the derivation is 
-theoreticallyclear, the implementation is challenging and the efficiency can not 
-be guaranteed.
+theoretically clear, the implementation is challenging and the efficiency can 
+not be guaranteed.
 
@@
 In the atomistic neural network (\textbf{ANN}) framework, the total energy, 
-$E^{total}$, of a structure with $N$ atoms, is the sum of all atomic energies:
+$E^{total}$, of a structure with $N$ atoms, can be expressed as the sum of all 
+atomic energies:
 \begin{equation}
@@
 Here $\mathbf{G}_i$ is a vector representing atomic descriptors of atom $i$. 
-$\mathbf{G}_i$ typically only depends on local environments, i.e.  
-neighbors of atom $i$:
+$\mathbf{G}_i$ typically only depends on local environment of atom $i$, i.e.  
+its neighbors:
 \begin{equation}
@@
 \end{equation}
-where $F_G$ can be arbitrary function, $r_c$ is the cutoff radius and $\rijn$ is 
-the interatomic distance considering the periodic boundary conditions: 
+where $F_G$ is a specifc feature function, $r_c$ is the cutoff radius and 
+$\rijn$ is the interatomic distance considering the periodic boundary 
+conditions: 
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{r}_i^{(0)}$ and $\mathbf{r}_j^{(0)}$ denote positions of $i$ and 
-$j$ in the primitive cell, $\mathbf{n}$ is a column vector specifying the cell 
-shifts along $(X,Y,Z)$ directions 
+where $\mathbf{r}_i^{(0)}$ and $\mathbf{r}_j^{(0)}$ denote positions of atoms 
+$i$ and $j$ in the primitive cell, $\mathbf{n}$ is a column vector specifying 
+the cell shifts along $(X,Y,Z)$ directions
 \begin{equation}
@@
 arbitrary structure and the subscript 'ijk' denotes triples 
-(or three-atoms interactions). $\nijmax$ and $\nijkmax$ only depend on 
+(or three-atoms) interactions. $\nijmax$ and $\nijkmax$ only depend on 
 $r_{cut}$ and the associated codes are given in Appendix(B). 

### 2019-08-16 doc/papers/ml-eam/manuscript.tex
Initial commit to the ML-EAM paper.

\documentclass[prb,reprint]{revtex4-2}

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
\raggedbottom           % don't add extra vertical space
\begin{comment}
\end{comment}

\bibliographystyle{apsrev4-2}

\begin{document}

\title{
    Machine-learned embedded atom method
}

\author{Xin Chen, 
        Li-Fang Wang, 
        De-Ye Lin$^\mathrm{*}$, 
        Hai-Feng Song$^\mathrm{*}$}

\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}

\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Abstract
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{abstract}
\end{abstract}

\maketitle

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 1. Introduction
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Introduction}
\label{sec:introduction}

Atomistic modeling plays a vital role in materials science. \textit{ab initio} 
calculation or force-field based molecular dynamics simulation (MD) are 
effective ways to study, understand or predict chemical and physical properties 
of materials. \textit{ab initio} approaches are generally much more precise but 
they are rarely used on large-scale metallic systems due to their extremely-high 
computation expenses. Physical model based empirical potential (force-field), 
such as the embedded-atom method (EAM), modified embedded-atom method (MEAM), 
bond-order potential (BoP), or angular-dependent potential (ADP), still plays 
the major role in long-time simulations and these empirical methods can achieve 
reasonable accuracy with much lower computation costs.

In the last decade, machine learning (ML) has become one of the hottest 
topics in many research areas. In the materials science, researchers have made 
great efforts on developing ML models to describe atomic interactions. Such ML 
models are considered as machine learning interaction potentials (MLIPs). Until 
now, hundreds of MLIPs have been proposed. Among them, the symmetry-function 
based atomistic neural network (ANN) model by Parinello and Behler is the most 
popular choice in modeling metallic interactions. The smooth overlap atomic 
positions descriptor based gaussian approximation potential (SOAP-GAP) can give
extremely accurate results, although it's a bit computationally expensive. 
Spectral neighbor analysis potential (SNAP) is another quantum-accurate MLIP and
it performs very well on a broad range of metals and alloys.

Compared with empirical potentials, MILPs have some noticable advantages.

Traditionally, to find optimal parameters of an EAM potential, global 
optimization approaches (such as Basin Hopping or Genetic Algorithm) will be 
used because the analytical gradients of the total loss with respect to model
parameters are difficult to derive and implement \textit{by hand}. In this 
paper, we chose a new route to address this issue: to 'ask' machine learning 
platform to handle derivations and implementations.

This paper is organized as follows. Section \ref{sec:method} describes the 
theoretical background of this work, including the formalism of the embedded 
atom method, the expressions of the empirical potential and the algorithms for 
integrating EAM with machine learning. Section \ref{sec:results} summarizes the 
training results and the optimal parameters. Applications of the new potentials 
are discussed in Section \ref{sec:discussions}. Technical details can be found 
in the appendix.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 2. Method
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Method}
\label{sec:method}

% ------------------
% Section 2.1 Theory
% ------------------
\subsection{Theory}
\label{sec:theory}

In the original EAM formalism, the total energy, $E^{total}$, is the sum of 
atomic energies:
\begin{align}
E^{total} = & \sum_{i}^{N}{E_{i}} \nonumber \\
\label{eq:eam_total_energy}
= & \sum_{i}^{N}{F_{a}(\rho_i)} + 
    \frac{1}{2}\sum_{i}^{N}{\sum_{j \neq i}^{r_{ij} < r_c}{
    \phi_{ab}(r_{ij})
}}
\end{align}
where $r_c$ is the cutoff radius, $a$ and $b$ represents species of atoms $i$ 
and $j$, $\phi_{ab}(r_{ij})$ is energy of the pairwise interaction between $i$ 
and $j$, $F_{a}(\rho_{i})$ is the embedding energy and $\rho_{i}$ is the local 
electron density. Typically, $\rho_{i}$ can be calculated with the following 
equation:
\begin{equation}
\label{eq:rho_eam}
\rho_{i} = \sum_{j}^{r_{ij} < r_{c}}{
    \rho_{b}(r_{ij})
}
\end{equation}
where $\rho_{b}$ is the electron density function of specie $b$. In the 
Finnis-Sinclair model, the electron density has a slightly modified form:
\begin{equation}
\label{eq:rho_fs}
\rho_{i}^{\mathrm{FS}} = \sum_{j}^{r_{ij} < r_{c}}{
    \rho_{ab}(r_{ij})
}
\end{equation}

The original EAM potential does not inlcude angular-dependent interactions. To 
fix this problem, Baskes modified the original EAM and got MEAM (modified 
embedded-atom method), Lenosky proposed an alternative spline-based interpretion 
of MEAM  while Mishin developed the angular-dependent potential (ADP). The ADP 
formalism introduces three additional terms to the total energy:
\begin{align}
\label{eq:adp}
E^{total} 
& = E^{\mathrm{EAM}} \nonumber \\
& + \frac{1}{2}\sum_{i}{\sum_{\alpha}{(\mu_{i}^{\alpha})^2}} \nonumber \\
& + \frac{1}{2}\sum_{i}{
    \sum_{\alpha}{\sum_{\beta}{(\lambda_{i}^{\alpha\beta})^2}}} \nonumber \\
& - \frac{1}{6}\sum_{i}{\nu_{i}^{2}}
\end{align}
These terms represent non-central bonding contributions and they can be computed
with the following equations:
\begin{align}
\label{eq:adp_mu}
\mu_{i}^{\alpha} & = \sum_{j \neq i}{\mu_{ab}(r_{ij}) r_{ij}^{\alpha}} \\
\label{eq:adp_lambda}
\lambda_{i}^{\alpha\beta} & = \sum_{j \neq i}{
    \omega_{ab}(r_{ij}) r_{ij}^{\alpha}r_{ij}^{\beta}} \\
\label{eq:adp_nu}
\nu_{i} & = \sum_{\alpha}{\lambda_{i}^{\alpha\alpha}}
\end{align}
where $\mu_{ab}(r)$ and $\omega_{ab}(r)$ can be viewed as measures of the 
strengths of dipole and quadrupole interactions.

In this work, we use the EAM potential published by Zhou, Johnson and Wadley 
(Zjw04) as an example to validate our machine learning approach. Zjw04 is a 
quite popular EAM potential and it is applicable to a number of metals and 
alloys. In the Zjw04 model, the electron density function has the following 
form:
\begin{equation}
\label{eq:zjw04_rho}
\rho_{b}(r) = \frac{
    f_{e} \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]
}{
    1 + \left(r/r_{e} - \lambda\right)^{20}
}
\end{equation}
where $r_e$ is a constant equal to equilibrium spacing between nearest neighors, 
$f_{e}$, $\beta$, $\lambda$ are adjustable parameters. The pairwise potential 
between the same species can be computed with:
\begin{equation}
\label{eq:zjw04_phi_aa}
\phi_{aa}(r) = 
\frac{A \exp\left[ -\alpha\left( r/r_{e} - 1 \right) \right]}
     {1 + \left(r / r_{e} - \kappa\right)^{20}} - 
\frac{B \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]}
     {1 + \left(r / r_{e} - \lambda\right)^{20}}
\end{equation}
where $A$, $\alpha$ and $\kappa$ are also trainable parameters, $B$, $\beta$ and 
$\kappa$ are used in Equation \ref{eq:zjw04_rho} already. For the pairwise 
interaction between two atoms of different species, Zhou et al proposed an 
interpolation form:
\begin{equation}
\label{eq:zjw04_phi_ab}
\phi_{ab}(r) = \frac{1}{2}\left(
    \frac{\rho_{b}(r)}{\rho_{a}(r)}\phi_{aa}(r) +
    \frac{\rho_{a}(r)}{\rho_{b}(r)}\phi_{bb}(r) 
\right)
\end{equation}
The embedding function has a more complicated form as it requires to fit a much 
wider range of electron density values:
\begin{equation}
\label{eq:zjw04_embed}
F(\rho) = \begin{cases}
    \sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} &
    \rho < \rho_{n} \\
    \sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} &
    \rho_{n} \leq \rho < \rho_{0} \\
    F_{e}\left[ 
        1 - \eta\ln\left( \frac{\rho}{\rho_s}\right) 
    \right](\frac{\rho}{\rho_s})^{\eta} & \rho_{0} \leq \rho
\end{cases}
\end{equation}
where $F_{ni}$, $F_{i}$, $\rho_e$, $\rho_s$, $\eta$ and $F_{e}$ are trainable 
parameters, $\rho_n=0.85\rho_e$ and $\rho_0=1.15\rho_e$. For each metal, there 
are 15 adjustable parameters. The original embedding potential is a stepwise 
function. Thus, the minimization requires some tricks to ensure its continuity.
To make it simpler, we slightly modified Equation \ref{eq:zjw04_embed}:
\begin{align}
\label{eq:zjw04xc_embed}
F(\rho) 
= & c_1 \cdot
\sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} \nonumber \\
+ & c_2 \cdot 
\sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} \nonumber \\
+ & c_3 \cdot
F_{e}\left[1 - \eta\ln\left( \frac{\rho}{\rho_s}\right)\right]
(\frac{\rho}{\rho_s})^{\eta} \\
\label{eq:frho_c1}
c_{1} = & \frac{1}{1 + e^{-2\left(\rho_{n} - \rho\right)}} \\
\label{eq:frho_c3}
c_{3} = & \frac{1}{1 + e^{-2\left(\rho - \rho_{0}\right)}} \\
c_{2} = & 1 - c_1 - c_3
\end{align}
The new equation can be minimized without considering about boundary continuity.
$\omega_1$ and $\omega_3$ are just damping factors calculated by the sigmoid 
functions (Equations \ref{eq:frho_c1} and \ref{eq:frho_c3}).

The dipole ($\mu_{ab}$) and quadrupole ($\lambda_{ab}$) functions have the same 
form (developed by Mishin):
\begin{align}
\label{eq:adp_dipole}
\mu_{ab}(r) & = \left[
    d_{1}^{ab} \exp\left( -d_{2}^{ab}r \right) + d_{3}^{ab}
\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right) \\
\omega_{ab}(r) & = \left[
    q_{1}^{ab} \exp\left( -q_{2}^{ab}r \right) + q_{3}^{ab}
\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right)
\end{align}
where $d_{i}$, $q_{i}$, $r_0$ and $r_{h}$ are trainable parameters and $\psi(x)$
is a damping function:
\begin{equation}
\label{eq:mishin_cutoff}
\psi(x) = \begin{cases}
    0 & x \ge 0 \\
    \frac{x^4}{1 + x^4} & x < 0 
\end{cases}
\end{equation}

% -----------
% Section 2.2 Transformation
% -----------
\subsection{Transformation}
\label{sec:transformation}

To integrate EAM/ADP with machine learning, the original total energy expression 
(Equation \ref{eq:eam_total_energy}) must be transformed to a vectorizable form. 
Without loss of generality, we take a binary alloy, AB, to demonstrate how to 
derive this equation.

\newcommand{\niaa}{N_{i}^{\mathrm{AA}}}
\newcommand{\niab}{N_{i}^{\mathrm{AB}}}
\newcommand{\nibb}{N_{i}^{\mathrm{BB}}}
\newcommand{\niba}{N_{i}^{\mathrm{BA}}}
\newcommand{\riaa}{\vec{\mathbf{r}}_{i}^{\mathrm{AA}}}
\newcommand{\riab}{\vec{\mathbf{r}}_{i}^{\mathrm{AB}}}
\newcommand{\ribb}{\vec{\mathbf{r}}_{i}^{\mathrm{BB}}}
\newcommand{\riba}{\vec{\mathbf{r}}_{i}^{\mathrm{BA}}}
\newcommand{\namax}{N_{\mathrm{A}}^{\mathrm{max}}}
\newcommand{\nbmax}{N_{\mathrm{B}}^{\mathrm{max}}}
\newcommand{\nnl}{N_{\mathrm{nl}}}

The energy of atom $i$ of specie $A$ can be calculated with the following 
expanded equation (the cutoff radius $r_c$ is fixed):
\begin{align}
\label{eq:e_atom_phase_1}
E_{i}^{A} 
= & 
\frac{1}{2}\sum_{j\neq i}^{\niaa}\phi_{\mathrm{AA}}(r_{ij}) +
\frac{1}{2}\sum_{j\neq i}^{\niab}\phi_{\mathrm{AB}}(r_{ij}) \nonumber \\
+ & F_{\mathrm{A}}\left(
    \sum_{j\neq i}^{\niaa}{\rho_{\mathrm{A}}(r_{ij})} +
    \sum_{j\neq i}^{\niab}{\rho_{\mathrm{B}}(r_{ij})} 
\right)
\end{align}
where $\niaa$ represents the number of neighors of specie $A$ of atom $i$ and 
$\niab$ represents the number of neighors of specie $B$. $E_{i}^{B}$ has a 
similar expression. For each atom, we can calculate its $\niaa$ and $\niab$. 
Thus, we can find the maximum neighor list size $\nnl$:
\begin{equation}
\label{eq:nnl}
\nnl = \max{\left(
    \max\left({\niaa}\right), 
    \max\left({\niab}\right),
    \max\left({\nibb}\right)
\right)}
\end{equation}
$\nnl$ is a constant during training because both the dataset and $r_c$ are 
fixed.

Assume $H(x)$ represents the heaviside step function:
\begin{equation}
\label{eq:heaviside}
H(x) = \begin{cases}
    1 & x > 0 \\
    0 & x \leq 0 \\
\end{cases}
\end{equation}
Then,
\begin{align}
\sum_{j\neq i}^{\niaa}\phi_{\mathrm{AA}}(r_{ij}) = &
\sum_{j\neq i}^{\niaa}\phi_{\mathrm{AA}}(r_{ij}) \cdot 1 + 
\sum_{j\neq i}^{\nnl - \niaa}\phi_{\mathrm{AA}}(0) \cdot 0 \nonumber \\
= & \phi_{\mathrm{AA}}(\vec{\mathbf{r}}_{i}^{\mathrm{AA}})^T
H(\vec{\mathbf{r}}_{i}^{\mathrm{AA}})
\end{align}
where $\vec{\mathbf{r}}_{i}^{\mathrm{AA}}$ is a $\nnl$-length column vector 
whose last $\nnl - \niaa$ elements are padding zeros.

We can write Equation \ref{eq:e_atom_phase_1} in an equivalent expression:
\begin{align}
E_{i}^{\mathrm{A}} 
\label{eq:e_atom_A}
= &
\frac{1}{2}\left( 
    \phi_{\mathrm{AA}}(\vec{\mathbf{r}}_{i}^{\mathrm{AA}})^T
    H(\vec{\mathbf{r}}_{i}^{\mathrm{AA}}) +
    \phi_{\mathrm{AB}}(\vec{\mathbf{r}}_{i}^{\mathrm{AB}})^T
    H(\vec{\mathbf{r}}_{i}^{\mathrm{AB}})
\right) \nonumber \\
+ &
F_{\mathrm{A}}\left( 
    \rho_{\mathrm{AA}}(\vec{\mathbf{r}}_{i}^{\mathrm{AA}})^T
    H(\vec{\mathbf{r}}_{i}^{\mathrm{AA}}) +
    \rho_{\mathrm{AB}}(\vec{\mathbf{r}}_{i}^{\mathrm{AB}})^T
    H(\vec{\mathbf{r}}_{i}^{\mathrm{AB}})
\right)
\end{align}
Here $\vec{\mathbf{r}}_{i}^{\mathrm{AB}}$ is also a $\nnl$-length vector. For 
atom $j$ of specie $B$, we can also derive its energy $E^{\mathrm{B}}_{j}$:
\begin{align}
E_{j}^{\mathrm{B}}
\label{eq:e_atom_B}
= &
\frac{1}{2}\left( 
    \phi_{\mathrm{BB}}(\vec{\mathbf{r}}_{j}^{\mathrm{BB}})^T
    H(\vec{\mathbf{r}}_{j}^{\mathrm{BB}}) +
    \phi_{\mathrm{BA}}(\vec{\mathbf{r}}_{j}^{\mathrm{BA}})^T
    H(\vec{\mathbf{r}}_{j}^{\mathrm{BA}})
\right) \nonumber \\
+ &
F_{\mathrm{A}}\left( 
    \rho_{\mathrm{BB}}(\vec{\mathbf{r}}_{j}^{\mathrm{BB}})^T
    H(\vec{\mathbf{r}}_{j}^{\mathrm{BB}}) +
    \rho_{\mathrm{BA}}(\vec{\mathbf{r}}_{j}^{\mathrm{BA}})^T
    H(\vec{\mathbf{r}}_{j}^{\mathrm{BA}})
\right)
\end{align}

Since $\riaa$, $\riab$, $\ribb$ and $\riba$ all have the same length ($\nnl$), 
we can use a (redundant) matrix, $\mathbf{g}_{i}$, to describe all neighbors of 
atom $i$:
\begin{equation}
\mathbf{g}_i = \begin{bmatrix}
    \riaa & \riab & \ribb & \riba \\
\end{bmatrix}
\end{equation}
$\mathbf{g}_i$ is a $\nnl \times 4$ matrix. If the specie of atom $i$ is A, only
the first two columns have non-zero values. Similarly, the last two columns will
have non-zeros values if atom $i$ is a B-type atom. In fact, $\mathbf{g}_i$ can
be viewed as the EAM descriptors for atom $i$. Hence, each structure can be 
expressed with a 3D matrix, $\mathbf{G}$ , of shape $N \times \nnl \times 4$.

During the training phase, the maximum appearances of element A and B in any 
structure ($\namax$ and $\nbmax$) are also constants. Thus, any $\mathbf{G}$ can 
be expanded to a $(\namax + \nbmax) \times \nnl \times 4$ matrix, $\mathbf{G}'$, 
with zero-padding. As $\mathbf{G}'$ is a fixed-shape matrix and $\rho(r)$, 
$\phi(r)$ and $F(\rho)$ are all elementwise functions, we can use any modern 
machine learning platform (TensorFlow, PyTorch, MXNet, etc) to implement the EAM 
model. In this paper, we chose TensorFlow as our coding framework. Based on the 
virtual atom approach, we successfully designed a route to build the machine 
learning computation graph directly from positions to total energy. Thus, 
analytically-derived EAM force and virial stress can be calculated without pain.
\begin{align}
\label{eq:forces}
f_{i} = & -\frac{\partial E^{total}}{\partial r_{i}} \\
\label{eq:stress}
V \cdot \epsilon = & -\mathbf{F}^{T}\mathbf{R} + \left(
    \frac{\partial E^{total}}{\partial \mathbf{h}}
\right)^T \mathbf{h}
\end{align}
where $V$ is the volume, $\epsilon$ is the $3 \times 3$ virial stress tensor, 
$\mathbf{h}$ is the \textit{row-major} $3 \times 3$ lattice tensor, $\mathbf{F}$ 
and $\mathbf{R}$ are $N \times 3$ matrices representing the total forces and 
atomic positions. 
The derivation of Equation \ref{eq:stress} has been published elsewhere. The 
details of the virtual atom approach can be found in the appendix. The last step 
is to find optimal parameters. This can be done by minimizing the mini-batch 
loss function:
\begin{align}
\label{eq:loss}
\mathbf{Loss} & = \sqrt{\frac{1}{N_{b}}\sum_{i=1}^{N_{b}}{\left(
    E_{i} - E_{i}^{\mathrm{dft}}
\right)^2}} \nonumber \\
& + \chi_{\mathrm{f}}\sqrt{
    \frac{1}{3\sum_{i}^{N_{b}}{N_i}}\sum_{i}^{N_b}{\sum_{j}^{N_i}{
        \sum_{\alpha}{
            \left(f_{ij\alpha} - f_{ij\alpha}^{\mathrm{dft}}\right)^2
        }
    }}
} \nonumber \\
& + \chi_{\mathrm{s}}\sqrt{\frac{1}{6N_b}\sum_{i}^{N_b}{
    \sum_{j}^{6}{
        \left(
            \epsilon^{\mathrm{voigt}}_{j} - \epsilon^{\mathrm{voigt,dft}}_{j}
        \right)^2
    }
}} 
\end{align} 
where $N_{b}$ is the batch size and $N_i$ is the number of atoms in structure 
$i$. The superscript 'voigt' means that stress tensors should be converted to 
Voigt form. The Adam optimizer is used to minimize Equation \ref{eq:loss}. 
In most cases, we use 0.01 as the initial learning rate and the batch size 
ranges from 20 to 50.

% -----------
% Section 2.3 Implementation
% -----------
\subsection{Implementation}
\label{sec:implementation}

% -----------
% Section 2.4 Constraints
% -----------
\subsection{Constraints}
\label{sec:constraints}

The Rose constraint incoporates the universal equation of state (Rose et al) 
into the total loss function. The Mishin-modified equation 
\begin{equation}
\label{eq:rose_eos}
E(y) = E_{0}\left[
    1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
    e^{-\alpha x}
\end{equation}
is used because the original form tends to underestimate energies under high 
pressures. In Equation \ref{eq:rose_eos}, $E_{0}$ is the energy of the 
equilibrium structure, $x = a / a_{0} - 1$ is the relative isotropic scaling 
factor ($a$ is the lattice constant), $\beta$ is a chosen parameter and 
\begin{equation}
\label{eq:rose_alpha}
\alpha = \sqrt{-\frac{9 V_{0} B }{E_{0}}}
\end{equation}
where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
of the Rose constraint guarantees the exact prediction of the bulk modulus and 
the energy-volume curve. The loss of the Rose EOS constraint 
$\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
differences between $E(x)^{\mathrm{Rose}}$ and their corresponding predicted 
$E(x)$: 
\begin{equation}
\label{eq:rose_loss}
\mathbf{L}^{\mathrm{Rose}} =
\sum_{i}{\mathbf{RMSE}(E_{i}(x), E_{i}(x)^{\mathrm{Rose}})}
\end{equation}

In this work, for each included crystal, we use the same choices of $x$: 
$x_{t} = x_{0} + \Delta x \cdot t, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
\Delta x=0.01$.

Elastic constraints are common metrics for tuning empirical potentials. In the
ML framework, fitting elastic constants of specific crystals is also possible.
The elastic constant $c_{ijkl}$ can be derived from $E^{total}$ directly:
\begin{equation}
\label{eq:cijkl}
c_{ijkl} |_{\epsilon \to 0, \mathbf{F} \to 0} = \frac{1}{V}\left[
    \left( 
        \frac{\partial{\epsilon_{ij}}}{\partial{\mathbf{h}}}
    \right)^{\mathrm{T}}\mathbf{h}
\right]_{kl}
\end{equation}
In this work, the loss $\mathbf{L}^{\mathrm{elastic}}$ contributed by the 
elastic constraint is also measured by the RMSE between $c_{ijkl}$ and 
$c_{ijkl}^{\mathrm{dft}}$:
\begin{align}
\label{eq:cijkl_loss}
\mathbf{L}^{\mathrm{elastic}} 
& = \sum_{i}{c_{i} \cdot \mathbf{RMSE_{i}} + {|\epsilon|} + {|\mathbf{F}|}} \\
\label{eq:cijkl_loss_gate}
c_{i} & = \mathbf{ReLU}(\mathbf{MAE_{i}} - \tau) \\
\label{eq:relu}
\mathbf{ReLU}(x) & = \begin{cases}
    x & x \ge 0 \\
    0 & x < 0
\end{cases}
\end{align}
where $\sum_{i}$ loops through all included crystals, $\mathbf{MAE}$ is the mean 
absolute error and $\tau$ is a pre-selected gate parameter. When $\mathbf{MAE}$ 
is below $\tau$, $\mathbf{L}^{\mathrm{elastic}}$ will not contribute to the 
total loss. In this work, $\tau$ is set to 1 GPa.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 3. Results
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Results and Discussions}
\label{sec:results}

The publicly available Ni-Mo dataset is use to demonstrate our ML-EAM approach. 
This dataset is built by Shyue Ping Ong and co-workers. It contains 3973 unique
Ni-Mo solids, including 373 elemental Ni and 284 elemental Mo. DFT calculations 
were done by VASP at the PBE level with projector augmented-wave approach.

Table \ref{table:parameters} shows the optimization results. All these 
minimization tasks include energy, force and stress terms in their total losses.
The $\chi_{\mathrm{f}}$ in Equation \ref{eq:loss} is set to 10 and 
$\chi_{\mathrm{s}}$ is fixe to 80. In this paper, the superscript tag 'old' 
denotes the original Zjw04, 'res' means restricted optimization and 'unres' 
means unrestricted optimization. Here 'unrestricted' indicates the parameter 
$r_e$ will be treated as a common adjustable variable.

Table \ref{table:MAE} demonstrates the prediction errors of the machine learned
EAM models and reference models.

\begin{table*}[h]
\centering
\begin{tabular}{lcccccccc}
\hline
    & Ni$^{\mathrm{old}}$ & Ni & Ni$^{\mathrm{alloy}}$ 
    & Mo$^{\mathrm{old}}$ & Mo & Mo$^{\mathrm{alloy}}$ \\
\hline
$r_e$ & 2.488746 & 2.124480 & & 2.728100 & & \\
$f_e$ & 2.007018 & 2.633256 & & 2.723710 & & \\
$\rho_e$ & 27.562015 & 27.233315 & \\ 
$\rho_s$ & 27.930410 & 26.392414 &\\
$\alpha$ & 8.383453 & 8.452753 & \\
$\beta$ & 4.471175 & 3.285651 & \\
$A$ & 0.429046 & 0.9802988 & \\
$B$ & 0.633531 & 0.8919016 & \\
$\kappa$ & 0.443599 & 0.5685785 & \\
$\lambda$ & 0.820658 & 1.1653832 & \\
$F_{n0}$ & -2.693513 & -3.4354472 & \\
$F_{n1}$ & -0.076445 & 0.3544341 & \\
$F_{n2}$ & 0.241442 & -2.5563858 & \\
$F_{n3}$ & -2.375626 & -7.1984844 & \\
$F_{0}$ & -2.70 & -3.236908 & \\
$F_{1}$ & 0 & 1.4576268 & \\
$F_{2}$ & 0.265390 & 2.1785288 & \\
$F_{3}$ & -0.152856 & -1.642411 & \\
$\eta$ & 0.469000 & 4.305329 & \\
$F_e$ & -2.699486 & -3.6163342 & \\
\hline
\end{tabular}
\caption{\label{table:parameters} The original (labeled as 'old'), elemental and 
alloy parameters.}
\end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lcccccccc}
\hline
    & Model & Mo & Ni$_4$Mo & Ni$_3$Mo & Ni$_{\mathrm{Mo}}$ & Mo$_{\mathrm{Ni}}$ 
    & Ni & Overall \\
\hline
Energy (meV/atom) & SNAP & 16.2 & 4.0 & 5.2 & 22.7 & 33.9 & 7.9 & 22.5 \\
    & EAM & 58.9 & 211.2 & 255.6 & 46.5 & 147.6 & 10.6 & 117.2 \\
    & \color{red} ML-EAM & \color{red} 45.0 & \color{red} 10.6 
    & \color{red} 7.1 & \color{red} 39.0 & \color{red} 29.8 & \color{red} 10.4 
    & \color{red} 27.4 \\
    & NN (esf) & 30.0 & 6.1 & 9.0 & 16.6 & 26.2 & 7.8 & 19.1 \\
\hline
Force (eV/\AA) & SNAP & 0.29 & 0.14 & 0.16 & 0.13 & 0.55 & 0.11 & 0.23 \\
& EAM & 0.31 & 0.20 & 0.19 & 0.21 & 0.57 & 0.06 & 0.26 \\
& \color{red} ML-EAM & \color{red} 0.31 & \color{red} 0.17 & \color{red} 0.15 
& \color{red} 0.23 & \color{red} 0.18 & \color{red} 0.09 & \color{red} 0.17 \\
& NN (esf) & 0.36 & 0.10 & 0.11 & 0.08 & 0.16 & 0.06 & 0.12 \\
% \hline
% Stress (GPa) & Mo SNAP & \textbf{0.87} & & & & & & \\
% & Mo SFNN & 1.00 & & & & & & \\
% & Ni-Mo SFNN & 5.77 & \textbf{1.72} & 1.74 & 1.45 & 3.75 & 1.97 & 2.83 \\
% & Ni-Mo SFNN (esf) & \textbf{1.84} & 2.05 & \textbf{1.38} & \textbf{0.57} & 
%     \textbf{1.22} & \textbf{1.91} & \textbf{1.27} \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to DFT.}
\end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lccccc}
\hline
    & DFT & Ni-Mo SNAP & ML-EAM & EAM & Experiment \\
\hline
Mo \\
$c_{11}$ & 472 & 475 (0.6\%) & 477 (1.1\%) & 457 (-3.2\%) & 479 \\
$c_{12}$ & 158 & 163 (3.2\%) & 166 (5.1\%) & 168 (6.3\%) & 165 \\
$c_{44}$ & 106 & 111 (4.7\%) & 101 (-4.7\%) & 116 (9.4\%) & 108 \\
$B_{\mathrm{VRH}}$ & 263 & 267 (1.5\%) & 270 (2.7\%) & 264 (0.4\%) & 270 \\
$G_{\mathrm{VRH}}$ & 124 & 127 (2.4\%) & 127 (2.4\%) & 127 (2.4\%) & 125 \\
$\mu$ & 0.30 & 0.29 (-3.3\%) & 0.31 (3.3\%) & 0.29 (-3.3\%) & 0.30 \\
\hline
Ni \\
$c_{11}$ & 276 & 269 (-2.5\%) & 268 (-2.9\%) & 248 (-10.1\%) & 261 \\
$c_{12}$ & 159 & 150 (-5.7\%) & 165 (3.8\%) & 147 (-7.5\%) & 151 \\
$c_{44}$ & 132 & 135 (2.3\%) & 116 (-12.1\%) & 125 (-5.3\%) & 132 \\
$B_{\mathrm{VRH}}$ & 198 & 190 (-4.0\%) & 200 (1.0\%) & 181 (-8.6\%) & 188 \\
$G_{\mathrm{VRH}}$ & 95 & 97 (2.1\%) & 84 (-11.6\%) & 87 (-8.4\%) & 479 \\
$\mu$ & 0.29 & 0.28 (-3.4\%) & 0.31 (6.8\%) & 0.29 (0.0\%) & 0.29 \\
\hline
Ni$_3$Mo \\
$c_{11}$ & 385 & 420 (9.1\%) & 430 (11.7\%) & 195 (-49.4\%) & \\
$c_{12}$ & 166 & 197 (18.7\%) & 187 (12.7\%) & 98 (-41.0\%) & \\
$c_{13}$ & 145 & 162 (11.7\%) & 180 (24.1\%) & 98 (-32.4\%) & \\
\color{blue} $c_{23}$ & 131 & 145 (10.7\%) & 210 (60.3\%) & 107 (-18.3\%) & \\
$c_{22}$ & 402 & 360 (-10.4\%) & 457 (13.7\%) & 98 (-75.6\%) & \\
\color{blue} $c_{33}$ & 402 & 408 (-1.5\%) & 412 (2.5\%) & 295 (-26.6\%) & \\
\color{blue} $c_{66}$ & 94 & 84 (-10.5\%) & 27 (-71.3\%) & 36 (-61.7\%) & \\
$B_{\mathrm{VRH}}$ & 230 & 243 (5.7\%) & 280 (21.7\%) & 156 (-32.2\%) &  \\
$G_{\mathrm{VRH}}$ & 89 & 100 (12.4\%) & 66 (-25.8\%) & 61 (-31.5\%) & \\
$\mu$ & 0.33 & 0.32 (-3.0\%) & 0.39 (18.2\%) & 0.33 (0.0\%) & \\
\hline
Ni$_4$Mo \\
$c_{11}$ & 300 & 283 (-5.7\%) & 278 (-7.3\%) & 172 (-42.7\%) & \\
$c_{12}$ & 186 & 179 (-3.8\%) & 184 (-1.1\%) & 158 (-15.1\%) & \\
$c_{22}$ & 313 & 326 (4.2\%) & 278 (-11.2\%) & 158 (-49.5\%) & \\
\color{blue} $c_{23}$ & 166 & 164 (-1.2\%) & 230 (38.6\%) & 80 (-51.8\%) & \\
\color{blue} $c_{66}$ & 130 & 126 (-3.1\%) & 87 (-33.1\%) & 125 (-3.8\%) & \\
$B_{\mathrm{VRH}}$ & 223 & 220 (-1.3\%) & 233 (10.5\%) & 161 (-27.8\%) & \\
$G_{\mathrm{VRH}}$ & 91 & 95 (4.4\%) & 57 (37.4\%) & -156 (-162\%) & \\
$\mu$ & 0.33 & 0.31 (-6.1\%) & 0.39 (18.2\%) & 0.70 (112\%) & \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 4. Discussions
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Discussions}
\label{sec:discussions}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 5. Conclusions
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Conclusions}
\label{sec:conclusions}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Acknowlegements
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section*{Acknowledgments}
\label{sec:acknowledgments}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% References
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\bibliography{manuscript.bib}

\end{document}

### 2019-08-16 compile.py
Start creating a CPC tensoralloy.

@@ -1,105 +1,0 @@
-# coding=utf-8
-"""
-Compile the entire package to a cython static library.
-"""
-from __future__ import print_function, absolute_import
-
-import os
-import glob
-from os.path import join, isdir, splitext
-
-from distutils.core import setup
-from distutils.cmd import Command
-from setuptools import find_packages
-from distutils.extension import Extension
-from Cython.Distutils.build_ext import new_build_ext as build_ext
-
-from setup import __version__
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-# `cython (<=0.29.1)` can not handle `dataclass` or `nametuple` correctly.
-avoid_to_cythonize = [
-    'tensoralloy/transformer/indexed_slices.py',
-    'tensoralloy/descriptor/cutoff.py',
-    'tensoralloy/cli.py',
-]
-ext_modules = []
-files_to_delete = []
-packages = []
-
-
-for package in find_packages(exclude=['datasets', 'test_files', 'tools']):
-    folders = package.split('.')
-    if folders[-1] == 'tests':
-        continue
-    packages.append(package)
-    cwd = join(*folders)
-    for name in os.listdir(cwd):
-        path = join(cwd, name)
-        if path in avoid_to_cythonize:
-            continue
-        if name.startswith('.') or \
-                isdir(path) or \
-                name.endswith('.toml') or \
-                name.endswith(".so") or \
-                name.endswith('.c'):
-            continue
-        ext_modules.append(Extension(f'{package}.{splitext(name)[0]}', [path]))
-
-        files_to_delete.append(f"{splitext(path)[0]}.cpython-*.so")
-        files_to_delete.append(f"{splitext(path)[0]}.c")
-
-
-class CleanExt(Command):
-    """
-    Delete the generated .c and .so files.
-    """
-
-    description = "Delete the generated .c and .so files."
-    user_options = []
-
-    def initialize_options(self):
-        """
-        Set default values for all the options that this command supports.
-        """
-        pass
-
-    def finalize_options(self):
-        """
-        Set final values for all the options that this command supports.
-        """
-        pass
-
-    def run(self):
-        """
-        Run this command.
-        """
-        for pattern in files_to_delete:
-            paths = list(glob.glob(pattern))
-            if len(paths) == 1:
-                os.remove(paths[0])
-                print(f"Delete: {paths[0]}")
-            elif len(paths) > 1:
[…]

### 2019-08-16 doc/papers/nn/figures/cpc_speed.py

@@ -1,146 +1,0 @@
-from __future__ import print_function, absolute_import
-
-import numpy as np
-
-from matplotlib import pyplot as plt
-from matplotlib.ticker import MultipleLocator
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-workstation = """
-Number of atoms: 2000
-* ASE neighbor time: 0.5930616855621338
-* Python feed dict time: 1.5961778163909912
-* TensorFlow execution time: 0.04986286163330078
-Number of atoms: 6750
-* ASE neighbor time: 1.2973895072937012
-* Python feed dict time: 3.7827587127685547
-* TensorFlow execution time: 0.12984418869018555
-Number of atoms: 16000
-* ASE neighbor time: 3.7363853454589844
-* Python feed dict time: 9.718251943588257
-* TensorFlow execution time: 0.17889857292175293
-Number of atoms: 31250
-* ASE neighbor time: 5.931849002838135
-* Python feed dict time: 16.419432401657104
-* TensorFlow execution time: 0.3449971675872803
-Number of atoms: 54000
-* ASE neighbor time: 10.83665919303894
-* Python feed dict time: 28.86913824081421
-* TensorFlow execution time: 0.6041886806488037
-Number of atoms: 85750
-* ASE neighbor time: 19.667125940322876
-* Python feed dict time: 51.148345708847046
-* TensorFlow execution time: 0.38422513008117676
-Number of atoms: 128000
-* ASE neighbor time: 26.636351346969604
-* Python feed dict time: 70.64423513412476
-* TensorFlow execution time: 1.0043096542358398"""
-
-
-cpu_only = """Number of atoms: 2000
-* ASE neighbor time: 0.623563289642334
-* Python feed dict time: 1.633838415145874
-* TensorFlow execution time: 0.10250282287597656
-Number of atoms: 6750
-* ASE neighbor time: 1.3154628276824951
-* Python feed dict time: 3.6260945796966553
-* TensorFlow execution time: 0.32638072967529297
-Number of atoms: 16000
-* ASE neighbor time: 3.5952367782592773
-* Python feed dict time: 9.219270467758179
-* TensorFlow execution time: 0.6607975959777832
-Number of atoms: 31250
[…]

### 2019-08-16 doc/papers/nn/figures/qm7.py

@@ -1,153 +1,0 @@
-#!coding=utf-8
-from __future__ import print_function
-
-import numpy as np
-import pandas as pd
-
-from matplotlib import pyplot as plt
-from matplotlib.gridspec import GridSpec
-
-orders = [
-    ('CPU', 'Radial'), ('CPU', 'Angular'), 
-    ('GPU', 'Radial'), ('GPU', 'Angular'),
-]
-
-fig = plt.figure(figsize=[12, 10])
-grid_spec = GridSpec(2, 24)
-
-# ----------
-# Fig.A
-# ----------
-
-ax = plt.subplot(grid_spec[0, 0: 11])
-assert isinstance(ax, plt.Axes)
-
-df1 = pd.read_csv("qm7/qm7.speed.csv", index_col=0)
-speed_flatten = np.zeros((4, 4))
-batch_size_idx_map = {1: 0, 25: 1, 50: 2, 100: 3}
-
-for i, (device, sf) in enumerate(orders):
-    if device == "CPU":
-        use_cpu = True
-    else:
-        use_cpu = False
-    if sf == "Angular":
-        angular = True
-    else:
-        angular = False
-    rows = df1.loc[(df1["cpu"] == use_cpu) &
-                   (df1["angular"] == angular) &
-                   (df1["arch"] == "AtomicResNN")]
-    for _, row in rows.iterrows():
-        j = batch_size_idx_map[row.batch_size]
-        speed_flatten[i, j] = row.examples_per_sec
-
-n_groups = 5
-bar_width = 0.2
-index = np.arange(4) * 1.5
-
-ax.bar(
-    index + bar_width * 0,
-    np.array(speed_flatten[0]), 
-    bar_width, 
-    alpha=0.4, color='r', label=f"{orders[0][0]}/{orders[0][1]}")
-ax.bar(
-    index + bar_width * 1,
-    np.array(speed_flatten[2]),
-    bar_width,
-    alpha=0.4, color='g', label=f"{orders[2][0]}/{orders[2][1]}")
-ax.bar(
-    index + bar_width * 2,
-    np.array(speed_flatten[1]),
-    bar_width,
-    alpha=0.4, color='b', label=f"{orders[1][0]}/{orders[1][1]}")
-ax.bar(
-    index + bar_width * 3,
-    np.array(speed_flatten[3]),
-    bar_width,
-    alpha=0.4, color='k', label=f"{orders[3][0]}/{orders[3][1]}")
-
[…]

### 2019-08-16 tensoralloy/analysis/__init__.py

@@ -1,8 +1,0 @@
-#!coding=utf-8
-"""
-This subpackage contains routines for analyzing material properties.
-"""
-from __future__ import print_function, absolute_import
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'

### 2019-08-16 tensoralloy/analysis/fingerprints.py

@@ -1,534 +1,0 @@
-# coding=utf-8
-"""
-This script implements Oganov's Fingerprints and the similarity kernel.
-
-The code is (probably) written by Lasse B. Vilhelmsen.
-"""
-
-from __future__ import print_function
-
-import numpy as np
-
-from itertools import product, combinations_with_replacement
-from math import erf, sqrt
-from copy import copy
-from typing import Union, List
-
-
-class FingerprintsComparator:
-    """
-    Implementation of structural similarity comparison based on Oganov's
-    fingerprint function:
-
-    * http://dx.doi.org/10.1063/1.3079326
-    * http://dx.doi.org/10.1016/j.cpc.2010.06.007
-
-    The advantages of cosine distances are that (1) they can only take values
-    between 0 and 1, enabling universal distance criteria (e.g. 0.01 – very
-    small distance, 0.20 – large, 0.5 – very large distance) and (2) cosine
-    distances are less affected by the “distance concentration effects” that
-    generally create trouble in multidimensional spaces.
-
-    """
-
-    def __init__(self, atomic_numbers: Union[List[int], np.ndarray], n_top=None,
-                 cell=None, dE=1.0, cos_dist_max=5e-3, rcut=20., binwidth=0.05,
-                 pbc=(True, True, True), maxdims=(0, 0, 0), sigma=0.025,
-                 nsigma=4):
-        """
-        Initialization method.
-
-        Parameters
-        ----------
-        atomic_numbers : array_like
-            The ordered atomic numbers of ths system.
-        n_top : int
-            The number of atoms to optimize (everything except the substrate).
-        dE : float
-            Energy difference above which two structures are automatically
-            considered to be different.
-        cell : np.ndarray
-            The base cell matrix to use.
-        cos_dist_max : float
-            The maximal cosine distance between two structures in order to
-            be still considered the same structure.
-        rcut : float
-            The cut-off radius for the fingerprints.
-        binwidth : float
-            Width of the bins over which the fingerprints are discretized.
-        pbc: List[bool]
-            Conditions (PBC) along each of the three unit cell vectors
-            when calculating the fingerprint.
-
-            Note: for isolated systems (pbc = [False,False,False]), the pair
-            correlation function itself is always short-ranged (i.e. decays to
[…]

### 2019-08-16 tensoralloy/analysis/phonon.py

@@ -1,245 +1,0 @@
-# coding=utf-8
-"""
-This module defines a custom implementation of `phonopy.Phonopy`.
-"""
-from __future__ import print_function, absolute_import
-
-import matplotlib.pyplot as plt
-import numpy as np
-
-from phonopy import Phonopy as base_Phonopy
-from phonopy.phonon import band_structure
-from phonopy import __version__ as phonopy_version
-from mpl_toolkits.axes_grid1 import ImageGrid
-from matplotlib.ticker import MultipleLocator
-from typing import List
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def print_phonopy():
-    """
-    Print the phonopy logo.
-    """
-    print(r"""        _
-  _ __ | |__   ___  _ __   ___   _ __  _   _
- | '_ \| '_ \ / _ \| '_ \ / _ \ | '_ \| | | |
- | |_) | | | | (_) | | | | (_) || |_) | |_| |
- | .__/|_| |_|\___/|_| |_|\___(_) .__/ \__, |
- |_|                            |_|    |___/""")
-
-
-# noinspection PyUnresolvedReferences
-def print_phonopy_version():
-    """
-    Print phonopy version.
-    """
-    version = phonopy_version
-    version_text = ('%s' % version).rjust(44)
-    try:
-        import pkg_resources
-        dist = pkg_resources.get_distribution("phonopy")
-        if dist.has_version():
-            ver = dist.version.split('.')
-            if len(ver) > 3:
-                rev = ver[3]
-                version_text = ('%s-r%s' % (version, rev)).rjust(44)
-    except ImportError:
-        pass
-    except Exception as err:
-        if (err.__module__ == 'pkg_resources' and
-                err.__class__.__name__ == 'DistributionNotFound'):
-            pass
-        else:
-            raise
-    finally:
-        print(version_text)
-
-
-class BandStructure(band_structure.BandStructure):
-    """
-    A customized `BandStructure` class.
-    """
-
-    def plot(self, ax: ImageGrid, labels=None, path_connections=None,
-             is_legacy=False, use_wavenumber=False, plot_vertical_lines=False):
-        r"""
-        The plot function.
-
-        Parameters
-        ----------
-        ax : ImageGrid
-            The `ImageGrid` instance for plotting this band.
-        labels : None or List[str]
-            A list of str as the labels of the high-symmetry positions.
-            For example `['$\Gamma$', '$\mathrm{X}$']`.
[…]

### 2019-08-16 tensoralloy/cli/compute.py

@@ -1,551 +1,0 @@
-#!coding=utf-8
-"""
-Command-line programs under the `compute` scope.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import pandas as pd
-import tensorflow as tf
-import argparse
-import glob
-import os
-import warnings
-
-from os.path import dirname, join, basename, exists
-from ase.build import bulk
-from ase.io import read
-from ase.units import GPa
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy import TensorAlloyCalculator, InputReader, TrainingManager
-from tensoralloy.analysis.elastic import get_lattice_type
-from tensoralloy.analysis.elastic import get_elementary_deformations
-from tensoralloy.analysis.elastic import get_elastic_tensor
-from tensoralloy.analysis.eos import EquationOfState
-from tensoralloy.cli.cli import CLIProgram
-from tensoralloy.nn.constraint.data import read_external_crystal
-from tensoralloy.precision import precision_scope
-from tensoralloy.utils import Defaults
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class ComputeMetricsProgram(CLIProgram):
-    """
-    A collection of programs for computing advanced evaluation metrics.
-    """
-
-    def __init__(self):
-        """
-        Initiazliation method.
-        """
-        super(ComputeMetricsProgram, self).__init__()
-
-        self._programs = [
-            ComputeEvaluationPercentileProgram(),
-            EquationOfStateProgram(),
-            ComputeElasticTensorProgram(),
-        ]
-
-    @property
-    def name(self):
-        """
-        The name of this CLI program.
-        """
-        return "compute"
-
-    @property
-    def help(self):
-        """
-        The help message
-        """
-        return "Compute advanced evaluation metrics."
-
-    def config_subparser(self, subparser: argparse.ArgumentParser):
-        """
-        Config the subparaser.
-        """
-        subsubparsers = subparser.add_subparsers(title=self.name,
-                                                 help=self.help)
-        for prog in self._programs:
-            subsubparser = subsubparsers.add_parser(prog.name, help=prog.help)
-            prog.config_subparser(subsubparser)
-        super(ComputeMetricsProgram, self).config_subparser(subparser)
-
-    @property
-    def main_func(self):
-        """ The main function. This is just a program-collection, so this
-        function is empty. """
-        def func(_):
-            pass
[…]

### 2019-08-16 tensoralloy/descriptor/eam.py

@@ -1,272 +1,0 @@
-# coding=utf-8
-"""
-This module implements the Embedded-atom method.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import tensorflow as tf
-
-from collections import Counter
-from typing import List
-
-from tensoralloy.descriptor.base import AtomicDescriptor
-from tensoralloy.utils import get_elements_from_kbody_term, AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-__all__ = ["EAM", "BatchEAM"]
-
-
-class EAM(AtomicDescriptor):
-    """
-    A tensorflow based implementation of Embedded Atom Method (EAM).
-    """
-
-    gather_fn = staticmethod(tf.gather)
-
-    def __init__(self, rc: float, elements: List[str]):
-        """
-        Initialization method.
-
-        Parameters
-        ----------
-        rc : float
-            The cutoff radius.
-        elements : List[str]
-            A list of str as the ordered elements.
-
-        """
-        super(EAM, self).__init__(rc, elements, k_max=2, periodic=True)
-
-        kbody_index = {}
-        for kbody_term in self._all_kbody_terms:
-            center = get_elements_from_kbody_term(kbody_term)[0]
-            kbody_index[kbody_term] = \
-                self._kbody_terms[center].index(kbody_term)
-
-        self._max_n_terms = max(map(len, self._kbody_terms.values()))
-        self._kbody_index = kbody_index
-        self._graph_scope_name = "EAM"
-
-    def _get_g_shape(self, placeholders):
-        """
-        Return the shape of the descriptor matrix.
-        """
-        return [self._max_n_terms,
-                placeholders.n_atoms_plus_virt,
-                placeholders.nnl_max]
-
-    def _get_v2g_map(self, placeholders, **kwargs):
-        """
-        A wrapper function to get `v2g_map` or re-indexed `v2g_map`.
-        """
-        splits = tf.split(placeholders.v2g_map, [-1, 1], axis=1)
-        v2g_map = tf.identity(splits[0], name='v2g_map')
-        v2g_mask = tf.identity(splits[1], name='v2g_mask')
-        return v2g_map, v2g_mask
-
-    def _get_row_split_sizes(self, placeholders):
-        """
-        Return the sizes of the rowwise splitted subsets of `g`.
-        """
-        return placeholders.row_splits
-
-    @staticmethod
-    def _get_row_split_axis():
-        """
[…]

### 2019-08-16 tensoralloy/descriptor/meam.py

@@ -1,351 +1,0 @@
-#!coding=utf-8
-"""
-The Modified Embedded-Atom Method (Lenosky Style) descriptor.
-
-Notes
------
-The Baskes derived 1NN/2NN MEAM is not suitable for this project.
-
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from typing import List
-
-from tensoralloy.descriptor.base import AtomicDescriptor
-from tensoralloy.descriptor.cutoff import meam_cutoff
-from tensoralloy.utils import AttributeDict, get_elements_from_kbody_term
-from tensoralloy.utils import GraphKeys
-from tensoralloy.precision import get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class MEAM(AtomicDescriptor):
-    """
-    A tensorflow based implementation of Modified Embedded-Atom Method (MEAM).
-
-    References
-    ----------
-    Modelling Simul. Mater. Sci. Eng. 8 (2000) 825–841.
-    Computational Materials Science 124 (2016) 204–210.
-
-    """
-
-    gather_fn = staticmethod(tf.gather)
-
-    def __init__(self, rc: float, elements: List[str], angular_rc_scale=1.0):
-        """
-        Initialization method.
-
-        Parameters
-        ----------
-        rc : float
-            The cutoff radius.
-        elements : List[str]
-            A list of str as the ordered elements.
-        angular_rc_scale : float
-            The scaling factor of `rc` for angular interactions.
-
-        """
-        super(MEAM, self).__init__(rc, elements, k_max=3, periodic=True)
-
-        self._angular_rc_scale = angular_rc_scale
-        self._angular_rc = rc * angular_rc_scale
-
-        kbody_index = {}
-        for kbody_term in self._all_kbody_terms:
-            atom_types = get_elements_from_kbody_term(kbody_term)
-            center = atom_types[0]
-            kbody_index[kbody_term] = \
-                self._kbody_terms[center].index(kbody_term)
-
-        self._max_n_terms = max(map(len, self._kbody_terms.values()))
-        self._kbody_index = kbody_index
-
-        angular_kbody_terms = []
-        for symboli in self._elements:
-            for symbolj in self._elements:
-                for symbolk in self._elements:
-                    angular_kbody_terms.append(f'{symboli}{symbolj}{symbolk}')
-
[…]

### 2019-08-16 tensoralloy/descriptor/tests/__init__.py

@@ -1,4 +1,0 @@
-from __future__ import print_function, absolute_import
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'

### 2019-08-16 tensoralloy/extension/__init__.py

@@ -1,8 +1,0 @@
-#!coding=utf-8
-"""
-C/C++ extensions for tensoralloy.
-"""
-from __future__ import print_function, absolute_import
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'

### 2019-08-16 tensoralloy/extension/interp/__init__.py

@@ -1,6 +1,0 @@
-from __future__ import print_function, absolute_import
-
-from tensoralloy.extension.interp import build_ext
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'

### 2019-08-16 tensoralloy/extension/interp/build_ext.py

@@ -1,281 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Compile the cpp codes.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import os
-import re
-import sys
-import glob
-import copy
-import subprocess
-import setuptools
-
-from os.path import join, dirname
-from setuptools.command.build_ext import build_ext
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-__all__ = ["BuildExtension", "CppExtension", 'CUDAExtension',
-           "get_interp_extension"]
-
-
-def get_interp_extension() -> setuptools.Extension:
-    """
-    Construct an external op.
-    """
-    path = join(dirname(__file__), "src")
-    cpp_files = glob.glob(join(path, "*.cc"))
-    cuda_files = glob.glob(join(path, "*.cu"))
-
-    flags = []
-    if sys.platform == "darwin":
-        flags += ["-mmacosx-version-min=10.9"]
-    ext_name = f"tensoralloy.extension.interp.cubic_op"
-
-    if tf.test.is_built_with_cuda() and len(cuda_files):
-        flags.append("-DGOOGLE_CUDA=1")
-        return CUDAExtension(
-            ext_name,
-            cpp_files + cuda_files,
-            include_dirs=[path, "include"],
-            extra_compile_args={
-                "cxx": flags,
-                "nvcc": flags + ["--expt-relaxed-constexpr"],
-            },
-            extra_link_args=flags,
-        )
-
-    return CppExtension(
-        ext_name,
-        cpp_files,
-        include_dirs=[path, "include"],
-        extra_compile_args=flags,
-        extra_link_args=flags,
-    )
-
-
-def _find_cuda_home():
-    """
-    Finds the CUDA install path.
-    """
-    # Guess #1
-    cuda_home = os.environ.get('CUDA_HOME') or os.environ.get('CUDA_PATH')
-    if cuda_home is None:
-        # Guess #2
-        if sys.platform == 'win32':
-            cuda_home = glob.glob(
-                'C:/Program Files/NVIDIA GPU Computing Toolkit/CUDA/v*.*')
-        else:
-            cuda_home = '/usr/local/cuda'
-        if not os.path.exists(cuda_home):
-            # Guess #3
-            try:
-                which = 'where' if sys.platform == 'win32' else 'which'
-                nvcc = subprocess.check_output(
[…]

### 2019-08-16 tensoralloy/extension/interp/solver.py

@@ -1,52 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-The solver function.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensoralloy.extension.interp.utils import load_op_library
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-__all__ = ["tri_diag_solve"]
-
-
-try:
-    ops = load_op_library("cubic_op")
-except Exception:
-    ops = None
-
-
-def tri_diag_solve(diag, upper, lower, y, **kwargs):
-    """
-    Solve the tri-diagonal matrix system Ax = y.
-    """
-    return ops.tri_diag_solve(diag, upper, lower, y, **kwargs)
-
-
-@tf.RegisterGradient("TriDiagSolve")
-def _tri_diag_solve_grad(op, *grads):
-    """
-    The corresponding gradient op.
-    """
-    diag, upper, lower, y = op.inputs
-    x = op.outputs[0]
-    bx = grads[0]
-    by = ops.tri_diag_solve(diag, lower, upper, bx)
-    axes = tf.range(tf.rank(diag), tf.rank(y))
-    bdiag = -tf.reduce_sum(x * by, axis=axes)
-
-    n_inner = tf.shape(diag)[-1]
-    axis = tf.rank(diag) - 1
-    bupper = -tf.reduce_sum(
-        tf.gather(x, tf.range(1, n_inner), axis=axis) *
-        tf.gather(by, tf.range(n_inner-1), axis=axis),
-        axis=axes)
-    blower = -tf.reduce_sum(
-        tf.gather(x, tf.range(n_inner-1), axis=axis) *
-        tf.gather(by, tf.range(1, n_inner), axis=axis),
-        axis=axes)
-
-    return [bdiag, bupper, blower, by]

### 2019-08-16 tensoralloy/extension/tests/test_custom_grad_ops.py

@@ -1,134 +1,0 @@
-#!coding=utf-8
-"""
-Unit tests of the `grad_ops` module.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from nose.tools import assert_almost_equal, assert_true
-
-from tensoralloy.extension.grad_ops import safe_pow
-from tensoralloy.precision import precision_scope, get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_safe_pow():
-    """
-    Test the function `safe_pow`.
-    """
-
-    def assert_equal(a, b):
-        """ A wrapper. """
-        return assert_almost_equal(a, b, delta=1e-12)
-
-    with precision_scope("high"):
-        dtype = get_float_dtype()
-        with tf.Graph().as_default():
-            x = tf.placeholder(dtype, name='x')
-            y = tf.placeholder(dtype, name='y')
-            origin = tf.pow(x, y, name='origin')
-            z = safe_pow(x, y)
-
-            g1 = tf.gradients(origin, x)[0]
-            g2 = tf.gradients(g1, x, name='g')[0]
-
-            g1x = tf.gradients(z, x, name='g1x')[0]
-            g2x = tf.gradients(g1x, x, name='g2x')[0]
-            g3x = tf.gradients(g2x, x, name='g3x')[0]
-            g1y = tf.gradients(z, y, name='g1y')[0]
-            g2y = tf.gradients(g1y, y, name='g2y')[0]
-
-            ops = [z, g1x, g2x, g3x, g1y, g2y]
-
-            with tf.Session() as sess:
-                results = np.asarray(sess.run(ops, feed_dict={x: 3.0, y: 4.0}))
-                assert_equal(results[0], 81.0)
-                assert_equal(results[1], 108.0)
-                assert_equal(results[2], 108.0)
-                assert_equal(results[3], 72.0)
-                assert_almost_equal(
-                    results[4], np.log(3) * np.exp(4 * np.log(3)), delta=1e-12)
-
-                results = np.asarray(sess.run(ops, feed_dict={x: 0.0, y: 1.0}))
-                assert_equal(results[0], 0.0)
-                assert_equal(results[1], 1.0)
-                assert_equal(results[2], 0.0)
-                assert_equal(results[3], 0.0)
-                assert_equal(results[4], 0.0)
[…]

### 2019-08-16 tensoralloy/io/tests/test_lammps.py

@@ -1,70 +1,0 @@
-#!coding=utf-8
-"""
-Unit tests of Lammps I/O helper functions.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import nose
-
-from nose.tools import assert_almost_equal, assert_equal
-from os.path import join
-
-from tensoralloy.io.lammps import read_eam_alloy_setfl, read_adp_setfl
-from tensoralloy.test_utils import test_dir
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_read_eam_alloy():
-    """
-    Test the function `read_eam_alloy`.
-    """
-    filename = join(test_dir(), 'lammps', 'Zhou_AlCu.alloy.eam')
-    setfl = read_eam_alloy_setfl(filename)
-
-    assert_equal(setfl.elements, ['Al', 'Cu'])
-    assert_equal(setfl.nr, 2000)
-    assert_equal(setfl.nrho, 2000)
-    assert_equal(setfl.lattice_types, ['fcc', 'fcc'])
-    assert_equal(setfl.lattice_constants, [0.0, 0.0])
-    assert_almost_equal(setfl.atomic_masses[0], 26.98, delta=1e-3)
-    assert_almost_equal(setfl.embed['Al'][1, 10], -1.8490865619220642e-01,
-                        delta=1e-10)
-    assert_almost_equal(setfl.phi['CuCu'][1, 1] * setfl.phi['CuCu'][0, 1],
-                        3.8671050028993639e+00,
-                        delta=1e-10)
-
-
-def test_read_adp_setfl():
-    """
-    Test the function `read_adp_setfl`.
-    """
-    filename = join(test_dir(), 'lammps', 'AlCu.adp')
-    adpfl = read_adp_setfl(filename)
-
-    assert_equal(adpfl.elements, ['Al', 'Cu'])
-    assert_equal(adpfl.nr, 10000)
-    assert_equal(adpfl.nrho, 10000)
-
-    assert_almost_equal(adpfl.drho, 2.2770502180000001e-03, delta=1e-8)
-    assert_almost_equal(adpfl.dr, 6.2872099999999995e-04, delta=1e-8)
-
-    assert_equal(np.all(adpfl.quadrupole['CuCu'][1] == 0.0), True)
[…]

### 2019-08-16 tensoralloy/io/tests/test_read.py

@@ -1,99 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests for file-io functions.
-"""
-import nose
-
-from ase import Atoms
-from ase.units import GPa, Ha
-from ase.geometry import cell_to_cellpar
-from nose.tools import assert_equal, assert_almost_equal, assert_true
-from nose.tools import assert_dict_equal
-from os.path import join
-
-from tensoralloy.io.read import read_file
-from tensoralloy.utils import get_pulay_stress
-from tensoralloy.test_utils import test_dir
-
-
-def test_read_xyz():
-    """
-    Test reading normal xyz files.
-    """
-    xyzfile = join(test_dir(), 'B28.xyz')
-    database = read_file(xyzfile, verbose=False, num_examples=2)
-    atoms = database.get_atoms('id=2')
-    assert_equal(len(database), 2)
-    assert_almost_equal(atoms.positions[1, 1], 10.65007390)
-    assert_almost_equal(atoms.get_total_energy(), -78.51063520)
-    assert_true(atoms.cell.sum() > 1e-8)
-
-
-def test_read_extxyz():
-    """
-    Test reading ext xyz files.
-    """
-    xyzfile = join(test_dir(), 'examples.extxyz')
-    database = read_file(xyzfile, verbose=False)
-    atoms = database.get_atoms('id=2', add_additional_information=True)
-    weights = atoms.info['data']['weights']
-    thres = 1e-6
-    metadata = database.metadata
-    max_occurs = {'C': 10, 'H': 8, 'O': 4}
-    assert_equal(len(database), 2)
-    assert_equal(len(atoms), 21)
-    assert_almost_equal(atoms.get_forces()[0, 2], 2.49790655, delta=thres)
-    assert_almost_equal(atoms.get_total_energy(), -17637.613286, delta=thres)
-    assert_dict_equal(metadata['max_occurs'], max_occurs)
-    assert_equal(metadata['periodic'], False)
-    assert_equal(weights[0], 1.0)
-    assert_equal(weights[1], 1.0)
-    assert_equal(weights[2], 1.0)
-    assert_equal(atoms.info['key_value_pairs']['source'], '')
-
-
-def test_read_snap_stress():
-    """
-    Test reading an example SNAP/Ni extxyz file.
-
-    The unit of the stress tensor in this file is kbar.
-    """
[…]

### 2019-08-16 tensoralloy/io/tests/test_sqlite.py

@@ -1,43 +1,0 @@
-# codingf=utf-8
-"""
-This module defines tests for finding neighbor sizes.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from nose.tools import assert_equal
-from os.path import join
-
-from tensoralloy.io.db import connect
-from tensoralloy.io.read import read_file
-from tensoralloy.test_utils import test_dir, datasets_dir
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_find_neighbor_size_limits():
-    """
-    Test the function `find_neighbor_size_limits`.
-    """
-    xyzfile = join(test_dir(), 'examples.extxyz')
-    db = read_file(xyzfile, verbose=False)
-
-    db.update_neighbor_meta(angular=True, rc=6.0, n_jobs=1, verbose=False)
-    db.update_neighbor_meta(angular=False, rc=6.5, n_jobs=1, verbose=False)
-
-    assert_equal(db.get_nij_max(rc=6.0), 358)
-
-
-def test_read():
-    """
-    Test the function `read_neighbor_sizes`.
-    """
-    db = connect(join(datasets_dir(), 'snap-Ni.db'))
-    assert_equal(db.get_nij_max(rc=6.5), 14494)
-    assert_equal(db.get_nnl_max(rc=6.5), 136)
-
-
-if __name__ == "__main__":
-    nose.main()

### 2019-08-16 tensoralloy/io/tests/test_units.py

@@ -1,51 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests for unit conversions.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from ase.units import kcal, mol, Hartree, eV, GPa
-from nose.tools import assert_almost_equal
-
-from tensoralloy.io.read import read_file
-from tensoralloy.io.units import get_conversion_units
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_unit_conversion():
-    """
-    Test the unit conversion function.
-    """
-    to_eV, _, to_eV_Ang3 = get_conversion_units({
-        'energy': 'kcal/mol*Hartree/eV',
-        'stress': '0.1*GPa',
-    })
-    assert_almost_equal(to_eV, (kcal / mol * Hartree / eV) / eV)
-    assert_almost_equal(to_eV_Ang3, 0.1 * GPa)
-
-    _, _, to_eV_Ang3 = get_conversion_units({
-        'stress': 'kbar',
-    })
-    assert_almost_equal(to_eV_Ang3, 0.1 * GPa)
-
-    _, _, to_eV_Ang3 = get_conversion_units({
-        'stress': 'eV/Angstrom**3',
-    })
-    assert_almost_equal(to_eV_Ang3, 1.0)
-
-    xyzfile = 'test_files/examples.extxyz'
-    database = read_file(xyzfile, verbose=False,
-                         units={'energy': 'kcal/mol'})
-    atoms = database.get_atoms(id=2)
-    thres = 1e-6
-    unit = kcal / mol / eV
-    assert_almost_equal(atoms.get_total_energy(), -17637.613286 * unit,
-                        delta=thres)
-
-
-if __name__ == "__main__":
-    nose.run()

### 2019-08-16 tensoralloy/nn/atomic/tests/test_atomic_nn.py

@@ -1,220 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests of `AtomicNN` and its variants.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-import os
-
-from ase.db import connect
-from os.path import exists, join, dirname
-from nose.tools import assert_equal, assert_list_equal, with_setup
-from nose.tools import assert_true, assert_false
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.nn.atomic import AtomicNN, AtomicResNN
-from tensoralloy.test_utils import test_dir, datasets_dir
-from tensoralloy.transformer import SymmetryFunctionTransformer
-from tensoralloy.transformer import BatchSymmetryFunctionTransformer
-from tensoralloy.utils import GraphKeys, AttributeDict
-from tensoralloy.precision import precision_scope
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_as_dict():
-    """
-    Test the method `AtomicNN.as_dict`.
-    """
-    elements = ['Al', 'Cu']
-    hidden_sizes = 32
-    old_nn = AtomicNN(elements, hidden_sizes,
-                      activation='tanh',
-                      minimize_properties=['energy', ],
-                      export_properties=['energy', ])
-
-    d = old_nn.as_dict()
-
-    assert_equal(d['class'], 'AtomicNN')
-    d.pop('class')
-
-    new_nn = AtomicNN(**d)
-
-    assert_list_equal(new_nn.elements, old_nn.elements)
-    assert_list_equal(new_nn.minimize_properties, old_nn.minimize_properties)
-    assert_equal(new_nn.hidden_sizes, old_nn.hidden_sizes)
-
-
-def test_as_dict_advanced():
-    """
-    Test the method `AtomicResNN.as_dict`.
-    """
-    db = connect(join(datasets_dir(), 'qm7.db'))
-    max_occurs = db.metadata['max_occurs']
-
-    eta = [0.1, 0.5, 1.0, 2.0, 4.0, 8.0, 12.0, 16.0, 20.0, 40.0]
-    omega = [0.0, 3.2]
-    rc = 6.5
-    nij_max = 506
-    batch_size = 10
-
-    bsf = BatchSymmetryFunctionTransformer(rc=rc, max_occurs=max_occurs,
-                                           nij_max=nij_max, nijk_max=0,
-                                           batch_size=batch_size, eta=eta,
[…]

### 2019-08-16 tensoralloy/nn/constraint/elastic.py

@@ -1,261 +1,0 @@
-#!coding=utf-8
-"""
-This module can be used to infer RMSE loss of elastic constants.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensorflow_estimator import estimator as tf_estimator
-from ase.units import GPa
-from typing import List, Union, Tuple
-
-from tensoralloy.nn.constraint.data import Crystal, get_crystal
-from tensoralloy.nn.constraint.voigt import voigt_notation, voigt_to_ij
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.dataclasses import ElasticConstraintOptions
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.utils import GraphKeys
-
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def _get_cijkl_op(total_stress: tf.Tensor, cell: tf.Tensor, volume: tf.Tensor,
-                  i: int, j: int, kl: List[Tuple[int, int]]):
-    """
-    Return the Op to compute C_{ijkl}.
-    """
-    dsdhij = tf.identity(tf.gradients(
-        total_stress[i, j],
-        cell)[0], name=f'dsdh{i}{j}')
-    cij = tf.matmul(
-        tf.transpose(dsdhij),
-        tf.identity(cell),
-        name=f'h_dsdh{i}{j}')
-    cij = tf.math.truediv(cij, volume)
-    cij = tf.math.truediv(
-        cij, tf.convert_to_tensor(GPa, dtype=cell.dtype, name='GPa'),
-        name=f'c{i}{j}xx/GPa')
-    groups = {}
-    for (k, l) in kl:
-        name = f'c{i}{j}{k}{l}'
-        groups[(k, l)] = tf.identity(cij[k, l], name=name)
-    return groups
-
-
-def get_elastic_constat_tensor_op(total_stress: tf.Tensor, cell: tf.Tensor,
-                                  volume: tf.Tensor, name='elastic',
-                                  verbose=False):
-    """
-    Return the Op to compute the full elastic constant tensor.
-
-    Parameters
-    ----------
-    total_stress : tf.Tensor
-        The total stress (with unit 'eV') tensor. The shape should be `[3, 3]`.
-    cell : tf.Tensor
-        The 3x3 lattice tensor. The shape should be `[3, 3]`.
-    volume : tf.Tensor
-        The lattice volume tensor.
-    name : str
[…]

### 2019-08-16 tensoralloy/nn/constraint/rose.py

@@ -1,246 +1,0 @@
-#!coding=utf-8
-"""
-The Rose Equation of State constraint for training a `BasicNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from ase import Atoms
-from ase.calculators.singlepoint import SinglePointCalculator
-from ase.units import GPa
-from typing import List
-from collections import Counter
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.nn.constraint.data import get_crystal
-from tensoralloy.nn.dataclasses import RoseLossOptions
-from tensoralloy.neighbor import find_neighbor_size_of_atoms, NeighborSize
-from tensoralloy.transformer.base import BatchDescriptorTransformer
-from tensoralloy.utils import AttributeDict, GraphKeys
-from tensoralloy.precision import get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def get_batch_transformer(original_clf: BatchDescriptorTransformer,
-                          trajectory: List[Atoms],
-                          sizes: List[NeighborSize],
-                          max_occurs: Counter):
-    """
-    Return a `BatchDescriptorTransformer` for the trajectory.
-
-    Parameters
-    ----------
-    original_clf : BatchDescriptorTransformer
-        The original batch descriptor transformer.
-    trajectory : List[Atoms]
-        A list of scaled `Atoms` object.
-    sizes : List[NeighborSize]
-        The corresponding `NeighborSize` for each `Atoms`.
-    max_occurs : Counter
-        The max occurances of the elements.
-
-    Returns
-    -------
-    clf : BatchDescriptorTransformer
-        The newly created batch descriptor transformer for this trajectory.
-
-    """
-    configs = original_clf.as_dict()
-    cls = configs.pop('class')
-
-    if cls == 'BatchSymmetryFunctionTransformer':
-        nij_max = max(map(lambda x: x.nij, sizes))
-        if configs['angular']:
-            nijk_max = max(map(lambda x: x.nijk, sizes))
-        else:
-            nijk_max = 0
-        configs['nij_max'] = nij_max
-        configs['nijk_max'] = nijk_max
-
-    elif cls == "BatchEAMTransformer" or cls == "BatchADPTransformer":
-        nij_max = max(map(lambda x: x.nij, sizes))
[…]

### 2019-08-16 tensoralloy/nn/constraint/tests/test_data.py

@@ -1,39 +1,0 @@
-#!coding=utf-8
-"""
-The unit tests of the built-in constraint data module.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from os.path import join
-from nose.tools import assert_equal, assert_in
-
-from tensoralloy.nn.constraint.data import built_in_crystals
-from tensoralloy.nn.constraint.data import read_external_crystal
-from tensoralloy.test_utils import test_dir
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_read_external_crystal():
-    """
-    Test the function `read_external_crystal`.
-    """
-    toml_file = join(test_dir(), "crystals", "Ni3Mo_elastic_tensor.toml")
-    crystal = read_external_crystal(toml_file)
-    builtin = built_in_crystals['Ni3Mo']
-
-    assert_equal(builtin.name, crystal.name)
-    assert_equal(builtin.phase, crystal.phase)
-    assert_equal(7, len(crystal.elastic_constants))
-
-    for elastic_constant in crystal.elastic_constants:
-        assert_in(elastic_constant, builtin.elastic_constants)
-
-    assert_equal(crystal.elastic_constants[-1].weight, 0.0)
-
-
-if __name__ == "__main__":
-    nose.run()

### 2019-08-16 tensoralloy/nn/constraint/tests/test_rose.py

@@ -1,151 +1,0 @@
-#!coding=utf-8
-"""
-Test the Rose Equation of State Constraint.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from ase.build import bulk
-from ase.units import GPa
-from os.path import join
-from collections import Counter
-from sklearn.metrics import mean_absolute_error
-from nose.tools import assert_almost_equal, assert_equal
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.nn.constraint.rose import get_rose_constraint_loss
-from tensoralloy.nn.constraint.data import built_in_crystals
-from tensoralloy.nn import EamAlloyNN
-from tensoralloy.nn.dataclasses import TrainParameters, OptParameters
-from tensoralloy.nn.dataclasses import LossParameters, RoseLossOptions
-from tensoralloy.transformer import BatchEAMTransformer
-from tensoralloy.precision import precision_scope
-from tensoralloy.test_utils import test_dir, assert_array_almost_equal
-from tensoralloy.calculator import TensorAlloyCalculator
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.utils import AttributeDict
-
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_rose_eos_constraint():
-    """
-    Test the function `get_rose_constraint_loss`.
-    """
-    atoms = bulk('Mo', cubic=True)
-    calc = TensorAlloyCalculator(join(test_dir(), 'models', 'Mo.zhou04.pb'))
-    atoms.calc = calc
-    cell = atoms.cell
-
-    bulk_modulus = 259.0 * GPa
-    e0 = calc.get_potential_energy(atoms)
-    v0 = atoms.get_volume()
-    alpha = np.sqrt(np.abs(9.0 * v0 * bulk_modulus / e0))
-    beta = 0.5e-2
-    dx = 0.10
-    delta = 0.01
-
-    y_rose_list = []
-    y_list = []
-    vol_list = []
-    ax_list = []
-
-    for ratio in np.linspace(1.0 - dx, 1.0 + dx, num=21, endpoint=True):
-        atomsi = atoms.copy()
-        atomsi.set_cell(cell * ratio, scale_atoms=True)
-
-        # Eq. 12: x = a / a0 - 1
[…]

### 2019-08-16 tensoralloy/nn/constraint/voigt.py

@@ -1,55 +1,0 @@
-#!coding=utf-8
-"""
-Voigt helper functions.
-"""
-from __future__ import print_function, absolute_import
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def voigt_notation(i, j, is_py_index=True, return_py_index=False):
-    """
-    Return the Voigt notation given two indices (start from zero).
-    """
-    if not is_py_index:
-        i -= 1
-        j -= 1
-    if i == j:
-        idx = i + 1
-    elif (i == 1 and j == 2) or (i == 2 and j == 1):
-        idx = 4
-    elif (i == 0 and j == 2) or (i == 2 and j == 0):
-        idx = 5
-    else:
-        idx = 6
-    if return_py_index:
-        return idx - 1
-    else:
-        return idx
-
-
-def voigt_to_ij(vi: int, is_py_index=False):
-    """
-    Return the corresponding Python index tuple (i, j).
-    """
-    if not is_py_index:
-        vi -= 1
-    if vi < 3:
-        return vi, vi
-    elif vi == 3:
-        return 1, 2
-    elif vi == 4:
-        return 0, 2
-    else:
-        return 0, 1
-
-
-def voigt_to_ijkl(vi: int, vj: int, is_py_index=False):
-    """
-    Return the corresponding Python index tuple (i, j, k, l).
-    """
-    ijkl = []
-    for val in (vi, vj):
-        ijkl.extend(voigt_to_ij(val, is_py_index=is_py_index))
-    return tuple(ijkl)

### 2019-08-16 tensoralloy/nn/eam/__init__.py

@@ -1,14 +1,0 @@
-# coding=utf-8
-"""
-This module defines `EamNN` and its variants.
-"""
-from __future__ import print_function, absolute_import
-
-from tensoralloy.nn.eam.fs import EamFsNN
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.nn.eam.adp import AdpNN
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-__all__ = ["EamFsNN", "EamAlloyNN", "AdpNN"]

### 2019-08-16 tensoralloy/nn/eam/adp.py

@@ -1,885 +1,0 @@
-#!coding=utf-8
-"""
-This module defines ADP potential.
-"""
-from __future__ import print_function, absolute_import
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-import tensorflow as tf
-import numpy as np
-
-from tensorflow_estimator import estimator as tf_estimator
-from collections import Counter
-from datetime import datetime
-from os.path import join, dirname
-from ase import data
-from atsim.potentials import Potential, EAMPotential
-from functools import partial
-from typing import Dict
-
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.nn.eam.eam import plot_potential
-from tensoralloy.utils import AttributeDict, get_elements_from_kbody_term
-from tensoralloy.utils import get_kbody_terms, Defaults, safe_select
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.io.lammps import write_adp_setfl
-
-
-class AdpNN(EamAlloyNN):
-    """
-    The ADP model is just an extension of the EAM/Alloy model. Dipole and
-    quadrupole interactions are introduced to the ADP model.
-    """
-
-    def __init__(self, *args, **kwargs):
-        """
-        Initialization method.
-        """
-        super(AdpNN, self).__init__(*args, **kwargs)
-        self._nn_scope = "nnADP"
-
-    @property
-    def tag(self):
-        """ Return the tag. """
-        return "adp"
-
-    def _get_hidden_sizes(self, hidden_sizes):
-        """
-        Setup the hidden layer sizes.
-
-        Parameters
-        ----------
-        hidden_sizes : int or List[int] or Dict[str, Dict[str, List[int]]]
-            This can be an int, a list of int or a nested dict.
-
-        Returns
-        -------
-        results : Dict[str, Dict[str, int]]
-            A nested dict.
-
-        """
-        kbody_terms = get_kbody_terms(self._elements, k_max=2)[1]
-        hidden_sizes = safe_select(hidden_sizes, Defaults.hidden_sizes)
-
-        unique_kbody_terms = []
-        for element in self._elements:
-            for kbody_term in kbody_terms[element]:
-                a, b = get_elements_from_kbody_term(kbody_term)
-                if a == b:
-                    unique_kbody_terms.append(kbody_term)
-                else:
-                    ab = "".join(sorted([a, b]))
[…]

### 2019-08-16 tensoralloy/nn/eam/alloy.py

@@ -1,387 +1,0 @@
-# coding=utf-8
-"""
-This module defines the EAM/Alloy model.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from tensorflow_estimator import estimator as tf_estimator
-from datetime import datetime
-from os.path import dirname, join
-from ase import data
-from collections import Counter
-from typing import List, Dict, Tuple
-from atsim.potentials import Potential, EAMPotential, writeSetFL
-
-from tensoralloy.utils import get_elements_from_kbody_term, get_kbody_terms
-from tensoralloy.utils import GraphKeys, AttributeDict, Defaults, safe_select
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.eam.eam import EamNN, plot_potential
-from tensoralloy.precision import get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class EamAlloyNN(EamNN):
-    """
-    The tensorflow based implementation of the EAM/Alloy model.
-    """
-
-    default_collection = GraphKeys.EAM_ALLOY_NN_VARIABLES
-
-    @property
-    def tag(self):
-        """ Return the tag. """
-        return "alloy"
-
-    def _get_hidden_sizes(self, hidden_sizes):
-        """
-        Setup the hidden layer sizes.
-
-        Parameters
-        ----------
-        hidden_sizes : int or List[int] or Dict[str, Dict[str, List[int]]]
-            This can be an int, a list of int or a nested dict.
-
-        Returns
-        -------
-        results : Dict[str, Dict[str, int]]
-            A nested dict.
-
-        """
-        kbody_terms = get_kbody_terms(self._elements, k_max=2)[1]
-        hidden_sizes = safe_select(hidden_sizes, Defaults.hidden_sizes)
-
-        unique_kbody_terms = []
-        for element in self._elements:
-            for kbody_term in kbody_terms[element]:
-                a, b = get_elements_from_kbody_term(kbody_term)
-                if a == b:
-                    unique_kbody_terms.append(kbody_term)
-                else:
-                    ab = "".join(sorted([a, b]))
-                    if ab not in unique_kbody_terms:
-                        unique_kbody_terms.append(ab)
-
-        self._unique_kbody_terms = unique_kbody_terms
-        self._kbody_terms = kbody_terms
-
-        results = {}
-
-        def _safe_update(section):
[…]

### 2019-08-16 tensoralloy/nn/eam/eam.py

@@ -1,713 +1,0 @@
-# coding=utf-8
-"""
-This module defines the basic EAM-NN model.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import re
-
-from matplotlib import pyplot as plt
-from collections import Counter
-from functools import partial
-from typing import List, Dict, Callable
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.utils import get_elements_from_kbody_term, AttributeDict
-from tensoralloy.nn.convolutional import convolution1x1
-from tensoralloy.nn.basic import BasicNN
-from tensoralloy.nn.utils import get_activation_fn, log_tensor
-from tensoralloy.nn.eam.potentials import available_potentials
-from tensoralloy.nn.eam.potentials import EamFSPotential, EamAlloyPotential
-from tensoralloy.nn.eam.potentials.spline import CubicSplinePotential
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-_spline_pot_patt = re.compile(r"spline@(.*)")
-
-
-def plot_potential(nx: int, dx: float, func: Callable, filename: str,
-                   x0=0.0, xt=None, xlabel=None, ylabel=None, title=None):
-    """
-    Plot an empirical or NN potential.
-
-    Parameters
-    ----------
-    nx : int
-        The number of points.
-    dx : float
-        The gap of two adjacent points.
-    func : Callable
-        The function to compute f(x).
-    filename : str
-        The name of the output image.
-    x0 : float
-        The initial `x`.
-    xt : float
-        The final `x`.
-    xlabel : str
-        The label of X axis.
-    ylabel : str
-        The label of Y axis.
-    title : str
-        The title of the figure.
-
-    """
-    fig = plt.figure(1, figsize=[6, 6])
-
-    x0 = int(x0 / dx) * dx
-    if xt is None:
-        xt = nx * dx
-    else:
-        xt = min(nx * dx, xt)
-
-    x = np.linspace(x0, xt, num=int((xt - x0) / dx), endpoint=False)
-    y = [func(xi) for xi in x]
-
-    plt.plot(x, y, 'r-', linewidth=0.8)
-
-    if title:
-        plt.title(title, fontsize=15, fontname='arial')
-    if xlabel:
-        plt.xlabel(xlabel, fontsize=13, fontname='arial')
-    if ylabel:
[…]

### 2019-08-16 tensoralloy/nn/eam/fs.py

@@ -1,397 +1,0 @@
-# coding=utf-8
-"""
-This module defines the EAM/Finnis-Sinclair model.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from collections import Counter
-from os.path import join, dirname
-from datetime import datetime
-from ase.data import atomic_masses, atomic_numbers
-from atsim.potentials import writeSetFLFinnisSinclair, Potential, EAMPotential
-from typing import Dict, List
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.utils import get_kbody_terms, get_elements_from_kbody_term
-from tensoralloy.utils import GraphKeys, AttributeDict, Defaults, safe_select
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.eam.eam import EamNN, plot_potential
-from tensoralloy.nn.eam.potentials import available_potentials
-from tensoralloy.precision import get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class EamFsNN(EamNN):
-    """
-    The tensorflow based implementation of the EAM/Finnis-Sinclair model.
-    """
-
-    default_collection = GraphKeys.EAM_FS_NN_VARIABLES
-
-    @property
-    def all_kbody_terms(self) -> List[str]:
-        """
-        Return a list of str as all the ordered k-body terms.
-        """
-        return self._all_kbody_terms
-
-    @property
-    def tag(self):
-        """ Return the tag. """
-        return "fs"
-
-    def _get_hidden_sizes(self, hidden_sizes):
-        """
-        Setup the hidden layer sizes.
-
-        Parameters
-        ----------
-        hidden_sizes : int or List[int] or Dict[str, Dict[str, List[int]]]
-            This can be an int, a list of int or a nested dict.
-
-        Returns
-        -------
-        results : Dict[str, Dict[str, int]]
-            A nested dict.
-
-        """
-        all_kbody_terms, kbody_terms = \
-            get_kbody_terms(self._elements, k_max=2)[:2]
-        hidden_sizes = safe_select(hidden_sizes, Defaults.hidden_sizes)
-
-        unique_kbody_terms = []
-        for element in self._elements:
-            for kbody_term in kbody_terms[element]:
-                a, b = get_elements_from_kbody_term(kbody_term)
-                if a == b:
-                    unique_kbody_terms.append(kbody_term)
[…]

### 2019-08-16 tensoralloy/nn/eam/meam.py

@@ -1,116 +1,0 @@
-#!coding=utf-8
-"""
-This module defines the MeamNN.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensorflow_estimator import estimator as tf_estimator
-from typing import List
-
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.utils import AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class MeamNN(EamAlloyNN):
-    """
-    The tensorflow-based implementation of the Modified Embedded-Atom Method.
-    """
-
-    def __init__(self,
-                 elements: List[str],
-                 custom_potentials=None,
-                 hidden_sizes=None,
-                 activation=None,
-                 minimize_properties=('energy', 'forces'),
-                 export_properties=('energy', 'forces', 'hessian')):
-        """
-        Initialization method.
-        """
-        self._unique_kbody_terms = None
-        self._kbody_terms = None
-
-        super(MeamNN, self).__init__(
-            elements=elements,
-            custom_potentials=custom_potentials,
-            hidden_sizes=hidden_sizes,
-            activation=activation,
-            minimize_properties=minimize_properties,
-            export_properties=export_properties)
-
-    def as_dict(self):
-        """
-        Return a JSON serializable dict representation of this `BasicNN`.
-        """
-        return super(MeamNN, self).as_dict()
-
-    def _get_model_outputs(self,
-                           features: AttributeDict,
-                           descriptors: AttributeDict,
-                           mode: tf_estimator.ModeKeys,
-                           verbose=False):
-        """
-        Return raw NN-EAM model outputs.
-
-        Parameters
-        ----------
-        features : AttributeDict
-            A dict of tensors, includeing raw properties and the descriptors:
-                * 'positions' of shape `[batch_size, N, 3]`.
-                * 'cells' of shape `[batch_size, 3, 3]`.
-                * 'mask' of shape `[batch_size, N]`.
-                * 'volume' of shape `[batch_size, ]`.
-                * 'n_atoms' of dtype `int64`.'
-        descriptors : AttributeDict
-            A dict of (element, (value, mask)) where `element` represents the
-            symbol of an element, `value` is the descriptors of `element` and
-            `mask` is the mask of `value`.
-        mode : tf_estimator.ModeKeys
-            Specifies if this is training, evaluation or prediction.
-        verbose : bool
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/__init__.py

@@ -1,26 +1,0 @@
-# coding=utf-8
-from __future__ import print_function, absolute_import
-
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential, EamFSPotential
-from tensoralloy.nn.eam.potentials.sutton90 import AgSutton90
-from tensoralloy.nn.eam.potentials.zjw04 import Zjw04, Zjw04xc, Zjw04uxc
-from tensoralloy.nn.eam.potentials.zjw04 import Zjw04xcp
-from tensoralloy.nn.eam.potentials.msah11 import AlFeMsah11
-from tensoralloy.nn.eam.potentials.grimmes import RWGrimes
-from tensoralloy.nn.eam.potentials.mishin import MishinH, AlCuSplineAdp
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-available_potentials = {
-    'sutton90': AgSutton90,
-    'zjw04': Zjw04,
-    'zjw04xc': Zjw04xc,
-    'zjw04uxc': Zjw04uxc,
-    'zjw04xcp': Zjw04xcp,
-    'msah11': AlFeMsah11,
-    'grimes': RWGrimes,
-    "mishinh": MishinH,
-    "adp/AlCu": AlCuSplineAdp,
-}

### 2019-08-16 tensoralloy/nn/eam/potentials/generic.py

@@ -1,102 +1,0 @@
-#!coding=utf-8
-"""
-This module defines generic potential functions.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensorflow.python.framework import ops
-
-from tensoralloy.extension.grad_ops import safe_pow
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def morse(r, D, gamma, r0, name='Morse'):
-    """
-    The generic Morse potential.
-
-        f(x) = D[ exp(-2 * gamma * (r - r0)) - 2 * exp(-gamma * (r - r0)) ]
-
-    """
-    with tf.name_scope(name):
-        r = tf.convert_to_tensor(r, name='r')
-        diff = tf.math.subtract(r, r0, name='diff')
-        g_diff = tf.multiply(gamma, diff, name='g_diff')
-        dtype = r.dtype
-        two = tf.constant(2.0, dtype=dtype)
-        c = tf.exp(-two * g_diff) - two * tf.exp(-g_diff)
-        return tf.multiply(c, D, name='value')
-
-
-def buckingham(r, A, rho, C, order=6, name='Buckingham'):
-    """
-    The generic Buckingham potential.
-
-        f(x) = A * exp(-r / rho) - C / r**order
-
-    """
-    with tf.name_scope(name):
-        r = tf.convert_to_tensor(r, name='r')
-        dtype = r.dtype
-        order = tf.constant(order, dtype=tf.int32, name='order')
-        rs = tf.math.pow(r, order, name='rs')
-        rho = tf.convert_to_tensor(rho, name='rho', dtype=dtype)
-        C = tf.convert_to_tensor(C, name='C', dtype=dtype)
-        return tf.math.subtract(A * tf.exp(-r / rho),
-                                tf.div_no_nan(C, rs, name='right'),
-                                name='value')
-
-
-def mishin_cutoff(x, name=None):
-    """
-    The cutoff function proposed by Y. Mishin:
-
-        psi(x) = x**4 / (1 + x**4)  x <  0
-                 0                  x >= 0
-
-    """
-    with ops.name_scope(name, "Psi", [x]):
-        x = tf.nn.relu(-x, name='ix')
-        four = tf.convert_to_tensor(4.0, dtype=x.dtype, name='four')
-        x4 = safe_pow(x, four)
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/grimmes.py

@@ -1,124 +1,0 @@
-#!coding=utf-8
-"""
-This module introduces EAM potentials for Pu and other actinides developed by
-R.W. Grimes.
-
-The long-range electrostatic term is ignored.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential
-from tensoralloy.nn.eam.potentials.generic import morse, buckingham
-from tensoralloy.nn.utils import log_tensor
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class RWGrimes(EamAlloyPotential):
-    """
-    Journal of Nuclear Materials 461 (2015) 206–214
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        super(RWGrimes, self).__init__()
-
-    @property
-    def defaults(self):
-        """
-        The default parameters.
-        """
-        defaults = {'PuPu': {'A': 18600.0, 'rho': 0.2637, 'C': 0.0,
-                             'D': 0.70185, 'gamma': 1.98008, 'r0': 2.34591},
-                    'Pu': {'G': 2.168, 'n': 3980.058}}
-        return defaults
-
-    def phi(self, r: tf.Tensor, kbody_term: str, variable_scope: str,
-            verbose=False):
-        """
-        The pairwise potential function.
-        """
-        with tf.variable_scope('RWGrimes'):
-            dtype = r.dtype
-            assert isinstance(variable_scope, str)
-            variable_scope = f"{variable_scope}/{kbody_term}"
-            A = self._get_variable('A', dtype, kbody_term, variable_scope)
-            rho = self._get_variable('rho', dtype, kbody_term, variable_scope)
-            C = self._get_variable('C', dtype, kbody_term, variable_scope)
-            D = self._get_variable('D', dtype, kbody_term, variable_scope)
-            gamma = self._get_variable(
-                'gamma', dtype, kbody_term, variable_scope)
-            r0 = self._get_variable('r0', dtype, kbody_term, variable_scope)
-
-            phi = tf.math.add(morse(r, D, gamma, r0),
-                              buckingham(r, A, rho, C),
-                              name='phi')
-            if verbose:
-                log_tensor(phi)
-            return phi
-
-    def rho(self, r: tf.Tensor, element: str, variable_scope: str,
-            verbose=False):
-        """
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/mishin.py

@@ -1,533 +1,0 @@
-#!coding=utf-8
-"""
-This module defines the empirical functions for ADP developed by Y. Mishin
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from os.path import join
-
-from tensoralloy.nn.eam.potentials.generic import mishin_cutoff, mishin_polar
-from tensoralloy.utils import get_elements_from_kbody_term
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.extension.grad_ops import safe_pow
-from tensoralloy.extension.interp.cubic import CubicInterpolator
-from tensoralloy.test_utils import test_dir
-from tensoralloy.io.lammps import read_adp_setfl
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class MishinH(EamAlloyPotential):
-    """
-    The ADP potential functions of the Mishin H-style.
-
-    References
-    ----------
-    F. Apostol and Y. Mishin, PHYSICAL REVIEW B 82, 144115 2010
-
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        super(MishinH, self).__init__()
-
-        self._name = 'MishinH'
-        self._implemented_potentials = ('rho', 'phi', 'embed', 'dipole',
-                                        'quadrupole')
-
-    @property
-    def defaults(self):
-        """
-        Return the default parameters.
-        """
-        params = {
-            # Self-fitted parameters
-            "Mo": {
-                "s1": -2.00695289e-01, "s2": -3.12178751e-04,
-                "s3": 7.86343222e-05, "s4": 5.29721645e+00,
-                "s5": 3.79481951e-02, "s6": 1.11800974e+02, "s7": 4.05948858e+00
-            },
-            "Al": {
-                "s1": -3.72848864e-01, "s2": 6.52035828e-03,
-                "s3": 9.71742655e-05, "s4": 7.64264116e+00,
-                "s5": 6.88604789e-02, "s6": 1.55694016e+01, "s7": 5.38646368e+00
-            },
-            # Parameters fitted by Mishin
-            "H": {
-                "s1": 8.08612, "s2": 1.46294e-2, "s3": -6.86143e-3,
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/msah11.py

@@ -1,433 +1,0 @@
-# coding=utf-8
-"""
-This module defines the empirical potential of Al-Fe proposed by Mendelev et al.
-at 2011.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import functools
-import warnings
-
-from typing import List
-
-from tensoralloy.nn.eam.potentials import EamFSPotential
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.precision import get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class AlFeMsah11(EamFSPotential):
-    """
-    The Al-Fe proposed by Mendelev et al. at 2011.
-
-    References
-    ----------
-    M.I. Mendelev, et al., J. Mater. Res. 20 (2011) 208.
-
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        super(AlFeMsah11, self).__init__()
-
-        if get_float_dtype() == tf.float32:
-            warnings.warn("It's not recommended to use float32 for MSAH11.")
-
-    @property
-    def defaults(self):
-        """
-        The Msah11 potential does not have trainable parameters.
-        """
-        defaults = {"Al": {}, "Fe": {}}
-        return defaults
-
-    @staticmethod
-    def _pairwise_func(lowcuts: np.ndarray, highcuts: np.ndarray,
-                       c1: np.ndarray, c2: np.ndarray, coef: List[np.ndarray]):
-        """
-        Construct a pairwise function, phi(r), using the given parameters.
-        """
-        nfuncs = len(lowcuts)
-        assert nfuncs == len(highcuts)
-        assert nfuncs == len(coef) + 2
-
-        def _poly(factors: np.ndarray, lowcut: float, highcut: float,
-                  orders: np.ndarray, dtype=tf.float64):
-            """
-            A helper function to construct polynomial potentials.
-            """
-            def _func(r: tf.Tensor):
-                lc = tf.convert_to_tensor(lowcut, name=f'lowcut', dtype=dtype)
-                hc = tf.convert_to_tensor(highcut, name=f'highcut', dtype=dtype)
-                idx = tf.where(
-                    tf.logical_and(tf.greater_equal(r, lc), tf.less(r, hc)))
-                x = tf.gather_nd(r, idx)
-                shape = tf.shape(r, out_type=idx.dtype)
-                values = []
-                for i in range(len(factors)):
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/potentials.py

@@ -1,378 +1,0 @@
-# coding=utf-8
-"""
-This module defines general classical potential function layers for NN-EAM.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from typing import List, Dict, Tuple
-from abc import ABC
-
-from tensoralloy.utils import GraphKeys, safe_select
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def get_variable(name,
-                 dtype=None,
-                 shape=None,
-                 initializer=None,
-                 regularizer=None,
-                 trainable=None,
-                 collections=None,
-                 validate_shape=True):
-    """
-    A wrapper of `tf.get_variable`.
-    """
-    _collections = [tf.GraphKeys.GLOBAL_VARIABLES]
-    if trainable:
-        _collections.append(tf.GraphKeys.TRAINABLE_VARIABLES)
-    if collections is not None:
-        assert isinstance(collections, (tuple, list, set))
-        for collection in collections:
-            if collection not in _collections:
-                _collections.append(collection)
-    return tf.get_variable(name, shape=shape or (), dtype=dtype,
-                           initializer=initializer, regularizer=regularizer,
-                           trainable=trainable, collections=_collections,
-                           validate_shape=validate_shape)
-
-
-class EamEmpiricalPotential:
-    """
-    An `EmpiricalPotential` represents a tensorflow based implemetation of an
-    empirical EAM potential.
-    """
-
-    def __init__(self, params=None, fixed=None):
-        """
-        Initialization method.
-
-        Parameters
-        ----------
-        params : Dict[str, Dict[str, Union[float, int]]] or None
-            A nested dict to update the default values.
-        fixed : Dict[str, List[str]] or None
-            A dict of (kbody_term, [var1, ...]) where `[var1, ...]` is a list of
-            str as the fixed (non-trainable) parameters for `kbody_term`.
-
-        """
-        super(EamEmpiricalPotential, self).__init__()
-
-        fixed = safe_select(fixed, {})
-        params = safe_select(params, {})
-
-        self._params = self.defaults.copy()
-        for section, values in params.items():
-            if section in self._params:
-                self._params[section].update(values)
-            else:
-                raise KeyError(
-                    f"{self.__class__.__name__} does not support `{section}`")
-
-        self._fixed = {}
-        for section in fixed:
-            if self.__contains__(section):
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/spline.py

@@ -1,183 +1,0 @@
-#!coding=utf-8
-"""
-Cubic spline based EAM/ADP potentials.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import pandas as pd
-
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential
-from tensoralloy.nn.eam.potentials.potentials import get_variable
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.extension.interp.cubic import CubicInterpolator
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class CubicSplinePotential(EamAlloyPotential):
-    """
-    A general cubic spline based EAM/ADP potential container.
-    """
-
-    def __init__(self, filename: str):
-        """
-        Initialization method.
-
-        Parameters
-        ----------
-        filename : str
-            The initial guess file. This should be a csv file without index.
-
-        """
-        super(CubicSplinePotential, self).__init__()
-        self._name = "Spline"
-        self._df = pd.read_csv(filename, index_col=None)
-
-    @property
-    def defaults(self):
-        """
-        The default parameters.
-        """
-        return {}
-
-    def is_avaiblable(self, key):
-        """
-        Return True if the potential is available.
-        """
-        keys = self._df.keys()
-        return f"{key}.x" in keys and f"{key}.y" in keys
-
-    def _make(self, t: tf.Tensor, pot: str, name: str):
-        """
-        Make a spline potential.
-
-        nr = self._adpfl.nr
-            x = self._adpfl.rho[element][0][0:nr:self._interval]
-            y = self._adpfl.rho[element][1][0:nr:self._interval]
-            f = CubicInterpolator(x, y, natural_boundary=True, name='Spline')
-            shape = tf.shape(r, name='shape')
-            rho = f.evaluate(tf.reshape(r, (-1,), name='r/flat'))
-            rho = tf.reshape(rho, shape, name='rho')
-            if verbose:
-                log_tensor(rho)
-            return rho
-
-        """
-        if not self.is_avaiblable(pot):
-            raise ValueError(f"{pot} is not available!")
-
-        dtype = t.dtype
-        xval = self._df[f"{pot}.x"].to_numpy(dtype.as_numpy_dtype)
-        yval = self._df[f"{pot}.y"].to_numpy(dtype.as_numpy_dtype)
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/sutton90.py

@@ -1,119 +1,0 @@
-# coding=utf-8
-"""
-This module defines the empirical potential of Ag proposed by Sutton et al. at
-1990.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.extension.grad_ops import safe_pow
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class AgSutton90(EamAlloyPotential):
-    """
-    The Ag potential proposed by Sutton et al. at 1990.
-
-    References
-    ----------
-    A.P. Sutton, and J. Chen, Philos. Mag. Lett. 61 (1990) 139.
-
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        super(AgSutton90, self).__init__()
-
-    @property
-    def defaults(self):
-        """
-        The default parameters.
-        """
-        defaults = {'Ag': {'a': 2.928323832},
-                    'AgAg': {'b': 2.485883762}}
-        return defaults
-
-    def phi(self, r: tf.Tensor, kbody_term: str, variable_scope: str,
-            verbose=False):
-        """
-        The pairwise potential function:
-
-            phi(r) = (b / r)**12
-
-        """
-        with tf.variable_scope('Sutton'):
-            assert isinstance(variable_scope, str)
-            variable_scope = f"{variable_scope}/{kbody_term}"
-            one = tf.constant(1.0, r.dtype, name='one')
-            b = self._get_variable('b', r.dtype, kbody_term, variable_scope)
-            with tf.name_scope("ussafe_div"):
-                r = tf.div_no_nan(one, r, name='r_inv')
-            scale = tf.constant(12.0, dtype=r.dtype, name='scale')
-            phi = tf.identity(safe_pow(b * r, scale), 'phi')
-            if verbose:
-                log_tensor(phi)
-            return phi
-
-    def rho(self, r: tf.Tensor, element: str, variable_scope: str,
-            verbose=False):
-        """
-        The electron density function:
-
-            rho(r) = (a / r)**6
-
-        """
-        with tf.variable_scope('Sutton'):
-            assert isinstance(variable_scope, str)
-            variable_scope = f"{variable_scope}/{element}"
-            one = tf.constant(1.0, r.dtype, name='one')
-            a = self._get_variable('a', r.dtype, element, variable_scope)
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/tests/test_mishin.py

@@ -1,129 +1,0 @@
-#!coding=utf-8
-"""
-Unit tests of the `AdpNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import nose
-import unittest
-import shutil
-
-from tensorflow_estimator import estimator as tf_estimator
-from ase.build import bulk
-from ase.calculators.lammpsrun import LAMMPS
-from ase import Atoms
-from os.path import join, exists
-from os import makedirs
-from typing import List
-from nose.tools import assert_almost_equal
-
-from tensoralloy.test_utils import test_dir, assert_array_almost_equal
-from tensoralloy.transformer.adp import ADPTransformer
-from tensoralloy.nn.eam.adp import AdpNN
-from tensoralloy.precision import precision_scope
-from tensoralloy.io.lammps import LAMMPS_COMMAND
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class AlCuAdpTest(unittest.TestCase):
-
-    def setUp(self):
-        """
-        The setup function.
-        """
-        self.work_dir = join(test_dir(), 'lammps', 'adp')
-        if not exists(self.work_dir):
-            makedirs(self.work_dir)
-
-    def tearDown(self) -> None:
-        """
-        The cleanup function.
-        """
-        if exists(self.work_dir):
-            shutil.rmtree(self.work_dir)
-
-    def get_lammps_calculator(self, elements: List[str], use_official=False):
-        """
-        Return a LAMMPS calculator.
-        """
-        if use_official:
-            pot_file = join(test_dir(), 'lammps', 'AlCu.adp')
-        else:
-            pot_file = join(self.work_dir, 'AlCu.adp')
-        work_dir = join(self.work_dir, ''.join(elements))
-        if not exists(work_dir):
-            makedirs(work_dir)
-
-        return LAMMPS(files=[pot_file],
-                      binary_dump=False,
-                      write_velocities=False,
-                      tmp_dir=work_dir,
-                      keep_tmp_files=False,
-                      keep_alive=False,
-                      no_data_file=False,
-                      pair_style="adp",
-                      command=LAMMPS_COMMAND,
-                      pair_coeff=[f"* * AlCu.adp {' '.join(elements)}"])
-
-    def _run(self, atoms: Atoms, rc=7.5):
-        """
-        Run a test.
-        """
-        with precision_scope("high"):
-            with tf.Graph().as_default():
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/tests/test_msah11.py

@@ -1,280 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests for the MSAH11 Al-Fe potential.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import math
-import nose
-
-from tensoralloy.nn.eam.potentials.msah11 import AlFeMsah11
-from tensoralloy.test_utils import assert_array_almost_equal
-from tensoralloy.precision import get_float_dtype, precision_scope, Precision
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def atsim_embed_al(rho):
-    """
-    The embedding function of Al by ATSIM.
-    """
-    if rho == 0.0:
-        return 0.0
-    y1 = -math.sqrt(rho)
-    y2 = 0.000093283590195398 * rho ** 2
-    y3 = - 0.0023491751192724 * rho * math.log(rho)
-    return y1 + y2 + y3
-
-
-def atsim_embed_fe(rho):
-    """
-    The embedding function of Fe by ATSIM.
-    """
-    y1 = -math.sqrt(rho)
-    y2 = - 0.00067314115586063 * rho ** 2
-    y3 = 0.000000076514905604792 * rho ** 4
-    return y1 + y2 + y3
-
-
-def atsim_density_alal(r):
-    """
-    The density function of Al-Al by ATSIM.
-    """
-    funcs = [
-        (2.5, lambda x: 0.00019850823042883 * (2.5 - x) ** 4),
-        (2.6, lambda x: 0.10046665347629 * (2.6 - x) ** 4),
-        (2.7, lambda x: 1.0054338881951E-01 * (2.7 - x) ** 4),
-        (2.8, lambda x: 0.099104582963213 * (2.8 - x) ** 4),
-        (3.0, lambda x: 0.090086286376778 * (3.0 - x) ** 4),
-        (3.4, lambda x: 0.0073022698419468 * (3.4 - x) ** 4),
-        (4.2, lambda x: 0.014583614223199 * (4.2 - x) ** 4),
-        (4.8, lambda x: -0.0010327381407070 * (4.8 - x) ** 4),
-        (5.6, lambda x: 0.0073219994475288 * (5.6 - x) ** 4),
-        (6.5, lambda x: 0.0095726042919017 * (6.5 - x) ** 4)]
-    vals = [func(r) for cutoff, func in funcs if r <= cutoff]
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/tests/test_potentials.py

@@ -1,47 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests for the module `tensoralloy.nn.layers.layers`.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from nose.tools import assert_dict_equal
-
-from tensoralloy.nn.eam.potentials.potentials import EamEmpiricalPotential
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-# noinspection PyAbstractClass
-class _ParamPotential(EamEmpiricalPotential):
-    """
-    A layer with default parameters 'a', 'b', 'c' and 'd'.
-    """
-
-    defaults = {
-        'AlCu': {'a': 1.0, 'b': 1.0, 'c': 1.0, 'd': 1.0}
-    }
-
-
-def test_layer_init():
-    """
-    Test the initialization of `PotentialFunctionLayer`.
-    """
-    layer = EamEmpiricalPotential()
-
-    assert_dict_equal(layer.params, {})
-    assert_dict_equal(layer.fixed, {})
-
-    layer = _ParamPotential()
-    assert_dict_equal(layer.params, {'AlCu': {'a': 1.0, 'b': 1.0,
-                                              'c': 1.0, 'd': 1.0}})
-
-    layer = _ParamPotential(params={'AlCu': {"a": 2.0, "b": 3.0}})
-    assert_dict_equal(layer.params,
-                      {'AlCu': {'a': 2.0, 'b': 3.0, 'c': 1.0, 'd': 1.0}})
-
-
-if __name__ == "__main__":
-    nose.run()

### 2019-08-16 tensoralloy/nn/eam/potentials/tests/test_sutton90.py

@@ -1,157 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `AgSutton90`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import nose
-import os
-import unittest
-
-from tensorflow_estimator import estimator as tf_estimator
-from ase.build import bulk
-from ase.calculators.lammpsrun import LAMMPS
-from collections import Counter
-from os.path import join, exists
-from shutil import rmtree
-from unittest import skipUnless
-from nose.tools import assert_almost_equal
-
-from tensoralloy.transformer import BatchEAMTransformer, EAMTransformer
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.utils import AttributeDict
-from tensoralloy.test_utils import test_dir
-from tensoralloy.io.lammps import LAMMPS_COMMAND
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-@skipUnless(exists(LAMMPS_COMMAND), f"LAMMPS not found!")
-class EamSutton90Test(unittest.TestCase):
-
-    def setUp(self):
-        """
-        The setup function.
-        """
-        self.tmp_dir = join(test_dir(absolute=True), 'lammps', 'sutton90')
-        if not exists(self.tmp_dir):
-            os.makedirs(self.tmp_dir)
-
-    def get_lammps_calculator(self):
-        """
-        Return a LAMMPS calculator for Ag.
-        """
-        eam_file = join(test_dir(absolute=True), 'lammps', 'Ag.funcfl.eam')
-        return LAMMPS(files=[eam_file],
-                      binary_dump=False,
-                      write_velocities=False,
-                      tmp_dir=self.tmp_dir,
-                      keep_tmp_files=False,
-                      keep_alive=False,
-                      no_data_file=False,
-                      pair_style="eam",
-                      command=LAMMPS_COMMAND,
-                      pair_coeff=['1 1 Ag.funcfl.eam'])
-
-    def tearDown(self):
-        """
-        Delete the tmp dir.
-        """
-        if exists(self.tmp_dir):
-            rmtree(self.tmp_dir, ignore_errors=True)
-
-    def test_eam_sutton90_batch_transformer(self):
-        """
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/tests/test_zjw04.py

@@ -1,370 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests for ZJW04 functions.
-
-The reference codes are provided by `atsim.potentials`:
-
-https://atsimpotentials.readthedocs.io/en/latest/index.html
-
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-import math
-
-from tensorflow.python.framework.ops import IndexedSlicesValue
-from nose.tools import assert_equal, assert_false
-
-from tensoralloy.test_utils import assert_array_equal, assert_array_almost_equal
-from tensoralloy.nn.eam.potentials.zjw04 import Zjw04, Zjw04xc, Zjw04uxc
-from tensoralloy.utils import GraphKeys, AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def atsim_make_func(a, b, r_e, c):
-    """
-    Creates functions of the form used for density function.
-    Functional form also forms components of pair potential.
-    """
-    def func(r):
-        """
-        The exponential-type potential function.
-        """
-        return (a * math.exp(-b * (r / r_e - 1))) / (1 + (r / r_e - c) ** 20.0)
-    return func
-
-
-def atsim_make_pairpot_aa(A, gamma, r_e, kappa,
-                          B, omega, lamda):
-    """
-    Function factory that returns functions parameterised for homogeneous pair
-    interactions.
-    """
-    f1 = atsim_make_func(A, gamma, r_e, kappa)
-    f2 = atsim_make_func(B, omega, r_e, lamda)
-
-    def func(r):
-        """
-        Return f1(r) - f2(r)
-        """
-        return f1(r) - f2(r)
-    return func
-
-
-def atsim_make_pairpot_ab(dens_a, phi_aa, dens_b, phi_bb):
-    """
-    Function factory that returns functions parameterised for heterogeneous pair
-    interactions.
-    """
-    def func(r):
-        """
-        phi_ab(r) = 0.5 * (
-            rho_a(r) / rho_b(r) * phi_bb(r) + rho_b(r) / rho_a(r) * phi_aa(r)
-        )
-        """
-        v1 = dens_b(r) / dens_a(r) * phi_aa(r)
-        v2 = dens_a(r) / dens_b(r) * phi_bb(r)
-        return 0.5 * (v1 + v2)
[…]

### 2019-08-16 tensoralloy/nn/eam/potentials/zjw04.py

@@ -1,683 +1,0 @@
-# coding=utf-8
-"""
-This module defines the empirical potential of Al-Cu proposed by Zhou et al. at
-2004.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-
-from tensoralloy.nn.eam.potentials.potentials import EamAlloyPotential
-from tensoralloy.nn.utils import log_tensor
-from tensoralloy.nn.eam.potentials.generic import zhou_exp
-from tensoralloy.utils import get_elements_from_kbody_term
-from tensoralloy.extension.grad_ops import safe_pow
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-zjw04_defaults = {
-    'Al': {
-        'r_eq': 2.863924, 'f_eq': 1.403115,
-        'rho_e': 20.418205, 'rho_s': 23.195740,
-        'alpha': 6.613165, 'beta': 3.527021,
-        'A': 0.314873, 'B': 0.365551,
-        'kappa': 0.379846, 'lamda': 0.759692,
-        'Fn0': -2.807602, 'Fn1': -0.301435,
-        'Fn2': 1.258562, 'Fn3': -1.247604,
-        'F0': -2.83, 'F1': 0.0, 'F2': 0.622245, 'F3': -2.488244,
-        'eta': 0.785902, 'Fe': -2.824528,
-    },
-    'Cu': {
-        'r_eq': 2.556162, 'f_eq': 1.554485,
-        'rho_e': 21.175871, 'rho_s': 21.175395,
-        'alpha': 8.127620, 'beta': 4.334731,
-        'A': 0.396620, 'B': 0.548085,
-        'kappa': 0.308782, 'lamda': 0.756515,
-        'Fn0': -2.170269, 'Fn1': -0.263788,
-        'Fn2': 1.088878, 'Fn3': -0.817603,
-        'F0': -2.19, 'F1': 0.0, 'F2': 0.561830, 'F3': -2.100595,
-        'eta': 0.310490, 'Fe': -2.186568,
-    },
-    'Ni': {
-        'r_eq': 2.488746, 'f_eq': 2.007018,
-        'rho_e': 27.562015, 'rho_s': 27.930410,
-        'alpha': 8.383453, 'beta': 4.471175,
-        'A': 0.429046, 'B': 0.633531,
[…]

### 2019-08-16 tensoralloy/nn/eam/tests/test_adp_nn.py

@@ -1,101 +1,0 @@
-#!coding=utf-8
-"""
-This module defines unit tests of `AdpNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from tensorflow_estimator import estimator as tf_estimator
-from os.path import join
-from ase.io import read
-from ase.calculators.singlepoint import SinglePointCalculator
-from nose.tools import assert_equal
-from collections import Counter
-
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.nn.eam.adp import AdpNN
-from tensoralloy.transformer.adp import ADPTransformer, BatchADPTransformer
-from tensoralloy.test_utils import test_dir
-from tensoralloy.utils import AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_dynamic_partition():
-    """
-    Test the modified implementation of `_dynamic_partition`.
-    """
-    atoms = read(join(test_dir(), "crystals",
-                      "Ni4Mo_mp-11507_conventional_standard.cif"))
-    atoms.calc = SinglePointCalculator(
-        atoms, **{'energy': 0.0, 'forces': np.zeros_like(atoms.positions)})
-
-    rc = 6.5
-    elements = ['Mo', 'Ni']
-
-    with tf.Graph().as_default():
-
-        nn = AdpNN(elements=elements)
-        adp = ADPTransformer(rc, elements)
-        adp.get_placeholder_features()
-
-        with tf.name_scope("Symmetric"):
-
-            op, max_occurs = nn._dynamic_partition(
-                adp.get_descriptors(adp.get_placeholder_features()),
-                mode=tf_estimator.ModeKeys.PREDICT,
-                merge_symmetric=True)
-
-            with tf.Session() as sess:
-                tf.global_variables_initializer().run()
-
-                partitions = sess.run(
-                    op, feed_dict=adp.get_feed_dict(atoms))
-
-                assert_equal(len(partitions), 3)
-                for key, (descriptor, mask) in partitions.items():
-                    assert_equal(descriptor.shape[0], 4)
-                    assert_equal(mask.shape[0], 1)
-
-    with tf.Graph().as_default():
-        nn = AdpNN(elements=elements)
-
-        size = find_neighbor_size_of_atoms(atoms, rc)
-        max_occurs = Counter(atoms.get_chemical_symbols())
-
-        adp = BatchADPTransformer(rc=rc,
[…]

### 2019-08-16 tensoralloy/nn/eam/tests/test_eam_alloy_nn.py

@@ -1,810 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `EamAlloyNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-import os
-import shutil
-import unittest
-
-from tensorflow_estimator import estimator as tf_estimator
-from pymatgen import Lattice, Structure
-from pymatgen.core.surface import SlabGenerator
-from pymatgen.io.ase import AseAtomsAdaptor
-from nose.tools import assert_equal, assert_tuple_equal, assert_almost_equal
-from nose.tools import assert_dict_equal, assert_list_equal, with_setup
-from os.path import join, exists
-from os import remove
-from collections import Counter
-from unittest import skipUnless
-from ase.calculators.lammpsrun import LAMMPS
-from ase.build import bulk
-from ase.db import connect
-from ase.units import GPa
-from ase.io import read
-
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.transformer import EAMTransformer, BatchEAMTransformer
-from tensoralloy.test_utils import assert_array_equal, datasets_dir
-from tensoralloy.test_utils import assert_array_almost_equal, test_dir
-from tensoralloy.utils import GraphKeys, AttributeDict, Defaults
-from tensoralloy.calculator import TensorAlloyCalculator
-from tensoralloy.io.lammps import LAMMPS_COMMAND
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class AlCuFakeData:
-    """
-    A fake dataset for unit tests in this module.
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        self.batch_size = 10
-        self.max_n_terms = 2
-        self.max_n_al = 5
-        self.max_n_cu = 7
-        self.max_n_atoms = self.max_n_al + self.max_n_cu
-        self.max_occurs = Counter({'Al': self.max_n_al, 'Cu': self.max_n_cu})
-        self.nnl = 10
-        self.elements = sorted(['Cu', 'Al'])
-
-        shape_al = (4,
-                    self.batch_size,
-                    self.max_n_terms,
-                    self.max_n_al,
-                    self.nnl)
-        shape_cu = (4,
[…]

### 2019-08-16 tensoralloy/nn/eam/tests/test_eam_fs_nn.py

@@ -1,301 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `EamFsNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-import os
-import shutil
-import unittest
-
-from tensorflow_estimator import estimator as tf_estimator
-from unittest import skipUnless
-from nose.tools import assert_list_equal, assert_dict_equal, with_setup
-from nose.tools import assert_equal, assert_almost_equal
-from os.path import exists, join
-from os import remove
-from ase.calculators.lammpsrun import LAMMPS
-from ase.build import bulk
-
-from tensoralloy.nn.eam import EamFsNN
-from tensoralloy.transformer import EAMTransformer
-from tensoralloy.test_utils import assert_array_almost_equal, test_dir
-from tensoralloy.utils import get_elements_from_kbody_term, GraphKeys
-from tensoralloy.utils import AttributeDict
-from tensoralloy.io.lammps import LAMMPS_COMMAND
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class AlFeFakeData:
-    """
-    A fake dataset for unit tests in this module.
-    """
-
-    def __init__(self):
-        """
-        Initialization method.
-        """
-        self.batch_size = 10
-        self.max_n_terms = 2
-        self.max_n_al = 5
-        self.max_n_fe = 7
-        self.max_n_atoms = self.max_n_al + self.max_n_fe + 1
-        self.nnl = 10
-        self.elements = sorted(['Fe', 'Al'])
-
-        shape_al = (4,
-                    self.batch_size,
-                    self.max_n_terms,
-                    self.max_n_al,
-                    self.nnl)
-        shape_fe = (4,
-                    self.batch_size,
-                    self.max_n_terms,
-                    self.max_n_fe,
-                    self.nnl)
-
-        self.g_al = np.random.randn(*shape_al)
-        self.m_al = np.random.randint(0, 2, shape_al[1:]).astype(np.float64)
-        self.g_fe = np.random.randn(*shape_fe)
-        self.m_fe = np.random.randint(0, 2, shape_fe[1:]).astype(np.float64)
-
-        with tf.name_scope("Inputs"):
-            self.descriptors = AttributeDict(
-                Al=(tf.convert_to_tensor(self.g_al, tf.float64, 'g_al'),
-                    tf.convert_to_tensor(self.m_al, tf.float64, 'm_al')),
[…]

### 2019-08-16 tensoralloy/nn/tests/test_basic_nn.py

@@ -1,272 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `BasicNN`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from tensorflow_estimator import estimator as tf_estimator
-from nose.tools import assert_dict_equal, assert_equal, assert_true
-from nose.tools import assert_almost_equal
-from ase.db import connect
-from ase.build import bulk
-from ase.units import GPa
-from os.path import join
-from collections import Counter
-from typing import List
-from tensorflow.core.framework import graph_pb2
-from tensorflow.python.framework import importer
-
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.nn.basic import BasicNN
-from tensoralloy.nn.atomic import AtomicNN
-from tensoralloy.nn.eam.alloy import EamAlloyNN
-from tensoralloy.nn.dataclasses import LossParameters
-from tensoralloy.transformer import BatchSymmetryFunctionTransformer
-from tensoralloy.transformer import EAMTransformer
-from tensoralloy.utils import AttributeDict, Defaults, set_pulay_stress
-from tensoralloy.test_utils import assert_array_equal, datasets_dir, test_dir
-from tensoralloy.test_utils import assert_array_almost_equal
-from tensoralloy.precision import precision_scope
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_energy_pv():
-    """
-    Test the total energy Op and the stress Op after the introduction of `E_pv`.
-    """
-    atoms = bulk('Ni')
-    volume = atoms.get_volume()
-    rc = 6.0
-    elements = ['Ni']
-    mode = tf_estimator.ModeKeys.PREDICT
-
-    with precision_scope("high"):
-
-        with tf.Graph().as_default():
-
-            nn = EamAlloyNN(elements, custom_potentials='zjw04',
-                            export_properties=['energy', 'forces', 'stress'])
-            clf = EAMTransformer(rc, elements)
-            nn.attach_transformer(clf)
-
-            with tf.name_scope("0GPa"):
-                zero_ops = nn.build(
-                    clf.get_constant_features(atoms), mode=mode, verbose=False)
-
-            with tf.name_scope("10GPa"):
-                set_pulay_stress(atoms, 10.0 * GPa)
-                ten_ops = nn.build(
-                    clf.get_constant_features(atoms), mode=mode, verbose=False)
-
[…]

### 2019-08-16 tensoralloy/nn/tests/test_convolutional.py

@@ -1,72 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests of `tensoralloy.nn.convolutional`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from nose.tools import assert_almost_equal
-
-from tensoralloy.nn.convolutional import convolution1x1
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_convolution1x1():
-    """
-    Test the function `convolution1x1`.
-    """
-    with tf.Graph().as_default():
-
-        x = tf.convert_to_tensor(np.random.rand(5, 100, 8), name='x')
-        y_nn = convolution1x1(x, activation_fn=tf.nn.tanh,
-                              collections=[tf.GraphKeys.MODEL_VARIABLES],
-                              hidden_sizes=[128, 64],
-                              variable_scope='NN',
-                              l2_weight=0.01)
-        y_true = tf.convert_to_tensor(np.random.rand(5, 100, 1), name='y_true')
-        loss = tf.reduce_mean(tf.squared_difference(y_nn, y_true))
-        tf.train.AdamOptimizer().minimize(loss)
-
-        reg_loss = tf.losses.get_regularization_loss()
-
-        l2_losses = []
-        for var in tf.get_collection(tf.GraphKeys.MODEL_VARIABLES):
-            l2_losses.append(tf.nn.l2_loss(var))
-        l2_loss = tf.add_n(l2_losses)
-
-        with tf.Session() as sess:
-            tf.global_variables_initializer().run()
-            l2_value, reg_value = sess.run([l2_loss, reg_loss])
-
-            assert_almost_equal(l2_value * 0.01, reg_value, delta=1e-8)
-
-
-def test_convolution1x1_without_l2_reg():
-    """
-    Test the function `convolution1x1` without l2 regularization.
-    """
-    with tf.Graph().as_default():
-
-        x = tf.convert_to_tensor(np.random.rand(5, 100, 8), name='x')
-        y_nn = convolution1x1(x, activation_fn=tf.nn.tanh,
-                              hidden_sizes=[128, 64],
-                              variable_scope='NN',
-                              l2_weight=0.0)
-        y_true = tf.convert_to_tensor(np.random.rand(5, 100, 1), name='y_true')
-        loss = tf.reduce_mean(tf.squared_difference(y_nn, y_true))
[…]

### 2019-08-16 tensoralloy/nn/tests/test_dataclasses.py

@@ -1,58 +1,0 @@
-#!coding=utf-8
-"""
-This module defines unit tests of the data classes.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from nose.tools import assert_equal, assert_raises, assert_is_none
-
-from tensoralloy.nn.dataclasses import OptParameters, LossParameters
-from tensoralloy.nn.dataclasses import TrainParameters
-from tensoralloy.utils import AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_dataclasses():
-    """
-    Test some data classes.
-    """
-    hparams = AttributeDict(
-        opt=dict(decay_steps=100, method='rmsprop'),
-        loss=dict(
-            energy=dict(per_atom_loss=True),
-            forces=dict(method='logcosh'),
-            elastic=dict(crystals=['Ni'], constraint=dict(stress_weight=1.5))
-        ),
-        train=dict(model_dir="..",
-                   ckpt=dict(restore_all_variables=False,
-                             use_ema_variables=False))
-    )
-
-    opt_parameters = OptParameters(**hparams.opt)
-
-    assert_equal(opt_parameters.decay_steps, 100)
-    assert_equal(opt_parameters.method, 'rmsprop')
-
-    loss_parameters = LossParameters(**hparams.loss)
-
-    assert_equal(loss_parameters.energy.per_atom_loss, True)
-    assert_equal(loss_parameters.forces.method, 'logcosh')
-    assert_equal(loss_parameters.elastic.crystals, ['Ni'])
-    assert_equal(loss_parameters.elastic.constraint.stress_weight, 1.5)
-
-    assert_is_none(loss_parameters.rose.crystals, None)
-    assert_equal(loss_parameters.rose.dx, 0.10)
-
-    train_parameters = TrainParameters(**hparams['train'])
-    assert_equal(train_parameters.ckpt.use_ema_variables, False)
-
-    with assert_raises(Exception):
-        _ = OptParameters(**AttributeDict(decay_method='adam'))
-
-
-if __name__ == "__main__":
-    nose.run()

### 2019-08-16 tensoralloy/nn/tests/test_losses.py

@@ -1,124 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of the module `losses`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from nose.tools import assert_less, assert_equal
-from sklearn.metrics import mean_absolute_error, mean_squared_error
-
-from tensoralloy.nn.losses import get_energy_loss, get_forces_loss
-from tensoralloy.nn.losses import get_stress_loss
-from tensoralloy.precision import precision_scope, get_float_dtype
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_energy_loss():
-    """
-    Test the function `get_energy_loss`.
-    """
-    with precision_scope('medium'):
-
-        dtype = get_float_dtype()
-
-        x = np.random.uniform(0.0, 3.0, size=(6, )).astype(dtype.as_numpy_dtype)
-        y = np.random.uniform(0.0, 3.0, size=(6, )).astype(dtype.as_numpy_dtype)
-        n = np.random.randint(1, 5, size=(6, )).astype(dtype.as_numpy_dtype)
-
-        y_rmse = np.sqrt(mean_squared_error(x / n, y / n))
-        y_mae = mean_absolute_error(x / n, y / n)
-
-        with tf.Graph().as_default():
-
-            x = tf.convert_to_tensor(x)
-            y = tf.convert_to_tensor(y)
-            n = tf.convert_to_tensor(n)
-
-            rmse = get_energy_loss(x, y, weights=None,
-                                   n_atoms=n, collections=['UnitTest'])
-            assert_equal(len(tf.get_collection('UnitTest')), 3)
-
-            mae = tf.get_default_graph().get_tensor_by_name('Energy/mae:0')
-
-            with tf.Session() as sess:
-                assert_less(y_rmse - sess.run(rmse), 1e-8)
-                assert_less(y_mae - sess.run(mae), 1e-8)
-
-
-def test_forces_loss():
-    """
-    Test the function `get_forces_loss`.
-    """
-    with precision_scope('high'):
-
-        x = np.random.uniform(0.0, 3.0, size=(6, 8, 3))
-        y = np.random.uniform(0.0, 3.0, size=(6, 8, 3))
-        n_atoms = np.asarray([5, 6, 4, 8, 5, 3])
-        mask = np.zeros((6, 9))
[…]

### 2019-08-16 tensoralloy/nn/tests/test_opt.py

@@ -1,112 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests of module `tensoralloy.nn.ops`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import nose
-
-from os.path import join
-from nose.tools import assert_equal
-from tensorflow_estimator import estimator as tf_estimator
-
-from tensoralloy.test_utils import test_dir
-from tensoralloy.dataset import Dataset
-from tensoralloy.io.db import connect
-from tensoralloy.transformer import BatchSymmetryFunctionTransformer
-from tensoralloy.nn.opt import get_train_op
-from tensoralloy.nn.atomic import AtomicNN
-from tensoralloy.nn.dataclasses import OptParameters, LossParameters
-from tensoralloy.utils import Defaults
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def _get_train_op(trainable=False):
-    """
-    A helper function to created a `train_op`.
-    """
-    work_dir = join(test_dir(), 'Ni')
-
-    database = connect(join(work_dir, 'Ni.db'))
-    clf = BatchSymmetryFunctionTransformer(
-        rc=Defaults.rc,
-        max_occurs=database.max_occurs,
-        nij_max=database.get_nij_max(Defaults.rc),
-        nijk_max=0,
-        angular=False,
-        trainable=trainable)
-
-    dataset = Dataset(database, name='Ni', transformer=clf, serial=True)
-
-    if not dataset.load_tfrecords(work_dir):
-        dataset.to_records(work_dir, test_size=1)
-    assert_equal(dataset.test_size, 1)
-
-    input_fn = dataset.input_fn(mode=tf_estimator.ModeKeys.TRAIN,
-                                batch_size=1,
-                                num_epochs=None,
-                                shuffle=False)
-
-    features, labels = input_fn()
-
-    loss_parameters = LossParameters()
-    loss_parameters.energy.weight = 1.0
-
-    opt_parameters = OptParameters(learning_rate=0.01, decay_function=None,
-                                   decay_rate=0.9, staircase=False,
-                                   method='Adam')
-
-    nn = AtomicNN(elements=dataset.transformer.elements)
-    nn.attach_transformer(dataset.transformer)
-
-    predictions = nn.build(features, tf_estimator.ModeKeys.TRAIN)
-    total_loss, losses = nn.get_total_loss(
[…]

### 2019-08-16 tensoralloy/tests/test_calculator.py

@@ -1,220 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `TensorAlloyCalculator`.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import nose
-import shutil
-import os
-import unittest
-
-from unittest import skipUnless
-from datetime import datetime
-from nose.tools import assert_almost_equal, assert_equal
-from nose.tools import assert_list_equal, assert_is_not_none, assert_less
-from os.path import join, exists
-from ase.db import connect
-from ase.calculators.lammpsrun import LAMMPS
-from ase.build import bulk
-from sklearn.metrics import mean_absolute_error
-from sklearn.model_selection import train_test_split
-from pymatgen import Lattice, Structure
-from pymatgen.core.surface import SlabGenerator
-from pymatgen.io.ase import AseAtomsAdaptor
-
-from tensoralloy.calculator import TensorAlloyCalculator
-from tensoralloy.transformer import EAMTransformer
-from tensoralloy.nn import EamAlloyNN
-from tensoralloy.utils import Defaults
-from tensoralloy.io.lammps import LAMMPS_COMMAND
-from tensoralloy.test_utils import test_dir, datasets_dir
-from tensoralloy.test_utils import assert_array_almost_equal
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-
-class ModelTimeStampTest(unittest.TestCase):
-
-    def setUp(self):
-        """
-        Setup this test case.
-        """
-        self.pb_file = 'Ni.test.pb'
-
-    def test_get_model_timestamp(self):
-        """
-        Test the method `get_model_timestamp`.
-        """
-        nn = EamAlloyNN(['Ni'], 'zjw04xc',
-                        export_properties=['energy', 'forces', 'stress',
-                                           'hessian'])
-        nn.attach_transformer(EAMTransformer(6.0, ['Ni']))
-        nn.export(self.pb_file, keep_tmp_files=False)
-
-        calc = TensorAlloyCalculator(self.pb_file)
-        timestamp = calc.get_model_timestamp()
-        assert_is_not_none(timestamp)
-
-        encoded = datetime.fromisoformat(timestamp)
-        now = datetime.now()
-
[…]

### 2019-08-16 tensoralloy/tests/test_cli.py

@@ -1,47 +1,0 @@
-#!coding=utf-8
-"""
-This module defines tests of the `CLI` module.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-import unittest
-
-from os.path import join, exists
-from os import remove
-from nose.tools import assert_equal
-
-from tensoralloy.cli.entry import PrintEvaluationSummaryProgram
-from tensoralloy.test_utils import test_dir
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class PrintSummaryTest(unittest.TestCase):
-
-    def setUp(self):
-        """
-        The setup function.
-        """
-        self.csv_file = join(test_dir(), 'summary.csv')
-
-    def test_print_summary(self):
-        """
-        Test `PrintEvaluationSummaryProgram`.
-        """
-        program = PrintEvaluationSummaryProgram()
-        df = program.print_evaluation_summary(join(test_dir(), "logfile"))
-        assert_equal(df.index.tolist(), [500, 1000])
-        assert_equal(exists(self.csv_file), True)
-
-    def tearDown(self):
-        """
-        The cleanup function.
-        """
-        if exists(self.csv_file):
-            remove(self.csv_file)
-
-
-if __name__ == "__main__":
-    nose.main()

### 2019-08-16 tensoralloy/tests/test_dtypes.py

@@ -1,29 +1,0 @@
-#!coding=utf-8
-"""
-The unit tests of `tensoralloy.dtypes` module.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from nose.tools import assert_equal
-
-from tensoralloy.precision import precision_scope, get_float_precision, Precision
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_set_precision():
-    """
-    Test the with statement of `set_precision`.
-    """
-    with precision_scope(Precision.medium):
-        assert_equal(get_float_precision(), Precision.medium)
-
-    with precision_scope(Precision.high):
-        assert_equal(get_float_precision(), Precision.high)
-
-
-if __name__ == "__main__":
-    nose.run()

### 2019-08-16 tensoralloy/tests/test_utils.py

@@ -1,124 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `tensoralloy.utils`.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import nose
-
-from nose.tools import assert_equal, assert_list_equal, assert_dict_equal
-
-from tensoralloy.utils import cantor_pairing
-from tensoralloy.utils import nested_get, nested_set
-from tensoralloy.utils import get_elements_from_kbody_term, get_kbody_terms
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_nested_set():
-    """
-    Test the function `nested_set`.
-    """
-    d = {}
-    nested_set(d, 'a.b.c', 4)
-    assert_dict_equal(d, {'a': {'b': {'c': 4}}})
-
-    nested_set(d, ['a', 'b'], {'x': [2, 3]})
-    assert_dict_equal(d, {'a': {'b': {'x': [2, 3]}}})
-
-
-def test_nested_get():
-    """
-    Test the function `nested_get`.
-    """
-    d = {
-        'a': {
-            'b': 2,
-            'c': {
-                'd': 4
-            }
-        }
-    }
-    assert_dict_equal(nested_get(d, "a.c"), {'d': 4})
-    assert_equal(nested_get(d, 'a.b.c.d'), None)
-    assert_equal(nested_get(d, ['a', 'c', 'd']), 4)
-
-
-def test_cantor_pairing():
-    """
-    Test the pairing function: `cantor`.
-    """
-    x = np.arange(0, 100, 1)
-    y = np.arange(0, 100, 1)
-    xx, yy = np.meshgrid(x, y)
-    z = cantor_pairing(xx.flatten(), yy.flatten()).tolist()
-    assert_equal(len(set(z)), xx.size)
-
-
-def test_get_elements_from_kbody_term():
-    """
-    Test `get_elements_from_kbody_term`.
-    """
-    assert_list_equal(get_elements_from_kbody_term("AlCu"), ['Al', 'Cu'])
-    assert_list_equal(get_elements_from_kbody_term("CuH"), ['Cu', 'H'])
-    assert_list_equal(get_elements_from_kbody_term("HH"), ['H', 'H'])
-    assert_list_equal(get_elements_from_kbody_term("HHCu"), ['H', 'H', 'Cu'])
-    assert_list_equal(get_elements_from_kbody_term("HHH"), ['H', 'H', 'H'])
-
[…]

### 2019-08-16 tensoralloy/train/tests/test_training.py

@@ -1,246 +1,0 @@
-# coding=utf-8
-"""
-This module defines tests of `TrainingManager`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import nose
-import shutil
-import glob
-import os
-import unittest
-
-from tensorflow_estimator import estimator as tf_estimator
-from unittest import skipUnless
-from os.path import join, exists
-from nose.tools import assert_equal, assert_is_none, assert_in
-from nose.tools import with_setup, assert_dict_equal, assert_true
-
-from tensoralloy.utils import Defaults
-from tensoralloy.train.training import TrainingManager
-from tensoralloy.nn import EamAlloyNN, AtomicResNN
-from tensoralloy.test_utils import test_dir, assert_array_almost_equal
-from tensoralloy.transformer import BatchSymmetryFunctionTransformer
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class InitializationTest(unittest.TestCase):
-
-    def tearDown(self):
-        """
-        The cleanup function.
-        """
-        model_dir = join(test_dir(), 'inputs', 'model')
-        if exists(model_dir):
-            shutil.rmtree(model_dir, ignore_errors=True)
-
-    @staticmethod
-    def test_initialization():
-        """
-        Test the initialization of a `TrainingManager`.
-        """
-        input_file = join(test_dir(), 'inputs', 'Ni.behler.k2.toml')
-        manager = TrainingManager(input_file)
-        transformer = manager.dataset.transformer
-        hparams = manager.hparams
-        nn = manager.nn
-
-        assert_equal(manager.dataset.transformer.descriptor, 'behler')
-        assert_equal(manager.dataset.test_size, 1)
-        assert_equal(manager.dataset.transformer.rc, 6.0)
-
-        assert isinstance(transformer, BatchSymmetryFunctionTransformer)
-        assert_equal(transformer.trainable, True)
-
-        assert_equal(hparams.opt.method, 'sgd')
-        assert_equal(hparams.opt.learning_rate, 0.01)
-        assert_is_none(hparams.opt.decay_function)
-        assert_equal(hparams.precision, 'medium')
-        assert_equal(hparams.seed, 1958)
-        assert_dict_equal(hparams.opt.additional_kwargs,
-                          {'use_nesterov': True, 'momentum': 0.8})
-
-        assert_true(isinstance(nn, AtomicResNN))
-        assert_true(nn.fixed_static_energy)
[…]

### 2019-08-16 tensoralloy/transformer/behler.py

@@ -1,760 +1,0 @@
-# coding=utf-8
-"""
-This module defines the feature transformers (flexible, fixed) for Behler's
-Symmetry Function descriptor.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from collections import Counter
-from typing import Dict, Tuple
-from ase import Atoms
-from ase.neighborlist import neighbor_list
-
-from tensoralloy.descriptor import SymmetryFunction, BatchSymmetryFunction
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.transformer.base import DescriptorTransformer
-from tensoralloy.transformer.base import BatchDescriptorTransformer
-from tensoralloy.transformer.base import bytes_feature
-from tensoralloy.transformer.index_transformer import IndexTransformer
-from tensoralloy.transformer.indexed_slices import G2IndexedSlices
-from tensoralloy.transformer.indexed_slices import G4IndexedSlices
-from tensoralloy.utils import AttributeDict, Defaults, get_pulay_stress
-
-
-# TODO: universal v2gmap
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-__all__ = ["SymmetryFunctionTransformer", "BatchSymmetryFunctionTransformer"]
-
-
-class SymmetryFunctionTransformer(SymmetryFunction, DescriptorTransformer):
-    """
-    A tranformer for providing the feed dict to calculate symmetry function
-    descriptors of an `Atoms` object.
-    """
-
-    def __init__(self, rc, elements, eta=Defaults.eta, omega=Defaults.omega,
-                 beta=Defaults.beta, gamma=Defaults.gamma, zeta=Defaults.zeta,
-                 angular=False, periodic=True, trainable=False,
-                 cutoff_function='cosine'):
-        """
-        Initialization method.
-        """
-        SymmetryFunction.__init__(
-            self, rc=rc, elements=elements, eta=eta, omega=omega, beta=beta,
-            gamma=gamma, zeta=zeta, angular=angular, periodic=periodic,
-            trainable=trainable, cutoff_function=cutoff_function)
-        DescriptorTransformer.__init__(self)
-
-    def as_dict(self):
-        """
-        Return a JSON serializable dict representation of this transformer.
-        """
-        d = {'class': self.__class__.__name__, 'rc': self._rc,
-             'elements': self._elements, 'angular': self._angular,
[…]

### 2019-08-16 tensoralloy/transformer/eam.py

@@ -1,470 +1,0 @@
-# coding=utf-8
-"""
-This module defines the fixed transformer for EAM.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from collections import Counter
-from typing import Dict, Tuple, List
-from ase import Atoms
-from ase.neighborlist import neighbor_list
-
-from tensoralloy.descriptor.eam import EAM, BatchEAM
-from tensoralloy.utils import AttributeDict, get_pulay_stress
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.transformer.indexed_slices import G2IndexedSlices
-from tensoralloy.transformer.index_transformer import IndexTransformer
-from tensoralloy.transformer.base import BatchDescriptorTransformer
-from tensoralloy.transformer.base import DescriptorTransformer
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-__all__ = ["BatchEAMTransformer", "EAMTransformer"]
-
-
-class EAMTransformer(EAM, DescriptorTransformer):
-    """
-    The feature transformer for the EAM potential.
-    """
-
-    def __init__(self, rc: float, elements: List[str]):
-        """
-        Initialization method.
-        """
-        EAM.__init__(self, rc=rc, elements=elements)
-        DescriptorTransformer.__init__(self)
-
-    def as_dict(self):
-        """
-        Return a JSON serializable dict representation of this transformer.
-        """
-        d = {'class': self.__class__.__name__,
-             'rc': self._rc,
-             'elements': self._elements}
-        return d
-
-    def _initialize_placeholders(self):
-        """
-        Initialize the placeholders.
-        """
-        graph = tf.get_default_graph()
-
-        # Make sure the all placeholder ops are placed under the absolute path
-        # of 'Placeholders/'. Placeholder ops can be recovered from graph
-        # directly.
-        with tf.name_scope("Placeholders/"):
-
-            def _get_or_create(dtype, shape, name):
-                try:
-                    return graph.get_tensor_by_name(f'Placeholders/{name}:0')
-                except KeyError:
-                    return tf.placeholder(dtype, shape, name)
-                except Exception as excp:
-                    raise excp
-
-            float_dtype = get_float_dtype()
-
-            def _float(name):
-                return _get_or_create(float_dtype, (), name)
-
[…]

### 2019-08-16 tensoralloy/transformer/meam.py

@@ -1,438 +1,0 @@
-#!coding=utf-8
-"""
-Descriptor transformers of MEAM.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-
-from ase import Atoms
-from ase.neighborlist import neighbor_list
-from typing import List, Dict
-from collections import Counter
-
-from tensoralloy.descriptor.meam import MEAM
-from tensoralloy.transformer.base import DescriptorTransformer
-from tensoralloy.transformer import IndexTransformer
-from tensoralloy.transformer.indexed_slices import G2IndexedSlices
-from tensoralloy.transformer.indexed_slices import G4IndexedSlices
-from tensoralloy.precision import get_float_dtype
-from tensoralloy.utils import AttributeDict
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class MeamTransformer(MEAM, DescriptorTransformer):
-    """
-    The feature transformer for the EAM model.
-    """
-
-    def __init__(self, rc: float, elements: List[str], angular_rc_scale=1.0):
-        """
-        Initialization method.
-        """
-        MEAM.__init__(self,
-                      rc=rc,
-                      elements=elements,
-                      angular_rc_scale=angular_rc_scale)
-        DescriptorTransformer.__init__(self)
-
-    def as_dict(self):
-        """
-        Return a JSON serializable dict representation of this transformer.
-        """
-        d = {'class': self.__class__.__name__,
-             'rc': self._rc,
-             'elements': self._elements,
-             'angular_rc_scale': self._angular_rc_scale}
-        return d
-
-    def _initialize_placeholders(self):
-        """
-        Initialize the placeholders.
-        """
-        graph = tf.get_default_graph()
-
-        # Make sure the all placeholder ops are placed under the absolute path
-        # of 'Placeholders/'. Placeholder ops can be recovered from graph
-        # directly.
-        with tf.name_scope("Placeholders/"):
-
-            def _get_or_create(dtype, shape, name):
-                try:
-                    return graph.get_tensor_by_name(f'Placeholders/{name}:0')
-                except KeyError:
-                    return tf.placeholder(dtype, shape, name)
-                except Exception as excp:
-                    raise excp
-
-            float_dtype = get_float_dtype()
-
[…]

### 2019-08-16 tensoralloy/transformer/tests/test_behler.py

@@ -1,905 +1,0 @@
-# coding=utf-8
-"""
-This module defines the unit tests for implementations of Behler's symmetry
-functions.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from nose.tools import assert_less, assert_equal, assert_dict_equal
-from ase import Atoms
-from ase.io import read
-from ase.neighborlist import neighbor_list
-from sklearn.metrics import pairwise_distances
-from sklearn.model_selection import ParameterGrid
-from itertools import product
-from typing import List, Union, Tuple
-from collections import Counter
-from dataclasses import dataclass
-from os.path import join
-
-from tensoralloy.precision import precision_scope, Precision, get_float_dtype
-from tensoralloy.test_utils import Pd3O2, qm7m, test_dir
-from tensoralloy.test_utils import assert_array_equal, assert_array_almost_equal
-from tensoralloy.descriptor import compute_dimension, cosine_cutoff
-from tensoralloy.utils import get_kbody_terms, AttributeDict, Defaults
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.transformer.indexed_slices import G2IndexedSlices
-from tensoralloy.transformer.indexed_slices import G4IndexedSlices
-from tensoralloy.transformer import SymmetryFunctionTransformer
-from tensoralloy.transformer import BatchSymmetryFunctionTransformer
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-grid = ParameterGrid({'beta': Defaults.beta, 'gamma': Defaults.gamma,
-                      'zeta': Defaults.zeta})
-
-
-@dataclass(frozen=True)
-class LegacyRadialIndexedSlices:
-    """
-    A `dataclass` contains indexed slices for radial functions.
-
-    'v2g_map' : array_like
-        A list of (atomi, etai, termi) where atomi is the index of the center
-        atom, etai is the index of the `eta` and termi is the index of the
-        corresponding 2-body term.
-    'ilist' : array_like
-        A list of first atom indices.
-    'jlist' : array_like
-        A list of second atom indices.
-    'Slist' : array_like
-        A list of (i, j) pairs where i is the index of the center atom and j is
-        the index of its neighbor atom.
-
-    Notes
-    -----
[…]

### 2019-08-16 tensoralloy/transformer/tests/test_eam.py

@@ -1,162 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `BatchEAMTransformer`.
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import nose
-
-from ase.atoms import Atoms
-from ase.neighborlist import neighbor_list
-from collections import Counter
-from os.path import join
-
-from tensoralloy.io.db import connect
-from tensoralloy.neighbor import find_neighbor_size_of_atoms
-from tensoralloy.utils import get_kbody_terms, AttributeDict
-from tensoralloy.test_utils import assert_array_equal, datasets_dir
-from tensoralloy.transformer.index_transformer import IndexTransformer
-from tensoralloy.transformer.eam import BatchEAMTransformer, EAMTransformer
-from tensoralloy.precision import precision_scope
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def eam(atoms: Atoms, max_occurs: Counter, nnl: int, rc=6.5):
-    """
-    A numpy based implementation of the Embedded-Atom Method.
-    """
-    symbols = atoms.get_chemical_symbols()
-    ilist, jlist, dlist = neighbor_list('ijd', atoms, cutoff=rc)
-    clf = IndexTransformer(max_occurs, symbols)
-
-    kbody_terms = get_kbody_terms(sorted(max_occurs.keys()), k_max=2)[1]
-    max_n_atoms = sum(max_occurs.values()) + 1
-    max_n_terms = max(map(len, kbody_terms.values()))
-
-    counters = {atomi: Counter() for atomi in range(len(symbols))}
-
-    g = np.zeros((1, max_n_terms, max_n_atoms, nnl))
-    for k in range(len(ilist)):
-        atomi = ilist[k]
-        atomj = jlist[k]
-        center = symbols[atomi]
-        other = symbols[atomj]
-
-        kbody_term = f'{center}{other}'
-
-        idx1 = kbody_terms[center].index(kbody_term)
-        idx2 = clf.inplace_map_index(atomi + 1)
-        idx3 = counters[atomi][idx1]
-        counters[atomi][idx1] += 1
-
-        g[0, idx1, idx2, idx3] = dlist[k]
-
-    mask = np.asarray(g > 0.0).astype(np.float64)
-    return {'g': g, 'mask': mask}
-
-
-def test_eam_transformer():
-    """
-    Test `EAMTransformer`.
-    """
[…]

### 2019-08-16 tensoralloy/transformer/tests/test_index_transformer.py

@@ -1,90 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests for `IndexTransformer`.
-"""
-from __future__ import print_function, absolute_import
-
-import numpy as np
-import nose
-
-from collections import Counter
-from unittest import TestCase
-from os.path import join
-from ase.build import bulk
-from nose.tools import assert_equal, assert_list_equal, assert_less
-
-from tensoralloy.transformer.index_transformer import IndexTransformer
-from tensoralloy.test_utils import Pd3O2, Pd2O2Pd, test_dir
-from tensoralloy.calculator import TensorAlloyCalculator
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class IndexTransformerTest(TestCase):
-    """
-    A set of unit tests for the class `IndexTransformer`.
-    """
-
-    def setUp(self):
-        """
-        Setup the tests.
-        """
-        symbols = Pd3O2.get_chemical_symbols()
-        self.max_occurs = Counter({'Pd': 4, 'O': 5})
-        self.clf = IndexTransformer(self.max_occurs, symbols)
-
-    def test_forward(self):
-        assert_equal(len(self.clf.reference_chemical_symbols), 9)
-        assert_equal(len(self.clf.chemical_symbols), 5)
-        assert_equal(self.clf.n_atoms, 5)
-        assert_equal(self.clf.max_n_atoms, 9)
-
-        array = np.expand_dims([1, 2, 3, 4, 5], axis=1)
-        results = self.clf.map_array(array, reverse=False).flatten().tolist()
-        assert_list_equal(results, [0, 4, 5, 0, 0, 0, 1, 2, 3, 0])
-
-    def test_reverse(self):
-        array = np.expand_dims([0, 4, 5, 0, 0, 0, 1, 2, 3, 0], axis=1)
-        results = self.clf.map_array(array, reverse=True).flatten().tolist()
-        assert_list_equal(results, [1, 2, 3, 4, 5])
-
-    def test_call(self):
-        assert_equal(self.clf.inplace_map_index(1), 6)
-        assert_equal(self.clf.inplace_map_index(1, exclude_extra=True), 5)
-
-    def test_mask(self):
-        assert_list_equal(self.clf.mask.tolist(),
-                          [0, 1, 1, 0, 0, 0, 1, 1, 1, 0])
-
[…]

### 2019-08-16 tools/lmptool.py

@@ -1,695 +1,0 @@
-#!/usr/bin/env python3
-# coding=utf-8
-"""
-TensorAlloy - STEPMAX - Lammps Utility Tools
-"""
-from __future__ import print_function, absolute_import
-
-import tensorflow as tf
-import numpy as np
-import pandas as pd
-import toml
-import re
-import sys
-
-from dataclasses import dataclass
-from argparse import ArgumentParser, Namespace
-from ase.calculators.lammpsrun import write_lammps_data, LAMMPS, Prism
-from ase.io import write, read
-from ase.units import Hartree
-from ase.geometry import cell_to_cellpar
-from ase import Atoms
-from os.path import dirname, exists, join
-from typing import List
-from dscribe.descriptors import SOAP
-from dscribe.kernels import REMatchKernel
-from enum import Enum
-
-from tensoralloy.io.xyz import read_stepmax_xyz, write_stepmax_xyz
-from tensoralloy.cli.cli import CLIProgram
-from tensoralloy.transformer import SymmetryFunctionTransformer
-from tensoralloy.analysis.elastic import get_lattice_type
-from tensoralloy.utils import set_pulay_stress
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-class SimilarityAlgorithm(Enum):
-    """
-    The algorithm for computing the similarity of any two structures.
-    """
-    sf = 0
-    soap = 1
-
-
-@dataclass(frozen=True)
-class SpaceGroup:
-    lattice: str
-    name: str
-    number: int
-
-
-@dataclass(frozen=True)
-class BestRow:
-    order: int
-    enthalpy: float
-    dH: float
-    seq: int
-    energy: float
-    descriptors: np.ndarray
-    spacegroup: SpaceGroup
-    atoms: Atoms
-
-
-@dataclass(frozen=True)
-class BestFile:
-    rows: List[BestRow]
-
-    def __getitem__(self, item: int) -> BestRow:
-        return self.__dict__['rows'][item]
-
-    def __len__(self):
-        return len(self.__dict__['rows'])
-
-
-def read_best_file(best_file: str,
-                   pulay_stress=0.0,
-                   vasp=True,
-                   algo=SimilarityAlgorithm.soap) -> BestFile:
-    """
-    Read the `best.txt` generated by STEPMAX.
-    """
-    best_dir = dirname(best_file)
-    jobs_dir = join(best_dir, '..', 'jobs')
[…]

### 2019-08-17 doc/papers/ml-eam/manuscript.tex
Minor update.

@@
 the major role in long-time simulations and these empirical methods can achieve 
-reasonable accuracy with much lower computation costs.
+reasonable accuracy with much lower computation costs. Empirical potentials 
+generally have very few learnable parameters and traditionally both microscopic 
+observables (energy, forces, virial, etc.) and macroscopic observables (melting 
+point, surface energy, etc.) can be used to tune these parameters.
 
@@
 
-Compared with empirical potentials, MILPs have some noticable advantages.
+Compared with empirical potentials, MILPs typically have several orders of 
+magnitudes more model parameters. The redundant parameter space greatly reduces 
+the difficulty of fitting complicated potential energy surfaces with MLIPs. 
+However, it also raises some new challenges. To effectively train MLIPs with 
+large numbers of parameters, typically tens of thousands high-quality 
+\textit{ab initio} data points are necessary. The cost of building training 
+datasets can not be ignored. The lack of physical background makes the 
+performances of MILPs outside the training 'zone' not stable. For large-scale 
+alloy systems, computation efficiency becomes a major concern.
 

### 2019-08-17 setup.py
Update the install settings.

@@ -4,26 +4,13 @@ The setup module.
 """
 from __future__ import print_function, absolute_import
 
-import sys
-
 from setuptools import setup, find_packages
 from wheel.bdist_wheel import bdist_wheel as _bdist_wheel
-
-from tensoralloy.extension.interp import build_ext as interp_build_ext
 
 
 __version__ = "1.0"
 __author__ = "Xin Chen"
 __email__ = "Bismarrck@me.com"
-
-
-if sys.version_info < (3, 7, 0):
-    sys.exit('Python < 3.7.0 is not supported')
-
-
-extensions = [
-    interp_build_ext.get_interp_extension(),
-]
 
 
 # noinspection PyMissingOrEmptyDocstring,PyPep8Naming,PyAttributeOutsideInit
@@ -46,11 +33,6 @@ if __name__ == "__main__":
         author=__author__,
         author_email=__email__,
         version=__version__,
-        cmdclass={
-            'bdist_wheel': bdist_wheel,
-            "build_ext": interp_build_ext.BuildExtension
-        },
-        ext_modules=extensions,
         description="Tensor-graph based machine learning framework for alloys.",
         packages=packages,
         include_package_data=True,

### 2019-08-17 tensoralloy/transformer/__init__.py
Restore this file from git.

@@ -7,14 +7,10 @@ from __future__ import print_function, absolute_import
 
 from tensoralloy.transformer.behler import BatchSymmetryFunctionTransformer
 from tensoralloy.transformer.behler import SymmetryFunctionTransformer
-from tensoralloy.transformer.eam import BatchEAMTransformer, EAMTransformer
-from tensoralloy.transformer.adp import BatchADPTransformer, ADPTransformer
 from tensoralloy.transformer.index_transformer import IndexTransformer
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
 __all__ = ["IndexTransformer",
-           "BatchSymmetryFunctionTransformer", "SymmetryFunctionTransformer",
-           "BatchEAMTransformer", "EAMTransformer",
-           "BatchADPTransformer", "ADPTransformer"]
+           "BatchSymmetryFunctionTransformer", "SymmetryFunctionTransformer"]

### 2019-08-17 tensoralloy/transformer/behler.py

@@ -1,0 +1,760 @@
+# coding=utf-8
+"""
+This module defines the feature transformers (flexible, fixed) for Behler's
+Symmetry Function descriptor.
+"""
+from __future__ import print_function, absolute_import
+
+import tensorflow as tf
+import numpy as np
+
+from collections import Counter
+from typing import Dict, Tuple
+from ase import Atoms
+from ase.neighborlist import neighbor_list
+
+from tensoralloy.descriptor import SymmetryFunction, BatchSymmetryFunction
+from tensoralloy.precision import get_float_dtype
+from tensoralloy.transformer.base import DescriptorTransformer
+from tensoralloy.transformer.base import BatchDescriptorTransformer
+from tensoralloy.transformer.base import bytes_feature
+from tensoralloy.transformer.index_transformer import IndexTransformer
+from tensoralloy.transformer.indexed_slices import G2IndexedSlices
+from tensoralloy.transformer.indexed_slices import G4IndexedSlices
+from tensoralloy.utils import AttributeDict, Defaults, get_pulay_stress
+
+
+# TODO: universal v2gmap
+
+__author__ = 'Xin Chen'
+__email__ = 'Bismarrck@me.com'
+
+__all__ = ["SymmetryFunctionTransformer", "BatchSymmetryFunctionTransformer"]
+
+
+class SymmetryFunctionTransformer(SymmetryFunction, DescriptorTransformer):
+    """
+    A tranformer for providing the feed dict to calculate symmetry function
+    descriptors of an `Atoms` object.
+    """
+
+    def __init__(self, rc, elements, eta=Defaults.eta, omega=Defaults.omega,
+                 beta=Defaults.beta, gamma=Defaults.gamma, zeta=Defaults.zeta,
+                 angular=False, periodic=True, trainable=False,
+                 cutoff_function='cosine'):
+        """
+        Initialization method.
+        """
+        SymmetryFunction.__init__(
+            self, rc=rc, elements=elements, eta=eta, omega=omega, beta=beta,
+            gamma=gamma, zeta=zeta, angular=angular, periodic=periodic,
+            trainable=trainable, cutoff_function=cutoff_function)
+        DescriptorTransformer.__init__(self)
+
+    def as_dict(self):
+        """
+        Return a JSON serializable dict representation of this transformer.
+        """
+        d = {'class': self.__class__.__name__, 'rc': self._rc,
+             'elements': self._elements, 'angular': self._angular,
[…]

### 2019-08-17 tensoralloy/dataset/dataset.py
The codes are further modified for CPC.

@@ -404,15 +404,11 @@ class Dataset:
                     shape = batch_of_tensors.shape.as_list()
                     if shape[0] is None:
                         batch_of_tensors.set_shape([batch_size] + shape[1:])
-            labels = AttributeDict(energy=batch.pop('y_true'),
-                                   energy_confidence=batch.pop('y_conf'))
+            labels = AttributeDict(energy=batch.pop('y_true'))
             if self._database.has_forces:
                 labels['forces'] = batch.pop('f_true')
-                labels['forces_confidence'] = batch.pop('f_conf')
             if self._database.has_stress:
                 labels['stress'] = batch.pop('stress')
-                labels['stress_confidence'] = batch.pop('s_conf')
-                labels['total_pressure'] = batch.pop('total_pressure')
             return batch, labels
 
         return _input_fn

### 2019-08-17 tensoralloy/descriptor/__init__.py

@@ -5,9 +5,9 @@ various descriptors directly from atomic positions.
 """
 from __future__ import print_function, absolute_import
 
-from .behler import *
-from .cutoff import *
-from .eam import *
+from tensoralloy.descriptor.behler import SymmetryFunction
+from tensoralloy.descriptor.behler import BatchSymmetryFunction
+from tensoralloy.descriptor.cutoff import cosine_cutoff, polynomial_cutoff
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'

### 2019-08-17 tensoralloy/io/input/reader.py

@@ -9,7 +9,6 @@ import toml
 from os.path import dirname, join
 from typing import List, Union
 
-from tensoralloy.utils import get_elements_from_kbody_term
 from tensoralloy.utils import nested_get, nested_set
 
 __author__ = 'Xin Chen'
@@ -156,41 +155,10 @@ class InputReader:
         if nested_get(results, 'dataset.name').find("-") >= 0:
             raise ValueError("'-' is not allowed in 'dataset.name'.")
 
-        descriptor = nested_get(configs, 'dataset.descriptor')
-
-        if descriptor == 'behler':
-            layers = nested_get(configs, 'nn.atomic.layers')
-            if isinstance(layers, dict):
-                for key, val in layers.items():
-                    nested_set(results, f'nn.atomic.layers.{key}', val)
-
-            if 'eam' in results['nn']:
-                del results['nn']['eam']
-
-        else:
-            for attr in ('constant', 'type'):
-                values = nested_get(configs, f"nn.eam.setfl.lattice.{attr}")
-                if isinstance(values, dict):
-                    for element in values.keys():
-                        _safe_update(f"nn.eam.setfl.lattice.{attr}.{element}")
-
-            for func in ('embed', 'phi', 'rho', 'dipole', 'quadrupole'):
-                pots = nested_get(configs, f"nn.eam.{func}")
-                if isinstance(pots, dict):
-                    for key in pots.keys():
-                        src = f"nn.eam.{func}.{key}"
-                        if func in ('phi', 'dipole', 'quadrupole'):
-                            key = "".join(
-                                sorted(get_elements_from_kbody_term(key)))
-                            dst = f"nn.eam.{func}.{key}"
-                        else:
-                            dst = None
-                        _safe_update(src, dst)
-
-            if 'behler' in results:
-                del results['behler']
-            if 'atomic' in results['nn']:
-                del results['nn']['atomic']
+        layers = nested_get(configs, 'nn.atomic.layers')
+        if isinstance(layers, dict):
+            for key, val in layers.items():
+                nested_set(results, f'nn.atomic.layers.{key}', val)
 
         # Convert the paths
         for keypath in ("dataset.sqlite3",
@@ -201,18 +169,5 @@ class InputReader:
             if keypath == "train.ckpt.checkpoint_filename" and path is False:
                 continue
             nested_set(results, keypath, _convert_filepath(path))
-
-        for keypath in ("nn.loss.elastic.crystals",
-                        "nn.loss.rose.crystals"):
[…]

### 2019-08-17 tensoralloy/io/input/tests/test_reader.py

@@ -1,122 +1,0 @@
-# coding=utf-8
-"""
-This module defines unit tests of `tensoralloy.io.input.InputReader`.
-"""
-from __future__ import print_function, absolute_import
-
-import nose
-
-from nose.tools import assert_equal, assert_list_equal
-from nose.tools import assert_not_in
-from os.path import join, realpath
-
-from tensoralloy.io.input.reader import InputReader
-from tensoralloy.utils import nested_get
-from tensoralloy.test_utils import test_dir, datasets_dir, project_dir
-
-__author__ = 'Xin Chen'
-__email__ = 'Bismarrck@me.com'
-
-
-def test_read_behler_angular_toml():
-    """
-    Test `InputReader` with file 'qm7.behler.k3.toml'.
-    """
-    reader = InputReader(join(test_dir(), 'inputs', 'qm7.behler.k3.toml'))
-    configs = reader.configs
-
-    assert_equal(reader['precision'], 'medium')
-    assert_equal(reader['nn.atomic.behler.trainable'], True)
-
-    assert_equal(realpath(reader['dataset.sqlite3']),
-                 realpath(join(datasets_dir(True), 'qm7.db')))
-    assert_equal(realpath(reader['dataset.tfrecords_dir']),
-                 realpath(join(project_dir(True), 'experiments/qm7-k3')))
-    assert_equal(realpath(reader['train.model_dir']),
-                 realpath(join(project_dir(True), 'experiments/qm7-k3/train')))
-    assert_equal(reader['train.ckpt.checkpoint_filename'], False)
-
-    assert_equal(nested_get(configs, 'dataset.descriptor'), 'behler')
-    assert_equal(nested_get(configs, 'nn.atomic.arch'), 'AtomicNN')
-    assert_equal(nested_get(configs, 'nn.atomic.kernel_initializer'),
-                 'truncated_normal')
-    assert_list_equal(nested_get(configs, 'nn.atomic.behler.eta'),
-                      [0.01, 0.1, 0.5, 1.0, 2.0, 4.0, 20.0, 40.0])
-    assert_list_equal(reader['nn.atomic.behler.omega'],
-                      [0.0, 1.0, 2.0, 3.0, 4.0, 5.0])
-    assert_equal(nested_get(configs, 'nn.atomic.behler.angular'), True)
[…]

### 2019-08-17 tensoralloy/nn/__init__.py

@@ -5,7 +5,6 @@
 from __future__ import print_function, absolute_import
 
 from tensoralloy.nn.atomic import AtomicResNN, AtomicNN
-from tensoralloy.nn.eam import EamAlloyNN, EamFsNN, AdpNN
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'

### 2019-08-17 tensoralloy/nn/losses.py

@@ -6,9 +6,8 @@ from __future__ import print_function, absolute_import
 
 import tensorflow as tf
 
-from typing import List, Union
+from typing import List
 from enum import Enum
-from os.path import basename
 
 from tensoralloy.precision import get_float_dtype
 from tensoralloy.nn.dataclasses import L2LossOptions
@@ -45,8 +44,7 @@ def _logcosh(x, dtype=None, name=None):
                             name=name)
 
 
-def _get_relative_rmse_loss(labels: tf.Tensor, predictions: tf.Tensor,
-                            weights: Union[tf.Tensor, None]):
+def _get_relative_rmse_loss(labels: tf.Tensor, predictions: tf.Tensor):
     """
     Return the relative RMSE as the loss of atomic forces.
     """
@@ -55,13 +53,11 @@ def _get_relative_rmse_loss(labels: tf.Tensor, predictions: tf.Tensor,
         upper = tf.linalg.norm(diff, axis=1, keepdims=False, name='upper')
         lower = tf.linalg.norm(labels, axis=1, keepdims=False, name='lower')
         ratio = tf.math.truediv(upper, lower, name='ratio')
-        if weights is not None:
-            ratio = tf.math.multiply(ratio, weights, name='ration/conf')
         loss = tf.reduce_mean(ratio, name='loss')
     return loss
 
 
-def _get_rmse_loss(x: tf.Tensor, y: tf.Tensor, weights=None,
+def _get_rmse_loss(x: tf.Tensor, y: tf.Tensor,
                    is_per_atom_loss=False):
     """
     Return the RMSE loss tensor. The MAE loss will also be calculated.
@@ -71,16 +67,7 @@ def _get_rmse_loss(x: tf.Tensor, y: tf.Tensor, weights=None,
     else:
         suffix = ""
     mae = tf.reduce_mean(tf.abs(x - y), name='mae' + suffix)
-    if weights is None:
-        mse = tf.reduce_mean(tf.squared_difference(x, y), name='mse' + suffix)
-    else:
-        if x.shape.ndims == 2:
-            weights = tf.reshape(weights, (-1, 1))
-        mse = tf.reduce_mean(
-            tf.math.multiply(weights,
-                             tf.squared_difference(x, y),
-                             name='conf'),
-            name='mse' + suffix)
+    mse = tf.reduce_mean(tf.squared_difference(x, y), name='mse' + suffix)
     dtype = get_float_dtype()
[…]

### 2019-08-17 tensoralloy/test_utils.py

@@ -4,92 +4,10 @@ This module defines unit tests related functions and vars.
 """
 from __future__ import print_function, absolute_import
 
-import numpy as np
-
-from collections import Counter
 from os.path import join, dirname, abspath
-from ase import Atoms
-from ase.io import read
-from nose.tools import assert_less, assert_equal
-
-from tensoralloy.utils import AttributeDict
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
-
-
-def assert_array_almost_equal(a: np.ndarray, b: np.ndarray, delta, msg=None):
-    """
-    Fail if the two arrays are unequal as determined by their maximum absolute
-    difference rounded to the given number of decimal places (default 7) and
-    comparing to zero, or by comparing that the between the two objects is more
-    than the given delta.
-    """
-    assert_less(np.abs(a - b).max(), delta, msg)
-
-
-def assert_array_equal(a: np.ndarray, b: np.ndarray, msg=None):
-    """
-    Fail if the two arrays are unequal with threshold 0 (int) or 1e-6 (float32)
-    or 1e-12 (float64).
-    """
-    assert_equal(a.dtype, b.dtype)
-    if np.issubdtype(a.dtype, np.int_):
-        delta = 0
-    elif a.dtype == np.float64:
-        delta = 1e-12
-    else:
-        delta = 1e-6
-    assert_array_almost_equal(a, b, delta, msg=msg)
-
-
-# Pd3O2
-Pd3O2 = Atoms(symbols='Pd3O2', pbc=np.array([True, True, False], dtype=bool),
-              cell=np.array([[7.78, 0., 0.],
-                             [0., 5.50129076, 0.],
-                             [0., 0., 15.37532269]]),
-              positions=np.array([[3.89, 0., 8.37532269],
-                                  [0., 2.75064538, 8.37532269],
-                                  [3.89, 2.75064538, 8.37532269],
-                                  [5.835, 1.37532269, 8.5],
-                                  [5.835, 7.12596807, 8.]]))
-
-
-# A permutation of Pd3O2
-Pd2O2Pd = Atoms(symbols='Pd2O2Pd',
-                pbc=np.array([True, True, False], dtype=bool),
-                cell=np.array([[7.78, 0., 0.],
-                               [0., 5.50129076, 0.],
-                               [0., 0., 15.37532269]]),
-                positions=np.array([[3.89, 0., 8.37532269],
[…]

### 2019-08-17 tensoralloy/transformer/behler.py

@@ -23,9 +23,6 @@ from tensoralloy.transformer.indexed_slices import G2IndexedSlices
 from tensoralloy.transformer.indexed_slices import G4IndexedSlices
 from tensoralloy.utils import AttributeDict, Defaults, get_pulay_stress
 
-
-# TODO: universal v2gmap
-
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
@@ -644,7 +641,6 @@ class BatchSymmetryFunctionTransformer(BatchSymmetryFunction,
                 'cells': tf.FixedLenFeature([], tf.string),
                 'volume': tf.FixedLenFeature([], tf.string),
                 'y_true': tf.FixedLenFeature([], tf.string),
-                'y_conf': tf.FixedLenFeature([], tf.string),
                 'g2.indices': tf.FixedLenFeature([], tf.string),
                 'g2.shifts': tf.FixedLenFeature([], tf.string),
                 'mask': tf.FixedLenFeature([], tf.string),
@@ -653,14 +649,10 @@ class BatchSymmetryFunctionTransformer(BatchSymmetryFunction,
             }
             if self._use_forces:
                 feature_list['f_true'] = tf.FixedLenFeature([], tf.string)
-                feature_list['f_conf'] = tf.FixedLenFeature([], tf.string)
 
             if self._use_stress:
                 feature_list['stress'] = \
                     tf.FixedLenFeature([], tf.string)
-                feature_list['total_pressure'] = \
-                    tf.FixedLenFeature([], tf.string)
-                feature_list['s_conf'] = tf.FixedLenFeature([], tf.string)
 
             if self._k_max == 3:
                 feature_list.update({

### 2019-08-20 doc/papers/nn/manuscript.tex
Switch to the CPC latex format.

@@
-\documentclass[preprint]{revtex4-2}
-
+%% This template can be used to write a paper for
+%% Computer Physics Communications using LaTeX.
+%% For authors who want to write a computer program description,
+%% an example Program Summary is included that only has to be
+%% completed and which will give the correct layout in the
+%% preprint and the journal.
+%% The `elsarticle' style is used and more information on this style
+%% can be found at 
+%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
+%%
+%%
+%% \documentclass[preprint,12pt]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+\documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
 \usepackage{amsmath}    % need for subequations
@@
 \usepackage{hyperref}   % use for hypertext links, including those to external
-\raggedbottom           % don't add extra vertical space
-\begin{comment}
-\pagestyle{empty}       % use if page numbers not wanted
-\end{comment}
-
-\bibliographystyle{apsrev4-2}
+
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%
+%% \biboptions{comma,round}
+
+% \biboptions{}
+
+%% This list environment is used for the references in the
+%% Program Summary
+%%
+\newcounter{bla}
+\newenvironment{refnummer}{%
+\list{[\arabic{bla}]}%
+{\usecounter{bla}%
+ \setlength{\itemindent}{0pt}%
+ \setlength{\topsep}{0pt}%
+ \setlength{\itemsep}{0pt}%
+ \setlength{\labelsep}{2pt}%
+ \setlength{\listparindent}{0pt}%
+ \settowidth{\labelwidth}{[9]}%
+ \setlength{\leftmargin}{\labelwidth}%
+ \addtolength{\leftmargin}{\labelsep}%
+ \setlength{\rightmargin}{0pt}}}
+ {\endlist}
+
+\journal{Computer Physics Communications}
 
@@
 
-\title{
-    TensorAlloy: an automatic atomistic neural network program for alloys
-}
-\author{Xin Chen}
-\author{Xing-Yu Gao}
-\author{Ya-Fan Zhao}
-\author{De-Ye Lin}
-\email{lindeye0716@163.com}
-\author{Wei-Dong Chu}
-\author{Hai-Feng Song}
-\email{song\_haifeng@iapcm.ac.cn}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+\title{TensorAlloy: an automatic atomistic neural network program for alloys}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
+
+\author[a]{Xin Chen}
+\author[a]{Xing-Yu Gao}
+\author[b]{Ya-Fan Zhao}
+\author[b]{De-Ye Lin\corref{author}}
+\author[a]{Wei-Dong Chu}
+\author[a,b]{Hai-Feng Song\corref{author}}
+
+\cortext[author] {Corresponding author.
+\\\textit{E-mail address:} lindeye0716@163.com}
+\address[a]{Institute of Applied Physics and Computational Mathematics, 
 Beijing 100088, China}
-\affiliation{
-    CAEP Software Center for High Performance Numerical Simulation, 
+\address[b]{CAEP Software Center for High Performance Numerical Simulation, 
 Beijing 100088, China}
@@
 
-\maketitle
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+Machine Learning; Alloy; Materials Modeling; Computational Physics; 
+Neural Network
+
+\end{keyword}
+
+\end{frontmatter}
+
+%%
+%% Start line numbering here if you want
+%%
+% \linenumbers
+
+% Computer program descriptions should contain the following
+% PROGRAM SUMMARY.
+
+{\bf PROGRAM SUMMARY} \\
+\begin{small}
+\noindent
+{\em Program Title: TensorAlloy} \\
+{\em Licensing provisions(please choose one): Apache-2.0}     \\
+{\em Programming language: Python 3.7}                        \\
+{\em Supplementary material:}                                 \\
+{\em Journal reference of previous version:}                  \\
+{\em Does the new version supersede the previous version?:}   \\
+{\em Reasons for the new version:} \\
+{\em Summary of revisions:}*\\
+{\em Nature of problem:} \\
+  Modeling interatomic interactions with the symmetry function descriptor based
+  atomistic neural networks.
+{\em Solution method:} \\
+  The TensorAlloy program is built upon TensorFlow and the virtual-atom 
+  approach. TensorAlloy can build direct computation graph from atomic positions 
+  to total energy. Atomic forces and virial stress tensors are handled by 
+  TensorFlow automatically and efficiently.
+{\em Additional comments including Restrictions and Unusual features}\\
+  This program needs TensorFlow 1.13.*. Neither newer or older TensorFlow is 
+  supported. \\
+\end{small}
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\newpage
-
 \section{Introduction}
@@
 \ref{section:appendix} gives derivation and implementation details of key 
-routines of VAP. The full implementation and demo codes can be obtained from 
-GitHub (https://github.com/Bismarrck/vap) freely.
+routines of VAP.
 
@@
 visualized in the figures. Python3.7 implementations of key algorithms and 
-functions are given in the appendix. A full demo (including the alloy datasets) 
-can be obtained from GitHub freely (https://github.com/Bismarrck/vap).
+functions are given in the appendix.
 
@@
 \centering
-\includegraphics[scale=0.68]{figures/Fig1.pdf}
+\includegraphics[scale=0.55]{figures/Fig1.pdf}
 \caption{\label{fig:program_design} The general design of TensorAlloy. 
@@
 \centering
-\includegraphics[scale=0.95]{figures/Fig5.pdf}
+\includegraphics[scale=0.75]{figures/Fig5.pdf}
 \caption{\label{fig:Fig5} The calculation of 
@@
     $\mathbf{r}^{\mathrm{GSL}}$ with the given $\tau$-th $(\eta, \omega)$ pair 
-    to obtain raw descriptors $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. 
+    to obtain $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$. 
     $g^{\mathrm{GSL}}_{2}((\eta, \omega)_{\tau})$ is a vector of length 
@@
 \centering
-\includegraphics[scale=0.54]{figures/qm7_speed.pdf}
+\includegraphics[scale=0.44]{figures/qm7_speed.pdf}
 \caption{\label{fig:benchmark_qm7} 
@@
 \centering
-\begin{tabular}{cccc|ccc|cc}
+\begin{tabular}{cccc}
 \hline
- & \multicolumn{3}{c|}{Energy (meV/atom)} & \multicolumn{3}{c|}{Force (eV/\AA)}
- & \multicolumn{2}{c}{Stress (GPa)} \\
+Subset & Energy (meV/atom) & Force (eV/\AA) & Stress (GPa) \\
 \hline
-NN Model & Mo & Ni & Ni-Mo & Mo & Ni & Ni-Mo & Mo & Ni-Mo \\
-\hline
-Mo & 4.9 (13.2) & & 16.5 (16.2) & 0.19 (0.25) & & 0.28 (0.29) & 0.24 (0.87) 
-   & 0.75 \\
-Ni & & 1.2 (1.2) & 4.5 (7.9) & & 0.04 (0.05) & 0.07 (0.11) & & 0.83 \\
-Ni$_4$Mo & & & 4.1 (4.0) & & & 0.09 (0.14) & & 0.98 \\ 
-Ni$_3$Mo & & & 4.5 (5.2) & & & 0.11 (0.16) & & 1.19 \\
-Ni$_{\mathrm{Mo}}$ & & & 12.9 (22.7) & & & 0.09 (0.13) & & 0.34 \\
-Mo$_{\mathrm{Ni}}$ & & & 12.9 (33.9) & & & 0.12 (0.55) & & 0.45 \\
-Overall & & & 10.8 (22.5) & & & 0.11 (0.23) & & 0.59 \\
+Mo & 16.5 (16.2) & 0.28 (0.29) & 0.75 \\
+Ni & 4.5 (7.9)   & 0.07 (0.11) & 0.83 \\
+Ni$_4$Mo & 4.1 (4.0) & 0.09 (0.14) & 0.98 \\ 
+Ni$_3$Mo & 4.5 (5.2) & 0.11 (0.16) & 1.19 \\
+Ni$_{\mathrm{Mo}}$ & 12.9 (22.7) & 0.09 (0.13)& 0.34 \\
+Mo$_{\mathrm{Ni}}$ & 12.9 (33.9) & 0.12 (0.55)& 0.45 \\
+Overall & 10.8 (22.5)& 0.11 (0.23) & 0.59 \\
 \hline
 \end{tabular}
-
 \caption{\label{table:MAE}
 Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
-stress (GPa) relative to DFT for TensorAlloy-trained models and their
+stress (GPa) relative to DFT of each subset for the binary Mo-Ni model and the
 corresponding SNAP benchmarks (bracket)}
@@
 
-Table \ref{table:MAE} summarizes the energy, force and stress prediction 
-performances of TensorAlloy-trained models compared with their corresponding 
-SNAP benchmarks. The original SNAP formalism contains both radial and angular 
+\begin{table}[h]
+\centering
+\begin{tabular}{ccc|cc|c}
+\hline
+  & \multicolumn{2}{c|}{Energy (meV/atom)} & \multicolumn{2}{c|}{Force (eV/\AA)}
+  & Stress (GPa) \\
+\hline
+Elementary Model & Mo & Ni & Mo & Ni & Mo \\
+\hline
+Mo & 4.9 (13.2) & & 0.19 (0.25) & & 0.24 (0.87) \\
+Ni & & 1.2 (1.2) & & 0.04 (0.05) & \\
+\hline
+\end{tabular}
+\caption{\label{table:MAE1}
+Comparion of the MAEs in predicted energies (mev/atom), forces (eV/\AA) and 
+stress (GPa) relative to DFT for the two elementary models (Ni, Mo) and their
+corresponding SNAP benchmarks (bracket)}
+\end{table}
+
+Table \ref{table:MAE} and \ref{table:MAE1} summarizes the energy, force and 
+stress prediction performances of our trained models compared with their 
+corresponding SNAP benchmarks. 
+The original SNAP formalism contains both radial and angular 
 interactions. However, in most cases, the radial-only TensorAlloy-trained 
@@
     \centering
-    \includegraphics[scale=0.64]{figures/Prediction-speed.pdf}
+    \includegraphics[scale=0.5]{figures/Prediction-speed.pdf}
 \caption{\label{fig:prediction_speed} Benchmarks of the \textbf{NN}(Mo-Ni) model 
@@
     \centering
-    \includegraphics[scale=0.8]{figures/Ni_EoS.pdf}
+    \includegraphics[scale=0.65]{figures/Ni_EoS.pdf}
 \caption{\label{fig:energy_volume_Ni} The energy vs volume curves of fcc Ni for
@@
     \centering
-    \includegraphics[scale=0.8]{figures/Ni_surface_energy.pdf}
+    \includegraphics[scale=0.65]{figures/Ni_surface_energy.pdf}
 \caption{\label{fig:surface_energy_Ni} Surface formation energies ($J/m^2$) of 
@@
 \end{figure}
-
-The benchmark function and the trained models can be accessed from the VAP 
-GitHub repo (https://github.com/Bismarrck/vap) freely.
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+\bibliographystyle{elsarticle-num}
 \bibliography{manuscript.bib}
-
-\newpage
 
@@
                 n2[count] = vectors[atom_gsl_i][k]
-                n3[count] = vectors[atom_gsl_i][k] - vectors[atom_gsl_i][j]
+                n3[count] = n2[count] - n1[count]
                 index = interactions.index(interaction)
@@
 
-The demo script can be found on GitHub: https://github.com/Bismarrck/vap.
-
 \begin{verbatim}
@@
 
-    def __init__(self, rc, elements, eta=np.array([0.05, 4.0, 20.0, 80.0]),
+    def __init__(self, rc, elements, eta=np.array([0.05, 4, 20, 80]),
                  omega=np.array([0.0]), beta=np.array([0.005, ]),
@@
             'zeta': np.arange(len(zeta), dtype=int)})
-        self.initial_values = {'eta': eta, 'omega': omega, 'gamma': gamma,
+        self.initial_values = {'eta': eta, 'omega': omega, 
+                               'gamma': gamma,
                                'beta': beta, 'zeta': zeta}
@@
             if self.periodic:
-                pbc = self.get_pbc_displacements(shift, cells, dtype=dtype)
+                pbc = self.get_pbc_displacements(shift, cells, dtype)
                 Dij = tf.add(Dij, pbc, name='pbc')
@@
                                      axis=column_split_axis,
-                                     name='{}_block'.format(element))[idx]
+                                     name=f'{element}_block')[idx]
                     blocks.append(block)
@@
         with tf.name_scope("Einsum"):
-            shift = tf.convert_to_tensor(shift, dtype=dtype, name='shift')
-            cells = tf.convert_to_tensor(cells, dtype=dtype, name='cells')
+            shift = tf.convert_to_tensor(shift, dtype, name='shift')
+            cells = tf.convert_to_tensor(cells, dtype, name='cells')
             return tf.einsum(
@@
 \end{document}
+
+%%
+%% End of file

### 2019-08-22 doc/papers/nn/manuscript.tex
Minor update.

@@
 derivations of forces and virial can be handled by TensorFlow automatically and 
-efficiently. This new approach is implemented in our program TensorAlloy, which 
-supports constructing machine learning interaction potentials for both 
-\textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used 
-to demostrate the performances of our program.
+efficiently. This new approach is implemented in our open-source program 
+TensorAlloy, which supports constructing machine learning interaction potentials 
+for both \textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets 
+are used to demostrate the performances of our program.
 \end{abstract}
@@
 {\em Program Title: TensorAlloy} \\
-{\em Licensing provisions(please choose one): Apache-2.0}     \\
+{\em Licensing provisions(please choose one): LGPL}           \\
 {\em Programming language: Python 3.7}                        \\
@@
   to total energy. Atomic forces and virial stress tensors are handled by 
-  TensorFlow automatically and efficiently.
+  TensorFlow automatically and efficiently. \\
 {\em Additional comments including Restrictions and Unusual features}\\
@@
 \hline
+\multicolumn{4}{c}{Binary Mo-Ni model} \\
+\hline
 Subset & Energy (meV/atom) & Force (eV/\AA) & Stress (GPa) \\
@@
 This work was supported by the National Key Research and Development Program of 
-China under Grant No. 2016YFB0201203, the Science Challenge Project under Grant 
+China under Grant No. 2016YFB0201204, the Science Challenge Project under Grant 
 No. TZ2018002 and the National Natural Science Foundation of China under Grant 

### 2019-08-23 doc/papers/nn/manuscript.tex
Minor update.

@@
 (batch size 100, angular symmetry functions included), the test MAE will reach 5 
-meV/atom (1.5 kcal/mol per structure) in just one GPU hour.
+meV/atom (1.5 kcal/mol per structure) in just one GPU hour on our workstation.
 

### 2019-08-23 make_one_file.py
This file is updated.

@@ -5,23 +5,35 @@ A script to merge all Python files and TOML files into a single txt file.
 from __future__ import print_function, absolute_import
 
 from os import walk
-from os.path import join
+from os.path import join, splitext
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
-content = ""
+out = ""
 
 for root, sub_folders, files in walk("."):
-    if root in ("datasets", "examples", "experiments", "models"):
+    if root.startswith("./"):
+        root = root[2:]
+    tops = root.split("/")
+    if tops[0] in ("datasets", "experiments", "models", ".git", ".idea"):
+        continue
+    if tops[-1] == "__pycache__":
         continue
     for afile in files:
         if afile == "test.py" or afile == "make_one_file.py":
             continue
-        if afile.endswith("py") or afile.endswith("toml"):
+        if afile.startswith("."):
+            continue
+        ext = splitext(afile)[1]
+        if ext in (".py", ".toml", ".md", ".txt"):
             filename = join(root, afile)
             with open(filename) as fp:
-                content += f"tensoralloy/{afile}\n" + fp.read() + "\n"
+                if root == ".":
+                    header = f"tensoralloy/{afile}"
+                else:
+                    header = f"tensoralloy/{root}/{afile}"
+                out += f"Path={header}\n{fp.read()}\n"
 
 with open("all_codes", "w") as fp:
-    fp.write(content)
+    fp.write(out)

### 2019-08-26 doc/papers/nn/manuscript.tex
The manuscript is slightly updated.

--- 2019-08-22 doc/papers/nn/manuscript.tex
@@
 of using larger batch size: the trainings can be much faster. For the best case 
-(batch size 100, angular symmetry functions included), the test MAE will reach 5 
-meV/atom (1.5 kcal/mol per structure) in just one GPU hour.
+(batch size 100, angular symmetry functions included), the test MAE will reach 6 
+meV/atom (1.8 kcal/mol per structure) in just one GPU hour on our workstation.
 
@@
 \hline
-Mo & 4.9 (13.2) & & 0.19 (0.25) & & 0.24 (0.87) \\
-Ni & & 1.2 (1.2) & & 0.04 (0.05) & \\
+Mo & 4.5 (13.2) & & 0.19 (0.25) & & 0.28 (0.87) \\
+Ni & & 1.3 (1.2) & & 0.04 (0.05) & \\
 \hline

### 2019-09-11 doc/papers/ml-eam/manuscript.tex
The ML-EAM manuscript is improved quite a lot.

--- 2019-08-16 doc/papers/ml-eam/manuscript.tex
@@
 the major role in long-time simulations and these empirical methods can achieve 
-reasonable accuracy with much lower computation costs.
+reasonable accuracy with much lower computation costs. Empirical potentials 
+generally have very few learnable parameters and both microscopic observables 
+(energy, forces, virial, etc.) and macroscopic observables (melting 
+point, surface energy, etc.) can be used to tune these parameters. Finding 
+optimal parameters of empirical potentials is always a challenging task. Global 
+optimization (GO) approaches (Basin-Hopping, genetic algorithm, etc) are 
+traditionally used to find the best possible parameters. However, the gradients 
+of the losses with respect to model parameters are difficult or even impossible 
+to calcualte. Hence, GO optimizations are generally not that effective.
 
@@
 now, hundreds of MLIPs have been proposed. Among them, the symmetry-function 
-based atomistic neural network (ANN) model by Parinello and Behler is the most 
-popular choice in modeling metallic interactions. The smooth overlap atomic 
-positions descriptor based gaussian approximation potential (SOAP-GAP) can give
-extremely accurate results, although it's a bit computationally expensive. 
-Spectral neighbor analysis potential (SNAP) is another quantum-accurate MLIP and
-it performs very well on a broad range of metals and alloys.
+based atomistic neural network (ANN) model, published by Parinello and Behler in 
+2007, is still the most popular choice in modeling metallic interactions. 
+The smooth overlap atomic positions descriptor based gaussian approximation 
+potential (SOAP-GAP), developed by Bartòk et al, can give extremely accurate 
+prediction results, although it's a bit computationally expensive. 
+Recently, Thompson and co-workers proposed another quantum-accurate MLIP named 
+the spectral neighbor analysis potential (SNAP) and it has been proven working  
+on a broad range of metals and alloys.
 
-Compared with empirical potentials, MILPs have some noticable advantages.
+In many cases, MILPs can easily outperform state-of-art empirical potentials. 
+Compared with empirical potentials, MLIPs generally have orders of magnitudes 
+more model paramters. The redundant parameter space greatly reduces the 
+difficulty of fitting complicated potential energy surfaces. But, to effectively 
+train a MLIP and avoid overfitting, a large high-quality (versatile) training 
+dataset is probably needed. However, MILPs \textbf{can really} take advantages 
+of "big data" for two reasons. First, MLIPs typically only have 
+\textit{basic} or \textit{simple} arithmetic operations. Thus, MILPs can be 
+implemented within modern deep learning frameworks (TensorFlow, PyTorch, etc) 
+so that the gradients of the total loss with respect to fitting parameters can 
+be can obtained with the backpropagation algorithm automatically and 
+efficiently. Second, MLIPs are mostly vectorizable. Hence, GPUs can be utilized
+to significantly accelerate training and using of MILPs.
 
-Traditionally, to find optimal parameters of an EAM potential, global 
-optimization approaches (such as Basin Hopping or Genetic Algorithm) will be 
-used because the analytical gradients of the total loss with respect to model
-parameters are difficult to derive and implement \textit{by hand}. In this 
-paper, we chose a new route to address this issue: to 'ask' machine learning 
-platform to handle derivations and implementations.
+However, MLIPs also have challenges. The large parameter space and lack of 
+physical background makes the "big data" a necessarity. The cost of dataset is 
+non-negligible. Besides, even "big data" can only cover a small portion of real 
+physical environments (temperature, external pressure, etc). Outside the 
+training zone, the performances of MILPs may not that stable. For long-time 
+molecular dynamics (MD) simulations of large-scale ($10^5$ or more) systems, 
+computation efficiency also becomes a major concern. Recent benchmark tests 
+suggest that MILPs are still too expensive. At present, most MLIPs are used to 
+examine small to medium ($10^3$ to $10^4$) systems.
+
+In this work, instead of designing new atomic descriptors, we chose a new route 
+to develop MLIP: combining machine learning with empirical potentials. We 
+successfully implemented EAM and its variant ADP within TensorFlow so that 
+machine learning approaches can be used directly to tune EAM and ADP potentials. 
+Our results suggest ML-EAM or ML-ADP can be as precise as the SNAP machine 
+learning method.
 
@@
 theoretical background of this work, including the formalism of the embedded 
-atom method, the expressions of the empirical potential and the algorithms for 
-integrating EAM with machine learning. Section \ref{sec:results} summarizes the 
-training results and the optimal parameters. Applications of the new potentials 
-are discussed in Section \ref{sec:discussions}. Technical details can be found 
-in the appendix.
+atom method and algorithms and details of the machine learned EAM. 
+Section \ref{sec:results} summarizes the training results and the optimal 
+parameters. Applications of the new potentials are discussed in 
+Section \ref{sec:discussions}.
 
@@
 % ------------------
-% Section 2.1 Theory
+% Section 2.A Theory
 % ------------------
@@
 and $j$, $F_{a}(\rho_{i})$ is the embedding energy and $\rho_{i}$ is the local 
-electron density. Typically, $\rho_{i}$ can be calculated with the following 
+electron density of atom $i$. $\rho_{i}$ can be calculated with the following 
 equation:
@@
 \end{equation}
+$F$, $\rho$ and $\phi$ can be either parameterized functions or cubic splines.
 
-The original EAM potential does not inlcude angular-dependent interactions. To 
+The original EAM formalism does not inlcude angular-dependent interactions. To 
 fix this problem, Baskes modified the original EAM and got MEAM (modified 
@@
 
-In this work, we use the EAM potential published by Zhou, Johnson and Wadley 
-(Zjw04) as an example to validate our machine learning approach. Zjw04 is a 
-quite popular EAM potential and it is applicable to a number of metals and 
-alloys. In the Zjw04 model, the electron density function has the following 
-form:
-\begin{equation}
-\label{eq:zjw04_rho}
-\rho_{b}(r) = \frac{
-    f_{e} \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]
-}{
-    1 + \left(r/r_{e} - \lambda\right)^{20}
-}
-\end{equation}
-where $r_e$ is a constant equal to equilibrium spacing between nearest neighors, 
-$f_{e}$, $\beta$, $\lambda$ are adjustable parameters. The pairwise potential 
-between the same species can be computed with:
-\begin{equation}
-\label{eq:zjw04_phi_aa}
-\phi_{aa}(r) = 
-\frac{A \exp\left[ -\alpha\left( r/r_{e} - 1 \right) \right]}
-     {1 + \left(r / r_{e} - \kappa\right)^{20}} - 
-\frac{B \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]}
-     {1 + \left(r / r_{e} - \lambda\right)^{20}}
-\end{equation}
-where $A$, $\alpha$ and $\kappa$ are also trainable parameters, $B$, $\beta$ and 
-$\kappa$ are used in Equation \ref{eq:zjw04_rho} already. For the pairwise 
-interaction between two atoms of different species, Zhou et al proposed an 
-interpolation form:
-\begin{equation}
-\label{eq:zjw04_phi_ab}
-\phi_{ab}(r) = \frac{1}{2}\left(
-    \frac{\rho_{b}(r)}{\rho_{a}(r)}\phi_{aa}(r) +
-    \frac{\rho_{a}(r)}{\rho_{b}(r)}\phi_{bb}(r) 
-\right)
-\end{equation}
-The embedding function has a more complicated form as it requires to fit a much 
-wider range of electron density values:
-\begin{equation}
-\label{eq:zjw04_embed}
-F(\rho) = \begin{cases}
-    \sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} &
-    \rho < \rho_{n} \\
-    \sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} &
-    \rho_{n} \leq \rho < \rho_{0} \\
-    F_{e}\left[ 
-        1 - \eta\ln\left( \frac{\rho}{\rho_s}\right) 
-    \right](\frac{\rho}{\rho_s})^{\eta} & \rho_{0} \leq \rho
-\end{cases}
-\end{equation}
-where $F_{ni}$, $F_{i}$, $\rho_e$, $\rho_s$, $\eta$ and $F_{e}$ are trainable 
-parameters, $\rho_n=0.85\rho_e$ and $\rho_0=1.15\rho_e$. For each metal, there 
-are 15 adjustable parameters. The original embedding potential is a stepwise 
-function. Thus, the minimization requires some tricks to ensure its continuity.
-To make it simpler, we slightly modified Equation \ref{eq:zjw04_embed}:
-\begin{align}
-\label{eq:zjw04xc_embed}
-F(\rho) 
-= & c_1 \cdot
-\sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} \nonumber \\
-+ & c_2 \cdot 
-\sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} \nonumber \\
-+ & c_3 \cdot
-F_{e}\left[1 - \eta\ln\left( \frac{\rho}{\rho_s}\right)\right]
-(\frac{\rho}{\rho_s})^{\eta} \\
-\label{eq:frho_c1}
-c_{1} = & \frac{1}{1 + e^{-2\left(\rho_{n} - \rho\right)}} \\
-\label{eq:frho_c3}
-c_{3} = & \frac{1}{1 + e^{-2\left(\rho - \rho_{0}\right)}} \\
-c_{2} = & 1 - c_1 - c_3
-\end{align}
-The new equation can be minimized without considering about boundary continuity.
-$\omega_1$ and $\omega_3$ are just damping factors calculated by the sigmoid 
-functions (Equations \ref{eq:frho_c1} and \ref{eq:frho_c3}).
-
-The dipole ($\mu_{ab}$) and quadrupole ($\lambda_{ab}$) functions have the same 
-form (developed by Mishin):
-\begin{align}
-\label{eq:adp_dipole}
-\mu_{ab}(r) & = \left[
-    d_{1}^{ab} \exp\left( -d_{2}^{ab}r \right) + d_{3}^{ab}
-\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right) \\
-\omega_{ab}(r) & = \left[
-    q_{1}^{ab} \exp\left( -q_{2}^{ab}r \right) + q_{3}^{ab}
-\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right)
-\end{align}
-where $d_{i}$, $q_{i}$, $r_0$ and $r_{h}$ are trainable parameters and $\psi(x)$
-is a damping function:
-\begin{equation}
-\label{eq:mishin_cutoff}
-\psi(x) = \begin{cases}
-    0 & x \ge 0 \\
-    \frac{x^4}{1 + x^4} & x < 0 
-\end{cases}
-\end{equation}
-
 % -----------
-% Section 2.2 Transformation
+% Section 2.B Transformation
 % -----------
@@
 (Equation \ref{eq:eam_total_energy}) must be transformed to a vectorizable form. 
-Without loss of generality, we take a binary alloy, AB, to demonstrate how to 
-derive this equation.
+Without loss of generality, we take the binary alloy, AB, to demonstrate how to 
+do the transformation.
 
@@
 \newcommand{\niab}{N_{i}^{\mathrm{AB}}}
-\newcommand{\nibb}{N_{i}^{\mathrm{BB}}}
-\newcommand{\niba}{N_{i}^{\mathrm{BA}}}
+\newcommand{\njbb}{N_{j}^{\mathrm{BB}}}
+\newcommand{\njba}{N_{j}^{\mathrm{BA}}}
 \newcommand{\riaa}{\vec{\mathbf{r}}_{i}^{\mathrm{AA}}}
@@
 \newcommand{\nbmax}{N_{\mathrm{B}}^{\mathrm{max}}}
-\newcommand{\nnl}{N_{\mathrm{nl}}}
+\newcommand{\nnl}{N^{\mathrm{nl}}}
+\newcommand{\nnli}{N^{\mathrm{nl}}_i}
 
-The energy of atom $i$ of specie $A$ can be calculated with the following 
-expanded equation (the cutoff radius $r_c$ is fixed):
+Suppose the cutoff radius $r_c$ is fixed, the energy of atom $i$ of specie $A$ 
+can be calculated with the following expanded equation:
 \begin{align}
@@
 \end{align}
-where $\niaa$ represents the number of neighors of specie $A$ of atom $i$ and 
-$\niab$ represents the number of neighors of specie $B$. $E_{i}^{B}$ has a 
-similar expression. For each atom, we can calculate its $\niaa$ and $\niab$. 
-Thus, we can find the maximum neighor list size $\nnl$:
+where $\niaa$ represents the number of A-type neighors of atom $i$ and 
+$\niab$ represents the number of B-type neighors. For atom $j$ of specie $B$, we
+can also write a similar form. 
+\begin{align}
+\label{eq:e_atom_phase_1}
+E_{j}^{B} 
+= & 
+\frac{1}{2}\sum_{i \neq j}^{\njbb}\phi_{\mathrm{BB}}(r_{ij}) +
+\frac{1}{2}\sum_{i \neq j}^{\njba}\phi_{\mathrm{AB}}(r_{ij}) \nonumber \\
++ & F_{\mathrm{B}}\left(
+    \sum_{j\neq i}^{\njbb}{\rho_{\mathrm{B}}(r_{ij})} +
+    \sum_{j\neq i}^{\njba}{\rho_{\mathrm{A}}(r_{ij})} 
+\right)
+\end{align}
+When $r_c$ is fixed, $\niaa$, $\niab$, $\njbb$ and $\njba$ are all constants and
+$\nnli$ is the maximum of these numbers. Finally, we can pre-determine the 
+maximum neighor list size $\nnl$:
 \begin{equation}
 \label{eq:nnl}
-\nnl = \max{\left(
-    \max\left({\niaa}\right), 
-    \max\left({\niab}\right),
-    \max\left({\nibb}\right)
-\right)}
+\nnl = \max{\left(\nnli\right)}
 \end{equation}
-$\nnl$ is a constant during training because both the dataset and $r_c$ are 
-fixed.
+$\nnl$ is also a constant in the training phase because both the training 
+dataset and $r_c$ are fixed.
 
-Assume $H(x)$ represents the heaviside step function:
+Next, assume $H(x)$ represents the heaviside step function:
 \begin{equation}
@@
 \end{equation}
-Then,
+then the pairwise term can be transformed to:
 \begin{align}
@@
 where $\vec{\mathbf{r}}_{i}^{\mathrm{AA}}$ is a $\nnl$-length column vector 
-whose last $\nnl - \niaa$ elements are padding zeros.
+whose last $\nnl - \niaa$ elements are zeros.
 
@@
 structure ($\namax$ and $\nbmax$) are also constants. Thus, any $\mathbf{G}$ can 
-be expanded to a $(\namax + \nbmax) \times \nnl \times 4$ matrix, $\mathbf{G}'$, 
-with zero-padding. As $\mathbf{G}'$ is a fixed-shape matrix and $\rho(r)$, 
-$\phi(r)$ and $F(\rho)$ are all elementwise functions, we can use any modern 
-machine learning platform (TensorFlow, PyTorch, MXNet, etc) to implement the EAM 
-model. In this paper, we chose TensorFlow as our coding framework. Based on the 
-virtual atom approach, we successfully designed a route to build the machine 
-learning computation graph directly from positions to total energy. Thus, 
-analytically-derived EAM force and virial stress can be calculated without pain.
+be expanded to a $(\namax + \nbmax) \times \nnl \times 4$ matrix $\mathbf{G}'$ 
+by zero-padding. In summary, arbitrary structure in the training dataset can be 
+converted to a fixed-shape descriptor matrix $\mathbf{G}'$.
+
+For the ADP formalism, the corresponding transformation is almost the same 
+except that $\mathbf{g}_{i}^{\mathrm{adp}}$ should also include the XYZ 
+components of $\vec{\mathbf{r}}_i$.
+
+% -----------
+% Section 2.C Functions
+% -----------
+\subsection{Functions}
+\label{sec:functions}
+
+In this work, we use the EAM potential published by Zhou, Johnson and Wadley 
+(Zjw04) as an example to validate our machine learning approach. Zjw04 is a 
+quite popular EAM potential. In the Zjw04 potential, the electron density 
+function has the following form:
+\begin{equation}
+\label{eq:zjw04_rho}
+\rho_{b}(r) = \frac{
+    f_{e} \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]
+}{
+    1 + \left(r/r_{e} - \lambda\right)^{20}
+}
+\end{equation}
+where $r_e$ is a constant equal to equilibrium spacing between nearest neighors, 
+$f_{e}$, $\beta$, $\lambda$ are adjustable parameters. The pairwise potential 
+between the same species can be computed with:
+\begin{equation}
+\label{eq:zjw04_phi_aa}
+\phi_{aa}(r) = 
+\frac{A \exp\left[ -\alpha\left( r/r_{e} - 1 \right) \right]}
+     {1 + \left(r / r_{e} - \kappa\right)^{20}} - 
+\frac{B \exp\left[ -\beta\left( r/r_{e} - 1 \right) \right]}
+     {1 + \left(r / r_{e} - \lambda\right)^{20}}
+\end{equation}
+where $A$, $B$, $\alpha$ and $\kappa$ are also trainable parameters, $\beta$ and 
+$\kappa$ are used in Equation \ref{eq:zjw04_rho} already. For the pairwise 
+interaction between two atoms of different species, Zhou et al proposed an 
+interpolation form:
+\begin{equation}
+\label{eq:zjw04_phi_ab}
+\phi_{ab}(r) = \frac{1}{2}\left(
+    \frac{\rho_{b}(r)}{\rho_{a}(r)}\phi_{aa}(r) +
+    \frac{\rho_{a}(r)}{\rho_{b}(r)}\phi_{bb}(r) 
+\right)
+\end{equation}
+The embedding function has a more complicated form as it requires to fit a much 
+wider range of electron density values:
+\begin{equation}
+\label{eq:zjw04_embed}
+F(\rho) = \begin{cases}
+    \sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} &
+    \rho < \rho_{n} \\
+    \sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} &
+    \rho_{n} \leq \rho < \rho_{0} \\
+    F_{e}\left[ 
+        1 - \eta\ln\left( \frac{\rho}{\rho_s}\right) 
+    \right](\frac{\rho}{\rho_s})^{\eta} & \rho_{0} \leq \rho
+\end{cases}
+\end{equation}
+where $F_{ni}$, $F_{i}$, $\rho_e$, $\rho_s$, $\eta$ and $F_{e}$ are trainable 
+parameters, $\rho_n=0.85\rho_e$ and $\rho_0=1.15\rho_e$. For each metal, there 
+are 15 adjustable parameters. The original embedding potential is a stepwise 
+function. Thus, the minimization requires some tricks to ensure its continuity.
+To make it simpler, we slightly modified Equation \ref{eq:zjw04_embed}:
 \begin{align}
-\label{eq:forces}
-f_{i} = & -\frac{\partial E^{total}}{\partial r_{i}} \\
-\label{eq:stress}
-V \cdot \epsilon = & -\mathbf{F}^{T}\mathbf{R} + \left(
-    \frac{\partial E^{total}}{\partial \mathbf{h}}
-\right)^T \mathbf{h}
+\label{eq:zjw04xc_embed}
+F(\rho) 
+= & c_1 \cdot
+\sum_{i=0}^{3}{F_{ni}\left( \frac{\rho}{\rho_n} - 1 \right)^{i}} \nonumber \\
++ & c_2 \cdot 
+\sum_{i=0}^{3}{F_{i}\left( \frac{\rho}{\rho_e} - 1 \right)^{i}} \nonumber \\
++ & c_3 \cdot
+F_{e}\left[1 - \eta\ln\left( \frac{\rho}{\rho_s}\right)\right]
+(\frac{\rho}{\rho_s})^{\eta} \\
+\label{eq:frho_c1}
+c_{1} = & \frac{1}{1 + e^{-2\left(\rho_{n} - \rho\right)}} \\
+\label{eq:frho_c3}
+c_{3} = & \frac{1}{1 + e^{-2\left(\rho - \rho_{0}\right)}} \\
+c_{2} = & 1 - c_1 - c_3
+\end{align}
+$\omega_1$ and $\omega_3$ are just damping factors calculated by the sigmoid 
+functions (Equations \ref{eq:frho_c1} and \ref{eq:frho_c3}).
+
+The dipole ($\mu_{ab}$) and quadrupole ($\lambda_{ab}$) functions have the same 
+form (developed by Mishin):
+\begin{align}
+\label{eq:adp_dipole}
+\mu_{ab}(r) & = \left[
+    d_{1}^{ab} \exp\left( -d_{2}^{ab}r \right) + d_{3}^{ab}
+\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right) \\
+\omega_{ab}(r) & = \left[
+    q_{1}^{ab} \exp\left( -q_{2}^{ab}r \right) + q_{3}^{ab}
+\right] \psi\left( \frac{r - r_{0}}{r_{h}} \right)
+\end{align}
+where $d_{i}$, $q_{i}$, $r_0$ and $r_{h}$ are trainable parameters and $\psi(x)$
+is a damping function:
+\begin{equation}
+\label{eq:mishin_cutoff}
+\psi(x) = \begin{cases}
+    0 & x \ge 0 \\
+    \frac{x^4}{1 + x^4} & x < 0 
+\end{cases}
+\end{equation}
+
+% -----------
+% Section 2.D Physical constraints
+% -----------
+\subsection{Physical constraints}
+\label{sec:constraints}
+
+Physical constraints are quite common in fitting traditional empirical 
+potentials. Physical constraints are typically static (cohesive energy, elastic 
+constants, etc) collected from experiments and they can be very effective when 
+training data is limited. For example, the cohesive energy, bulk modulus, 
+vacancy formation energy and other constraints were used to develop the original 
+Zjw04 potential. Mishin et al adopted the Rose universal equation of state to 
+ensure the performaces of his ADP potentials in the high pressure region. 
+However, such constraints are really rare in developing MILPs. One possible 
+explanation may be these constraints are generally derived properties and 
+implementing them in the loss function are technically difficult.
+
+In this work, we successfully integrated two constraints into the total loss:
+the Rose equation of state constraint and the elastic tensor constraint. These 
+two losses will be discussed later. The details of their implementations will be 
+described in another paper.
+
+The Rose constraint incoporates the universal equation of state (Rose et al) 
+into the total loss function. The Mishin-modified equation 
+\begin{equation}
+\label{eq:rose_eos}
+E(x) = E_{0}\left[
+    1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
+    e^{-\alpha x}
+\end{equation}
+is used because the original form tends to underestimate energies under high 
+pressures. In Equation \ref{eq:rose_eos}, $E_{0}$ is the energy of the 
+equilibrium structure, $x = a / a_{0} - 1$ is the relative isotropic scaling 
+factor ($a$ is the lattice constant), $\beta$ is a chosen parameter and 
+\begin{equation}
+\label{eq:rose_alpha}
+\alpha = \sqrt{-\frac{9 V_{0} B }{E_{0}}}
+\end{equation}
+where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
+of the Rose constraint guarantees the exact predictions of bulk modulus and 
+the energy-volume curve. The loss of the Rose EOS constraint 
+$\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
+differences between $E(x)^{\mathrm{Rose}}$ and their corresponding predicted 
+$E(x)$: 
+\begin{equation}
+\label{eq:rose_loss}
+\mathbf{L}^{\mathrm{Rose}} =
+\sum_{i}{\mathbf{RMSE}(E_{i}(x), E_{i}(x)^{\mathrm{Rose}})}
+\end{equation}
+In this work, for each included crystal, we use the same choices of $x$: 
+$x_{t} = x_{0} + \Delta x \cdot t, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
+\Delta x=0.01$. $\beta$ is fixed to 0.005.
+
+Elastic tensor is also a popular constraint for tuning empirical potentials but 
+rarely used directly in optimizing MILPs. Shyue Ping Ong used this constraint in 
+the outer loop (the global optimization based property-matching step) to find 
+optimal parameters of SNAP potentials.
+
+In this work, we successfully find a way to use elastic tensor directly as a 
+constraint. Given an equilibrium crystal structure, its elastic constant 
+$c_{ijkl}$ can be derived from $E^{total}$ directly:
+\begin{align}
+\label{eq:virial}
+V \cdot \epsilon & = -\mathbf{F}^{T}\mathbf{R} + \left(
+    \frac{\partial E^{total}}{\partial \mathbf{h}}\right)^T \mathbf{h} \\ 
+\label{eq:cijkl}
+c_{ijkl} |_{\epsilon \to 0, \mathbf{F} \to 0} & = \frac{1}{V}\left[
+    \left( 
+        \frac{\partial{\epsilon_{ij}}}{\partial{\mathbf{h}}}
+    \right)^{\mathrm{T}}\mathbf{h}
+\right]_{kl}
 \end{align}
@@
 atomic positions.
-The derivation of Equation \ref{eq:stress} has been published elsewhere. The 
-details of the virtual atom approach can be found in the appendix. The last step 
-is to find optimal parameters. This can be done by minimizing the mini-batch 
-loss function:
+
+In this work, the loss $\mathbf{L}^{\mathrm{elastic}}$ contributed by the 
+elastic tensor is also measured by the RMSE between $c_{ijkl}$ and 
+$c_{ijkl}^{\mathrm{dft}}$:
+\begin{align}
+\label{eq:cijkl_loss}
+\mathbf{L}^{\mathrm{elastic}} 
+& = \sum_{i}{c_{i} \cdot \mathbf{RMSE_{i}} + {|\epsilon|} + {|\mathbf{F}|}} \\
+\label{eq:cijkl_loss_gate}
+c_{i} & = \mathbf{ReLU}(\mathbf{MAE_{i}} - \tau) \\
+\label{eq:relu}
+\mathbf{ReLU}(x) & = \begin{cases}
+    x & x \ge 0 \\
+    0 & x < 0
+\end{cases}
+\end{align}
+where $\sum_{i}$ loops through all included crystals, $\mathbf{MAE}$ is the mean 
+absolute error and $\tau$ is a pre-selected gate parameter. When $\mathbf{MAE}$ 
+is below $\tau$, $\mathbf{L}^{\mathrm{elastic}}$ will not contribute to the 
+total loss. In this work, $\tau$ is set to 2 GPa.
+
+% -----------
+% Section 2.E Implementation
+% -----------
+\subsection{Implementation}
+\label{sec:implementation}
+
+The implementation of the machine learned embedded atom mathod and the physical
+constraints are beyond the scope of this work. The details will be discussed
+in another paper. Here, we will give a brief description.
+
+Both ML-EAM and ML-ADP are implemented within Google's TensorFlow. The 
+virtual-atom approach (VAP) is adopted so that we can construct a computation 
+graph from atomic positions to total energy directly. Thus, atomic forces 
+(Equation \ref{eq:forces}) and virial stress (Equation \ref{eq:virial}) can be 
+derived by the AutoGrad module of TensorFlow and calcualted automatically and 
+efficiently. 
+\begin{equation}
+\label{eq:forces}
+\mathbf{F} = -\frac{\partial E^{total}}{\partial \mathbf{R}}
+\end{equation}
+This direct computation graph also plays a key role in computing analytical 
+elastic tensor (Equation \ref{eq:cijkl}) and the Rose loss 
+(Equation \ref{eq:rose_eos}).
+
+To find optimal parameters of the funcitons in section \ref{sec:functions}, the 
+overall loss function shall be defined. Just like other machine learning tasks, 
+the mini-batch stochastic gradient descent algorithm is used to minimize the 
+loss function. Equation \ref{eq:loss} demonstrates the loss function used in 
+this work:
 \begin{align}
@@
     }
-}} 
+}} \nonumber \\
+& + \mathbf{L}^{\mathrm{Rose}} + \mathbf{L}^{\mathrm{elastic}}
 \end{align} 
 where $N_{b}$ is the batch size and $N_i$ is the number of atoms in structure 
-$i$. The superscript 'voigt' means that stress tensors should be converted to 
-Voigt form. The Adam optimizer is used to minimize Equation \ref{eq:loss}. 
-In most cases, we use 0.01 as the initial learning rate and the batch size 
-ranges from 20 to 50.
-
-% -----------
-% Section 2.3 Implementation
-% -----------
-\subsection{Implementation}
-\label{sec:implementation}
-
-% -----------
-% Section 2.4 Constraints
-% -----------
-\subsection{Constraints}
-\label{sec:constraints}
-
-The Rose constraint incoporates the universal equation of state (Rose et al) 
-into the total loss function. The Mishin-modified equation 
-\begin{equation}
-\label{eq:rose_eos}
-E(y) = E_{0}\left[
-    1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
-    e^{-\alpha x}
-\end{equation}
-is used because the original form tends to underestimate energies under high 
-pressures. In Equation \ref{eq:rose_eos}, $E_{0}$ is the energy of the 
-equilibrium structure, $x = a / a_{0} - 1$ is the relative isotropic scaling 
-factor ($a$ is the lattice constant), $\beta$ is a chosen parameter and 
-\begin{equation}
-\label{eq:rose_alpha}
-\alpha = \sqrt{-\frac{9 V_{0} B }{E_{0}}}
-\end{equation}
-where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
-of the Rose constraint guarantees the exact prediction of the bulk modulus and 
-the energy-volume curve. The loss of the Rose EOS constraint 
-$\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
-differences between $E(x)^{\mathrm{Rose}}$ and their corresponding predicted 
-$E(x)$: 
-\begin{equation}
-\label{eq:rose_loss}
-\mathbf{L}^{\mathrm{Rose}} =
-\sum_{i}{\mathbf{RMSE}(E_{i}(x), E_{i}(x)^{\mathrm{Rose}})}
-\end{equation}
-
-In this work, for each included crystal, we use the same choices of $x$: 
-$x_{t} = x_{0} + \Delta x \cdot t, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
-\Delta x=0.01$.
-
-Elastic constraints are common metrics for tuning empirical potentials. In the
-ML framework, fitting elastic constants of specific crystals is also possible.
-The elastic constant $c_{ijkl}$ can be derived from $E^{total}$ directly:
-\begin{equation}
-\label{eq:cijkl}
-c_{ijkl} |_{\epsilon \to 0, \mathbf{F} \to 0} = \frac{1}{V}\left[
-    \left( 
-        \frac{\partial{\epsilon_{ij}}}{\partial{\mathbf{h}}}
-    \right)^{\mathrm{T}}\mathbf{h}
-\right]_{kl}
-\end{equation}
-In this work, the loss $\mathbf{L}^{\mathrm{elastic}}$ contributed by the 
-elastic constraint is also measured by the RMSE between $c_{ijkl}$ and 
-$c_{ijkl}^{\mathrm{dft}}$:
-\begin{align}
-\label{eq:cijkl_loss}
-\mathbf{L}^{\mathrm{elastic}} 
-& = \sum_{i}{c_{i} \cdot \mathbf{RMSE_{i}} + {|\epsilon|} + {|\mathbf{F}|}} \\
-\label{eq:cijkl_loss_gate}
-c_{i} & = \mathbf{ReLU}(\mathbf{MAE_{i}} - \tau) \\
-\label{eq:relu}
-\mathbf{ReLU}(x) & = \begin{cases}
-    x & x \ge 0 \\
-    0 & x < 0
-\end{cases}
-\end{align}
-where $\sum_{i}$ loops through all included crystals, $\mathbf{MAE}$ is the mean 
-absolute error and $\tau$ is a pre-selected gate parameter. When $\mathbf{MAE}$ 
-is below $\tau$, $\mathbf{L}^{\mathrm{elastic}}$ will not contribute to the 
-total loss. In this work, $\tau$ is set to 1 GPa.
+$i$. $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ are overall weights of force 
+and virial stress contributions. The superscript 'voigt' means that virial 
+stress tensors should be converted to Voigt form. The Adam optimizer is used to 
+minimize Equation \ref{eq:loss}. In most cases, we use 0.01 as the initial 
+learning rate and the batch size ranges from 20 to 50. Since there are very few
+adjustable parameters, the optimization typically needs very few epochs to 
+converge. When the optimization is finished, the corresponding Lammps setfl 
+potential file will be exported.
 

### 2019-10-11 doc/papers/ml-eam/manuscript.tex
The ML-EAM manuscript is updated.

@@
 In this work, we successfully integrated two constraints into the total loss:
-the Rose equation of state constraint and the elastic tensor constraint. These 
-two losses will be discussed later. The details of their implementations will be 
-described in another paper.
+the Rose equation of state (EOS) constraint and the elastic tensor constraint. 
+These two losses will be discussed later. The details of their implementations 
+will be described in another paper.
 
@@
 $\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
-differences between $E(x)^{\mathrm{Rose}}$ and their corresponding predicted 
+differences between $E(x)^{\mathrm{dft}}$ and their corresponding predicted 
 $E(x)$: 
@@
 \label{eq:rose_loss}
-\mathbf{L}^{\mathrm{Rose}} =
-\sum_{i}{\mathbf{RMSE}(E_{i}(x), E_{i}(x)^{\mathrm{Rose}})}
+\mathbf{L}^{\mathrm{Rose}} = \sum_{\Omega}{
+    \sqrt{\sum_{i}{\left(E(x_i) - E(x_i)^{\mathrm{dft}}\right)^2}}
+}
 \end{equation}
-In this work, for each included crystal, we use the same choices of $x$: 
-$x_{t} = x_{0} + \Delta x \cdot t, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
-\Delta x=0.01$. $\beta$ is fixed to 0.005.
+Here $\Omega$ denotes all selected crystals. In this work, for each included 
+crystal, we use the same choices of $x$: 
+$x_{i} = x_{0} + \Delta x \cdot i, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
+\Delta x=0.01$. In this work, $\beta^{\mathrm{Ni}}$ is 0.005 and 
+$\beta^{\mathrm{Mo}}$ is 0.150.
 
@@
 \mathbf{L}^{\mathrm{elastic}} 
-& = \sum_{i}{c_{i} \cdot \mathbf{RMSE_{i}} + {|\epsilon|} + {|\mathbf{F}|}} \\
+& = \sum_{\Omega}{\left(
+    \omega_{\Omega} \cdot \mathbf{RMSE}_{\Omega} 
+    + ||\epsilon|| + ||\mathbf{F}||
+\right)}
+ \\
 \label{eq:cijkl_loss_gate}
-c_{i} & = \mathbf{ReLU}(\mathbf{MAE_{i}} - \tau) \\
+\omega_{\Omega} & = \mathbf{ReLU}(\mathbf{MAE}_{\Omega} - \tau) \\
 \label{eq:relu}
@@
 \end{align}
-where $\sum_{i}$ loops through all included crystals, $\mathbf{MAE}$ is the mean 
-absolute error and $\tau$ is a pre-selected gate parameter. When $\mathbf{MAE}$ 
-is below $\tau$, $\mathbf{L}^{\mathrm{elastic}}$ will not contribute to the 
-total loss. In this work, $\tau$ is set to 2 GPa.
+where $\sum_{\Omega}$ loops through all included crystals, 
+$\mathbf{MAE}_{\Omega}$ and $\mathbf{RMSE}_{\Omega}$ are the mean absolute error 
+and root mean squared error between predicted elastic constants and DFT elastic 
+constants. $\tau$ is a pre-selected gate parameter. 
+When $\mathbf{MAE}$ is below $\tau$, $\mathbf{L}^{\mathrm{elastic}}$ will not 
+contribute to the total loss. In this work, $\tau$ is set to 2 GPa.
 
@@
 }} \nonumber \\
-& + \mathbf{L}^{\mathrm{Rose}} + \mathbf{L}^{\mathrm{elastic}}
+& + \chi_{\mathrm{rose}}\mathbf{L}^{\mathrm{Rose}} 
++ \chi_{\mathrm{elastic}}\mathbf{L}^{\mathrm{elastic}}
 \end{align} 
 where $N_{b}$ is the batch size and $N_i$ is the number of atoms in structure 
-$i$. $\chi_{\mathrm{f}}$ and $\chi_{\mathrm{s}}$ are overall weights of force 
-and virial stress contributions. The superscript 'voigt' means that virial 
+$i$. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{s}}$, $\chi_{\mathrm{rose}}$ and 
+$\chi_{\mathrm{elastic}}$ are overall weights of force, virial stress, rose EOS 
+and elastic contributions. The superscript 'voigt' means that virial 
 stress tensors should be converted to Voigt form. The Adam optimizer is used to 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Results and Discussions}
+\section{Results}
 \label{sec:results}
 
-The publicly available Ni-Mo dataset is use to demonstrate our ML-EAM approach. 
-This dataset is built by Shyue Ping Ong and co-workers. It contains 3973 unique
-Ni-Mo solids, including 373 elemental Ni and 284 elemental Mo. DFT calculations 
-were done by VASP at the PBE level with projector augmented-wave approach.
+The publicly Ni-Mo dataset is used to evaluate our approach. This dataset is 
+provided by Shyue Ping Ong. It contains 3973 different Ni-Mo solids. All 
+calculations were done by VASP with the PBE functional and the projector 
+augmented-wave approach.
 
-Table \ref{table:parameters} shows the optimization results. All these 
-minimization tasks include energy, force and stress terms in their total losses.
-The $\chi_{\mathrm{f}}$ in Equation \ref{eq:loss} is set to 10 and 
-$\chi_{\mathrm{s}}$ is fixe to 80. In this paper, the superscript tag 'old' 
-denotes the original Zjw04, 'res' means restricted optimization and 'unres' 
-means unrestricted optimization. Here 'unrestricted' indicates the parameter 
-$r_e$ will be treated as a common adjustable variable.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.A
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Ni}
+\label{sec:elementary_Ni}
 
-Table \ref{table:MAE} demonstrates the prediction errors of the machine learned
-EAM models and reference models.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Ni - EAM - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}[h!]
+\centering
+\includegraphics[scale=0.57]{figures/Ni_eam.png}
+\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
+Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\end{figure*}
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Ni - EOS
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[h!]
+\centering
+\includegraphics[scale=0.65]{figures/Ni_all_eos.png}
+\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
+Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\end{figure}
+
+We first use the elementary fcc Ni dataset to show our approach. This dataset 
+has 461 structures in total. 400 were randomly selected to form the training 
+subset. In this experiment, $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and 
+$\chi_{\mathrm{elastic}}$ are set to 1, 3 and 0.05 respectively. In this 
+section, SNAP shall refer to the elementary SNAP Ni model. Table 
+\ref{table:elementary_Ni_mae} shows the MAEs of those models. The original EAM 
+model already has an accepetable performace on this dataset. Our machine 
+learning approach can further reduce the energy MAE to 4.1 meV/atom. All of 
+these models have similar force prediction performance.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni - MAE
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}[h]
+\centering
+\begin{tabular}{lccc}
+\hline
+    & SNAP & EAM & ML-EAM \\
+\hline
+Energy MAE (meV/atom) & 1.2 & 10.6 & 4.1 \\
+Force MAE (eV/\AA) & 0.05 & 0.06 & 0.05 \\
+\hline
+\end{tabular}
+\caption{\label{table:elementary_Ni_mae} Comparion of the energy and force 
+accuracy of the elementary SNAP Ni mode, the original EAM and the machine 
+learned EAM.
+}
+\end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni - Material Properties
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
 \begin{table*}[h]
 \centering
-\begin{tabular}{lcccccccc}
+\begin{tabular}{lcccccc}
 \hline
-    & Ni$^{\mathrm{old}}$ & Ni & Ni$^{\mathrm{alloy}}$ 
-    & Mo$^{\mathrm{old}}$ & Mo & Mo$^{\mathrm{alloy}}$ \\
+    & DFT & SNAP & EAM & ML-EAM & Expt. \\
 \hline
-$r_e$ & 2.488746 & 2.124480 & & 2.728100 & & \\
-$f_e$ & 2.007018 & 2.633256 & & 2.723710 & & \\
-$\rho_e$ & 27.562015 & 27.233315 & \\ 
-$\rho_s$ & 27.930410 & 26.392414 &\\
-$\alpha$ & 8.383453 & 8.452753 & \\
-$\beta$ & 4.471175 & 3.285651 & \\
-$A$ & 0.429046 & 0.9802988 & \\
-$B$ & 0.633531 & 0.8919016 & \\
-$\kappa$ & 0.443599 & 0.5685785 & \\
-$\lambda$ & 0.820658 & 1.1653832 & \\
-$F_{n0}$ & -2.693513 & -3.4354472 & \\
-$F_{n1}$ & -0.076445 & 0.3544341 & \\
-$F_{n2}$ & 0.241442 & -2.5563858 & \\
-$F_{n3}$ & -2.375626 & -7.1984844 & \\
-$F_{0}$ & -2.70 & -3.236908 & \\
-$F_{1}$ & 0 & 1.4576268 & \\
-$F_{2}$ & 0.265390 & 2.1785288 & \\
-$F_{3}$ & -0.152856 & -1.642411 & \\
-$\eta$ & 0.469000 & 4.305329 & \\
-$F_e$ & -2.699486 & -3.6163342 & \\
+$T_{m}$(K) & & 1785 & 1520 & 1765 & 1600 & 1728 \\
+$c_{11}$ (GPa) & 276 & 276 (0.0\%) & 248 (-10.1\%) & 260 (-5.8\%) & 274 (-0.7\%) & 261 \\
+$c_{12}$ (GPa) & 159 & 159 (0.0\%) & 147 (-7.5\%) & 151 (0.0\%) & 163 (2.5\%) & 151 \\
+$c_{44}$ (GPa) & 132 & 132 (0.0\%) & 125 (-5.3\%) & 131 (0.0\%) & 131 (-0.8\%) & 132 \\
+$E_{v}$ (eV) & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & 1.54–1.80 \\
+$E_{m}$ (eV) & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%) & 2.58 (0.0\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 2.77–2.95 \\
 \hline
 \end{tabular}
-\caption{\label{table:parameters} The original (labeled as 'old'), elemental and 
-alloy parameters.}
+\caption{\label{table:elementary_Ni} Comparison of the calculated and 
+experimental material properties of elementary Ni. $T_{m}$ is the melting 
+point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
+formation energy and migration energy, respectively. SNAP refers to the 
+elementary Ni SNAP model.
+}
 \end{table*}
+
+% Table \ref{table:parameters} shows the optimization results. All these 
+% minimization tasks include energy, force and stress terms in their total losses.
+% The $\chi_{\mathrm{f}}$ in Equation \ref{eq:loss} is set to 10 and 
+% $\chi_{\mathrm{s}}$ is fixe to 80. In this paper, the superscript tag 'old' 
+% denotes the original Zjw04, 'res' means restricted optimization and 'unres' 
+% means unrestricted optimization. Here 'unrestricted' indicates the parameter 
+% $r_e$ will be treated as a common adjustable variable.
+
+% Table \ref{table:MAE} demonstrates the prediction errors of the machine learned
+% EAM models and reference models.
+
+% \begin{table*}[h]
+% \centering
+% \begin{tabular}{lcccccccc}
+% \hline
+%     & Ni$^{\mathrm{old}}$ & Ni & Ni$^{\mathrm{alloy}}$ 
+%     & Mo$^{\mathrm{old}}$ & Mo & Mo$^{\mathrm{alloy}}$ \\
+% \hline
+% $r_e$ & 2.488746 & 2.124480 & & 2.728100 & & \\
+% $f_e$ & 2.007018 & 2.633256 & & 2.723710 & & \\
+% $\rho_e$ & 27.562015 & 27.233315 & \\ 
+% $\rho_s$ & 27.930410 & 26.392414 &\\
+% $\alpha$ & 8.383453 & 8.452753 & \\
+% $\beta$ & 4.471175 & 3.285651 & \\
+% $A$ & 0.429046 & 0.9802988 & \\
+% $B$ & 0.633531 & 0.8919016 & \\
+% $\kappa$ & 0.443599 & 0.5685785 & \\
+% $\lambda$ & 0.820658 & 1.1653832 & \\
+% $F_{n0}$ & -2.693513 & -3.4354472 & \\
+% $F_{n1}$ & -0.076445 & 0.3544341 & \\
+% $F_{n2}$ & 0.241442 & -2.5563858 & \\
+% $F_{n3}$ & -2.375626 & -7.1984844 & \\
+% $F_{0}$ & -2.70 & -3.236908 & \\
+% $F_{1}$ & 0 & 1.4576268 & \\
+% $F_{2}$ & 0.265390 & 2.1785288 & \\
+% $F_{3}$ & -0.152856 & -1.642411 & \\
+% $\eta$ & 0.469000 & 4.305329 & \\
+% $F_e$ & -2.699486 & -3.6163342 & \\
+% \hline
+% \end{tabular}
+% \caption{\label{table:parameters} The original (labeled as 'old'), elemental and 
+% alloy parameters.}
+% \end{table*}
 

### 2019-10-16 doc/papers/ml-eam/manuscript.tex
The ML-EAM manuscript is updated.

@@
 
+The melting points $T_{m}$ of bcc Mo and fcc Ni were measured with the 
+solid-liquid coexistence approach. For fcc Ni, $30 \times 10 \times 10$ 
+supercells were used and for bcc the supercells were $30 \times 15 \times 15$. 
+The time step was set to 1 fs. The simulation for each temperature was carried 
+out for 300 ps.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 % 
-% Figure: Ni - EAM - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure*}[h!]
-\centering
-\includegraphics[scale=0.57]{figures/Ni_eam.png}
-\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
-Zjw04 EAM and the machine learned EAM (ML-EAM).}
-\end{figure*}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
 % Figure: Ni - EOS
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}[h!]
+\begin{figure}[htp]
 \centering
 \includegraphics[scale=0.65]{figures/Ni_all_eos.png}
-\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
-Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\caption{\label{fig:Ni_eam_eos} The energy-volume curves of the original EAM, 
+SNAP, ML-EAM and DFT for the fcc Ni.}
 \end{figure}
@@
 subset. In this experiment, $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and 
-$\chi_{\mathrm{elastic}}$ are set to 1, 3 and 0.05 respectively. In this 
-section, SNAP shall refer to the elementary SNAP Ni model. Table 
-\ref{table:elementary_Ni_mae} shows the MAEs of those models. The original EAM 
-model already has an accepetable performace on this dataset. Our machine 
-learning approach can further reduce the energy MAE to 4.1 meV/atom. All of 
-these models have similar force prediction performance.
+$\chi_{\mathrm{elastic}}$ were set to 1, 3 and 0.05 respectively. The batch size
+was 25. Only the fcc Ni was included in $\Omega$ (Equation \ref{eq:rose_loss} 
+and \ref{eq:cijkl_loss}).
+
+Table \ref{table:elementary_Ni_mae} shows the MAEs of those models. The original 
+EAM model already has an accepetable performace on this fcc dataset. Its energy 
+MAE is 10.6 meV/atom and the force MAE is 0.06 eV/\AA. The MEAM performs 
+slightly worse on this dataset with an energy MAE of 17.6 meV/atom and force MAE
+of 0.08 eV/\AA. Our machine learning approach can further reduce the energy MAE 
+to 4.1 meV/atom and the force MAE to 0.05 eV/\AA, which are much closer to the 
+elementary SNAP Ni model.
+
+Figure \ref{fig:Ni_eam_eos} plots the equation of state curves obtained with the 
+DFT, SNAP, EAM and ML-EAM models. The whole fitting region ranges from 84\% to 
+118\% of the equilibrium volume. The original EAM significantly underestimates 
+the energy at both tensile and compress strains. However, our machine learning 
+approach together with the Rose constraint can fix this problem. The 
+energy-volume curve of ML-EAM overalps with the DFT curve very well for the 
+entire fitting region.
+
+Table \ref{table:elementary_Ni} summerizes the predicted material properties of 
+fcc Ni, including the melting point, the elastic constants, the vacancy 
+formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
+$E_{a}$. The original EAM already performs well on these properties. ML-EAM 
+further improves the elastic constants. The errors were significantly reduced 
+to around 1-2\%.
 
@@
 \centering
-\begin{tabular}{lccc}
+\begin{tabular}{lcccc}
 \hline
-    & SNAP & EAM & ML-EAM \\
+ MAE & SNAP & EAM & MEAM & ML-EAM \\
 \hline
-Energy MAE (meV/atom) & 1.2 & 10.6 & 4.1 \\
-Force MAE (eV/\AA) & 0.05 & 0.06 & 0.05 \\
+Energy (meV/atom) & 1.2 & 10.6 & 17.8 & 4.1 \\
+Force (eV/\AA) & 0.05 & 0.06 & 0.08 & 0.05 \\
 \hline
@@
 \caption{\label{table:elementary_Ni_mae} Comparion of the energy and force 
-accuracy of the elementary SNAP Ni mode, the original EAM and the machine 
-learned EAM.
+accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
+ML-EAM.
 }
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table*}[h]
+\begin{table*}[htp]
 \centering
@@
 \hline
-    & DFT & SNAP & EAM & ML-EAM & Expt. \\
+    & DFT & SNAP & EAM & MEAM & ML-EAM & Exp. \\
 \hline
-$T_{m}$(K) & & 1785 & 1520 & 1765 & 1600 & 1728 \\
+$T_{m}$(K) & & 1785 & 1520 & 1765 & 1520 & 1728 \\
 $c_{11}$ (GPa) & 276 & 276 (0.0\%) & 248 (-10.1\%) & 260 (-5.8\%) & 274 (-0.7\%) & 261 \\
@@
 \caption{\label{table:elementary_Ni} Comparison of the calculated and 
-experimental material properties of elementary Ni. $T_{m}$ is the melting 
+experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
 point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
@@
 \end{table*}
+
+Figure \ref{fig:Ni_eam} compares the $rho(r)$, $F(\rho)$ and $\phi(r)$ functions
+of ML-EAM with original Zjw04 EAM. The pairwise potential $\phi(r)$ almost 
+remains the same while the embedding function $F(\rho)$ and the electron density 
+function $\rho(r)$ changes significantly. Both $\rho(r)$ and $\phi(r)$ converge
+to zero at around $r=4.8$ \AA, which is rougly 2 times of the equilibrium 
+spacing between nearest neighbors.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Ni - EAM - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}[htp]
+\centering
+\includegraphics[scale=0.57]{figures/Ni_eam.png}
+\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
+Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.B
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Mo}
+\label{sec:elementary_Mo}
+
+The second test example is bcc Mo. This dataset has 284 structures. 34 of 
+them were used as the testing subset and the rest were used for training. 
+The training settings were the same with fcc Ni. An ADP potential was also 
+optimized for bcc Mo.
+
+Table \ref{table:elementary_Mo_mae} summerizes the energy and force MAEs on the 
+test subset. The original Zjw04 EAM performs significantly worse. The energy
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Mo - EAM/ADP - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}[htp]
+\centering
+\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
+\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
+Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
+ML-ADP.}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Mo - MAE
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}[h]
+\centering
+\begin{tabular}{lcccc}
+\hline
+ MAE   & SNAP & EAM & ML-EAM & ML-ADP \\
+\hline
+Energy (meV/atom) & 13.2 & 58.9 & 21.7 & 22.8 \\
+Force (eV/\AA) & 0.25 & 0.31 & 0.28 & 0.27 \\
+\hline
+\end{tabular}
+\caption{\label{table:elementary_Mo_mae} Comparion of the energy and force 
+accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
+ML-EAM.
+}
+\end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Mo - Material Properties
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}[htp]
+\centering
+\begin{tabular}{lcccccc}
+\hline
+    & DFT & SNAP & EAM & ML-EAM & ML-ADP & Exp. \\
+\hline
+$T_{m}$(K) & & 3000 & 3750 & 2940 & 2880 & 2890 \\
+$c_{11}$ (GPa) & 472 & 473 (0.2\%) & 456 (-3.4\%) & 260 (-5.8\%) & 274 (-0.7\%) & 479 \\
+$c_{12}$ (GPa) & 158 & 152 (-3.8\%) & 167 (5.7\%) & 151 (0.0\%) & 163 (2.5\%) & 165 \\
+$c_{44}$ (GPa) & 106 & 107 (0.9\%) & 115 (8.5\%) & 131 (0.0\%) & 131 (-0.8\%) & 108 \\
+$E_{v}$ (eV) & 2.87 & 2.61 (-9.1\%) & 3.02 (5.2\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & \\
+$E_{m}$ (eV) & 1.12 & 1.39 (24.1\%) & 1.54 (37.5\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 4.00 \\
+\hline
+\end{tabular}
+\caption{\label{table:elementary_Mo} Comparison of the calculated and 
+experimental material properties of elementary bcc Mo. SNAP refers to the 
+elementary Mo SNAP model.
+}
+\end{table*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 3.C
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\subsection{Mo-Ni}
+\label{sec:alloy}
 
@@
 
+The above results suggest that with machine learning and essential physical 
+constraints, for the fcc and bcc solids, the traditional empirical potentials, 
+EAM/ADP, can be improved to be as accurate as the SNAP method. However, 
+EAM/ADP are around $10^2$ to $10^3$ times faster than SNAP.
+
+The many-body expansion (MBE) is one of the most widely used schemes for fitting 
+potential energy surfaces. In the many-body expansion scheme, the total energy 
+of a system with N atoms can be expressed as the sum of all k-body terms where 
+$k \le 1$:
+\begin{equation}
+\label{eq:many_body_expansion}
+E = 
+\sum_{i}^{\mathrm{C^N_1}}{E^{(1)}_{i}} +
+\sum_{i,j}^{\mathrm{C^N_2}}{E^{(2)}_{ij}} + 
+\sum_{i,j,k}^{\mathrm{C^N_3}}{E^{(3)}_{ijk}} + \cdots 
+\end{equation}
+where $\mathrm{C^N_k}$ is the binomial coefficient and $E^{(k)}$ represents the 
+k-body contribution. In many cases, higher-order terms like $E_{ij}$ or 
+$E_{ijk}$ are symmetric: $E_{ij}=E_{ji}$, $E_{ijk}=E_{ikj}=E_{jik}=\cdots$. 
+Thus, Equation \ref{eq:many_body_expansion} can be further transformed to:
+\begin{align}
+\label{eq:MBE_atomic}
+E & = \sum_{i}^{\mathrm{N}}{\left(
+    E^{(1)}_{i} + 
+    \frac{1}{2!}\sum_{j \ne i}^{\mathrm{N}}{E^{(2)}_{ij}} +
+    \frac{1}{3!}\sum_{j \ne i}^{\mathrm{N}}{
+        \sum_{k \ne i,j}^{\mathrm{N}}{E^{(3)}_{ijk}}
+    } +
+    \cdots
+\right)} \nonumber \\
+& = \sum_{i}^{\mathrm{N}}{E_{i}}
+\end{align}
+where $E_{i}$ is the atomic energy of atom $i$.
+
+In fact, the EAM formalism can be considered as a variant of MBE truncated at 
+$k=2$ (Equation \ref{eq:eam_total_energy}). The embedding contribution $F(\rho)$ 
+serves as the one-body term. The pairwise contribution 
+$\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
+two-body term in Equation \ref{eq:MBE_atomic}. The ADP formalism uses a much 
+more complicated two-body term by introducing the pairwise dipole and quadrupole 
+terms.
+
+Although the SNAP method is quite complicated, the current formalism can still 
+be viewed as a variant of MBE truncated at $k=2$. The atomic energy
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2019-10-16 tensoralloy/nn/atomic/embed.py
Start working on a new ANN: atomic neural network with advanced one-body term.

@@ -1,0 +1,107 @@
+#coding=utf-8
+"""
+This module defines a variant of `AtomicNN`: `EmbeddedAtomicNN`.
+"""
+from __future__ import print_function, absolute_import
+
+__author__ = 'Xin Chen'
+__email__ = 'Bismarrck@me.com'
+
+
+import tensorflow as tf
+import numpy as np
+
+from tensorflow_estimator import estimator as tf_estimator
+
+from tensoralloy.nn.eam.potentials import available_potentials
+from tensoralloy.nn.atomic.atomic import AtomicNN
+from tensoralloy.nn.utils import log_tensor, get_activation_fn
+from tensoralloy.nn.convolutional import convolution1x1
+from tensoralloy.precision import get_float_dtype
+
+
+class EmbeddedAtomicNN(AtomicNN):
+    """
+    An variant of `AtomicResNN` whose one-body energy is calculated with the
+    EAM approach.
+    """
+
+    def _get_model_outputs(self,
+                           features: dict,
+                           descriptors: dict,
+                           mode: tf_estimator.ModeKeys,
+                           verbose=False):
+        """
+        Return the Op to compute internal energy E.
+        """
+        collections = [self.default_collection]
+
+        with tf.variable_scope("ANN"):
+            rho_min = tf.constant(1e-8, dtype=get_float_dtype())
+            activation_fn = get_activation_fn(self._activation)
+            outputs = []
+            for element, (value, atom_mask) in descriptors.items():
+                with tf.variable_scope(element, reuse=tf.AUTO_REUSE):
+                    x = tf.identity(value, name='input')
+                    if mode == tf_estimator.ModeKeys.PREDICT:
+                        assert x.shape.ndims == 2
+                        x = tf.expand_dims(x, axis=0, name='3d')
+                    with tf.name_scope("Embed"):
+                        rho = tf.identity(x, name='rho')
+                        safe_rho = tf.maximum(rho, rho_min, name='rho/safe')
+                        log_rho = tf.math.log(safe_rho, name='rho/log')
+
+
+                    if self._minmax_scale:
+                        with tf.name_scope("MinMax"):
+                            _collections = [
+                                               tf.GraphKeys.GLOBAL_VARIABLES,
+                                               tf.GraphKeys.MODEL_VARIABLES,
+                                           ] + collections
+                            _shape = [1, 1, x.shape[-1]]
+                            _dtype = x.dtype
+                            _get_initializer = \
[…]

### 2019-10-16 doc/papers/ml-eam/manuscript.tex
Add more data.

@@
 
+The optimized parameters are listed in the appendix.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
-% Table \ref{table:parameters} shows the optimization results. All these 
-% minimization tasks include energy, force and stress terms in their total losses.
-% The $\chi_{\mathrm{f}}$ in Equation \ref{eq:loss} is set to 10 and 
-% $\chi_{\mathrm{s}}$ is fixe to 80. In this paper, the superscript tag 'old' 
-% denotes the original Zjw04, 'res' means restricted optimization and 'unres' 
-% means unrestricted optimization. Here 'unrestricted' indicates the parameter 
-% $r_e$ will be treated as a common adjustable variable.
-
-% Table \ref{table:MAE} demonstrates the prediction errors of the machine learned
-% EAM models and reference models.
-
-% \begin{table*}[h]
-% \centering
-% \begin{tabular}{lcccccccc}
-% \hline
-%     & Ni$^{\mathrm{old}}$ & Ni & Ni$^{\mathrm{alloy}}$ 
-%     & Mo$^{\mathrm{old}}$ & Mo & Mo$^{\mathrm{alloy}}$ \\
-% \hline
-% $r_e$ & 2.488746 & 2.124480 & & 2.728100 & & \\
-% $f_e$ & 2.007018 & 2.633256 & & 2.723710 & & \\
-% $\rho_e$ & 27.562015 & 27.233315 & \\ 
-% $\rho_s$ & 27.930410 & 26.392414 &\\
-% $\alpha$ & 8.383453 & 8.452753 & \\
-% $\beta$ & 4.471175 & 3.285651 & \\
-% $A$ & 0.429046 & 0.9802988 & \\
-% $B$ & 0.633531 & 0.8919016 & \\
-% $\kappa$ & 0.443599 & 0.5685785 & \\
-% $\lambda$ & 0.820658 & 1.1653832 & \\
-% $F_{n0}$ & -2.693513 & -3.4354472 & \\
-% $F_{n1}$ & -0.076445 & 0.3544341 & \\
-% $F_{n2}$ & 0.241442 & -2.5563858 & \\
-% $F_{n3}$ & -2.375626 & -7.1984844 & \\
-% $F_{0}$ & -2.70 & -3.236908 & \\
-% $F_{1}$ & 0 & 1.4576268 & \\
-% $F_{2}$ & 0.265390 & 2.1785288 & \\
-% $F_{3}$ & -0.152856 & -1.642411 & \\
-% $\eta$ & 0.469000 & 4.305329 & \\
-% $F_e$ & -2.699486 & -3.6163342 & \\
-% \hline
-% \end{tabular}
-% \caption{\label{table:parameters} The original (labeled as 'old'), elemental and 
-% alloy parameters.}
-% \end{table*}
-
 \begin{table*}[h]
@@
 \hline
-    & Model & Mo & Ni$_4$Mo & Ni$_3$Mo & Ni$_{\mathrm{Mo}}$ & Mo$_{\mathrm{Ni}}$ 
-    & Ni & Overall \\
+                  & Model  & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
 \hline
@@
                   & EAM    & 58.9 & 211.2    & 255.6    & 46.5               & 147.6              & 10.6 & 117.2   \\
-    & \color{red} ML-EAM & \color{red} 45.0 & \color{red} 10.6 
-    & \color{red} 7.1 & \color{red} 39.0 & \color{red} 29.8 & \color{red} 10.4 
-    & \color{red} 27.4 \\
-    & NN (esf) & 30.0 & 6.1 & 9.0 & 16.6 & 26.2 & 7.8 & 19.1 \\
+                  & ML-EAM & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
+                  & ML-ADP & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
 \hline
 Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
-& EAM & 0.31 & 0.20 & 0.19 & 0.21 & 0.57 & 0.06 & 0.26 \\
-& \color{red} ML-EAM & \color{red} 0.31 & \color{red} 0.17 & \color{red} 0.15 
-& \color{red} 0.23 & \color{red} 0.18 & \color{red} 0.09 & \color{red} 0.17 \\
-& NN (esf) & 0.36 & 0.10 & 0.11 & 0.08 & 0.16 & 0.06 & 0.12 \\
-% \hline
-% Stress (GPa) & Mo SNAP & \textbf{0.87} & & & & & & \\
-% & Mo SFNN & 1.00 & & & & & & \\
-% & Ni-Mo SFNN & 5.77 & \textbf{1.72} & 1.74 & 1.45 & 3.75 & 1.97 & 2.83 \\
-% & Ni-Mo SFNN (esf) & \textbf{1.84} & 2.05 & \textbf{1.38} & \textbf{0.57} & 
-%     \textbf{1.22} & \textbf{1.91} & \textbf{1.27} \\
+                  & EAM    & 0.40 & 0.20     & 0.19     & 0.21               & 0.57               & 0.06 & 0.26    \\
+                  & ML-EAM & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
+                  & ML-ADP & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
 \hline
@@
 Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
-relative to DFT.}
+relative to the DFT on the entire Mo-Ni dataset.}
 \end{table*}
@@
 \hline
-    & DFT & Ni-Mo SNAP & ML-EAM & EAM & Experiment \\
-\hline
-Mo \\
-$c_{11}$ & 472 & 475 (0.6\%) & 477 (1.1\%) & 457 (-3.2\%) & 479 \\
-$c_{12}$ & 158 & 163 (3.2\%) & 166 (5.1\%) & 168 (6.3\%) & 165 \\
-$c_{44}$ & 106 & 111 (4.7\%) & 101 (-4.7\%) & 116 (9.4\%) & 108 \\
-$B_{\mathrm{VRH}}$ & 263 & 267 (1.5\%) & 270 (2.7\%) & 264 (0.4\%) & 270 \\
-$G_{\mathrm{VRH}}$ & 124 & 127 (2.4\%) & 127 (2.4\%) & 127 (2.4\%) & 125 \\
-$\mu$ & 0.30 & 0.29 (-3.3\%) & 0.31 (3.3\%) & 0.29 (-3.3\%) & 0.30 \\
-\hline
-Ni \\
-$c_{11}$ & 276 & 269 (-2.5\%) & 268 (-2.9\%) & 248 (-10.1\%) & 261 \\
-$c_{12}$ & 159 & 150 (-5.7\%) & 165 (3.8\%) & 147 (-7.5\%) & 151 \\
-$c_{44}$ & 132 & 135 (2.3\%) & 116 (-12.1\%) & 125 (-5.3\%) & 132 \\
-$B_{\mathrm{VRH}}$ & 198 & 190 (-4.0\%) & 200 (1.0\%) & 181 (-8.6\%) & 188 \\
-$G_{\mathrm{VRH}}$ & 95 & 97 (2.1\%) & 84 (-11.6\%) & 87 (-8.4\%) & 479 \\
-$\mu$ & 0.29 & 0.28 (-3.4\%) & 0.31 (6.8\%) & 0.29 (0.0\%) & 0.29 \\
+                   & DFT  & SNAP          & EAM           & ML-EAM        & ML-ADP        \\
 \hline
 Ni$_3$Mo \\
-$c_{11}$ & 385 & 420 (9.1\%) & 430 (11.7\%) & 195 (-49.4\%) & \\
-$c_{12}$ & 166 & 197 (18.7\%) & 187 (12.7\%) & 98 (-41.0\%) & \\
-$c_{13}$ & 145 & 162 (11.7\%) & 180 (24.1\%) & 98 (-32.4\%) & \\
-\color{blue} $c_{23}$ & 131 & 145 (10.7\%) & 210 (60.3\%) & 107 (-18.3\%) & \\
-$c_{22}$ & 402 & 360 (-10.4\%) & 457 (13.7\%) & 98 (-75.6\%) & \\
-\color{blue} $c_{33}$ & 402 & 408 (-1.5\%) & 412 (2.5\%) & 295 (-26.6\%) & \\
-\color{blue} $c_{66}$ & 94 & 84 (-10.5\%) & 27 (-71.3\%) & 36 (-61.7\%) & \\
-$B_{\mathrm{VRH}}$ & 230 & 243 (5.7\%) & 280 (21.7\%) & 156 (-32.2\%) &  \\
-$G_{\mathrm{VRH}}$ & 89 & 100 (12.4\%) & 66 (-25.8\%) & 61 (-31.5\%) & \\
-$\mu$ & 0.33 & 0.32 (-3.0\%) & 0.39 (18.2\%) & 0.33 (0.0\%) & \\
+$c_{11}$           & 385  & 420 (9.1\%)   & 195 (-49.4\%) & 403 (4.7\%)   & 374 (-2.9\%)  \\
+$c_{12}$           & 166  & 197 (18.7\%)  & 98 (-41.0\%)  & 208 (25.3\%)  & 160 (-3.6\%)  \\
+$c_{13}$           & 145  & 162 (11.7\%)  & 98 (-32.4\%)  & 230 (58.6\%)  & 176 (21.4\%)  \\
+$c_{22}$           & 402  & 360 (10.7\%)  & 351 (-12.7\%) & 443 (10.2\%)  & 386 (-4.0\%)  \\
+$c_{23}$           & 131  & 145 (-10.4\%) & 107 (13.7\%)  & 272 (107.6\%) & 214 (63.3\%)  \\
+$c_{33}$           & 402  & 408 (-10.4\%) & 295 (13.7\%)  & 474 (17.9\%)  & 398 (-0.5\%)  \\
+$c_{44}$           & 94   & 84 (-10.4\%)  & 36 (13.7\%)   & 25 (-73.4\%)  & 52 (-44.6\%)  \\
+$B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)   & 156 (-32.2\%) & 302 (31.3\%)  & 250 (8.7\%)   \\
+$G_{\mathrm{VRH}}$ & 89   & 100 (12.4\%)  & 61 (-31.5\%)  & 57 (36.0\%)   & 66 (25.8\%)   \\
+$\mu$              & 0.33 & 0.32 (-3.0\%) & 0.33 (0.0\%)  & 0.41 (24.2\%) & 0.38 (15.1\%) \\
 \hline
 Ni$_4$Mo \\
-$c_{11}$ & 300 & 283 (-5.7\%) & 278 (-7.3\%) & 172 (-42.7\%) & \\
-$c_{12}$ & 186 & 179 (-3.8\%) & 184 (-1.1\%) & 158 (-15.1\%) & \\
-$c_{22}$ & 313 & 326 (4.2\%) & 278 (-11.2\%) & 158 (-49.5\%) & \\
-\color{blue} $c_{23}$ & 166 & 164 (-1.2\%) & 230 (38.6\%) & 80 (-51.8\%) & \\
-\color{blue} $c_{66}$ & 130 & 126 (-3.1\%) & 87 (-33.1\%) & 125 (-3.8\%) & \\
-$B_{\mathrm{VRH}}$ & 223 & 220 (-1.3\%) & 233 (10.5\%) & 161 (-27.8\%) & \\
-$G_{\mathrm{VRH}}$ & 91 & 95 (4.4\%) & 57 (37.4\%) & -156 (-162\%) & \\
-$\mu$ & 0.33 & 0.31 (-6.1\%) & 0.39 (18.2\%) & 0.70 (112\%) & \\
+$c_{11}$           & 300  & 283 (-5.7\%)  & 172 (-42.7\%) & 282 (-6.0\%)  & 342 (14.0\%)  \\
+$c_{12}$           & 186  & 179 (-3.8\%)  & 158 (-15.1\%) & 125 (-32.8\%) & 217 (16.7\%)  \\
+$c_{22}$           & 313  & 326 (4.2\%)   & 158 (-49.5\%) & 282 (-10.0\%) & 342 (9.3\%)   \\
+$c_{23}$           & 166  & 164 (-1.2\%)  & 80 (-51.8\%)  & 156 (-6.0\%)  & 232 (39.8\%)  \\
+$c_{44}$           & 130  & 126 (-3.1\%)  & 125 (-3.8\%)  & 136 (4.6\%)   & 117 (-10.0\%) \\
+$B_{\mathrm{VRH}}$ & 223  & 220 (-1.3\%)  & 161 (-27.8\%) & 178 (-20.1\%) & 257 (15.2\%)  \\
+$G_{\mathrm{VRH}}$ & 91   & 95 (4.4\%)    & -156 (-162\%) & 80 (-12.1\%)  & 79 (-13.2\%)  \\
+$\mu$              & 0.33 & 0.31 (-6.1\%) & 0.70 (112\%)  & 0.31 (-6.1\%) & 0.36 (9.1\%)  \\
 \hline

### 2019-10-18 doc/papers/ml-eam/manuscript.tex
The ML-EAM manuscript is updated. The first version is finally finished.

@@
 contribute to the total loss. In this work, $\tau$ is set to 2 GPa.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Ni - EAM - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}
+\centering
+\includegraphics[scale=0.57]{figures/Ni_eam.png}
+\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
+Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni - Material Properties
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}
+\centering
+\begin{tabular}{lccccc}
+\hline
+                              & DFT  & SNAP          & EAM            & ML-EAM         & Exp.      \\
+\hline
+$T_{m}$(K)                    &      & 1785          & 1520           & 1520           & 1728      \\
+$c_{11}$ (GPa)                & 276  & 276 (0.0\%)   & 248 (-10.1\%)  & 274 (-0.7\%)   & 261       \\
+$c_{12}$ (GPa)                & 159  & 159 (0.0\%)   & 147 (-7.5\%)   & 163 (2.5\%)    & 151       \\
+$c_{44}$ (GPa)                & 132  & 132 (0.0\%)   & 125 (-5.3\%)   & 131 (-0.8\%)   & 132       \\
+$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)   & 181 (-8.6\%)   & 195 (0.0\%)    & 188       \\
+$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)    & 87 (-8.4\%)    & 93 (-2.1\%)    & 93        \\
+$\mu$                         & 0.29 & 0.29 (0.0\%)  & 0.29 (0.0\%)   & 0.29 (0.0\%)   & 0.29      \\
+$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%)  & 1.71 (17.1\%)  & 1.54–1.80 \\
+$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)  & 2.58 (0.0\%)   & 2.58 (0.0\%)   & 2.77–2.95 \\
+\hline
+\end{tabular}
+\caption{\label{table:Ni_properties} Comparison of the calculated and 
+experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
+point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
+formation energy and migration energy, respectively. SNAP refers to the 
+elementary Ni SNAP model.
+}
+\end{table*}
 
@@
 
-The melting points $T_{m}$ of bcc Mo and fcc Ni were measured with the 
-solid-liquid coexistence approach. For fcc Ni, $30 \times 10 \times 10$ 
-supercells were used and for bcc the supercells were $30 \times 15 \times 15$. 
-The time step was set to 1 fs. The simulation for each temperature was carried 
-out for 300 ps.
-
 The optimized parameters are listed in the appendix.
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{Ni}
-\label{sec:elementary_Ni}
+\subsection{Elementary Ni and Mo}
+\label{sec:elementary}
+
+We first use the two elementary datasets (Ni and Mo) to show our approach. These 
+two datasets has 461 and 284 structures, respectively. 61 and 34 were randomly 
+selected to form the test subsets. In these two experiments, 
+$\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and $\chi_{\mathrm{elastic}}$ were 
+set to 1, 3 and 0.05 respectively. The batch size was fixed to 25.
+
+The original Zjw04 potentials were fitted to experimentally obtained quantities.
+Thus, we use the relative MAE:
+\begin{equation}
+\mathbf{rMAE} = \frac{1}{N}\sum_{i=1}^{N}{
+    | \frac{(E_i - E_i^{dft})}{N_i} - (E_{eq} - E_{eq}^{dft}) |
+}
+\end{equation}
+to measure their performaces. Here $N_i$ is the number of atoms in structure 
+$i$, $E_i$ is the Zjw04 energy of structure $i$ while $E_i^{dft}$ represents its 
+corresponding DFT energy, $E_{eq}$ and $E_{eq}^{dft}$ refers to the equilibrium 
+energy of Zjw04 and DFT, respectively.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: r(Mo-Mo)
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
+\centering
+\includegraphics[scale=0.64]{figures/r_MoMo_hist.png}
+\caption{\label{fig:r_MoMo_hist} The energy-volume curves of the original EAM, 
+SNAP, ML-EAM and DFT for the fcc Ni.}
+\end{figure}
+
+Figure \ref{fig:Mo_eam_adp} compares the $\rho(r)$, $F(\rho)$, $\phi(r)$, 
+$\mu(r)$ and $\omega(r)$ functions. The differences between ML-EAM and ML-ADP 
+$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. Both the angular-dependent 
+dipole $\mu(r)$ and quadrupole $\omega(r)$ quickly descrease to zero at 2.5 \AA. 
+However, the equilibrium spacing between two adjacent Mo atoms is 2.7 \AA. This 
+may explain why ML-ADP does not outperform ML-EAM on this dataset: most 
+$r^{\mathrm{Mo-Mo}}$ are beyond 2.5 \AA (Figure \ref{fig:r_MoMo_hist}).
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}[htp]
+\begin{figure}
 \centering
 \includegraphics[scale=0.65]{figures/Ni_all_eos.png}
-\caption{\label{fig:Ni_eam_eos} The energy-volume curves of the original EAM, 
-SNAP, ML-EAM and DFT for the fcc Ni.}
+\caption{\label{fig:Ni_eos} The energy-volume curves of the original EAM, 
+ML-EAM and DFT for the fcc Ni.}
 \end{figure}
 
-We first use the elementary fcc Ni dataset to show our approach. This dataset 
-has 461 structures in total. 400 were randomly selected to form the training 
-subset. In this experiment, $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and 
-$\chi_{\mathrm{elastic}}$ were set to 1, 3 and 0.05 respectively. The batch size
-was 25. Only the fcc Ni was included in $\Omega$ (Equation \ref{eq:rose_loss} 
-and \ref{eq:cijkl_loss}).
-
-Table \ref{table:elementary_Ni_mae} shows the MAEs of those models. The original 
-EAM model already has an accepetable performace on this fcc dataset. Its energy 
-MAE is 10.6 meV/atom and the force MAE is 0.06 eV/\AA. The MEAM performs 
-slightly worse on this dataset with an energy MAE of 17.6 meV/atom and force MAE
-of 0.08 eV/\AA. Our machine learning approach can further reduce the energy MAE 
-to 4.1 meV/atom and the force MAE to 0.05 eV/\AA, which are much closer to the 
-elementary SNAP Ni model.
-
-Figure \ref{fig:Ni_eam_eos} plots the equation of state curves obtained with the 
-DFT, SNAP, EAM and ML-EAM models. The whole fitting region ranges from 84\% to 
-118\% of the equilibrium volume. The original EAM significantly underestimates 
-the energy at both tensile and compress strains. However, our machine learning 
-approach together with the Rose constraint can fix this problem. The 
-energy-volume curve of ML-EAM overalps with the DFT curve very well for the 
-entire fitting region.
-
-Table \ref{table:elementary_Ni} summerizes the predicted material properties of 
-fcc Ni, including the melting point, the elastic constants, the vacancy 
-formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
-$E_{a}$. The original EAM already performs well on these properties. ML-EAM 
-further improves the elastic constants. The errors were significantly reduced 
-to around 1-2\%.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Ni - MAE
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table}[h]
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Mo - EOS
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
 \centering
-\begin{tabular}{lcccc}
-\hline
- MAE & SNAP & EAM & MEAM & ML-EAM \\
-\hline
-Energy (meV/atom) & 1.2 & 10.6 & 17.8 & 4.1 \\
-Force (eV/\AA) & 0.05 & 0.06 & 0.08 & 0.05 \\
-\hline
-\end{tabular}
-\caption{\label{table:elementary_Ni_mae} Comparion of the energy and force 
-accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
-ML-EAM.
-}
-\end{table}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Ni - Material Properties
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table*}[htp]
+\includegraphics[scale=0.65]{figures/Mo_all_eos.png}
+\caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
+ML-EAM and DFT for the fcc Ni.}
+\end{figure}
+
+For the Ni dataset, the original Zjw04 already has a reasonable performace. 
+The energy \textbf{rMAE} is 10.6 meV/atom and the force MAE is just 0.06 eV/\AA 
+on the entire dataset. Our machine learning approach can further enhance the 
+performace. ML-EAM achieves 4.1 meV/atom and 0.05 eV/\AA on the test set and 
+3.9 meV/atom and 0.05 eV\AA on the entire dataset. ML-EAM is nearly as accurate 
+as SNAP (1.2 meV/atom, 0.05 eV\AA), but later has around three orders of 
+magnitude more computational expense. Figure \ref{fig:Ni_eam} demonstrates the 
+$\rho(r)$, $F(\rho)$ and $\phi(r)$ functions before (Zjw04) and after machine 
+learning optimization. The pairwise potential $\phi(r)$ almost remains the same 
+while the embedding function $F(\rho)$ and the electron density function 
+$\rho(r)$ changes significantly. Both $\rho(r)$ and $\phi(r)$ converge to zero 
+at around $r=4.8$ \AA, which is rougly 2 times of the equilibrium spacing 
+between nearest neighbors.
+
+For the Mo dataset, the situation is quite different. The original Zjw04 has 
+extremely large MAEs: the energy \textbf{rMAE} is $\sim 98$ meV/atom and the 
+force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
+error: ML-EAM can achieve test MAEs of 21.9 meV/atom and 0.28 eV/\AA and overall
+MAEs of 28.1 meV/atom and 0.32 eV/\AA. We also optimized an ADP potential for 
+this dataset. Interestingly, ML-ADP achieves almost exactly the same MAEs with 
+ML-EAM: 22.1 meV/atom and 0.27 eV\AA on the test set and 27.9 meV/atom and 0.33 
+eV/\AA on the entire dataset. On the contrast, the SNAP method (13.2 meV/atom, 
+0.25 eV/\AA) behaves better. But considering the computational cost, the 
+optimized EAM and ADP are totally accepetable.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Mo - Material Properties
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}
 \centering
@@
 \hline
-    & DFT & SNAP & EAM & MEAM & ML-EAM & Exp. \\
-\hline
-$T_{m}$(K) & & 1785 & 1520 & 1765 & 1520 & 1728 \\
-$c_{11}$ (GPa) & 276 & 276 (0.0\%) & 248 (-10.1\%) & 260 (-5.8\%) & 274 (-0.7\%) & 261 \\
-$c_{12}$ (GPa) & 159 & 159 (0.0\%) & 147 (-7.5\%) & 151 (0.0\%) & 163 (2.5\%) & 151 \\
-$c_{44}$ (GPa) & 132 & 132 (0.0\%) & 125 (-5.3\%) & 131 (0.0\%) & 131 (-0.8\%) & 132 \\
-$E_{v}$ (eV) & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & 1.54–1.80 \\
-$E_{m}$ (eV) & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%) & 2.58 (0.0\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 2.77–2.95 \\
+                              & DFT  & SNAP          & EAM           & ML-EAM         & ML-ADP         & Exp. \\
+\hline
+$T_{m}$(K)                    &      & 3000          & 3750          & 2940           & 2880           & 2890 \\
+$c_{11}$ (GPa)                & 472  & 473 (0.2\%)   & 457 (-3.2\%)  & 472 (0.0\%)    & 473 (0.2\%)    & 479  \\
+$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)  & 168 (6.3\%)   & 158 (0.0\%)    & 160 (1.2\%)    & 165  \\
+$c_{44}$ (GPa)                & 106  & 107 (0.9\%)   & 116 (9.4\%)   & 106 (0.0\%)    & 105 (-0.9\%)   & 108  \\
+$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)  & 264 (0.4\%)   & 262 (-0.4\%)   & 264 (0.4\%)    & 270  \\
+$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)   & 127 (2.4\%)   & 125 (0.8\%)    & 124 (0.0\%)    & 125  \\
+$\mu$                         & 0.30 & 0.29 (-3.3\%) & 0.29 (-3.3\%) & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30 \\
+$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%) & 3.02 (5.2\%)  & 1.16 (-20.5\%) & 1.71 (17.1\%)  &      \\
+$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%) & 1.54 (37.5\%) & 1.46 (30.5\%)  & 0.87 (-22.3\%) &      \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \\
 \hline
 \end{tabular}
-\caption{\label{table:elementary_Ni} Comparison of the calculated and 
-experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
-point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
-formation energy and migration energy, respectively. SNAP refers to the 
-elementary Ni SNAP model.
+\caption{\label{table:Mo_properties} Comparison of the calculated and 
+experimental material properties of elementary bcc Mo. SNAP refers to the 
+elementary Mo SNAP model.
 }
@@
 
-Figure \ref{fig:Ni_eam} compares the $rho(r)$, $F(\rho)$ and $\phi(r)$ functions
-of ML-EAM with original Zjw04 EAM. The pairwise potential $\phi(r)$ almost 
-remains the same while the embedding function $F(\rho)$ and the electron density 
-function $\rho(r)$ changes significantly. Both $\rho(r)$ and $\phi(r)$ converge
-to zero at around $r=4.8$ \AA, which is rougly 2 times of the equilibrium 
-spacing between nearest neighbors.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: Ni - EAM - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure*}[htp]
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Alloy EOS - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}
 \centering
-\includegraphics[scale=0.57]{figures/Ni_eam.png}
-\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
-Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\includegraphics[scale=0.5]{figures/alloy_eos.png}
+\caption{\label{fig:alloy_eos} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
+Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
+ML-ADP.}
 \end{figure*}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Section 3.B
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\subsection{Mo}
-\label{sec:elementary_Mo}
-
-The second test example is bcc Mo. This dataset has 284 structures. 34 of 
-them were used as the testing subset and the rest were used for training. 
-The training settings were the same with fcc Ni. An ADP potential was also 
-optimized for bcc Mo.
-
-Table \ref{table:elementary_Mo_mae} summerizes the energy and force MAEs on the 
-test subset. The original Zjw04 EAM performs significantly worse. The energy
+Figure \ref{fig:Ni_eos} and \ref{fig:Mo_eos} plot the equation of state 
+curves. The fitting region ranges from 84\% to 118\% of the corresponding 
+equilibrium volume. For both crystals, the original EAM significantly 
+underestimate the energy at both tensile and compress strains. However, our 
+constrained machine learning approach can fix this problem. The 
+energy-volume curves of ML-EAM and ML-ADP overalp with the DFT curves very well.
 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure*}[htp]
+\begin{figure}[htp]
 \centering
@@
 ML-ADP.}
-\end{figure*}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Mo - MAE
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table}[h]
-\centering
-\begin{tabular}{lcccc}
-\hline
- MAE   & SNAP & EAM & ML-EAM & ML-ADP \\
-\hline
-Energy (meV/atom) & 13.2 & 58.9 & 21.7 & 22.8 \\
-Force (eV/\AA) & 0.25 & 0.31 & 0.28 & 0.27 \\
-\hline
-\end{tabular}
-\caption{\label{table:elementary_Mo_mae} Comparion of the energy and force 
-accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
-ML-EAM.
-}
-\end{table}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Mo - Material Properties
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table*}[htp]
-\centering
-\begin{tabular}{lcccccc}
-\hline
-    & DFT & SNAP & EAM & ML-EAM & ML-ADP & Exp. \\
-\hline
-$T_{m}$(K) & & 3000 & 3750 & 2940 & 2880 & 2890 \\
-$c_{11}$ (GPa) & 472 & 473 (0.2\%) & 456 (-3.4\%) & 260 (-5.8\%) & 274 (-0.7\%) & 479 \\
-$c_{12}$ (GPa) & 158 & 152 (-3.8\%) & 167 (5.7\%) & 151 (0.0\%) & 163 (2.5\%) & 165 \\
-$c_{44}$ (GPa) & 106 & 107 (0.9\%) & 115 (8.5\%) & 131 (0.0\%) & 131 (-0.8\%) & 108 \\
-$E_{v}$ (eV) & 2.87 & 2.61 (-9.1\%) & 3.02 (5.2\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & \\
-$E_{m}$ (eV) & 1.12 & 1.39 (24.1\%) & 1.54 (37.5\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 4.00 \\
-\hline
-\end{tabular}
-\caption{\label{table:elementary_Mo} Comparison of the calculated and 
-experimental material properties of elementary bcc Mo. SNAP refers to the 
-elementary Mo SNAP model.
-}
-\end{table*}
+\end{figure}
+
+Table \ref{table:Ni_properties} and \ref{table:Mo_properties} summerize the 
+predicted material properties of fcc Ni and bcc Mo, including the melting point 
+$T_{m}$, the elastic constants ($c_{11}$, $c_{12}$ and $c_{44}$), the vacancy 
+formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
+$E_{a}$. The original Zjw04 potentials were developed by fitting material 
+properties so they already perform well on these metrics. Our ML-EAM and ML-ADP 
+not only inherit this feature but also gain significant improvement on 
+predicting elastic constants: the relative errors of the elastic constants as 
+well as the Voigt-Reuss-Hill bulk modulus, shear modulus and homogeneous 
+Poisson's ratio, for both bcc Mo and fcc Ni, are reduced from $\sim$10\% to 
+0-2\%.
+
+We further examined our ML-EAM and ML-ADP by calculating the melting temperature
+of fcc Ni and bcc Mo using the solid-liquid coexistence approach. For fcc Ni, 
+$30 \times 10 \times 10$ supercells were used and for bcc the supercells were 
+$30 \times 15 \times 15$. The time step was set to 1 fs. The simulation for each 
+temperature was carried out for at least 300 ps. For fcc Ni, $T_{m}$ remains the 
+same for ML-EAM, 200 K lower than the experiment $T_m$. However, the calculated 
+$T_{m}$ of Mo is greatly improved. The original Zjw04 $T_{m}$ is around 3750 K, 
+800 K higher than experiment (2890 K). Both ML-EAM and ML-ADP can give very 
+accurate melting temperature.
 
@@
 
-\begin{table*}[h]
+Secondly, we tested our method on the entire binary Mo-Ni dataset. 300 
+structures were randomly splitted to form the test dataset and the rest 3673 
+were used to train the potentials. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ 
+and $\chi_{\mathrm{elastic}}$ were set to 1, 1 and 0.05 respectively. The batch 
+size was increased to 50. Only the equilibrium fcc Ni and bcc Mo are included in 
+$\Omega$ of Equation \ref{eq:cijkl_loss} and \ref{eq:rose_loss}.
+
+The original EAM uses a simplified interpolation form to describe the pairwise 
+interaction of A-B (Equation \ref{eq:zjw04_phi_ab}). However, we did a minor 
+modification: by adding more fitting parameters we use Equation 
+\ref{eq:zjw04_phi_aa} directly. Thus, in total, there are 44 learnable 
+parameters for ML-EAM and 68 for ML-ADP. One should note that in this section, 
+SNAP, ML-EAM and ML-ADP all refer to their corresponding binary form.
+
+Table \ref{table:MAE} summarizes the energy and force MAEs of SNAP, ML-EAM and 
+ML-ADP on the different subsets. Amazingly, ML-ADP becomes the overally best. 
+Both the energy MAE (19.6 meV/atom) and the force MAE (0.20 eV/\AA) are smaller 
+than those of the binary SNAP (22.5 meV/atom and 0.23 eV/\AA). 
+The pure Mo is still a challenge for ML-ADP as the energy and force MAEs are 
+noticeably large (still much smaller than the original Zjw04 EAM). The binary 
+SNAP predicts well on pure Ni and Mo. But ML-ADP outperforms the SNAP model on 
+binary phases (Ni$_3$Mo, Ni-doped Mo and especially the Mo-doped Ni).
+On the contrast, ML-EAM performs significantly worse compared with ML-ADP. 
+Interestingly, our results suggest that Mo-Ni dipole and quadrupole interactions 
+are completely negligible (Figure S1 in the appendix). The Ni-Ni dipole and 
+quadrupole interactions are an order of magnitude weaken than those of Mo-Mo.
+
+Figure \ref{fig:alloy_eos} demonstrates the energy-volume curves of Ni$_3$Mo and
+Ni$_4$Mo. The original Zjw04 EAM can not properly describe the energy-volume 
+relations of these two crystals. The ML-ADP curves fit perfectly with the DFT 
+curves. ML-EAM fits well with tensile strains but overestimates the energy under 
+compress strains.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Mo-Ni MAE
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}
 \centering
@@
 Energy (meV/atom) & SNAP   & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
-                  & EAM    & 58.9 & 211.2    & 255.6    & 46.5               & 147.6              & 10.6 & 117.2   \\
                   & ML-EAM & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
@@
 Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
-                  & EAM    & 0.40 & 0.20     & 0.19     & 0.21               & 0.57               & 0.06 & 0.26    \\
                   & ML-EAM & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
@@
 
-\begin{table*}[h]
+Table \ref{table:NiMo_elastic_constants} summarizes the elastic constants 
+predictions of Ni$_3$Mo and Ni$_4$Mo. One should note that these two crystals 
+were not included in $\Omega$ of Equation \ref{eq:cijkl_loss} and 
+\ref{eq:rose_loss} but their elastic properties were used to tune the binary 
+SNAP model. The original Zjw04 EAM performs obviously poorly on predicting 
+elastic constants. Some absolute percentage errors can even exceed 100\%. With 
+our machine learning correction, ML-EAM, especially ML-ADP, can give much more  
+accurate predictions. For the Ni$_3$Mo crystal, the average absolute percentage 
+error is reduced from 40\% (Zjw04) to 20\% (ML-ADP). ML-ADP even beats SNAP on 4 
+($c_{11}$, $c_{12}$, $c_{22}$ and $c_{3}$) of the 7 elastic metrics. For the 
+Ni$_4$Mo crystal, the average absolute percentage error is also descreased.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Mo-Ni Elastic Constants
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}
 \centering
@@
 $c_{22}$           & 402  & 360 (10.7\%)  & 351 (-12.7\%) & 443 (10.2\%)  & 386 (-4.0\%)  \\
-$c_{23}$           & 131  & 145 (-10.4\%) & 107 (13.7\%)  & 272 (107.6\%) & 214 (63.3\%)  \\
-$c_{33}$           & 402  & 408 (-10.4\%) & 295 (13.7\%)  & 474 (17.9\%)  & 398 (-0.5\%)  \\
-$c_{44}$           & 94   & 84 (-10.4\%)  & 36 (13.7\%)   & 25 (-73.4\%)  & 52 (-44.6\%)  \\
+$c_{23}$           & 131  & 145 (-10.4\%) & 107 (-18.3\%) & 272 (107.6\%) & 214 (63.3\%)  \\
+$c_{33}$           & 402  & 408 (1.5\%)   & 295 (-26.6\%) & 474 (17.9\%)  & 398 (-0.5\%)  \\
+$c_{44}$           & 94   & 84 (-10.4\%)  & 36 (-61.7\%)  & 25 (-73.4\%)  & 52 (-44.6\%)  \\
 $B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)   & 156 (-32.2\%) & 302 (31.3\%)  & 250 (8.7\%)   \\
@@
 constraints, for the fcc and bcc solids, the traditional empirical potentials, 
-EAM/ADP, can be improved to be as accurate as the SNAP method. However, 
-EAM/ADP are around $10^2$ to $10^3$ times faster than SNAP.
-
-The many-body expansion (MBE) is one of the most widely used schemes for fitting 
-potential energy surfaces. In the many-body expansion scheme, the total energy 
-of a system with N atoms can be expressed as the sum of all k-body terms where 
-$k \le 1$:
+EAM/ADP, can be improved to be almost as accurate as the SNAP method. But, 
+EAM/ADP are around $10^2$ to $10^3$ times faster than SNAP. To understand this,
+we can start from the many-body expansion (MBE) scheme.
+
+MBE is one of the most widely used schemes for fitting potential energy 
+surfaces. In the many-body expansion scheme, the total energy of a system with N 
+atoms can be expressed as the sum of all k-body terms where $k \le 1$:
 \begin{equation}
@@
 
-In fact, the EAM formalism can be considered as a variant of MBE truncated at 
-$k=2$ (Equation \ref{eq:eam_total_energy}). The embedding contribution $F(\rho)$ 
-serves as the one-body term. The pairwise contribution 
+In fact, both the EAM and the SNAP formalisms can be considered as variants of 
+MBE truncated at $k=2$. For the EAM method, the embedding contribution $F(\rho)$ 
+serves as the one-body term and the overall pairwise contribution 
 $\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
-two-body term in Equation \ref{eq:MBE_atomic}. The ADP formalism uses a much 
-more complicated two-body term by introducing the pairwise dipole and quadrupole 
-terms.
-
-Although the SNAP method is quite complicated, the current formalism can still 
-be viewed as a variant of MBE truncated at $k=2$. The atomic energy
+two-body term in Equation \ref{eq:MBE_atomic}. The ADP formalism, which 
+introduces extra pairwise dipole and quadrupole interactions, does not change
+this nature. For the SNAP method, the atomic energy is calculated with the 
+following equation: 
+\begin{equation}
+\label{eq:snap_formalism}
+E_i = \beta_{0}^{\alpha_{i}} + \sum_{k}{\beta_{k}^{\alpha_{i}}B_{k}^i}
+\end{equation} 
+where $\beta_{0}^{\alpha_i}$ and $\beta_{k}^{\alpha_i}$ are learnable scalar
+parameters, $\alpha_i$ indicates the element type of atom $i$. $B_{k}^{i}$ is a 
+bispectrum coefficient. The calculation of $B_{k}^{i}$ is very complicated but 
+it is still a two-body term. The overall two-body contribution is a linear 
+combination of $B_{k}^{i}$. Thus, the SNAP formalism can be viewed as an 
+assemble of a simplified one-body term with a complicated two-body term. On the 
+other hand, the EAM formalism is built up with a 'complicated' one-body term and 
+a rather simple two-body term. Hence, for the fcc and bcc systems, both methods 
+perform similarly.
+
+As we analysed in Section \ref{sec:transformation}, the fundamental atomic 
+descriptor of EAM, the $N \times N^{\mathrm{nl}} \times 4$ matrix $\mathbf{G}$, 
+is composed of just raw interatomic distances. However, interatomic distances
+alone may not uniquely describe a structure. To avoid this problem, the cutoff 
+was raised up to 6.5 \AA. As a comparison, the overall $r_{cut}$ is 4.6 \AA for 
+the binary SNAP. But such descriptor is still too rough to describe complicated 
+potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, perhaps we 
+shall consider adding real three-body terms (e.g. Tersoff).
 
@@
 
+To conclude, we have successfully combined empirical potentials (EAM/ADP) with 
+machine learning. The machine learning approaches (big data, SGD, etc), together 
+with physical constraints (Rose EOS, elastic constants) can significantly boost
+the performaces of EAM/ADP. For the fcc Ni, bcc Mo and Mo-Ni alloys, ML-EAM and
+ML-ADP can be as accurate as SNAP, while later method is orders of magnitude 
+slower. Our work also indicates a new route to design and develop machine 
+learning interatomic potentials \textemdash the machine learning enhanced 
+empirical potential approach.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 
+This work was supported by the National Key Research and Development Program of 
+China under Grant No. 2016YFB0201204, the Science Challenge Project under Grant 
+No. TZ2018002 and the National Natural Science Foundation of China under Grant 
+No. U1630250.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2019-10-22 doc/papers/ml-eam/manuscript.tex
The manuscript is updated. References are also added.

@@
         Li-Fang Wang, 
+        Xing-Yu Gao,
+        Ya-Fan Zhao,
         De-Ye Lin$^\mathrm{*}$, 
+        Wei-Dong Chu,
         Hai-Feng Song$^\mathrm{*}$}
@@
 \begin{abstract}
+Interatomic potential or force-field plays a vital role in simulating materials. 
+Embedded atom method (EAM) and its variant angular-dependent potential (ADP) 
+have proven successful in modeling fcc and bcc metals qualitatively. In the past 
+few years, machine learning has became the central approach for modeling 
+interatomic interactions. Powered by big data and efficient optimizers, machine 
+learning interatomic potentials can generally approximate first-principle 
+accuracy. In this works, we successfully integrated machine learning with EAM 
+and ADP. Machine learning can significantly boost their performances. 
+For energy and force predictions, machine leaned EAM and ADP can be almost 
+as accurate as the spectral neighbor analysis potential (SNAP) on the fcc Ni, 
+bcc Mo and Mo-Ni alloy systems, while the later approach is nealy 1000 times 
+slower. ML-EAM and ML-ADP can also give first-principle accuracy key material 
+properties, such as elastic constants, melting temperatures. Our results suggest 
+a new and systematic route for developing machine learning interatomic 
+potentials. 
+Our 
 \end{abstract}
@@
 computation expenses. Physical model based empirical potential (force-field), 
-such as the embedded-atom method (EAM), modified embedded-atom method (MEAM), 
-bond-order potential (BoP), or angular-dependent potential (ADP), still plays 
-the major role in long-time simulations and these empirical methods can achieve 
-reasonable accuracy with much lower computation costs. Empirical potentials 
+such as the embedded-atom method (EAM) \cite{EAM0,EAM1,EAM2,EAM3,EAM4}, 
+modified embedded-atom method (MEAM) \cite{MEAM0,MEAM1,MEAM2,MEAM_Jelinek}, 
+bond-order potential (BoP) \cite{BOP0,BOP1,BOP2,BOP3}, or angular-dependent 
+potential (ADP) \cite{ADP0,ADP1,ADP2,ADP3,ADP_FeNi}, still plays the major role 
+in long-time simulations and these empirical methods can achieve reasonable 
+accuracy with much lower computation costs. Empirical potentials 
 generally have very few learnable parameters and both microscopic observables 
@@
 optimal parameters of empirical potentials is always a challenging task. Global 
-optimization (GO) approaches (Basin-Hopping, genetic algorithm, etc) are 
-traditionally used to find the best possible parameters. However, the gradients 
-of the losses with respect to model parameters are difficult or even impossible 
-to calcualte. Hence, GO optimizations are generally not that effective.
+optimization (GO) approaches (Basin-Hopping \cite{BH0,BH1}, genetic algorithm 
+\cite{PCIPY,PGA}, etc) are traditionally used to find the best possible 
+parameters. However, the gradients of the losses with respect to model 
+parameters are difficult or even impossible to calcualte. Hence, 
+GO optimizations are generally not that effective.
 
@@
 based atomistic neural network (ANN) model, published by Parinello and Behler in 
-2007, is still the most popular choice in modeling metallic interactions. 
+2007 \cite{SF2007,SF1,SF2,SF3,SF4}, is still the most popular choice in modeling 
+metallic interactions \cite{SFApp0,SFApp1,SFApp2}. 
 The smooth overlap atomic positions descriptor based gaussian approximation 
-potential (SOAP-GAP), developed by Bartòk et al, can give extremely accurate 
-prediction results, although it's a bit computationally expensive. 
+potential (SOAP-GAP) \cite{soap0,soap1,soap2,soap3}, developed by Bartòk et al, 
+can give extremely accurate prediction results, although it's a bit 
+computationally expensive. 
 Recently, Thompson and co-workers proposed another quantum-accurate MLIP named 
-the spectral neighbor analysis potential (SNAP) and it has been proven working  
-on a broad range of metals and alloys.
+the spectral neighbor analysis potential (SNAP) \cite{SNAP_Algo} and it has 
+been proven working on a broad range of metals and 
+alloys \cite{SNAP_Mo,SNAP,SNAP_New}.
 
@@
 \textit{basic} or \textit{simple} arithmetic operations. Thus, MILPs can be 
-implemented within modern deep learning frameworks (TensorFlow, PyTorch, etc) 
+implemented within modern deep learning frameworks 
+(TensorFlow \cite{tensorflow}, PyTorch \cite{pytorch}, etc) 
 so that the gradients of the total loss with respect to fitting parameters can 
@@
 molecular dynamics (MD) simulations of large-scale ($10^5$ or more) systems, 
-computation efficiency also becomes a major concern. Recent benchmark tests 
-suggest that MILPs are still too expensive. At present, most MLIPs are used to 
-examine small to medium ($10^3$ to $10^4$) systems.
+computation efficiency also becomes a major concern. Recent benchmark 
+tests \cite{SnapBenchmark} suggest that MILPs are still too expensive. 
+At present, most MLIPs are used to examine small to medium ($10^3$ to $10^4$) 
+systems \cite{SNAP,SFApp0,SFApp1,SFApp2,soap3}.
 
@@
 theoretical background of this work, including the formalism of the embedded 
-atom method and algorithms and details of the machine learned EAM. 
-Section \ref{sec:results} summarizes the training results and the optimal 
-parameters. Applications of the new potentials are discussed in 
-Section \ref{sec:discussions}.
+atom method and algorithms of the machine learned EAM. Section \ref{sec:results} 
+summarizes the results of ML-EAM and ML-ADP. Further discussions are given in 
+section \ref{sec:discussions}.
 
@@
 
-In the original EAM formalism, the total energy, $E^{total}$, is the sum of 
-atomic energies:
+In the original EAM formalism \cite{EAM0}, the total energy, $E^{total}$, is the 
+sum of atomic energies:
 \begin{align}
@@
 \end{equation}
-where $\rho_{b}$ is the electron density function of specie $b$. In the 
-Finnis-Sinclair model, the electron density has a slightly modified form:
-\begin{equation}
-\label{eq:rho_fs}
-\rho_{i}^{\mathrm{FS}} = \sum_{j}^{r_{ij} < r_{c}}{
-    \rho_{ab}(r_{ij})
-}
-\end{equation}
+where $\rho_{b}$ is the electron density function of specie $b$. 
 $F$, $\rho$ and $\phi$ can be either parameterized functions or cubic splines.
 
-The original EAM formalism does not inlcude angular-dependent interactions. To 
+The original EAM does not inlcude angular-dependent interactions. To 
 fix this problem, Baskes modified the original EAM and got MEAM (modified 
-embedded-atom method), Lenosky proposed an alternative spline-based interpretion 
-of MEAM  while Mishin developed the angular-dependent potential (ADP). The ADP 
+embedded-atom method) \cite{MEAM0}, Lenosky proposed an alternative spline-based 
+interpretion of MEAM \cite{MEAM_Lenosky} while Mishin developed the 
+angular-dependent potential (ADP) \cite{ADP0,ADP1,ADP2,ADP3,ADP4}. The ADP 
 formalism introduces three additional terms to the total energy:
@@
 In this work, we use the EAM potential published by Zhou, Johnson and Wadley 
-(Zjw04) as an example to validate our machine learning approach. Zjw04 is a 
-quite popular EAM potential. In the Zjw04 potential, the electron density 
-function has the following form:
+(Zjw04) \cite{ZJW0,ZJW1,ZJW2} as an example to validate our machine learning 
+approach. Zjw04 is a quite popular EAM potential. In the Zjw04 potential, the 
+electron density function has the following form:
 \begin{equation}
@@
 The dipole ($\mu_{ab}$) and quadrupole ($\lambda_{ab}$) functions have the same 
-form (developed by Mishin):
+form (developed by Mishin \cite{ADP0}):
 \begin{align}
@@
 In this work, we successfully integrated two constraints into the total loss:
-the Rose equation of state (EOS) constraint and the elastic tensor constraint. 
-These two losses will be discussed later. The details of their implementations 
-will be described in another paper.
+the Rose equation of state (EOS) \cite{Rose0,Rose1,Rose2} constraint and the 
+elastic tensor constraint. These two losses will be discussed later. The details 
+of their implementations will be described in another paper.
 
@@
 constraint. Given an equilibrium crystal structure, its elastic constant 
-$c_{ijkl}$ can be derived from $E^{total}$ directly:
+$c_{ijkl}$ can be derived from $E^{total}$ directly \cite{Elastic}:
 \begin{align}
@@
 \hline
-                              & DFT  & SNAP          & EAM            & ML-EAM         & Exp.      \\
-\hline
-$T_{m}$(K)                    &      & 1785          & 1520           & 1520           & 1728      \\
-$c_{11}$ (GPa)                & 276  & 276 (0.0\%)   & 248 (-10.1\%)  & 274 (-0.7\%)   & 261       \\
-$c_{12}$ (GPa)                & 159  & 159 (0.0\%)   & 147 (-7.5\%)   & 163 (2.5\%)    & 151       \\
-$c_{44}$ (GPa)                & 132  & 132 (0.0\%)   & 125 (-5.3\%)   & 131 (-0.8\%)   & 132       \\
+                              & DFT  & SNAP \cite{SNAP} & EAM              & ML-EAM         & Exp.                           \\
+\hline
+$T_{m}$(K)                    &      & 1785             & 1520 \cite{ZJW2} & 1520           & 1728                           \\
+$c_{11}$ (GPa)                & 276  & 276 (0.0\%)      & 248 (-10.1\%)    & 274 (-0.7\%)   & 261 \cite{Ni_Elastic_Exp}      \\
+$c_{12}$ (GPa)                & 159  & 159 (0.0\%)      & 147 (-7.5\%)     & 163 (2.5\%)    & 151 \cite{Ni_Elastic_Exp}      \\
+$c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
 $B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (0.0\%)    & 188                            \\
@@
 $\mu$                         & 0.29 & 0.29 (0.0\%)     & 0.29 (0.0\%)     & 0.29 (0.0\%)   & 0.29                           \\
-$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%)  & 1.71 (17.1\%)  & 1.54–1.80 \\
-$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)  & 2.58 (0.0\%)   & 2.58 (0.0\%)   & 2.77–2.95 \\
+$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%)    & 1.68 (15.1\%)    & 1.71 (17.1\%)  & 1.54–1.80 \cite{Ni_EvEmEa_Exp} \\
+$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%)    & 0.90 (-19.6\%)   & 0.87 (-22.3\%) & 1.01–1.48 \cite{Ni_EvEmEa_Exp} \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)     & 2.58 (0.0\%)     & 2.58 (0.0\%)   & 2.77–2.95 \cite{Ni_EvEmEa_Exp} \\
 \hline
@@
 } \nonumber \\
-& + \chi_{\mathrm{s}}\sqrt{\frac{1}{6N_b}\sum_{i}^{N_b}{
-    \sum_{j}^{6}{
-        \left(
-            \epsilon^{\mathrm{voigt}}_{j} - \epsilon^{\mathrm{voigt,dft}}_{j}
-        \right)^2
-    }
-}} \nonumber \\
 & + \chi_{\mathrm{rose}}\mathbf{L}^{\mathrm{Rose}} 
@@
 where $N_{b}$ is the batch size and $N_i$ is the number of atoms in structure 
-$i$. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{s}}$, $\chi_{\mathrm{rose}}$ and 
-$\chi_{\mathrm{elastic}}$ are overall weights of force, virial stress, rose EOS 
-and elastic contributions. The superscript 'voigt' means that virial 
-stress tensors should be converted to Voigt form. The Adam optimizer is used to 
-minimize Equation \ref{eq:loss}. In most cases, we use 0.01 as the initial 
-learning rate and the batch size ranges from 20 to 50. Since there are very few
-adjustable parameters, the optimization typically needs very few epochs to 
-converge. When the optimization is finished, the corresponding Lammps setfl 
-potential file will be exported.
+$i$. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and $\chi_{\mathrm{elastic}}$ 
+are overall weights of force, rose EOS and elastic contributions. 
+The Adam optimizer \cite{adam} is used to minimize Equation \ref{eq:loss}. 
+In most cases, we use 0.01 as the initial learning rate and the batch size 
+ranges from 20 to 50. Since there are very few adjustable parameters, the 
+optimization typically needs very few epochs to converge. When the optimization 
+is finished, the corresponding Lammps setfl potential file will be exported.
 
@@
 
-The publicly Ni-Mo dataset is used to evaluate our approach. This dataset is 
-provided by Shyue Ping Ong. It contains 3973 different Ni-Mo solids. All 
-calculations were done by VASP with the PBE functional and the projector 
-augmented-wave approach.
+The publicly Ni-Mo dataset \cite{SNAP} is used to evaluate our approach. This 
+dataset is provided by Shyue Ping Ong. It contains 3973 different Ni-Mo solids. 
+All calculations were done by VASP \cite{VASP} with the PBE \cite{PBE} 
+functional and the projector augmented-wave approach \cite{PAW}.
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: r(Mo-Mo)
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}
-\centering
-\includegraphics[scale=0.64]{figures/r_MoMo_hist.png}
-\caption{\label{fig:r_MoMo_hist} The energy-volume curves of the original EAM, 
-SNAP, ML-EAM and DFT for the fcc Ni.}
-\end{figure}
-
 Figure \ref{fig:Mo_eam_adp} compares the $\rho(r)$, $F(\rho)$, $\phi(r)$, 
@@
 $\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. Both the angular-dependent 
-dipole $\mu(r)$ and quadrupole $\omega(r)$ quickly descrease to zero at 2.5 \AA. 
-However, the equilibrium spacing between two adjacent Mo atoms is 2.7 \AA. This 
-may explain why ML-ADP does not outperform ML-EAM on this dataset: most 
-$r^{\mathrm{Mo-Mo}}$ are beyond 2.5 \AA (Figure \ref{fig:r_MoMo_hist}).
+dipole $\mu(r)$ and quadrupole $\omega(r)$ quickly descrease to zero at 2.5 \AA, 
+which is lower than the equilibrium spacing (2.7 \AA) between two adjacent Mo 
+atoms. Hence, the dipole and quadrupole terms only contribute a little to the 
+total energy for this test case.
 
@@
 \hline
-                              & DFT  & SNAP          & EAM           & ML-EAM         & ML-ADP         & Exp. \\
+                              & DFT  & SNAP \cite{SNAP_Mo} & EAM \cite{ZJW2} & ML-EAM         & ML-ADP         & Exp.                      \\
 \hline
 $T_{m}$(K)                    &      & 3000                & 3750            & 2940           & 2880           & 2890                      \\
-$c_{11}$ (GPa)                & 472  & 473 (0.2\%)   & 457 (-3.2\%)  & 472 (0.0\%)    & 473 (0.2\%)    & 479  \\
-$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)  & 168 (6.3\%)   & 158 (0.0\%)    & 160 (1.2\%)    & 165  \\
-$c_{44}$ (GPa)                & 106  & 107 (0.9\%)   & 116 (9.4\%)   & 106 (0.0\%)    & 105 (-0.9\%)   & 108  \\
-$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)  & 264 (0.4\%)   & 262 (-0.4\%)   & 264 (0.4\%)    & 270  \\
-$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)   & 127 (2.4\%)   & 125 (0.8\%)    & 124 (0.0\%)    & 125  \\
+$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 472 (0.0\%)    & 473 (0.2\%)    & 479 \cite{Mo_Elastic_Exp} \\
+$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 158 (0.0\%)    & 160 (1.2\%)    & 165 \cite{Mo_Elastic_Exp} \\
+$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 106 (0.0\%)    & 105 (-0.9\%)   & 108 \cite{Mo_Elastic_Exp} \\
+$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 262 (-0.4\%)   & 264 (0.4\%)    & 270 \cite{Mo_Elastic_Exp} \\
+$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 125 (0.8\%)    & 124 (0.0\%)    & 125 \cite{Mo_Elastic_Exp} \\
 $\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
@@
 $E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.46 (30.5\%)  & 0.87 (-22.3\%) &                           \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \cite{Mo_Ea_Exp}     \\
 \hline
@@
 \hline
-Energy (meV/atom) & SNAP   & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
+Energy (meV/atom) & SNAP \cite{SNAP} & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                   & ML-EAM           & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
@@
 \hline
-Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
+Force (eV/\AA)    & SNAP \cite{SNAP} & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                   & ML-EAM           & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
@@
 \hline
-                   & DFT  & SNAP          & EAM           & ML-EAM        & ML-ADP        \\
+                   & DFT  & SNAP \cite{SNAP} & EAM \cite{ZJW2} & ML-EAM        & ML-ADP        \\
 \hline
@@
 EAM/ADP are around $10^2$ to $10^3$ times faster than SNAP. To understand this,
-we can start from the many-body expansion (MBE) scheme.
+we can start from the many-body expansion (MBE) scheme \cite{kCON}.
 

### 2019-10-22 doc/papers/ml-eam/manuscript.tex
Fix some errors in the manuscript.

@@
 \caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
-ML-EAM and DFT for the fcc Ni.}
+ML-EAM and DFT for the bcc Mo.}
 \end{figure}
@@
 $\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
-$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.16 (-20.5\%) & 1.71 (17.1\%)  &                           \\
-$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.46 (30.5\%)  & 0.87 (-22.3\%) &                           \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \cite{Mo_Ea_Exp}     \\
+$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.99 (-30.7\%) & 2.01 (-30.0\%) &                           \\
+$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.27 (13.4\%)  &                           \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.32 (-16.8\%) & 3.28 (-17.8\%) & 4.00 \cite{Mo_Ea_Exp}     \\
 \hline
@@
 experimental material properties of elementary bcc Mo. SNAP refers to the 
-elementary Mo SNAP model.
+elementary SNAP Mo model.
 }
@@
 \includegraphics[scale=0.5]{figures/alloy_eos.png}
-\caption{\label{fig:alloy_eos} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
-Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
-ML-ADP.}
+\caption{\label{fig:alloy_eos} Energy-volume curves of Ni$_3$Mo and Ni$_4$Mo 
+obtained with the original Zjw04 EAM, ML-EAM, ML-ADP and DFT.}
 \end{figure*}
@@
 Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
-relative to the DFT on the entire Mo-Ni dataset.}
+relative to the DFT on the subsets (Mo, Ni$_4$Mo, Ni$_3$Mo, Ni-doped Mo, 
+Mo-doped Ni, Ni) and the entire Mo-Ni dataset.}
 \end{table*}
@@
 ($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
-GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
+GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, bcc Mo and binary 
 alloys Ni$_{3}$Mo and Ni$_{4}$Mo.

### 2019-10-28 doc/papers/nn/manuscript.tex
Slightly improves the manuscript to answer the questions of the last reviewer.

@@
 derivations of forces and virial can be handled by TensorFlow automatically and 
-efficiently. This new approach is implemented in our open-source program 
-TensorAlloy, which supports constructing machine learning interaction potentials 
-for both \textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets 
-are used to demostrate the performances of our program.
+efficiently. The virtual atom approach with AutoGrad within TensorFlow allows 
+for efficient training to not just energies and forces, but also virial stress. 
+This new approach is implemented in our open-source program TensorAlloy, which 
+supports constructing machine learning interaction potentials for both 
+\textit{molecules} and \textit{solids}. The QM7 and SNAP/Ni-Mo datasets are used 
+to demostrate the performances of our program.
 \end{abstract}
@@
 energy with respect to atomic positons (force) or lattice tensor (virial) can be 
-handled by TensorFlow directly and automatically.
+handled by TensorFlow directly and automatically. Hence, the technical barrier 
+of training ANNs with atomic forces and (especially) virial stress becomes 
+completely neglectable.
 
@@
 Mo               & 4.5 (13.2) &           & 0.19 (0.25)   &      & 0.28 (0.87) \\
-Ni & & 1.3 (1.2) & & 0.04 (0.05) & \\
+Ni               &            & 1.3 (1.2) & & 0.04 (0.05) & 2.05               \\
 \hline
@@
 interactions. However, in most cases, the radial-only TensorAlloy-trained 
-models can significantly outperform corresponding SNAP models. The trainings of 
-these models are also very fast. All these models are trained within 2 GPU hours
-on our workstation.
+models can significantly outperform corresponding SNAP models. We can also 
+notice that including virial stress in the total loss function can significantly
+reduce the stress prediction error. The virial stress 
+(Equation \ref{eq:stress}) consists of two parts: the net force contribution 
+$-F^TR$ and the partial force contribution 
+$\left(\partial E / \partial \mathbf{h}\right)^T\mathbf{h}$. The atomic forces 
+used by the total loss equation \ref{eq:loss} are net forces only but virial 
+stress only depends on the partial forces (the force between two atoms). 
+Compared with the binary \textbf{NN}(Mo-Ni) model, the elementary 
+\textbf{NN}(Ni) model has lower net force error (0.04 eV/\AA vs 0.07 eV\AA). 
+However, the elementary model trained with energy and forces only has much 
+larger stress MAE (2.05 GPa vs 0.83 GPa). These results clearly suggest that 
+including virial stress in the total loss function is necessary for obtaining 
+better virial stress accuracy.
 

### 2019-10-29 doc/papers/nn/manuscript.tex
Minor update.
The conclusion section is slightly modified.

@@
 \author[a]{Xing-Yu Gao}
-\author[b]{Ya-Fan Zhao}
-\author[b]{De-Ye Lin\corref{author}}
+\author[b,a]{Ya-Fan Zhao}
+\author[b,a]{De-Ye Lin\corref{author}}
 \author[a]{Wei-Dong Chu}
@@
 \cortext[author] {Corresponding author.
-\\\textit{E-mail address:} lindeye0716@163.com}
+\textit{E-mail address:} lindeye0716@163.com, song\_haifeng@iapcm.ac.cn}
 \address[a]{Institute of Applied Physics and Computational Mathematics, 
@@
 barrier of calculating NN-derived atomic forces and virial stress neglectable. 
-This new algorithm is implemented in our Python program, TensorAlloy.
+Hence, not only energies and forces, but also virial stress, can be used to 
+train atomistic neural networks. Our experiment also suggests that including 
+virial stress in the total loss function can significantly improve the accuracy
+of predicting stress. All the new algorithms are implemented in our open-source
+Python program TensorAlloy.
 

### 2019-12-12 doc/papers/ml-eam/manuscript.tex
The manuscript is updated.

@@
-\documentclass[prb,reprint]{revtex4-2}
+\documentclass[prb,reprint,superscriptaddress]{revtex4-2}
 
@@
 
-\author{Xin Chen, 
-        Li-Fang Wang, 
-        Xing-Yu Gao,
-        Ya-Fan Zhao,
-        De-Ye Lin$^\mathrm{*}$, 
-        Wei-Dong Chu,
-        Hai-Feng Song$^\mathrm{*}$}
-
+\author{Xin Chen}
 \affiliation{
@@
 
+\author{Li-Fang Wang}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\author{Xing-Yu Gao}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\author{Ya-Fan Zhao}
+\affiliation{
+    CAEP Software Center for High Performance Numerical Simulation, 
+    Beijing 100088, China}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\author{De-Ye Lin}
+\email{lindeye0716@163.com}
+\affiliation{
+    CAEP Software Center for High Performance Numerical Simulation, 
+    Beijing 100088, China}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\author{Wei-Dong Chu}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
+
+\author{Hai-Feng Song}
+\email{song_haifeng@iapcm.ac.cn}
+\affiliation{
+    Institute of Applied Physics and Computational Math, 
+    Beijing 100088, China}
 \affiliation{
@@
 \Delta x=0.01$. In this work, $\beta^{\mathrm{Ni}}$ is 0.005 and 
-$\beta^{\mathrm{Mo}}$ is 0.150.
+$\beta^{\mathrm{Mo}}$ is 0.008.
 
@@
 $c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
-$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (0.0\%)    & 188                            \\
+$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (-1.5\%)    & 188                           \\
 $G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)       & 87 (-8.4\%)      & 93 (-2.1\%)    & 93                             \\
@@
 force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
-error: ML-EAM can achieve test MAEs of 21.9 meV/atom and 0.28 eV/\AA and overall
-MAEs of 28.1 meV/atom and 0.32 eV/\AA. We also optimized an ADP potential for 
-this dataset. Interestingly, ML-ADP achieves almost exactly the same MAEs with 
-ML-EAM: 22.1 meV/atom and 0.27 eV\AA on the test set and 27.9 meV/atom and 0.33 
-eV/\AA on the entire dataset. On the contrast, the SNAP method (13.2 meV/atom, 
-0.25 eV/\AA) behaves better. But considering the computational cost, the 
-optimized EAM and ADP are totally accepetable.
+error: ML-EAM can achieve test MAEs of 23.8 meV/atom and 0.26 eV/\AA and overall
+MAEs of 26.7 meV/atom and 0.30 eV/\AA. We also optimized an ADP potential for 
+this dataset. Interestingly, ML-ADP gets better results: 20.6 meV/atom and 
+0.24 eV\AA on the test set and 18.7 meV/atom and 0.29 eV/\AA on the entire 
+dataset. On the contrast, the SNAP method (13.2 meV/atom, 0.25 eV/\AA) behaves 
+slightly better than ML-ADP. But considering the computational cost, the 
+ML-ADP is totally acceptable.
 
@@
 \hline
-$T_{m}$(K)                    &      & 3000                & 3750            & 2940           & 2880           & 2890                      \\
-$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 472 (0.0\%)    & 473 (0.2\%)    & 479 \cite{Mo_Elastic_Exp} \\
-$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 158 (0.0\%)    & 160 (1.2\%)    & 165 \cite{Mo_Elastic_Exp} \\
-$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 106 (0.0\%)    & 105 (-0.9\%)   & 108 \cite{Mo_Elastic_Exp} \\
-$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 262 (-0.4\%)   & 264 (0.4\%)    & 270 \cite{Mo_Elastic_Exp} \\
-$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 125 (0.8\%)    & 124 (0.0\%)    & 125 \cite{Mo_Elastic_Exp} \\
-$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
-$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.99 (-30.7\%) & 2.01 (-30.0\%) &                           \\
-$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.27 (13.4\%)  &                           \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.32 (-16.8\%) & 3.28 (-17.8\%) & 4.00 \cite{Mo_Ea_Exp}     \\
+$T_{m}$(K)                    &      & 3000                & 3750            & 2840           & 2910           & 2890                      \\
+$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 463 (-1.9\%)   & 469 (-0.6\%)   & 479 \cite{Mo_Elastic_Exp} \\
+$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 153 (-3.2\%)   & 159 (0.6\%)    & 165 \cite{Mo_Elastic_Exp} \\
+$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 98 (-7.5\%)    & 102 (-3.8\%)   & 108 \cite{Mo_Elastic_Exp} \\
+$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 256 (-2.7\%)   & 262 (-0.4\%)   & 270 \cite{Mo_Elastic_Exp} \\
+$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 118 (-4.8\%)   & 121 (-2.4\%)   & 125 \cite{Mo_Elastic_Exp} \\
+$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.0\%)   & 0.30 (0.0\%)   & 0.30                      \\
+$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.96 (-31.7\%) & 2.51 (-12.5\%) &                           \\
+$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.06 (-5.3\%)  &                           \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.29 (-17.5\%) & 3.57 (-10.5\%) & 4.00 \cite{Mo_Ea_Exp}     \\
 \hline
@@
 $E_{a}$. The original Zjw04 potentials were developed by fitting material 
-properties so they already perform well on these metrics. Our ML-EAM and ML-ADP 
-not only inherit this feature but also gain significant improvement on 
-predicting elastic constants: the relative errors of the elastic constants as 
-well as the Voigt-Reuss-Hill bulk modulus, shear modulus and homogeneous 
-Poisson's ratio, for both bcc Mo and fcc Ni, are reduced from $\sim$10\% to 
-0-2\%.
+properties so they already perform well on these metrics. For the fcc Ni, the 
+machine-learned EAM has gained better performances on predicting elastic 
+constants. For the bcc Mo, ML-ADP not only gives quality predictions on elastic 
+properties but also significantly reduces the error of predicting $E_m$. We also 
+tested these models with surface energy, as shown in Fig 
+\ref{fig:surface_energy}. One must note that all the slab structures are relaxed 
+independently with corresponding potentials. For the fcc Ni, ML-EAM can give 
+almost exactly the same results with DFT. For the more complicated bcc Mo, the 
+central-force ML-EAM model becomes not that good due to the directional d 
+bonding \cite{ADP0}. The angular correction, introduced by Mishin, shows 
+its importance. ML-ADP can give acceptable results, just like the SNAP method.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Surface Energy - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{figures/surface_energy.png}
+\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
+\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
+\end{figure}
 
@@
 $T_{m}$ of Mo is greatly improved. The original Zjw04 $T_{m}$ is around 3750 K, 
-800 K higher than experiment (2890 K). Both ML-EAM and ML-ADP can give very 
-accurate melting temperature.
+800 K higher than experiment (2890 K) while both ML-EAM and ML-ADP can give 
+quite accurate melting temperature.
 
@@
 $\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
-two-body term in Equation \ref{eq:MBE_atomic}. The ADP formalism, which 
-introduces extra pairwise dipole and quadrupole interactions, does not change
-this nature. For the SNAP method, the atomic energy is calculated with the 
-following equation: 
+two-body term in Equation \ref{eq:MBE_atomic}. For the SNAP method, the atomic 
+energy is calculated with the following equation: 
 \begin{equation}
@@
 other hand, the EAM formalism is built up with a 'complicated' one-body term and 
-a rather simple two-body term. Hence, for the fcc and bcc systems, both methods 
-perform similarly.
+a rather simple two-body term. The central-force EAM works well on fcc metals. 
+For bcc metals with partially filled d bands, the directional d bonding cannot
+be ignored. Hence, the pairwise dipole and quadrupole functions introduced by 
+ADP are necessary.
 
@@
 the binary SNAP. But such descriptor is still too rough to describe complicated 
-potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, perhaps we 
-shall consider adding real three-body terms (e.g. Tersoff).
+potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, complicated
+three--atoms interactions may be necessary.
 

### 2019-12-27 doc/papers/ml-eam/manuscript.tex
The ml-eam paper is updated.

@@
 \title{
-    Machine-learned embedded atom method
+    Machine learning enhanced empirical potentials for metals and alloys
 }
@@
 Interatomic potential or force-field plays a vital role in simulating materials. 
-Embedded atom method (EAM) and its variant angular-dependent potential (ADP) 
-have proven successful in modeling fcc and bcc metals qualitatively. In the past 
-few years, machine learning has became the central approach for modeling 
-interatomic interactions. Powered by big data and efficient optimizers, machine 
-learning interatomic potentials can generally approximate first-principle 
-accuracy. In this works, we successfully integrated machine learning with EAM 
-and ADP. Machine learning can significantly boost their performances. 
-For energy and force predictions, machine leaned EAM and ADP can be almost 
-as accurate as the spectral neighbor analysis potential (SNAP) on the fcc Ni, 
-bcc Mo and Mo-Ni alloy systems, while the later approach is nealy 1000 times 
-slower. ML-EAM and ML-ADP can also give first-principle accuracy key material 
-properties, such as elastic constants, melting temperatures. Our results suggest 
-a new and systematic route for developing machine learning interatomic 
-potentials. 
-Our 
+Empirical potentials like the embedded atom method (EAM) and its variant 
+angular-dependent potential (ADP) have proven successful in modeling many 
+metals qualitatively. In the past few years, machine learning has became the 
+key approach for modeling interatomic interactions. Powered by big data and 
+efficient optimizers, machine learning interatomic potentials can generally 
+approximate to the first-principles accuracy. In this works, we successfully 
+integrated machine learning with EAM and ADP. Machine learning can significantly 
+boost their performances. For energy and force predictions, machine leaned EAM 
+and ADP can be almost as accurate as the spectral neighbor analysis potential 
+(SNAP) on the fcc Ni, bcc Mo and Mo-Ni alloy systems, while the molecular 
+dynamics simulations performed by the later approach is nealy 1000 times 
+slower. Machine learned EAM and ADP can also give first-principle accuracy key 
+material properties, such as elastic constants, melting temperatures and surface 
+energies. Our results suggest a new and systematic route for developing machine 
+learning interatomic potentials. 
 \end{abstract}
@@
 
-To integrate EAM/ADP with machine learning, the original total energy expression 
-(Equation \ref{eq:eam_total_energy}) must be transformed to a vectorizable form. 
-Without loss of generality, we take the binary alloy, AB, to demonstrate how to 
-do the transformation.
+To integrate EAM/ADP with machine learning strategy, the original total energy 
+expression (Equation \ref{eq:eam_total_energy}) must be transformed to a 
+vectorizable form. Without loss of generality, we take the binary alloy, AB, to 
+demonstrate how to do the transformation.
 
@@
 When $r_c$ is fixed, $\niaa$, $\niab$, $\njbb$ and $\njba$ are all constants and
-$\nnli$ is the maximum of these numbers. Finally, we can pre-determine the 
-maximum neighor list size $\nnl$:
+$\nnli$ is the maximum of these numbers of structure $i$. Hence, we can 
+pre-determine the maximum neighor list size $\nnl$:
 \begin{equation}
@@
     \riaa & \riab & \ribb & \riba \\
-\end{bmatrix}
-\end{equation}
-$\mathbf{g}_i$ is a $\nnl \times 4$ matrix. If the specie of atom $i$ is A, only
+\end{bmatrix}^T
+\end{equation}
+$\mathbf{g}_i$ is a $4 \times \nnl$ matrix. If the specie of atom $i$ is A, only
 the first two columns have non-zero values. Similarly, the last two columns will
@@
 be viewed as the EAM descriptors for atom $i$. Hence, each structure can be 
-expressed with a 3D matrix, $\mathbf{G}$ , of shape $N \times \nnl \times 4$.
+expressed with a 3D matrix, $\mathbf{G}$ , of shape $N \times 4 \times \nnl$.
 
@@
 structure ($\namax$ and $\nbmax$) are also constants. Thus, any $\mathbf{G}$ can 
-be expanded to a $(\namax + \nbmax) \times \nnl \times 4$ matrix $\mathbf{G}'$ 
+be expanded to a $(\namax + \nbmax) \times 4 \times \nnl$ matrix $\mathbf{G}'$ 
 by zero-padding. In summary, arbitrary structure in the training dataset can be 
@@
 For the ADP formalism, the corresponding transformation is almost the same 
-except that $\mathbf{g}_{i}^{\mathrm{adp}}$ should also include the XYZ 
-components of $\vec{\mathbf{r}}_i$.
+except that $\mathbf{g}_{i}^{\mathrm{adp}}$ should also include the 
+$\alpha,\beta,\gamma$ components of $\vec{\mathbf{r}}_i$.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Transformation
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
+\centering
+\includegraphics[scale=0.3]{figures/transformation.png}
+\caption{\label{fig:transformation} Visualization of the descriptor matrix 
+$\mathbf{G}'$ of the binary AB system and $\nnl$ is 7. Non-colored cells are 
+padded zeros. \textbf{(a)} is a sample $\mathbf{g}_i$ of A-type atom and 
+\textbf{(b)} represents a B-type atom.}
+\end{figure}
+
+Fig \ref{fig:transformation} is the visualization of the descriptor matrix 
+$\mathbf{G}'$. $\mathbf{G}'$ has three axes: the neighbor axis, the interaction 
+axis and the atom axis. $\nnl$ is the maximum of the neighbor axis (in this case 
+$\nnl = 7$). For the binary AB system there are four types of interactions: AA, 
+AB, BB and BA. \textbf{(a)} and \textbf{(b)} are samples of $\mathbf{g}_i$ for 
+A-type atoms and B-type atoms.
 
@@
 $\kappa$ are used in Equation \ref{eq:zjw04_rho} already. For the pairwise 
-interaction between two atoms of different species, Zhou et al proposed an 
-interpolation form:
+interaction between two atoms of different species, the interpolation form is 
+used:
 \begin{equation}
@@
 \end{align}
-$\omega_1$ and $\omega_3$ are just damping factors calculated by the sigmoid 
+$c_1$ and $c_3$ are just damping factors calculated by the sigmoid 
 functions (Equations \ref{eq:frho_c1} and \ref{eq:frho_c3}).
@@
 \end{equation}
-where $V_0$ is the equilibrium volume and $B$ is the bulk modulus. The adoption
-of the Rose constraint guarantees the exact predictions of bulk modulus and 
-the energy-volume curve. The loss of the Rose EOS constraint 
+where $V_0$ is the equilibrium volume and $B$ is the corresponding bulk modulus. 
+The adoption of the Rose constraint guarantees the exact predictions of bulk 
+modulus and the energy-volume curve. The loss of the Rose EOS constraint 
 $\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
@@
 Here $\Omega$ denotes all selected crystals. In this work, for each included 
-crystal, we use the same choices of $x$: 
+crystal, we use the same choices of $x$, which determines the fitting region: 
 $x_{i} = x_{0} + \Delta x \cdot i, x_{0} = -0.1, N_{t}^{\mathrm{max}} = 20, 
-\Delta x=0.01$. In this work, $\beta^{\mathrm{Ni}}$ is 0.005 and 
-$\beta^{\mathrm{Mo}}$ is 0.008.
+\Delta x=0.01$. (-10\% to +10\% of the equilibrium volume). In this work, 
+$\beta^{\mathrm{Ni}}$ is 0.005 and $\beta^{\mathrm{Mo}}$ is 0.008.
 
@@
 
-In this work, we successfully find a way to use elastic tensor directly as a 
+In this work, we find a straightforward way to use elastic tensor directly as a 
 constraint. Given an equilibrium crystal structure, its elastic constant 
@@
 
+The adoption of physical constraints in optimizing MLIPs can be very helpful. 
+Without any physical constraint, adding high-quality data points is, perhaps, 
+the only effective way to tune MLIPs for specific purposes. On the contrast, 
+with physical constraints very few training samples are sufficient.
+As an example, the elementary SNAP potentials (Mo, Ni) were fitted with just 
+hundreds of structures but they performed quite well on elastic constants and 
+surface energies, as in the outer loop \cite{SNAP_Mo} of the fitting process 
+such material properties were already used. One must also note that data 
+consistency is important. Physical constrains are just supplementary roles in 
+developing MLIPs. So the values of the are preferred to be measured with 
+first-principle calculations.
+
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
@@
 Both ML-EAM and ML-ADP are implemented within Google's TensorFlow. The 
-virtual-atom approach (VAP) is adopted so that we can construct a computation 
-graph from atomic positions to total energy directly. Thus, atomic forces 
-(Equation \ref{eq:forces}) and virial stress (Equation \ref{eq:virial}) can be 
-derived by the AutoGrad module of TensorFlow and calcualted automatically and 
-efficiently. 
+virtual-atom approach (VAP) is adopted \cite{TensorAlloy} so that we can 
+construct a computation graph from atomic positions to total energy directly. 
+Thus, atomic forces (Equation \ref{eq:forces}) and virial stress 
+(Equation \ref{eq:virial}) can be derived by the AutoGrad module of TensorFlow 
+automatically and efficiently. 
 \begin{equation}
@@
 In most cases, we use 0.01 as the initial learning rate and the batch size 
-ranges from 20 to 50. Since there are very few adjustable parameters, the 
-optimization typically needs very few epochs to converge. When the optimization 
-is finished, the corresponding Lammps setfl potential file will be exported.
+ranges from 20 to 50. Since there are very few adjustable parameters compared 
+with neural networks, the optimization typically needs very few epochs to 
+converge. When the optimization is finished, the corresponding Lammps setfl 
+potential file will be exported.
 
@@
 
-The publicly Ni-Mo dataset \cite{SNAP} is used to evaluate our approach. This 
-dataset is provided by Shyue Ping Ong. It contains 3973 different Ni-Mo solids. 
-All calculations were done by VASP \cite{VASP} with the PBE \cite{PBE} 
-functional and the projector augmented-wave approach \cite{PAW}.
+The public Ni-Mo dataset \cite{SNAP} is used to evaluate our approach. This 
+dataset is provided by Shyue Ping Ong and co-workers along with their SNAP 
+models. It contains 3973 different Ni-Mo solids. All calculations were done by 
+VASP \cite{VASP} with the PBE \cite{PBE} functional and the projector 
+augmented-wave approach \cite{PAW}.
 
@@
 
-We first use the two elementary datasets (Ni and Mo) to show our approach. These 
+We firstly use the two elementary datasets (Ni and Mo) to show our approach. These 
 two datasets has 461 and 284 structures, respectively. 61 and 34 were randomly 
@@
 $\mu(r)$ and $\omega(r)$ functions. The differences between ML-EAM and ML-ADP 
-$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. Both the angular-dependent 
-dipole $\mu(r)$ and quadrupole $\omega(r)$ quickly descrease to zero at 2.5 \AA, 
-which is lower than the equilibrium spacing (2.7 \AA) between two adjacent Mo 
-atoms. Hence, the dipole and quadrupole terms only contribute a little to the 
-total energy for this test case.
+$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. For ML-ADP, both the dipole 
+and the quadrupole terms converge to zero at $\sim 4$ \AA. The dipole term gives
+the major contribution.
 
@@
 performace. ML-EAM achieves 4.1 meV/atom and 0.05 eV/\AA on the test set and 
-3.9 meV/atom and 0.05 eV\AA on the entire dataset. ML-EAM is nearly as accurate 
-as SNAP (1.2 meV/atom, 0.05 eV\AA), but later has around three orders of 
+3.9 meV/atom and 0.05 eV/\AA on the entire dataset. ML-EAM is nearly as accurate 
+as SNAP (1.2 meV/atom, 0.05 eV/\AA), but later has almost three orders of 
 magnitude more computational expense. Figure \ref{fig:Ni_eam} demonstrates the 
@@
 slightly better than ML-ADP. But considering the computational cost, the 
-ML-ADP is totally acceptable.
+performace of ML-ADP is totally acceptable.
 
@@
 almost exactly the same results with DFT. For the more complicated bcc Mo, the 
-central-force ML-EAM model becomes not that good due to the directional d 
-bonding \cite{ADP0}. The angular correction, introduced by Mishin, shows 
-its importance. ML-ADP can give acceptable results, just like the SNAP method.
+central-force ML-EAM model becomes not that good due to the lacking of 
+directional d bonding \cite{ADP0}. The angular correction, introduced by Mishin, 
+shows its importance. ML-ADP can give comparable results to the SNAP method.
 
@@
 of fcc Ni and bcc Mo using the solid-liquid coexistence approach. For fcc Ni, 
-$30 \times 10 \times 10$ supercells were used and for bcc the supercells were 
-$30 \times 15 \times 15$. The time step was set to 1 fs. The simulation for each 
-temperature was carried out for at least 300 ps. For fcc Ni, $T_{m}$ remains the 
+$30 \times 10 \times 10$ supercells were used and for bcc the supercells 
+$30 \times 15 \times 15$ were used. The time step was set to 1 fs. The 
+simulation for each temperature was carried out for at least 300 ps. 
+For fcc Ni, $T_{m}$ remains the 
 same for ML-EAM, 200 K lower than the experiment $T_m$. However, the calculated 
@@
 Secondly, we tested our method on the entire binary Mo-Ni dataset. 300 
-structures were randomly splitted to form the test dataset and the rest 3673 
+structures were randomly chosen to be the test dataset and the rest 3673 
 were used to train the potentials. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ 
@@
 
-The original EAM uses a simplified interpolation form to describe the pairwise 
+The original EAM uses a simplified combined form to describe the pairwise 
 interaction of A-B (Equation \ref{eq:zjw04_phi_ab}). However, we did a minor 
@@
 Table \ref{table:MAE} summarizes the energy and force MAEs of SNAP, ML-EAM and 
-ML-ADP on the different subsets. Amazingly, ML-ADP becomes the overally best. 
+ML-ADP on the different subsets. ML-ADP becomes the overally best. 
 Both the energy MAE (19.6 meV/atom) and the force MAE (0.20 eV/\AA) are smaller 
@@
 The pure Mo is still a challenge for ML-ADP as the energy and force MAEs are 
-noticeably large (still much smaller than the original Zjw04 EAM). The binary 
+noticeably large but still much smaller than the original Zjw04 EAM. The binary 
 SNAP predicts well on pure Ni and Mo. But ML-ADP outperforms the SNAP model on 
 binary phases (Ni$_3$Mo, Ni-doped Mo and especially the Mo-doped Ni).
-On the contrast, ML-EAM performs significantly worse compared with ML-ADP. 
-Interestingly, our results suggest that Mo-Ni dipole and quadrupole interactions 
-are completely negligible (Figure S1 in the appendix). The Ni-Ni dipole and 
-quadrupole interactions are an order of magnitude weaken than those of Mo-Mo.
+On the contrast, ML-EAM still performs significantly worse compared with ML-ADP 
+due to the restriction of the central-force model, as discussed before. 
+Interestingly, our results suggest that Mo-Ni dipole and quadrupole 
+contributions are completely negligible (Figure S1 in the appendix). The Ni-Ni 
+dipole and quadrupole interactions are an order of magnitude weaken than those 
+of Mo-Mo.
 
@@
 Ni$_4$Mo. The original Zjw04 EAM can not properly describe the energy-volume 
-relations of these two crystals. The ML-ADP curves fit perfectly with the DFT 
-curves. ML-EAM fits well with tensile strains but overestimates the energy under 
-compress strains.
+relations of these two crystals in wide range. The ML-ADP curves agrees 
+perfectly with the DFT curves. ML-EAM agrees well under tensile strains but 
+overestimates the energy under compress strains.
 
@@
 predictions of Ni$_3$Mo and Ni$_4$Mo. One should note that these two crystals 
-were not included in $\Omega$ of Equation \ref{eq:cijkl_loss} and 
+were not included in the $\Omega$ of Equation \ref{eq:cijkl_loss} and 
 \ref{eq:rose_loss} but their elastic properties were used to tune the binary 
@@
 constraints, for the fcc and bcc solids, the traditional empirical potentials, 
-EAM/ADP, can be improved to be almost as accurate as the SNAP method. But, 
-EAM/ADP are around $10^2$ to $10^3$ times faster than SNAP. To understand this,
-we can start from the many-body expansion (MBE) scheme \cite{kCON}.
+EAM/ADP, can be improved to be almost as accurate as the SNAP method using 
+exactly the same dataset. But, EAM/ADP are around $10^2$ to $10^3$ times faster 
+than SNAP. To understand this, we can start from the many-body expansion (MBE) 
+scheme \cite{kCON}.
 
@@
 surfaces. In the many-body expansion scheme, the total energy of a system with N 
-atoms can be expressed as the sum of all k-body terms where $k \le 1$:
+atoms can be expressed as the sum of all k-body terms where $k \le N$:
 \begin{equation}
@@
 In fact, both the EAM and the SNAP formalisms can be considered as variants of 
-MBE truncated at $k=2$. For the EAM method, the embedding contribution $F(\rho)$ 
-serves as the one-body term and the overall pairwise contribution 
-$\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is just a plain transcription of the 
-two-body term in Equation \ref{eq:MBE_atomic}. For the SNAP method, the atomic 
-energy is calculated with the following equation: 
+MBE. For the EAM method, the embedding contribution $F(\rho)$ 
+serves as a "special" one-body term because the many-body effect is considered.
+The overall pairwise contribution $\frac{1}{2}\sum_{j\ne i}{\phi(r_{ij})}$ is 
+just a plain transcription of the two-body term in Equation \ref{eq:MBE_atomic}. 
+For the SNAP method, the atomic energy is calculated with the following 
+equation: 
 \begin{equation}
@@
 parameters, $\alpha_i$ indicates the element type of atom $i$. $B_{k}^{i}$ is a 
-bispectrum coefficient. The calculation of $B_{k}^{i}$ is very complicated but 
-it is still a two-body term. The overall two-body contribution is a linear 
-combination of $B_{k}^{i}$. Thus, the SNAP formalism can be viewed as an 
-assemble of a simplified one-body term with a complicated two-body term. On the 
-other hand, the EAM formalism is built up with a 'complicated' one-body term and 
-a rather simple two-body term. The central-force EAM works well on fcc metals. 
-For bcc metals with partially filled d bands, the directional d bonding cannot
-be ignored. Hence, the pairwise dipole and quadrupole functions introduced by 
-ADP are necessary.
+bispectrum coefficient. The calculation of $B_{k}^{i}$ is very complicated 
+\cite{SNAP_Algo} but it is still a two-body term. The overall two-body 
+contribution is a linear combination of $B_{k}^{i}$. Thus, the SNAP formalism 
+can be viewed as an assemble of a simplified one-body term with a complicated 
+two-body term. 
+On the other hand, the EAM formalism is built up with a 'complicated' one-body 
+term and a rather simple two-body term. The central-force EAM works well on fcc 
+metals. For bcc metals with partially filled d bands, the directional d bonding 
+cannot be ignored. Hence, the pairwise dipole and quadrupole functions 
+introduced by ADP are necessary.
 
@@
 alone may not uniquely describe a structure. To avoid this problem, the cutoff 
-was raised up to 6.5 \AA. As a comparison, the overall $r_{cut}$ is 4.6 \AA for 
-the binary SNAP. But such descriptor is still too rough to describe complicated 
+was raised up to 6.5 \AA. As a comparison, the overall $r_{cut}$ for the binary 
+SNAP is 4.6 \AA. But such descriptor is still too rough to describe complicated 
 potential energy surfaces (e.g. bcc Mo). To further enhance EAM/ADP, complicated
@@
 machine learning. The machine learning approaches (big data, SGD, etc), together 
-with physical constraints (Rose EOS, elastic constants) can significantly boost
-the performaces of EAM/ADP. For the fcc Ni, bcc Mo and Mo-Ni alloys, ML-EAM and
-ML-ADP can be as accurate as SNAP, while later method is orders of magnitude 
-slower. Our work also indicates a new route to design and develop machine 
-learning interatomic potentials \textemdash the machine learning enhanced 
-empirical potential approach.
+with physical constraints (Rose EOS, elastic constants) can significantly 
+improve the performaces of EAM/ADP. For the fcc Ni, bcc Mo and Mo-Ni alloys, 
+ML-EAM and ML-ADP can be as accurate as SNAP, while later method is orders of 
+magnitude slower. Our work also indicates a new route to design and develop 
+machine learning interatomic potentials \textemdash the machine learning 
+enhanced empirical potential approach.
 

### 2020-01-02 tensoralloy/nn/eam/potentials/spline.py
Add `LinearlyExtendedSplinePotential` for the pair style `meam/spline`.

@@ -55,18 +55,6 @@ class CubicSplinePotential(EamAlloyPotential):
     def _make(self, t: tf.Tensor, pot: str, name: str):
         """
         Make a spline potential.
-
-        nr = self._adpfl.nr
-            x = self._adpfl.rho[element][0][0:nr:self._interval]
-            y = self._adpfl.rho[element][1][0:nr:self._interval]
-            f = CubicInterpolator(x, y, natural_boundary=True, name='Spline')
-            shape = tf.shape(r, name='shape')
-            rho = f.evaluate(tf.reshape(r, (-1,), name='r/flat'))
-            rho = tf.reshape(rho, shape, name='rho')
-            if verbose:
-                log_tensor(rho)
-            return rho
-
         """
         if not self.is_avaiblable(pot):
             raise ValueError(f"{pot} is not available!")
@@ -81,8 +69,9 @@ class CubicSplinePotential(EamAlloyPotential):
             collections=[tf.GraphKeys.MODEL_VARIABLES, ]
         )
         bc_start = self._df[f"{pot}.bc_start"]
-        bc_end = self._df[f"{pot}.bc_start"]
-        cubic = CubicInterpolator(x, y, natural_boundary=True,
+        bc_end = self._df[f"{pot}.bc_end"]
+        natural_boundary = self._df[f"{pot}.natural_boundary"]
+        cubic = CubicInterpolator(x, y, natural_boundary=natural_boundary,
                                   bc_start=bc_start, bc_end=bc_end)
         shape = tf.shape(t, name='shape')
         val = cubic.evaluate(tf.reshape(t, (-1, ), name='t/flat'), name='eval')
@@ -132,7 +121,7 @@ class CubicSplinePotential(EamAlloyPotential):
             with tf.variable_scope(
                     f"{variable_scope}/{element}",
                     reuse=tf.AUTO_REUSE):
-                embed = self._make(rho, f"{element}.embed", "phi")
+                embed = self._make(rho, f"{element}.embed", "embed")
                 if verbose:
                     log_tensor(embed)
                 return embed
@@ -221,3 +210,83 @@ class CubicSplinePotential(EamAlloyPotential):
                 if verbose:
                     log_tensor(fs)
                 return fs
+
+
+class LinearlyExtendedSplinePotential(CubicSplinePotential):
+    """
+    A special spline potential for pair style 'meam/spline'.
+
+    When x < xmin: f(x) = y[0] + (x - xmin) * deriv0
[…]

### 2020-01-02 tensoralloy/io/lammps.py
Minor update.

@@ -61,6 +61,7 @@ class Spline:
     bc_end: float
     x: np.ndarray
     y: np.ndarray
+    natural_boundary: bool
 
 
 @add_slots
@@ -85,12 +86,15 @@ class SetFL:
     lattice_types: List[str]
 
 
-def _init_spline_dict(nx: int, dx: float, bc_start=0.0, bc_end=0.0):
+def _init_spline_dict(nx: int, dx: float, bc_start=0.0, bc_end=0.0,
+                      deriv_order=2):
+    assert deriv_order == 1 or deriv_order == 2
     return {
         "bc_start": bc_start,
         "bc_end": bc_end,
         "x": np.linspace(0.0, nx * dx, nx, endpoint=False),
         "y": np.zeros(nx),
+        "natural_boundary": False if deriv_order == 1 else True,
     }
 
 
@@ -406,7 +410,8 @@ def _read_meam_spline_file(filename: str, element=None):
                     raise IOError(f"Line error: {line}")
                 bc_start = float(splits[0])
                 bc_end = float(splits[1])
-                spline = _init_spline_dict(nknots, 0.0, bc_start, bc_end)
+                spline = _init_spline_dict(
+                    nknots, 0.0, bc_start, bc_end, deriv_order=1)
                 if is_new_format:
                     stage = 4
                 else:

### 2020-01-02 tensoralloy/cli/build.py
Minor update.

@@ -203,6 +203,8 @@ class BuildSplineGuessProgram(CLIProgram):
                         getattr(lmp, pot)[key].y[::step].tolist()
                 data[f"{key}.{pot}.bc_start"] = getattr(lmp, pot)[key].bc_start
                 data[f"{key}.{pot}.bc_end"] = getattr(lmp, pot)[key].bc_end
+                data[f"{key}.{pot}.natural_boundary"] = \
+                    getattr(lmp, pot)[key].natural_boundary
 
             if exclude_types:
                 exclude_types = [x.strip().lower()

### 2020-01-02 tensoralloy/nn/eam/eam.py
Finally the Ti/meam/spline test passed.

@@ -21,12 +21,14 @@ from tensoralloy.nn.utils import get_activation_fn, log_tensor
 from tensoralloy.nn.eam.potentials import available_potentials
 from tensoralloy.nn.eam.potentials import EamFSPotential, EamAlloyPotential
 from tensoralloy.nn.eam.potentials.spline import CubicSplinePotential
+from tensoralloy.nn.eam.potentials.spline import LinearlyExtendedSplinePotential
 
 __author__ = 'Xin Chen'
 __email__ = 'Bismarrck@me.com'
 
 
-_spline_pot_patt = re.compile(r"spline@(.*)")
+_spline_pot_patt = re.compile(r"^spline@(.*)")
+_lext_spline_pot_patt = re.compile(r"^lspline@(.*)")
 
 
 def plot_potential(nx: int, dx: float, func: Callable, filename: str,
@@ -167,7 +169,8 @@ class EamNN(BasicNN):
         name = name.lower()
         if name == "nn" or \
                 name in available_potentials or \
-                name.startswith("spline@"):
+                name.startswith("spline@") or \
+                name.startswith("lspline@"):
             return True
         else:
             return False
@@ -176,15 +179,17 @@ class EamNN(BasicNN):
         """
         Insert the spline functions read from the given csv file.
         """
-        m = _spline_pot_patt.search(name.strip())
-        if m:
-            csv = m.group(1)
-            if csv not in self._empirical_functions:
-                spline = CubicSplinePotential(csv)
-                self._empirical_functions[csv] = spline
-            return csv
-        else:
-            return name
+        for (patt, cls) in (
+                (_spline_pot_patt, CubicSplinePotential),
+                (_lext_spline_pot_patt, LinearlyExtendedSplinePotential)):
+            m = patt.search(name.strip())
+            if m:
+                json = m.group(1)
+                if json not in self._empirical_functions:
+                    spline = cls(json)
+                    self._empirical_functions[json] = spline
+                return json
+        return name
 
     def _get_nn_fn(self, section, key, variable_scope, verbose=False):
         """

### 2020-01-02 tensoralloy/nn/eam/meam.py

@@ -400,6 +400,7 @@ class MeamNN(EamAlloyNN):
             splits = tf.split(
                 rho, num_or_size_splits=split_sizes, axis=split_axis)
             values = []
+            zero = tf.constant(0.0, dtype=rho.dtype, name='zero')
             for i, element in enumerate(self._elements):
                 with tf.name_scope(f"{element}"):
                     x = tf.expand_dims(splits[i], axis=-1, name=element)
@@ -408,6 +409,9 @@ class MeamNN(EamAlloyNN):
                     # Apply the embedding function on `x`
                     comput = self._get_embed_fn(element, verbose=verbose)
                     y = comput(x)
+                    with tf.name_scope("Baseline"):
+                        base = comput(zero)
+                    y = tf.math.subtract(y, base, name='relative')
                     embed = tf.squeeze(y, axis=squeeze_axis, name='atomic')
                     if verbose:
                         log_tensor(embed)

### 2020-01-02 tensoralloy/nn/eam/tests/test_meam_spline_nn.py

@@ -4,19 +4,21 @@ Test the implementation of MEAM/Spline.
 """
 from __future__ import print_function, absolute_import
 
+import numpy as np
 import tensorflow as tf
 import unittest
 import nose
 import os
 import shutil
 
+from nose.tools import assert_almost_equal
 from enum import Enum
 from os.path import dirname, join, exists
 from ase.build import bulk
 from ase.calculators.lammpsrun import LAMMPS
 from tensorflow_estimator import estimator as tf_estimator
 
-from tensoralloy.test_utils import test_dir
+from tensoralloy.test_utils import test_dir, assert_array_almost_equal
 from tensoralloy.io.lammps import LAMMPS_COMMAND
 from tensoralloy.nn.eam.meam import MeamNN
 from tensoralloy.transformer.universal import UniversalTransformer
@@ -74,18 +76,22 @@ class MeamSplineTest(unittest.TestCase):
         Test the meam/spline implementation with the Ti system.
         """
         atoms = bulk('Ti', cubic=True)
+        delta = np.random.uniform(-0.05, 0.05, size=(len(atoms), 3))
+        atoms.set_positions(atoms.positions + delta)
         elements = ['Ti']
-        spline = f"spline@{join(dirname(__file__), 'Ti.meam.spline.json')}"
+        spline = f"lspline@{join(dirname(__file__), 'Ti.meam.spline.json')}"
 
         calc = self.get_lammps_calculator(TestSystem.Ti)
+        calc.calculate(atoms, properties=['energy', 'forces'])
         pe = calc.get_potential_energy(atoms)
+        forces = calc.get_forces(atoms)
 
         nn = MeamNN(elements,
                     custom_potentials={"Ti": {"rho": spline,
                                               "fs": spline,
                                               "embed": spline},
                                        "TiTi": {"phi": spline, "gs": spline}})
-        clf = UniversalTransformer(elements, rcut=5.5, acut=4.1, angular=True,
+        clf = UniversalTransformer(elements, rcut=5.50, acut=4.41, angular=True,
                                    symmetric=False)
         nn.attach_transformer(clf)
 
@@ -96,8 +102,10 @@ class MeamSplineTest(unittest.TestCase):
                 verbose=True)
             with tf.Session() as sess:
                 tf.global_variables_initializer().run()
-                print(sess.run(predictions['energy']))
-                print(pe)
+                results = sess.run(predictions)
+                assert_almost_equal(results['energy'], pe,
[…]

### 2020-03-15 doc/papers/ml-eam/manuscript.tex
ML-EAM revision 2020 Feb.

@@
 approximate to the first-principles accuracy. In this works, we successfully 
-integrated machine learning with EAM and ADP. Machine learning can significantly 
-boost their performances. For energy and force predictions, machine leaned EAM 
-and ADP can be almost as accurate as the spectral neighbor analysis potential 
-(SNAP) on the fcc Ni, bcc Mo and Mo-Ni alloy systems, while the molecular 
-dynamics simulations performed by the later approach is nealy 1000 times 
-slower. Machine learned EAM and ADP can also give first-principle accuracy key 
-material properties, such as elastic constants, melting temperatures and surface 
-energies. Our results suggest a new and systematic route for developing machine 
-learning interatomic potentials. 
+integrated machine learning interatomic potential with EAM and ADP. Machine 
+learning can significantly boost their performances. For energy and force 
+predictions, machine leaned EAM and ADP can be almost as accurate as the 
+spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
+alloy systems, while the molecular dynamics simulations performed by the later 
+approach is nealy 1000 times slower. Machine learned EAM and ADP can also give 
+first-principle accuracy key material properties, such as elastic constants, 
+melting temperatures and surface energies. Our results suggest a new and 
+systematic route for developing machine learning interatomic potentials. 
 \end{abstract}
@@
 
-Atomistic modeling plays a vital role in materials science. \textit{ab initio} 
+Atomistic modeling plays a vital role in materials science. \textit{Ab initio} 
 calculation or force-field based molecular dynamics simulation (MD) are 
@@
 parameters are difficult or even impossible to calcualte. Hence, 
-GO optimizations are generally not that effective.
+global optimizations are generally not that effective.
 
@@
 However, MLIPs also have challenges. The large parameter space and lack of 
-physical background makes the "big data" a necessarity. The cost of dataset is 
+physical background makes the "big data" a requisite. The cost of dataset is 
 non-negligible. Besides, even "big data" can only cover a small portion of real 
@@
 such material properties were already used. One must also note that data 
-consistency is important. Physical constrains are just supplementary roles in 
-developing MLIPs. So the values of the are preferred to be measured with 
-first-principle calculations.
+consistency is important. Physical constraints are just supplementary roles in 
+developing MLIPs, so they are preferred to be measured with first-principle 
+calculations.
 
@@
 
-The implementation of the machine learned embedded atom mathod and the physical
+The implementation of the machine learned EAM and the physical
 constraints are beyond the scope of this work. The details will be discussed
@@
 
-Figure \ref{fig:Mo_eam_adp} compares the $\rho(r)$, $F(\rho)$, $\phi(r)$, 
+Figure \ref{fig:Ni_eam} compares the $\rho(r)$, $F(\rho)$, $\phi(r)$, 
 $\mu(r)$ and $\omega(r)$ functions. The differences between ML-EAM and ML-ADP 
@@
 \caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
-ML-EAM and DFT for the bcc Mo.}
+ML-EAM, ML-ADP and DFT for the bcc Mo.}
 \end{figure}
@@
 \caption{\label{fig:alloy_eos} Energy-volume curves of Ni$_3$Mo and Ni$_4$Mo 
-obtained with the original Zjw04 EAM, ML-EAM, ML-ADP and DFT.}
+obtained with the original Zjw04 EAM, ML-EAM, ML-ADP, SNAP and DFT.}
 \end{figure*}
@@
 \end{equation}
-where $\mathrm{C^N_k}$ is the binomial coefficient and $E^{(k)}$ represents the 
-k-body contribution. In many cases, higher-order terms like $E_{ij}$ or 
+where $\mathrm{C^N_k}$ (k=1,2,3) is the binomial coefficient and $E^{(k)}$ 
+represents the k-body contribution. In many cases, higher-order terms like 
+$E_{ij}$ or 
 $E_{ijk}$ are symmetric: $E_{ij}=E_{ji}$, $E_{ijk}=E_{ikj}=E_{jik}=\cdots$. 

### 2020-03-17 doc/papers/ml-eam/manuscript.tex
This is the final version for npj.

@@
 \author{Hai-Feng Song}
-\email{song_haifeng@iapcm.ac.cn}
+\email{song\_haifeng@iapcm.ac.cn}
 \affiliation{
@@
 approximate to the first-principles accuracy. In this works, we successfully 
-integrated machine learning interatomic potential with EAM and ADP. Machine 
-learning can significantly boost their performances. For energy and force 
+developed a route to express EAM and ADP within machine learning framework in 
+highly-vectorizable form and further enhanced the potentials with physical 
+constraints. Machine learning can significantly boost their performances with 
+few training data. 
+For energy and force 
 predictions, machine leaned EAM and ADP can be almost as accurate as the 
@@
 % 
+% Figure: Mo - EAM/ADP - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
+\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
+Zjw04 EAM, ML-EAM and ML-ADP for elementary Mo. \textbf{(d)} shows the $\mu(r)$ 
+and $\omega(r)$ of ML-ADP.}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni / Mo MAEs
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}
+\centering
+\begin{tabular}{lccccc}
+\hline
+            &    & EAM\cite{ZJW2} & SNAP\cite{SNAP} & ML-EAM & ML-ADP \\
+\hline
+Energy     & Ni & 10.6           & 1.2             & 3.9    &        \\
+(meV/atom) & Mo & 58.9           & 13.2            & 23.8   & 18.7   \\
+\hline
+Force      & Ni & 0.06           & 0.05            & 0.05   &        \\
+(eV/\AA)   & Mo & 0.31           & 0.25            & 0.30   & 0.29   \\
+\hline
+\end{tabular}
+\caption{\label{table:Mo_Ni_mae} Comparisons of the energy and force MAEs of 
+elementary Ni and Mo. 
+}
+\end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
 % Table: Ni - Material Properties
@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Surface Energy - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{figures/surface_energy.png}
+\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
+\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
+\end{figure}
+
 We firstly use the two elementary datasets (Ni and Mo) to show our approach. These 
-two datasets has 461 and 284 structures, respectively. 61 and 34 were randomly 
-selected to form the test subsets. In these two experiments, 
+two datasets has 461 and 284 structures, respectively. 61 and 34 structures were 
+randomly selected to form the test subsets. In these two experiments, 
 $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and $\chi_{\mathrm{elastic}}$ were 
@@
 $\mu(r)$ and $\omega(r)$ functions. The differences between ML-EAM and ML-ADP 
-$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. For ML-ADP, both the dipole 
-and the quadrupole terms converge to zero at $\sim 4$ \AA. The dipole term gives
-the major contribution.
+$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small.
 
@@
 For the Mo dataset, the situation is quite different. The original Zjw04 has 
-extremely large MAEs: the energy \textbf{rMAE} is $\sim 98$ meV/atom and the 
-force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
+extremely large MAEs: the energy \textbf{rMAE} is $\sim 59$ meV/atom and the 
+force MAE is more than 0.31 eV/\AA. Our method can significantly reduce the 
 error: ML-EAM can achieve test MAEs of 23.8 meV/atom and 0.26 eV/\AA and overall
@@
 slightly better than ML-ADP. But considering the computational cost, the 
-performace of ML-ADP is totally acceptable.
+performace of ML-ADP is totally acceptable. Figure \ref{fig:Mo_eam_adp} 
+demonstrates the potential functions. The $\rho(r)$, $F(\rho)$ and $\phi(r)$ 
+functions of ML-EAM and ML-ADP are quite similar. The additional accuracy of 
+ML-ADP mainly comes from the dipole function $\mu(r)$.
 
@@
 energy-volume curves of ML-EAM and ML-ADP overalp with the DFT curves very well.
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: Mo - EAM/ADP - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}[htp]
-\centering
-\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
-\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
-Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
-ML-ADP.}
-\end{figure}
 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: Surface Energy - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{figures/surface_energy.png}
-\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
-\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
-\end{figure}
-
 We further examined our ML-EAM and ML-ADP by calculating the melting temperature

### 2020-04-20 doc/papers/ml-eam/manuscript.tex
Minor update.

@@
 For energy and force 
-predictions, machine leaned EAM and ADP can be almost as accurate as the 
+predictions, machine learned EAM and ADP can be almost as accurate as the 
 spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
 alloy systems, while the molecular dynamics simulations performed by the later 
-approach is nealy 1000 times slower. Machine learned EAM and ADP can also give 
+approach is nearly 1000 times slower. Machine learned EAM and ADP can also give 
 first-principle accuracy key material properties, such as elastic constants, 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\section{Discussions}
+\subsection{Discussions}
 \label{sec:discussions}

### 2020-04-20 doc/papers/ml-eam/manuscript.tex
Minor update.

@@
 For energy and force 
-predictions, machine learned EAM and ADP can be almost as accurate as the 
+predictions, machine lear̦ned EAM and ADP can be almost as accurate as the 
 spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 

### 2020-04-22 doc/papers/ml-eam/manuscript.tex
The final version for npj.

--- 2020-04-20 doc/papers/ml-eam/manuscript.tex
@@
 efficient optimizers, machine learning interatomic potentials can generally 
-approximate to the first-principles accuracy. In this works, we successfully 
+approximate to the first-principle accuracy. In this works, we successfully 
 developed a route to express EAM and ADP within machine learning framework in 
@@
 For energy and force 
-predictions, machine learned EAM and ADP can be almost as accurate as the 
+predictions, machine lear̦ned EAM and ADP can be almost as accurate as the 
 spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
-alloy systems, while the molecular dynamics simulations performed by the later 
-approach is nearly 1000 times slower. Machine learned EAM and ADP can also give 
-first-principle accuracy key material properties, such as elastic constants, 
-melting temperatures and surface energies. Our results suggest a new and 
-systematic route for developing machine learning interatomic potentials. 
+alloy systems, while the molecular dynamics simulations performed by our 
+potentials are nearly 1000 times faster. Machine learned EAM and ADP can also 
+give first-principle accuracy key material properties, such as elastic 
+constants, melting temperatures and surface energies. Our results suggest a new 
+and systematic route for developing machine learning interatomic potentials. 
 \end{abstract}
@@
 \begin{align}
-\label{eq:e_atom_phase_1}
+\label{eq:e_atom_phase_2}
 E_{j}^{B} 
@@
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: Surface Energy - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{figures/surface_energy.png}
-\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
-\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
-\end{figure}
-
 We firstly use the two elementary datasets (Ni and Mo) to show our approach. These 
@@
 ML-EAM, ML-ADP and DFT for the bcc Mo.}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Surface Energy - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{figures/surface_energy.png}
+\caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
+\textbf{(a)} fcc Ni and \textbf{(b)} bcc Mo.}
 \end{figure}
@@
 To conclude, we have successfully combined empirical potentials (EAM/ADP) with 
-machine learning. The machine learning approaches (big data, SGD, etc), together 
-with physical constraints (Rose EOS, elastic constants) can significantly 
-improve the performaces of EAM/ADP. For the fcc Ni, bcc Mo and Mo-Ni alloys, 
-ML-EAM and ML-ADP can be as accurate as SNAP, while later method is orders of 
-magnitude slower. Our work also indicates a new route to design and develop 
-machine learning interatomic potentials \textemdash the machine learning 
+machine learning. The machine learning approaches (big data, optimization, etc), 
+together with physical constraints (Rose EOS, elastic constants) can 
+significantly improve the performaces of EAM/ADP. For the fcc Ni, bcc Mo and 
+Mo-Ni alloys, ML-EAM and ML-ADP can be as accurate as SNAP, while later method 
+is orders of magnitude slower. Our work also indicates a new route to design and 
+develop machine learning interatomic potentials \textemdash the machine learning 
 enhanced empirical potential approach.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Data Availability
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\section*{Data Availability}
+The optimized parameters of the associated EAM and ADP models are all listed in 
+the appendix. The learning datasets are originally created by Shyue Ping Ong 
+and can be accessed from 
+\href{https://github.com/materialsvirtuallab/snap}{GitHub} freely.
 
@@
 % 
+% Author Contributions
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section*{Author Contributions}
+X.C. designed the research project, wrote the related codes and build the 
+machine learning interatomic potentials. L.F.W did the molecular dynamics 
+simulations and calculations. X.Y.G., Y.F.Z., D.Y.L., W.D.C. and H.F.S. provided 
+valuable comments and suggestions to the work. X.C. and L.F.W. wrote the paper. 
+All authors contributed to discussions of the results.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Additional Information
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section*{Additional Information}
+
+\textbf{Competing interests}: The authors declare no Competing Financial or 
+Non-Financial Interests.
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
 % References

### 2020-05-20 doc/papers/ml-eam/manuscript.tex
The revision for PRB
Revision 1 for cpc.

@@
 constants, melting temperatures and surface energies. Our results suggest a new 
-and systematic route for developing machine learning interatomic potentials. 
+and systematic route for developing machine learning interatomic potentials. All 
+the new algorithms have been implemented in our program TensorAlloy.
 \end{abstract}
@@
 theoretical background of this work, including the formalism of the embedded 
-atom method and algorithms of the machine learned EAM. Section \ref{sec:results} 
-summarizes the results of ML-EAM and ML-ADP. Further discussions are given in 
-section \ref{sec:discussions}.
+atom method and algorithms of the machine learned EAM. 
+Section \ref{sec:implementation} describes the implementation details.
+Section \ref{sec:results} summarizes the results of ML-EAM and ML-ADP. 
+Further discussions are given in section \ref{sec:discussions}.
+
+All the new algorithms have been implemented in our program TensorAlloy 
+\cite{TensorAlloy}.
 
@@
 \centering
-\includegraphics[scale=0.3]{figures/transformation.png}
+\includegraphics[scale=0.3]{transformation.png}
 \caption{\label{fig:transformation} Visualization of the descriptor matrix 
@@
 \label{eq:rose_eos}
-E(x) = E_{0}\left[
+E^\mathrm{rose}(x) = E_{0}\left[
     1 + \alpha x + \beta \alpha^3 x^3 \frac{2x + 3}{(x - 1)^2} \right]
@@
 $\mathbf{L}^{\mathrm{Rose}}$  is measured as the 2-norm of the energy 
-differences between $E(x)^{\mathrm{dft}}$ and their corresponding predicted 
+differences between $E^{\mathrm{rose}}(x)$ and their corresponding predicted 
 $E(x)$: 
@@
 \mathbf{L}^{\mathrm{Rose}} = \sum_{\Omega}{
-    \sqrt{\sum_{i}{\left(E(x_i) - E(x_i)^{\mathrm{dft}}\right)^2}}
+    \sqrt{\sum_{i}{\left(E(x_i) - E^{\mathrm{rose}}(x_i)\right)^2}}
 }
@@
 % 
-% Figure: Ni - EAM - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure*}
+% Section 3. Implementation
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\section{Implementation}
+\label{sec:implementation}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Mo - EAM/ADP - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}
 \centering
-\includegraphics[scale=0.57]{figures/Ni_eam.png}
-\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
-Zjw04 EAM and the machine learned EAM (ML-EAM).}
-\end{figure*}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Figure: Mo - EAM/ADP - Plot
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{figure}[htp]
-\centering
-\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
-\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
-Zjw04 EAM, ML-EAM and ML-ADP for elementary Mo. \textbf{(d)} shows the $\mu(r)$ 
-and $\omega(r)$ of ML-ADP.}
+\includegraphics[scale=0.45]{tensoralloy.png}
+\caption{\label{fig:tensoralloy} The architecture of TensorAlloy.}
 \end{figure}
 
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Ni / Mo MAEs
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table}
-\centering
-\begin{tabular}{lccccc}
-\hline
-            &    & EAM\cite{ZJW2} & SNAP\cite{SNAP} & ML-EAM & ML-ADP \\
-\hline
-Energy     & Ni & 10.6           & 1.2             & 3.9    &        \\
-(meV/atom) & Mo & 58.9           & 13.2            & 23.8   & 18.7   \\
-\hline
-Force      & Ni & 0.06           & 0.05            & 0.05   &        \\
-(eV/\AA)   & Mo & 0.31           & 0.25            & 0.30   & 0.29   \\
-\hline
-\end{tabular}
-\caption{\label{table:Mo_Ni_mae} Comparisons of the energy and force MAEs of 
-elementary Ni and Mo. 
-}
-\end{table}
-
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-% 
-% Table: Ni - Material Properties
-%
-% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
-\begin{table*}
-\centering
-\begin{tabular}{lccccc}
-\hline
-                              & DFT  & SNAP \cite{SNAP} & EAM              & ML-EAM         & Exp.                           \\
-\hline
-$T_{m}$(K)                    &      & 1785             & 1520 \cite{ZJW2} & 1520           & 1728                           \\
-$c_{11}$ (GPa)                & 276  & 276 (0.0\%)      & 248 (-10.1\%)    & 274 (-0.7\%)   & 261 \cite{Ni_Elastic_Exp}      \\
-$c_{12}$ (GPa)                & 159  & 159 (0.0\%)      & 147 (-7.5\%)     & 163 (2.5\%)    & 151 \cite{Ni_Elastic_Exp}      \\
-$c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
-$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (-1.5\%)    & 188                           \\
-$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)       & 87 (-8.4\%)      & 93 (-2.1\%)    & 93                             \\
-$\mu$                         & 0.29 & 0.29 (0.0\%)     & 0.29 (0.0\%)     & 0.29 (0.0\%)   & 0.29                           \\
-$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%)    & 1.68 (15.1\%)    & 1.71 (17.1\%)  & 1.54–1.80 \cite{Ni_EvEmEa_Exp} \\
-$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%)    & 0.90 (-19.6\%)   & 0.87 (-22.3\%) & 1.01–1.48 \cite{Ni_EvEmEa_Exp} \\
-$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)     & 2.58 (0.0\%)     & 2.58 (0.0\%)   & 2.77–2.95 \cite{Ni_EvEmEa_Exp} \\
-\hline
-\end{tabular}
-\caption{\label{table:Ni_properties} Comparison of the calculated and 
-experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
-point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
-formation energy and migration energy, respectively. SNAP refers to the 
-elementary Ni SNAP model.
-}
-\end{table*}
-
-% -----------
-% Section 2.E Implementation
-% -----------
-\subsection{Implementation}
-\label{sec:implementation}
-
-The implementation of the machine learned EAM and the physical
-constraints are beyond the scope of this work. The details will be discussed
-in another paper. Here, we will give a brief description.
-
-Both ML-EAM and ML-ADP are implemented within Google's TensorFlow. The 
-virtual-atom approach (VAP) is adopted \cite{TensorAlloy} so that we can 
-construct a computation graph from atomic positions to total energy directly. 
-Thus, atomic forces (Equation \ref{eq:forces}) and virial stress 
-(Equation \ref{eq:virial}) can be derived by the AutoGrad module of TensorFlow 
-automatically and efficiently. 
-\begin{equation}
-\label{eq:forces}
-\mathbf{F} = -\frac{\partial E^{total}}{\partial \mathbf{R}}
-\end{equation}
-This direct computation graph also plays a key role in computing analytical 
-elastic tensor (Equation \ref{eq:cijkl}) and the Rose loss 
-(Equation \ref{eq:rose_eos}).
+Fig \ref{fig:tensoralloy} shows the architecture of the TensorAlloy program. The 
+program has two major steps: the first step is calculating the losses of energy,
+force and stress terms while the second step is measuring the contributions of 
+the physical constraints.
+
+For the first step, the implementation is almost the same with our previous 
+work \cite{TensorAlloy} except the formula of the potential energy. The direct
+computation graph from atomic positions to total energy can be built because of
+our virtual atom approach (VAP) \cite{TensorAlloy} and the vectorized EAM theory
+\ref{sec:transformation}. Hence, atomic forces and virial stress tensors can be 
+calculated automatically thanks to the AutoGrad featue of TensorFlow. The 
+batching scheme is adopted in this step.
+
+For the second step, VAP also plays the key role. Only very few specific 
+structures are needed to form physical constraints. Thus, the batching scheme is 
+no longer a prerequiste. Instead, we use the codes of the 'prediction' phase of 
+VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint and 
+each selected crystal structure, an independent computation graph shall be 
+generated by reusing the model parameters.
 
@@
 % 
-% Section 3. Results
+% Figure: Ni - EAM - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure*}
+\centering
+\includegraphics[scale=0.57]{Ni_eam.png}
+\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
+Zjw04 EAM and the machine learned EAM (ML-EAM).}
+\end{figure*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Figure: Mo - EAM/ADP - Plot
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{figure}[htp]
+\centering
+\includegraphics[scale=0.6]{Mo_eam_adp.png}
+\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
+Zjw04 EAM, ML-EAM and ML-ADP for elementary Mo. \textbf{(d)} shows the $\mu(r)$ 
+and $\omega(r)$ of ML-ADP.}
+\end{figure}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni / Mo MAEs
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table}
+\centering
+\begin{tabular}{lccccc}
+\hline
+            &    & EAM\cite{ZJW2} & SNAP\cite{SNAP} & ML-EAM & ML-ADP \\
+\hline
+Energy     & Ni & 10.6           & 1.2             & 3.9    &        \\
+(meV/atom) & Mo & 58.9           & 13.2            & 23.8   & 18.7   \\
+\hline
+Force      & Ni & 0.06           & 0.05            & 0.05   &        \\
+(eV/\AA)   & Mo & 0.31           & 0.25            & 0.30   & 0.29   \\
+\hline
+\end{tabular}
+\caption{\label{table:Mo_Ni_mae} Comparisons of the energy and force MAEs of 
+elementary Ni and Mo. 
+}
+\end{table}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Table: Ni - Material Properties
+%
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\begin{table*}
+\centering
+\begin{tabular}{lccccc}
+\hline
+                              & DFT  & SNAP \cite{SNAP} & EAM              & ML-EAM         & Exp.                           \\
+\hline
+$T_{m}$(K)                    &      & 1785             & 1520 \cite{ZJW2} & 1520           & 1728                           \\
+$c_{11}$ (GPa)                & 276  & 276 (0.0\%)      & 248 (-10.1\%)    & 274 (-0.7\%)   & 261 \cite{Ni_Elastic_Exp}      \\
+$c_{12}$ (GPa)                & 159  & 159 (0.0\%)      & 147 (-7.5\%)     & 163 (2.5\%)    & 151 \cite{Ni_Elastic_Exp}      \\
+$c_{44}$ (GPa)                & 132  & 132 (0.0\%)      & 125 (-5.3\%)     & 131 (-0.8\%)   & 132 \cite{Ni_Elastic_Exp}      \\
+$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)      & 181 (-8.6\%)     & 195 (-1.5\%)    & 188                           \\
+$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)       & 87 (-8.4\%)      & 93 (-2.1\%)    & 93                             \\
+$\mu$                         & 0.29 & 0.29 (0.0\%)     & 0.29 (0.0\%)     & 0.29 (0.0\%)   & 0.29                           \\
+$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%)    & 1.68 (15.1\%)    & 1.71 (17.1\%)  & 1.54–1.80 \cite{Ni_EvEmEa_Exp} \\
+$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%)    & 0.90 (-19.6\%)   & 0.87 (-22.3\%) & 1.01–1.48 \cite{Ni_EvEmEa_Exp} \\
+$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)     & 2.58 (0.0\%)     & 2.58 (0.0\%)   & 2.77–2.95 \cite{Ni_EvEmEa_Exp} \\
+\hline
+\end{tabular}
+\caption{\label{table:Ni_properties} Comparison of the calculated and 
+experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
+point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
+formation energy and migration energy, respectively. SNAP refers to the 
+elementary Ni SNAP model.
+}
+\end{table*}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+% 
+% Section 4. Results
 %
@@
 
-The public Ni-Mo dataset \cite{SNAP} is used to evaluate our approach. This 
+The public Ni-Mo dataset \cite{SNAP} is used to evaluate our program. This 
 dataset is provided by Shyue Ping Ong and co-workers along with their SNAP 
@@
 % 
-% Section 3.A
+% Section 4.A
 %
@@
 \centering
-\includegraphics[scale=0.65]{figures/Ni_all_eos.png}
+\includegraphics[scale=0.65]{Ni_all_eos.png}
 \caption{\label{fig:Ni_eos} The energy-volume curves of the original EAM, 
@@
 \centering
-\includegraphics[scale=0.65]{figures/Mo_all_eos.png}
+\includegraphics[scale=0.65]{Mo_all_eos.png}
 \caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
@@
 \centering
-\includegraphics[scale=0.4]{figures/surface_energy.png}
+\includegraphics[scale=0.4]{surface_energy.png}
 \caption{\label{fig:surface_energy} Comparison of calculated surface energies of 
@@
 \centering
-\includegraphics[scale=0.5]{figures/alloy_eos.png}
+\includegraphics[scale=0.5]{alloy_eos.png}
 \caption{\label{fig:alloy_eos} Energy-volume curves of Ni$_3$Mo and Ni$_4$Mo 
@@
 % 
-% Section 3.C
+% Section 4.C
 %
@@
 % 
-% Section 4. Discussions
+% Section 5. Discussions
 %

### 2020-05-20 doc/papers/ml-eam/manuscript.tex
Initial version for cpc.

@@
-\documentclass[prb,reprint,superscriptaddress]{revtex4-2}
+%% This template can be used to write a paper for
+%% Computer Physics Communications using LaTeX.
+%% For authors who want to write a computer program description,
+%% an example Program Summary is included that only has to be
+%% completed and which will give the correct layout in the
+%% preprint and the journal.
+%% The `elsarticle' style is used and more information on this style
+%% can be found at 
+%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
+%%
+%%
+%% \documentclass[preprint,12pt]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+\documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
 
@@
 \usepackage{hyperref}   % use for hypertext links, including those to external
-\raggedbottom           % don't add extra vertical space
-\begin{comment}
-\end{comment}
-
-\bibliographystyle{apsrev4-2}
+\usepackage{amssymb}
+
+\newcounter{bla}
+\newenvironment{refnummer}{%
+\list{[\arabic{bla}]}%
+{\usecounter{bla}%
+ \setlength{\itemindent}{0pt}%
+ \setlength{\topsep}{0pt}%
+ \setlength{\itemsep}{0pt}%
+ \setlength{\labelsep}{2pt}%
+ \setlength{\listparindent}{0pt}%
+ \settowidth{\labelwidth}{[9]}%
+ \setlength{\leftmargin}{\labelwidth}%
+ \addtolength{\leftmargin}{\labelsep}%
+ \setlength{\rightmargin}{0pt}}}
+{\endlist}
+
+\journal{Computer Physics Communications}
 
 \begin{document}
+\begin{frontmatter}
 
@@
 
-\author{Xin Chen}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
+\author[a]{Xin Chen}
+\author[a]{Li-Fang Wang}
+\author[a]{Xing-Yu Gao}
+\author[b,a]{Ya-Fan Zhao}
+\author[b,a]{De-Ye Lin\corref{author}}
+\author[a]{Wei-Dong Chu}
+\author[a,b]{Hai-Feng Song\corref{author}}
+
+\cortext[author] {Corresponding author.
+\textit{E-mail address:} lindeye0716@163.com, song\_haifeng@iapcm.ac.cn}
+\address[a]{Institute of Applied Physics and Computational Mathematics, 
 Beijing 100088, China}
-
-\author{Li-Fang Wang}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-
-\author{Xing-Yu Gao}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-
-\author{Ya-Fan Zhao}
-\affiliation{
-    CAEP Software Center for High Performance Numerical Simulation, 
-    Beijing 100088, China}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-
-\author{De-Ye Lin}
-\email{lindeye0716@163.com}
-\affiliation{
-    CAEP Software Center for High Performance Numerical Simulation, 
-    Beijing 100088, China}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-
-\author{Wei-Dong Chu}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-
-\author{Hai-Feng Song}
-\email{song\_haifeng@iapcm.ac.cn}
-\affiliation{
-    Institute of Applied Physics and Computational Mathematics, 
-    Beijing 100088, China}
-\affiliation{
-    CAEP Software Center for High Performance Numerical Simulation, 
+\address[b]{CAEP Software Center for High Performance Numerical Simulation, 
 Beijing 100088, China}
@@
 
-\maketitle
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+Machine Learning \sep Alloy \sep Materials Modeling \sep Computational Physics 
+\sep Empirical Potentials    
+\end{keyword}
+
+\end{frontmatter}
+
+% Computer program descriptions should contain the following
+% PROGRAM SUMMARY.
+
+{\bf PROGRAM SUMMARY} \\
+\begin{small}
+\noindent
+{\em Program Title: TensorAlloy} \\
+{\em Licensing provisions(please choose one): LGPL}             \\
+{\em Programming language: Python 3.7}                          \\
+{\em Supplementary material:}                                   \\
+{\em Journal reference of previous version: 
+https://doi.org/10.1016/j.cpc.2019.107057}                      \\
+{\em Does the new version supersede the previous version?:} YES \\
+{\em Reasons for the new version: This new version is a significant extension to 
+the previous version. Now machine learning approaches and physical constraints 
+can be used together to tune empirical potentials (for example the embbeded atom 
+method). Machine learning optimized empirical potentials can be almost as 
+accurate as machine learning interaction potentials but run much faster} \\
+{\em Summary of revisions:}*\\
+{\em Nature of problem:} \\
+  Optimizing empirical potentials with machine learning approaches and physical 
+  constraints. \\
+{\em Solution method:} \\
+  The TensorAlloy program is built upon TensorFlow and the virtual-atom 
+  approach. we successfully developed a route to express the embbeded atom 
+  method and the angular-dependent potential within machine learning framework 
+  in highly-vectorizable form and further enhanced the potentials with physical
+  constraints. Machine learning can significantly boost their performances with 
+  few training data.   \\
+{\em Additional comments including Restrictions and Unusual features}\\
+  This program needs TensorFlow 1.14.*. Neither newer or older TensorFlow is 
+  supported. \\
+\end{small}
 
@@
 differences between $E^{\mathrm{rose}}(x)$ and their corresponding predicted 
-$E(x)$: 
+energy $E(x)$: 
 \begin{equation}
@@
 % 
-% Figure: Mo - EAM/ADP - Plot
+% Figure: Arch
 %
@@
 \centering
-\includegraphics[scale=0.45]{tensoralloy.png}
+\includegraphics[scale=0.6]{tensoralloy.png}
 \caption{\label{fig:tensoralloy} The architecture of TensorAlloy.}
@@
 
-For the second step, VAP also plays the key role. Only very few specific 
+For the second step, only very few specific 
 structures are needed to form physical constraints. Thus, the batching scheme is 
-no longer a prerequiste. Instead, we use the codes of the 'prediction' phase of 
-VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint and 
+no longer a pre-requiste. Instead, we use the codes of the 'prediction' phase of 
+VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint of 
 each selected crystal structure, an independent computation graph shall be 
-generated by reusing the model parameters.
-
-To find optimal parameters of the funcitons in section \ref{sec:functions}, the 
-overall loss function shall be defined. Just like other machine learning tasks, 
-the mini-batch stochastic gradient descent algorithm is used to minimize the 
-loss function. Equation \ref{eq:loss} demonstrates the loss function used in 
+generated by reusing the model parameters. This can be easily achieved within 
+our VAP framework. Hence, the complicated derivatives of the losses with respect 
+to the model parameters can be solved by TensorFlow automatically.
+For example, for the Ni-Mo system, if we select the elastic constants of $c_11$, 
+$c_22$ and $c_44$ of fcc Ni and bcc Mo, and the Rose EOS of fcc Ni and bcc Mo as 
+the physical constraints, thereshould be $2 \times 2$ separate computation 
+graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, Rose/bcc/Mo}) under 
+the scope 'Constraint'.
+
+The total loss is just the sum of the two steps introduced above:
+Equation \ref{eq:loss} demonstrates the loss function used in 
 this work:
@@
 are overall weights of force, rose EOS and elastic contributions.
+
+To find optimal parameters of the funcitons in section \ref{sec:functions}, the 
+overall loss function shall be defined. Just like other machine learning tasks, 
+the mini-batch stochastic gradient descent algorithm is used to minimize the 
+loss function. 
 The Adam optimizer \cite{adam} is used to minimize Equation \ref{eq:loss}. 
@@
 \centering
-\includegraphics[scale=0.57]{Ni_eam.png}
+\includegraphics[scale=0.4]{Ni_eam.png}
 \caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
@@
 \centering
-\includegraphics[scale=0.5]{alloy_eos.png}
+\includegraphics[scale=0.4]{alloy_eos.png}
 \caption{\label{fig:alloy_eos} Energy-volume curves of Ni$_3$Mo and Ni$_4$Mo 
@@
 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+\bibliographystyle{elsarticle-num}
 \bibliography{manuscript.bib}

### 2020-05-20 doc/papers/ml-eam/manuscript.tex
Minor update.

@@
 to the model parameters can be solved by TensorFlow automatically.
-For example, for the Ni-Mo system, if we select the elastic constants of $c_11$, 
-$c_22$ and $c_44$ of fcc Ni and bcc Mo, and the Rose EOS of fcc Ni and bcc Mo as 
-the physical constraints, thereshould be $2 \times 2$ separate computation 
-graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, Rose/bcc/Mo}) under 
-the scope 'Constraint'.
+For example, for the Ni-Mo system, if we select the elastic constants of 
+$c_{11}$, $c_{22}$ and $c_{44}$ of fcc Ni and bcc Mo, and the Rose EOS of fcc 
+Ni and bcc Mo as the physical constraints, there should be $2 \times 2$ separate 
+computation graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, 
+Rose/bcc/Mo}) under the scope 'Constraint'.
 

### 2020-05-26 doc/papers/ml-eam/manuscript.tex
Revision 1 for cpc.

@@
 \begin{abstract}
-Interatomic potential or force-field plays a vital role in simulating materials. 
+Interatomic potential (i.e. force-field) plays a vital role in atomistic 
+simulation of materials. 
 Empirical potentials like the embedded atom method (EAM) and its variant 
 angular-dependent potential (ADP) have proven successful in modeling many 
-metals qualitatively. In the past few years, machine learning has became the 
-key approach for modeling interatomic interactions. Powered by big data and 
+metals qualitatively. In the past few years, machine learning has became a 
+compelling approach for modeling interatomic interactions. Powered by big data and 
 efficient optimizers, machine learning interatomic potentials can generally 
-approximate to the first-principle accuracy. In this works, we successfully 
+approximate to the the accuracy of the first-principles calculations based on 
+the quantum mechanics theory. In this works, we successfully 
 developed a route to express EAM and ADP within machine learning framework in 
-highly-vectorizable form and further enhanced the potentials with physical 
-constraints. Machine learning can significantly boost their performances with 
-few training data. 
+highly-vectorizable form and further incorperated several physical constraints 
+into the training. As it is proved in this work, the performances of empirical 
+potentials can be significantly boosted with few traning data.
 For energy and force 
@@
 potentials are nearly 1000 times faster. Machine learned EAM and ADP can also 
-give first-principle accuracy key material properties, such as elastic 
-constants, melting temperatures and surface energies. Our results suggest a new 
-and systematic route for developing machine learning interatomic potentials. All 
-the new algorithms have been implemented in our program TensorAlloy.
+reproduce some key materials properties, such as elastic constants, melting 
+temperatures and surface energies, close to the first-principles accuracy. 
+Our results suggest a new and systematic route for developing machine learning 
+interatomic potentials. All the new algorithms have been implemented in our 
+program TensorAlloy.
 \end{abstract}
@@
 For the first step, the implementation is almost the same with our previous 
-work \cite{TensorAlloy} except the formula of the potential energy. The direct
-computation graph from atomic positions to total energy can be built because of
-our virtual atom approach (VAP) \cite{TensorAlloy} and the vectorized EAM theory
-\ref{sec:transformation}. Hence, atomic forces and virial stress tensors can be 
-calculated automatically thanks to the AutoGrad featue of TensorFlow. The 
-batching scheme is adopted in this step.
-
-For the second step, only very few specific 
-structures are needed to form physical constraints. Thus, the batching scheme is 
-no longer a pre-requiste. Instead, we use the codes of the 'prediction' phase of 
-VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint of 
-each selected crystal structure, an independent computation graph shall be 
-generated by reusing the model parameters. This can be easily achieved within 
-our VAP framework. Hence, the complicated derivatives of the losses with respect 
-to the model parameters can be solved by TensorFlow automatically.
-For example, for the Ni-Mo system, if we select the elastic constants of 
-$c_{11}$, $c_{22}$ and $c_{44}$ of fcc Ni and bcc Mo, and the Rose EOS of fcc 
-Ni and bcc Mo as the physical constraints, there should be $2 \times 2$ separate 
+work \cite{TensorAlloy} except the formula of the potential energy. Briefly, 
+this step starts from checking through the training dataset and determine some
+key constants, including $N^{vap}$ and $N^{\mathrm{max}}_{\mathrm{ij}}$. 
+$N^{\mathrm{max}}_{\mathrm{ijk}}$ is not needed as neither EAM nor ADP contains 
+triple-atoms interaction. Then we can build the global symbol list (GSL). Hence,
+structures of any stoichiometries can be transformed to their corresponding 
+unversal GSL forms for batching. The descriptors (\ref{sec:transformation}) are 
+built upon these GSL arrays. Then the direct computation graph from atomic 
+positions (GSL) to total energy can be easily built. Hence, atomic forces and 
+virial stress tensors can be calculated automatically thanks to the AutoGrad 
+feature of TensorFlow.
+
+For the second step, the situation is quite different. Only a few structures, 
+which may vary significantly, will be used to form the physical constraints. 
+Hence, batching is no longer a concern for this step. Instead, we need a more 
+flexible way to model complicated physical equations. 
+Recall that the virtual-atom approach has two phases: training and prediction 
+\cite{TensorAlloy}. The training phase is designed for mini-batch training. 
+$N^{vap}$, $N^{\mathrm{max}}_{\mathrm{ij}}$ and the GSL are pre-determined 
+constants. On the other hand, the prediction phase targets on a single input 
+structure. $N^{vap}$, $N^{\mathrm{max}}_{\mathrm{ij}}$ and the GSL are 
+determined dynamically. Therefore, the prediction phase is much suitable for 
+modeling physical constraints. In our current implementation, for simplicity, we 
+just generate an independent compuation graph for each type of physical 
+constraint of each selected crystal structure. The model parameters are shared 
+across all the computation graphs (including the graph of step 1). For 
+example, for the Ni-Mo system, if we select the elastic constants of $c_{11}$, 
+$c_{22}$ and $c_{44}$ of fcc Ni and bcc Mo, and the Rose EOS of fcc Ni and bcc 
+Mo as the physical constraints, there should be $2 \times 2$ separate 
 computation graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, 
-Rose/bcc/Mo}) under the scope 'Constraint'.
+Rose/bcc/Mo}) under the scope 'Constraint'. The complicated derivatives of the 
+losses with respect to the model parameters can be solved by the AutoGrad module 
+of TensorFlow automatically.
 
@@
 $i$. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and $\chi_{\mathrm{elastic}}$ 
-are overall weights of force, rose EOS and elastic contributions.
+are overall weights of force, rose EOS and elastic contributions. Typicall 
+$\chi_{\mathrm{f}}$ is 2, $\chi_{\mathrm{rose}}$ is 10 and 
+$\chi_{\mathrm{elastic}}$ is set to 0.01.
 
@@
 ranges from 20 to 50. Since there are very few adjustable parameters compared 
-with neural networks, the optimization typically needs very few epochs to 
-converge. When the optimization is finished, the corresponding Lammps setfl 
-potential file will be exported.
+with neural network potentials, the optimization typically needs very few 
+training steps to converge. When the optimization is finished, the corresponding 
+Lammps setfl potential file will be exported.
 
@@
 
-To conclude, we have successfully combined empirical potentials (EAM/ADP) with 
-machine learning. The machine learning approaches (big data, optimization, etc), 
+To conclude, we have successfully combined the training of empirical potentials 
+with the machine learning approach into our TensorAlloy framework. The machine 
+learning approaches (big data, optimization, etc), 
 together with physical constraints (Rose EOS, elastic constants) can 
 significantly improve the performaces of EAM/ADP. For the fcc Ni, bcc Mo and 
-Mo-Ni alloys, ML-EAM and ML-ADP can be as accurate as SNAP, while later method 
-is orders of magnitude slower. Our work also indicates a new route to design and 
+Mo-Ni alloys, ML-EAM and ML-ADP can be as accurate as the SNAP method, while 
+later method is about three orders of magnitude slower. Our work also indicates 
+a new route to design and 
 develop machine learning interatomic potentials \textemdash the machine learning 
@@
 \section*{Author Contributions}
-X.C. designed the research project, wrote the related codes and build the 
-machine learning interatomic potentials. L.F.W did the molecular dynamics 
-simulations and calculations. X.Y.G., Y.F.Z., D.Y.L., W.D.C. and H.F.S. provided 
-valuable comments and suggestions to the work. X.C. and L.F.W. wrote the paper. 
-All authors contributed to discussions of the results.
+D.Y.L and H.F.S contributed the central conceptions of this study, designed 
+the research project, conducted the analyses and revised the manuscript. X.C. 
+designed the research project, wrote the related codes, trained the machine 
+learning interatomic potentials and conducted the analyses. L.F.W performed 
+molecular dynamics simulations and validated our models. X.Y.G., Y.F.Z. and 
+W.D.C: provided valuable comments and suggestions to the work. X.C. and L.F.W. 
+wrote the initial draft of the paper. All authors contributed to discussions of 
+the results.
 

### 2020-06-03 doc/papers/ml-eam/manuscript.tex
Minor update for cpc.

@@
 this step starts from checking through the training dataset and determine some
-key constants, including $N^{vap}$ and $N^{\mathrm{max}}_{\mathrm{ij}}$. 
-$N^{\mathrm{max}}_{\mathrm{ijk}}$ is not needed as neither EAM nor ADP contains 
-triple-atoms interaction. Then we can build the global symbol list (GSL). Hence,
-structures of any stoichiometries can be transformed to their corresponding 
-unversal GSL forms for batching. The descriptors (\ref{sec:transformation}) are 
+key constants, including the global symbol list and its size $N^{vap}$. For 
+arbitrary structure, it has $N_{ij}$ different atom-atom pairs within cutoff 
+$r_c$. For a concrete dataset, the corresponding maximum 
+$N^{\mathrm{max}}_{\mathrm{ij}}$ can also be determined before training. Hence,
+Structures of any stoichiometries can be transformed to their corresponding 
+universal GSL forms for batching. The descriptors (\ref{sec:transformation}) are 
 built upon these GSL arrays. Then the direct computation graph from atomic 

### 2021-04-27 doc/papers/ml-eam/manuscript.tex
The revised manuscript for CPC.

@@
 \author[a]{Xing-Yu Gao}
-\author[b,a]{Ya-Fan Zhao}
-\author[b,a]{De-Ye Lin\corref{author}}
+\author[b,c]{Ya-Fan Zhao}
+\author[b,c]{De-Ye Lin\corref{author}}
 \author[a]{Wei-Dong Chu}
-\author[a,b]{Hai-Feng Song\corref{author}}
+\author[a]{Hai-Feng Song\corref{author}}
 
@@
 \textit{E-mail address:} lindeye0716@163.com, song\_haifeng@iapcm.ac.cn}
-\address[a]{Institute of Applied Physics and Computational Mathematics, 
-Beijing 100088, China}
+\address[a]{Laboratory of Computational Physics, Institute of Applied Physics 
+and Computational Mathematics, Beijing 100088, China}
 \address[b]{CAEP Software Center for High Performance Numerical Simulation, 
 Beijing 100088, China}
+\address[c]{Institute of Applied Physics and Computational Mathematics, Beijing 
+100088, China}
 
@@
 Empirical potentials like the embedded atom method (EAM) and its variant 
-angular-dependent potential (ADP) have proven successful in modeling many 
-metals qualitatively. In the past few years, machine learning has became a 
-compelling approach for modeling interatomic interactions. Powered by big data and 
-efficient optimizers, machine learning interatomic potentials can generally 
+angular-dependent potential (ADP) have proven successful in many 
+metals. In the past few years, machine learning has became a 
+compelling approach for modeling interatomic interactions. Powered by big data 
+and efficient optimizers, machine learning interatomic potentials can generally 
 approximate to the the accuracy of the first-principles calculations based on 
@@
 For energy and force 
-predictions, machine lear̦ned EAM and ADP can be almost as accurate as the 
-spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
-alloy systems, while the molecular dynamics simulations performed by our 
-potentials are nearly 1000 times faster. Machine learned EAM and ADP can also 
+predictions, machine tuned EAM and ADP, can be 
+almost as accurate as the computationally expensive spectral neighbor analysis 
+potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni alloy systems. 
+Machine learned EAM and ADP can also 
 reproduce some key materials properties, such as elastic constants, melting 
@@
 method). Machine learning optimized empirical potentials can be almost as 
-accurate as machine learning interaction potentials but run much faster} \\
+accurate as machine learning interaction potentials but run much faster.} \\
 {\em Summary of revisions:}*\\
@@
 they are rarely used on large-scale metallic systems due to their extremely-high 
-computation expenses. Physical model based empirical potential (force-field), 
+computational expenses. Physical model based empirical potentials (force-field), 
 such as the embedded-atom method (EAM) \cite{EAM0,EAM1,EAM2,EAM3,EAM4}, 
@@
 bond-order potential (BoP) \cite{BOP0,BOP1,BOP2,BOP3}, or angular-dependent 
-potential (ADP) \cite{ADP0,ADP1,ADP2,ADP3,ADP_FeNi}, still plays the major role 
+potential (ADP) \cite{ADP0,ADP1,ADP2,ADP3,ADP_FeNi}, still play the major role 
 in long-time simulations and these empirical methods can achieve reasonable 
@@
 parameters. However, the gradients of the losses with respect to model 
-parameters are difficult or even impossible to calcualte. Hence, 
+parameters are difficult or even impossible to calculate. Hence, 
 global optimizations are generally not that effective.
@@
 In the last decade, machine learning (ML) has become one of the hottest 
-topics in many research areas. In the materials science, researchers have made 
-great efforts on developing ML models to describe atomic interactions. Such ML 
+topics in many research areas. In the field of materials science, researchers 
+have made great efforts on developing ML models to describe atomic interactions. 
+Such ML 
 models are considered as machine learning interaction potentials (MLIPs). Until 
@@
 be can obtained with the backpropagation algorithm automatically and 
-efficiently. Second, MLIPs are mostly vectorizable. Hence, GPUs can be utilized
-to significantly accelerate training and using of MILPs.
+efficiently. Second, MLIPs are mostly vectorizable. Hence, graphic processing 
+units (GPUs) can be utilized to significantly accelerate training and using of 
+MILPs.
 
@@
 training zone, the performances of MILPs may not that stable. For long-time 
-molecular dynamics (MD) simulations of large-scale ($10^5$ or more) systems, 
+molecular dynamics (MD) simulations of large-scale ($10^5$ or more) atoms, 
 computation efficiency also becomes a major concern. Recent benchmark 
@@
 At present, most MLIPs are used to examine small to medium ($10^3$ to $10^4$) 
-systems \cite{SNAP,SFApp0,SFApp1,SFApp2,soap3}.
+atoms \cite{SNAP,SFApp0,SFApp1,SFApp2,soap3}.
 
 In this work, instead of designing new atomic descriptors, we chose a new route 
-to develop MLIP: combining machine learning with empirical potentials. We 
-successfully implemented EAM and its variant ADP within TensorFlow so that 
+to develop MLIP: combining machine learning approach with empirical potentials. 
+We successfully implemented EAM and its variant ADP within TensorFlow so that 
 machine learning approaches can be used directly to tune EAM and ADP potentials. 
@@
 % -----------
-\subsection{Transformation}
+\subsection{Vectorizable Transformation}
 \label{sec:transformation}
@@
 
-To find optimal parameters of the funcitons in section \ref{sec:functions}, the 
-overall loss function shall be defined. Just like other machine learning tasks, 
-the mini-batch stochastic gradient descent algorithm is used to minimize the 
-loss function. 
 The Adam optimizer \cite{adam} is used to minimize Equation \ref{eq:loss}. 
@@
 Lammps setfl potential file will be exported.
+
+The number of trainable parameters in empirical potentials are quite limited. 
+According to our tests, typically tens of thousands of steps are sufficient to 
+finish a training. The training time mainly depends on the choices of losses. 
+Training with standard metrics (energy, forces and stress) only needs a few GPU 
+hours. Including the EOS constraint will just slightly increase the time cost.
+However, the elastic constraint is extremely complicated. Adding elastic term 
+to the total loss will significantly increase the training time to 
+approximately 20 to 40 GPU hours depending on your hardware and the number of 
+elastic losses. In our experience, training with energy, forces, stress and EOS 
+constraints first then restarting from a checkpoint with elastic constraints 
+appended is the best strategy.
 
@@
 
-The original Zjw04 potentials were fitted to experimentally obtained quantities.
-Thus, we use the relative MAE:
+The original Zjw04 potentials were fitted to experimental data. It would be 
+unfair if we calculate their relative errors based on DFT data directly. Hence, 
+in this work we also use the relative MAE (rMAE), 
+followed by Shyue Ping Ong\cite{SNAP,SNAP_Mo}:
 \begin{equation}
@@
 exactly the same dataset. But, EAM/ADP are around $10^2$ to $10^3$ times faster 
-than SNAP. To understand this, we can start from the many-body expansion (MBE) 
-scheme \cite{kCON}.
+than SNAP, according to the benchmark tests did by Trott and Thompson, who are 
+founders of SNAP\cite{SnapBenchmark}. To understand this, we can start from 
+the many-body expansion (MBE) scheme \cite{kCON}.
 
@@
 China under Grant No. 2016YFB0201204, the Science Challenge Project under Grant 
-No. TZ2018002 and the National Natural Science Foundation of China under Grant 
-No. U1630250.
+No. TZ2018002, the National Natural Science Foundation of China under Grant 
+No. U1630250, No. 12002064 and No. 12004046.
 
